### 2018-07-24 area_agg_seq_tsas.tex
Project created

\documentclass[acmlarge,review,natbib=false]{acmart}

%%drt24 hacks
%% Letter paper
%\setlength{\paperheight}{11in}
%\setlength{\paperwidth}{8.5in}

% Hack to try to make acmart work with biblatex: https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib

\let\citename\relax
\RequirePackage[abbreviate=true, dateabbrev=true, isbn=true, doi=true, urldate=comp, url=true, maxbibnames=9, backref=false, backend=bibtex, style=ACM-Reference-Format, language=american,natbib]{biblatex}

%\usepackage{textcomp}
%\renewcommand{\textuparrow}{$\uparrow$}

%\addbibresource{sample-bibliography-biblatex.bib}
\addbibresource{Reference/BibReference.bib}

\renewcommand{\bibfont}{\Small}

\usepackage{booktabs} % For formal tables
\input{area_agg_seq_tsas_setting}

%% Copyright
%%\setcopyright{none}
%%\setcopyright{acmcopyright}
%%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%%\setcopyright{usgov}
%%\setcopyright{usgovmixed}
%%\setcopyright{cagov}
%%\setcopyright{cagovmixed}
%
%
%% DOI
%\acmDOI{10.475/123_4}
%
%% ISBN
%\acmISBN{123-4567-24-567/08/06}
%
%%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA}
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmJournal{PACMHCI}
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}
\acmArticleSeq{11}

%\acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
%\acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2007}
\received{March 2009}
\received[accepted]{June 2009}

\begin{document}
\title{Finding Optimal Sequences for Area Aggregation  
	--\protect\\ 
	\Astar vs. Integer Linear Programming}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Dongliang Peng}
%\authornote{Dr.~Trovato insisted his name be first.}
\orcid{0000-0001-6848-3545}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin}
%  \state{Ohio}
%  \postcode{43017-6221}
  \country{Germany}
}
\email{dongliang.peng@uni-wuerzburg.de}

\author{Alexander Wolff}
\orcid{0000-0001-5872-718X}
\affiliation{%
  \institution{Chair of Computer Science I, 
  	University of W\"urzburg}
  \country{Germany}
}
\email{www1.informatik.uni-wuerzburg.de/wolff}

\author{Jan-Henrik Haunert}
\orcid{0000-0001-8005-943X}
\affiliation{%
  \institution{Institute of Geodesy and Geoinformation,  
  University of Bonn}
  \country{Germany}
}
\email{www.geoinfo.uni-bonn.de/haunert}

%% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
To provide users with maps of different scales and 
to allow them to zoom in and out without losing context,
automatic methods for map generalization are needed.
Given two maps of the same region at two different scales,
a relevant problem is to compute maps for any intermediate scale.
We approach this problem for land-cover maps.
Given two land-cover maps at different scales, 
we want to find a sequence of small incremental
% To help map users not to lose context during zooming,
% we try to provide maps that change as continuous as possible.
% Since maps at some different scales often exist, 
% a relevant problem is to find maps at any intermediate scales.
% Given two land-cover maps of different scales, 
% we wish to find a sequence of small incremental
changes that gradually transforms one map into the other.
We assume that the two input maps consist of polygons 
each of which belongs to a given land-cover class. 
Every polygon on the smaller-scale map
is the union of a set of polygons on the larger-scale map.

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
For solving such a problem optimally, standard approaches
are the \Astar algorithm or integer linear programming.
We compare how the two methods solve our problem.
To avoid long computing times, we allow the two methods to 
return nonoptimal results.
In addition, we present a greedy algorithm 
as a benchmark.
We tested the three methods with a
data set of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal solutions for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}
\keywords{Continuous map generalization, Land cover, 
	 Type chang, Compactness, Graph, Optimization, Exponential}

\maketitle

\section{Introduction}
\label{sec:Introduction}

Maps are the main tool to represent geographical information. 
As geographical information is usually scale-dependent
\parencite{Muller1995Generalization,Weibel1997}, 
users need to have access to maps at different scales.
In our digital age, people realize this access by zooming on 
computers or mobile phones.
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
A naive solution is 
to switch between maps at different scales.
This method, however, can result in 
large discrete changes, 
which tend to distract users.
A more advanced strategy is  
\emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which emphasizes on generalizing in real time.
Still, large discrete changes can be introduced.
To have a better zooming experience, 
users prefer the changes to be continuous.
This is why some digital maps such as Google Maps 
are trying to make zooming as continuous as they can,
though Google Maps is still based on switching between 
a certain number of maps at different scales.
The process of producing maps at any different scales
with smooth changes 
is called \emph{continuous map generalization} (CMG).
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area, 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them (e.g., \citealp{Cecconi2003,Noellenburg2008,Chazal2010BallMap,Deng2015,Li2017_Building,Li2017Annealing}).
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} presented a method for computing an optimum
correspondence between two given polylines according to some cost function.
While straight-line trajectories 
are often used for interpolation
(e.g., \citealp{Cecconi2003,Deng2015}),
\textcite{Whited2011BallMorph} considered four other alternatives, i.e., \emph{hat}, \emph{tangent}, 
\emph{circular}, and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land cover areas become too small to be seen.
These areas have to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as good as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{smallest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then we can say that the model is not reasonable.
In this case, we should try another model, say, 
to minimize the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
(e.g., \citealp{HaunertWolff2010AreaAgg,Haunert2016Partition}).
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

Optimization has been widely used in map generalization.
For example, \textcite{Harrie1999} displaced objects 
based on least-squares adjustments (LSA)
to solve spatial conflicts.
In his problem, the soft constraints 
for shapes and locations may contradict each other.
Therefore, it is necessary 
to mediate between these constraints, 
which is done by LSA.
\textcite{Sester2005Optimization} used LSA not only for 
displacing objects, but also for simplifying buildings. 
The output boundaries are required to 
be as close as possible to the original buildings.
\textcite{Tong2015AreaLSA} generalized land-cover areas,
where LSA was used to preserve the sizes of 
the land-cover areas.
\textcite{Regnauld2001} grouped buildings based on 
minimum spanning trees in order to typify
the buildings in a group.
\textcite{Burghardt2005Snakes} smoothed lines based on 
energy minimization. 
According to his setting, a line contains less energy
if it is smooth and close to the original line.
He repeatedly displace the line 
until finding a stable state 
in terms of minimizing his energy function.
\textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
based on mixed-integer linear programming.
This method is based on global optimization and minimizes 
type changes as well as a cost for non-compact shapes 
while satisfying constraints on the sizes of the output regions.
\textcite{Haunertwolff2010Building} simplified building
footprints by solving an integer linear program (ILP).
They aimed at minimizing the number of edges in the output under 
the restriction that the simplified buildings must be 
topologically safe,
that is, the selected and extended edges must not intersect with 
each other.
\textcite{Oehrlein2017Aggregation} aggregated the departments 
of France according to the unemployment rates based on integer 
linear programming; they used a cutting-plane method to 
speed up solving their ILP.
\textcite{Funke2017Simplification} simplified 
administrative boundaries based on an ILP.
Their aim was to minimize the number of edges
while keeping the result boundaries close to the original ones
and avoiding any intersection. 
At the same time, every city, which is represented by a point, stays in the same face as before.

%\todo{may cite \textcite{Bader2001Dissertation}}

\begin{figure}[tb]
	\centering
	\includegraphics{AreaAgg_example}
	\caption{The input and a possible output for an instance of 
		our problem}
	\label{fig:AreaAgg_example}
\end{figure}

\mypar{Optimization in \emph{continuous} map generalization}
Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map, 
but also for relations between maps. 
%
Nevertheless, some optimization techniques 
have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that 
a point, once disappeared, should not show up again 
during zooming out, 
and that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for the given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks, at each step.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

\mypar{Problem definition}
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
tiny polygons, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we want to remove these tiny polygons.
\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
proposed to split these tiny parcels 
and then to merge the split parts into the neighboring polygons.
\textcite{Meijers2016Split} developed an algorithm 
to split a polygon (the splittee) 
based on constrained Delaunay triangulation.
During splitting, their algorithm is capable of
taking into account
the attractivenesses between the splittee and its neighbors.
When merging, a more attractive neighbor 
will get a larger portion from the splittee.
However, our method does not consider splitting.
We focus on aggregating areas.
A \emph{land-cover map} is a planar subdivision in which each 
area belongs to a
land-cover class or \emph{type}.
Suppose that there are two land-cover maps of 
different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes 
that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

With the same motivation, a strategy of hierarchical schemes 
has been proposed.
This strategy generalizes a more-detailed representation 
to obtain a less-detailed representation 
based on small incremental changes, 
e.g., the Generalized Area Partitioning tree 
(GAP-tree),
which can be constructed if only the larger-scale map is given
\citep{vanOosterom1995Development} 
or if both the larger-scale map and the smaller-scale map 
are given \citep{HaunertDilo2009}.
Typically, the next change in such a sequence 
is determined locally, 
in a greedy fashion.  
If we insist on finding a sequence that is, 
according to some global measure, optimal, 
the problem becomes complicated.

We assume that there exist many-to-one relationships between the 
areas of the
start map and the areas of the goal map.
This assumption is based on the fact that many algorithms (e.g., \citealp{HaunertWolff2010AreaAgg,vanSmaalen2003,Oehrlein2017Aggregation})
that aggregate land-cover areas
result in many-to-one relationships.
The input and the generalized results of these methods 
can be used as our input.
We term the areas of the goal map \emph{regions}.
That is, every region is the union of a set of areas 
on the start map.
The type of a region may differ from the types of its 
components. 
For example, a small water area together with 
multiple adjacent forest areas may constitute 
a large forest region on the smaller-scale map.
However, we assume that every region, on the goal map, 
contains at least one area of the same type on the start map.
Our assumptions hold if the goal map has been produced 
with an automatic method for area aggregation, 
for example, with the method of \citet{HaunertWolff2010AreaAgg}.
That method produces a land-cover map at a single output scale, 
given a land-cover map at a larger scale.
Although the method of \textcite{HaunertWolff2010AreaAgg}
leads to results of high quality, 
it does not yield land-cover maps at intermediate scales.

To generate a good sequence of maps, 
we must consider the sequence of maps as a whole 
instead of considering each intermediate-scale map independently.
To simplify the problem,
we first consider each region of the goal map 
(with its components on the start map) 
independently of the other regions.
Once we have found an aggregation sequence for each region, 
we integrate all the sequences into an overall sequence 
that transforms the start map into the goal map. 
Our aggregation sequence may be cooperated with
the GAP-face tree \citep{vanOosterom2005},
the map cube model \citep{Timpf1998},
or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
to support on-the-fly visualization.
Smoothly (dis-)appearing areas can be realized
by integrating our results into the \emph{space-scale cube}
\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.

%\todo{may cite \textcite{Suba2014Merge}}

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(see \sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an integer linear program, 
and then solve this program, minimizing our cost function.
Our linear program uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a data set of the German topographic database ATKIS 
(see \sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

We do not deal with the simplification of lines in this paper, 
since this can be handled separately from the
aggregation of areas, for example, 
by using one method of 
\textcite{Douglas1973,Saalfeld1999,Wu2004DP}.
Those methods can be used to set up 
the binary line generalized (BLG) tree
\citep{vanOosterom1995Development},
which is a hierarchical data structure that 
defines a gradual line simplification process.

\section{Preliminaries}
\label{sec:AreaAgg_Preliminaries}

We show how to compute an aggregation sequence for one region. 
For a goal map with many regions, 
after having found a sequence for each of them
we ``interleaf'' these aggregation sequences
with respect to the order of the smallest patches 
(see for example \fig\ref{fig:AreaAgg_IntegrateSequence}).
This integration is similar to the merge step in the 
merge sort algorithm; 
see \textcite[pp.~29--37]{Cormen2009}.
To allow us to describe our method more easily,
below we assume that the goal map has only one region.
This region consists of~$n$ land-cover 
areas (components) on the start map. 
In other words, the union of the~$n$ land-cover areas 
is the only region on the goal map.
\begin{figure*}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_Preliminaries}
	\caption{Integrating two aggregation sequences 
		of different regions: 
		the resulting sequence contains the given sequences 
		as subsequences and 
		always takes the subdivision with smallest patch next.
		The gray arrows show the integration of the two regions.
	}
	\label{fig:AreaAgg_IntegrateSequence}
\end{figure*}

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors (adjacent areas)~$v$
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function.
This requirement ensures that the 
size of the smallest area in the map increases in each step
and thus the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
for simplicity we consider 
the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces the number of possible 
solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.

\mypar{Model}
We consider a directed graph $G$, 
which we call the \emph{subdivision graph} 
(see \fig\ref{fig:AreaAgg_SubdivisionName}). 
The node set $V$ of~$G$ contains a node for every
possible map (or \emph{subdivision}), including the start map, all
possible intermediate-scale maps, and the goal map.
The arc set~$E$ of~$G$ contains an arc $(\Pnode, P_{t+1,j})$ 
between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V$ 
if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
with a single aggregation operation,
involving the smallest area.
Then, any directed path in~$G$ from the start map to the goal map
defines a possible aggregation sequence.
Our idea is to compute an optimal aggregation sequence through 
computing a minimum-weight path from the start to the goal.
This idea obviously requires that the arc weights are 
set such that a minimum-weight start--goal
path does actually correspond to an aggregation sequence of 
maximum cartographic quality.  
Moreover, putting the idea to practice is far from trivial 
since the graph $G$ can be huge as we will argue below.
We compare a greedy algorithm, \Astar, and an ILP-based algorithm
in finding such paths.
Note that we only know subdivisions 
$\Pstart$ and $\Pgoal$ at the beginning.
We generate a subdivision (node) only when we want to visit it.

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_Preliminaries}
	\caption{The subdivision graph~$G$. 
		The nodes of the graph are the subdivisions. 
		There is an arc	from subdivision~\Pnode 
		to subdivision~${P}_{t+1,j}$ 
		if ${P}_{t+1,j}$ is the result of 
		aggregating a smallest area~$p$ of~\Pnode with a 
		neighbor of~$p$.}
	\label{fig:AreaAgg_SubdivisionName}
\end{figure}

\mypar{Notation}
We represent each land-cover area by a polygon with a type.
We denote by $P$ the set of polygons on the start map.
We use~$p$, $q$, $r$, or~$o$ to denote polygons.
A \emph{patch} is a set of polygons whose union is connected. 
The patch also has the property type.
We use~$u$ or~$v$ to denote patches.

Recall that we are dealing with a single region and 
there are~$n$ land-cover areas on the start map in this region. 
Hence, the desired aggregation sequence consists of~$n-1$ steps. 
There are~$n$ subdivisions on a path 
from the start map to the goal map. 
We use~$t \in {T}=\{1,2,\dots,n\}$ to denote \emph{time}. 
When~$t=1$, the subdivision consists of~$n$ patches, 
and there is only one patch remaining when~$t=n$.
The subdivision graph consists of layers~${L}_1,\dots,{L}_n$, 
where layer~${L}_t=\{{P}_{t,1},\dots,{P}_{t,n_t}\}$
contains every possible subdivision~\Pnode\ with~$n-t+1$ patches (see \fig\ref{fig:AreaAgg_ExponentialSize}).

\begin{figure}[tb]
	\centering
	\includegraphics[page=3]{AreaAgg_Preliminaries}
	\caption{An example to show that the size of our problem 
		has an exponential lower bound.}
	\label{fig:AreaAgg_ExponentialSize}
\end{figure}

\mypar{Exponential lower bound}
We now analyze the size of the subdivision graph~$G$.
Consider an instance that consists of 
a start map with $n=2k+1$ rectangles in a row and
a goal map that is simply the union of the $n$ rectangles
(see \fig\ref{fig:AreaAgg_ExponentialSize}).
At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
intermediate vertical boundaries. 
For this, the number of choices is~$
{{2k}\choose{k}}
= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
{k\cdot (k-1)\cdot \ldots \cdot 1}
\ge 2^k = 2^{(n-1)/2}$.
As a result, the size of our model
has an exponential lower bound.

\section{Cost Functions}
\label{sec:AreaAgg_CostFunctions}

\fig\ref{fig:AreaAgg_SubdivisionName} shows that there are many 
ways to aggregate from the start map to the goal map.
Apparently, some of the ways are more reasonable than 
others.
In our example, we consider 
the sequence~$(P_{1,1}, P_{2,1},P_{3,1},P_{4,1})$ 
more reasonable than 
the sequence~$(P_{1,1}, P_{2,4},P_{3,5},P_{4,1})$.
The reason is that the dark area should not expand so much
as the target color is gray.
We want to provide users with a most reasonable sequence as we 
believe that an unreasonable sequence irritates users.
To find a most reasonable sequence, we introduce cost functions 
in our problem of finding shortest paths.
In the cost functions, we charge a higher penalty 
when an aggregation step is less reasonable.
As a result, by minimizing the overall cost of an aggregation 
sequence, we find a most reasonable sequence.

It is difficult to define exactly what reasonable means 
because users may have different preferences.
Four preferences are discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
They are aggregating a small land-cover area into one 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one is based on semantics and 
the other is based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, aggregating 
an area with type \emph{swamp} into an area with type \emph{wet 
	ground} rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by human being 
if it is more compact.
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness:
we consider a subdivision~\Pnode as more compact than
another subdivision~$P_{t,i'}$ if the total length of the interior boundaries of~\Pnode is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
see, for example, \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a reasonable replacement
when compactness is considered in an ILP
(e.g., \citealp{Minas2016,Wright1983}).
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is the centroid
that minimizes the sum.
The sum of the distances can also be computed linearly.
We use the length of interior boundaries 
instead of the distance because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

\begin{figure}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_CostFunctions}
	\caption{Aggregating land-cover areas according to different 
		preferences.
		Aggregating a small land-cover area into one 
		that isolates the area (b), 
		that is the largest neighbor (c), 
		that shares the longest boundary (d), or 
		that has the most similar type (e).}
	\label{fig:AreaAgg_Preferences}	
\end{figure}

\subsection{Cost of type change}
\label{sec:AreaAgg_f_type}

We define the cost of type change as follows.
Suppose that we are at the step of aggregating 
from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$. 
In this step, patch~$u$ is aggregated into patch~$v$
(see \figs\ref{fig:AreaAgg_FirstStep}a 
and \ref{fig:AreaAgg_FirstStep}b).
We denote the types of the two patches by~$T(u)$ and~$T(v)$. 
We define the cost of type change of this step by
\begin{equation}
\label{eq:f_type}
f_\mathrm{type}(P_{s,i},P_{s+1,j})=\frac{A_{u}}{A_R}
\cdot
\frac{d(T(u),T(v))}{T_{\max}},
\end{equation}
where~$A_u$ is the area of patch~$u$, 
and~$A_R$ is the area of region~$R$.
We use~$A_R$ and~$T_{\max}$ 
to normalize the cost of type change. 
Constant~$T_{\max}$, the maximum cost over all type changes,  
is known from the input. 
The input specifies, for each pair~$(T_1,T_2)$ of types, 
cost~$d(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
Specifically, we denote by~$T_\mathrm{goal}$ the type of 
the patch on the goal map.
For simplicity, we use a metric 
as the cost function of type change
(see \sect\ref{sec:AreaAgg_CaseStudy}); 
see \textcite[chapter 2]{Choudhary1992Elements}
for the definition of a metric.
A metric distance is symmetric, 
which is different from the unsymmetric one used in
\textcite{Dilo2009tGAP}.
In their definition, for example, 
the distance from type \emph{building} to type \emph{road} is~$0.5$,
but the distance is~$0$ the other way around.

For path $\Pistar=(P_{1,i_1}, P_{2,i_2}, \dots, 
P_{\tstar,i_{\tstar}})$,
we define the cost of type change over the steps so far by
\begin{equation}
\label{eq:g_type}
g_\mathrm{type}(\Pistar)=
\sum_{s=1}^{t-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}})
\end{equation}

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_CostFunctions}
	\caption{An aggregation step, 
		where patch~$u$, the dark patch at the top,
		is aggregated into patch~$v$.
		Figures~(c) and~(d) respectively show the number of 
		edges and the lengths of the interior polylines after 
		the aggregation.}
	\label{fig:AreaAgg_FirstStep}	
\end{figure}

\subsection{Cost of compactness}
\label{sec:AreaAgg_f_comp}

We use the compactness definition of \citet{Frolov1975}, 
i.e., the compactness value for patch~$u$ is
\begin{equation*}
\label{eq:comp}
c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
\end{equation*}
where~$A_u$ and~$l_u$ are 
the area and the perimeter. 
For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
the set of the patches' compactnesses.

We wish to maximize the sum of the average compactnesses 
over all intermediate maps,
while our objective will be
minimizing a cost function.
To adapt the average compactness to our methods, 
we define and minimize a cost related to compactness.
Recalling that at time~$s$ there are~$n-s+1$ patches,
we define the cost of compactness for subdivision~\Psnode as
\begin{equation}
\label{eq:f_comp}
f_{\mathrm{comp}}(\Psnode)=
\frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
\end{equation}
where we use values~$n-s+1$ and~$n-2$ to normalize 
the cost of compactness.

For path $\Pistar$ (see \sect\ref{sec:AreaAgg_f_type}),  
we define the cost of compactness over all 
intermediate maps
(that is, neglecting~$P_{1,1}$ 
and the last subdivision in the path) by
\begin{equation}
\label{eq:g_comp}
g_\mathrm{comp}(\Pistar)=
\sum_{s=2}^{\tstar-1}f_{\mathrm{comp}}(P_{s,i_s}).
\end{equation}

\subsection{Cost of length}
\label{sec:AreaAgg_costlength}

We denote the set of interior boundaries 
for a subdivision~$\Psnode$ by~$B(\Psnode)$.
The cost in terms of interior length of 
this subdivision is defined as
\begin{equation}
\label{eq:f_length}
f_{\mathrm{lgth}}(\Psnode)=
\frac{\big(\sum_{b\in B (\Psnode)} 
	|b|\big)\big/D(s)}{n-2}, 
\end{equation} 
where 
\begin{equation}
\label{eq:AreaAgg_Norm}
D(s)=\frac{n-s}{n-1} \sum_{b\in B (\Pstart)} |b|.
\end{equation}
Function~$D(s)$ computes the ``expected'' total length of 
the interior boundaries at time~$s$,
where we expect that this total length decreases linearly
according to time~$s$.
In special,~$D(1) = \sum_{b\in B (\Pstart)} |b|$
and~$D(n) = 0$.
Similarly to \eq\ref{eq:f_comp}, 
we use~$D(s)$ and~$n-2$ to normalize 
the cost of length.

For path~$\Pistar$ (see \sect\ref{sec:AreaAgg_f_type}), 
we define the cost of length over all 
intermediate maps 
(that is, neglecting~$P_{1,1}$ 
and the last subdivison in the path) by
\begin{equation}
\label{eq:g_length}
g_\mathrm{lgth}(\Pistar)=
\sum_{s=2}^{\tstar-1}f_{\mathrm{lgth}}(P_{s,i_s}).
\end{equation}

\subsection{Combining cost functions}
\label{sec:AreaAgg_Combining}
In order to minimize the type change 
and maximize the compactness,
we combine the two cost functions as
\begin{equation}
\label{eq:g_1}
g_1(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{comp}(\Pistar),
\end{equation}
where~$\lambda \in [0,1]$ is a parameter 
to assign importances 
of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
We simply use~$\lambda=0.5$ in our experiments. 
We want to find a path~$\Pi$ from~$\Pstart$ to~$\Pnode$ 
that minimizes, among all such paths,~$g(\Pistar)$.
Slightly abusing notation, we denote the cost of
this optimal path from~${P}_{\mathrm{start}}$ to~\Pnode 
by~$g_1(\Pnode)$.
Using $g_1(\Pnode)$, we compare a greedy algorithm and \Astar
in finding optimal sequences for area aggregation.

As said before, we want to make a comparison involving
integer linear programming.
Therefore, we also introduce a combination
that can be computed linearly, as
\begin{equation}
\label{eq:g_2}
g_2(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{lgth}(\Pistar).
\end{equation}
We compare the greedy algorithm, \Astar, and an ILP-based 
algorithm using $g_2$.

\section{A Greedy Algorithm}
\label{sec:AreaAgg_Greedy}
At any time~$t$,
our greedy algorithm aggregates the smallest patch
with one of its neighbors.
Suppose that patch~$u$ is the smallest patch,
and patch~$v$ is one of~$u$'s neighbors.
We aggregate~$u$ into~$v$ 
if the type distances fulfill that
$d(T(u), T_\mathrm{goal}) \ge d(T(v), T_\mathrm{goal})$;
otherwise, we aggregate~$v$ into~$u$.
Recall that when we aggregate a patch into another patch,
the union takes the type of the latter.
We compute the costs of aggregating the smallest patch 
with each of the neighbors, 
and select the aggregation that costs least.
In other words, the smallest patch is aggregated with 
its most \emph{compatible} neighbor.
This idea is the same as that of \textcite{vanOosterom2005},
except we have a different definition for the compatible.
In accordance 
with our two combinatorial costs in 
\sect\ref{sec:AreaAgg_Combining},
we define two cost functions.
Suppose that we are at the step of 
aggregating from subdivision $P_{s,i}$ to subdivision 
$P_{s+1,j}$.
The first cost function is 
\begin{equation}
\label{eq:f_1}
f_1(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{comp}}(P_{s+1,j}). \nonumber
\end{equation}
The second cost function is
\begin{equation}
\label{eq:f_2}
f_2(P_{s,i},P_{s+1,j})=
(1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
+\lambda f_{\mathrm{lgth}}(P_{s+1,j}). \nonumber
\end{equation}

\section{Using the \Astar Algorithm}
\label{sec:AreaAgg_AStar}

%\mypar[inline]{Motivate \Astar by comparison with Dijkstra.}

We try to find a shortest path,
from the start map to the goal map,
using \Astar \citep{Hart1968}.  
As the graph~$G$---our search space---can be of exponential size 
(see \sect\ref{sec:AreaAgg_Preliminaries}), 
we avoid computing the whole graph explicitly.
To save time and memory, 
we generate a subdivision \Pnode only 
when we are going to visit it.
\Astar uses a clever best-first search 
to find a shortest path 
from subdivisions~$\Pstart$ to~$\Pgoal$.  
For subdivision \Pnode,
\Astar considers the exact cost of a shortest path 
from~\Pstart to~\Pnode 
and estimates the cost to get from~\Pnode to~\Pgoal.  
\Astar can be seen as a refinement of Dijkstra's algorithm
where nodes are explored earlier 
if they are estimated to be closer to the goal.

More formally, we define $g(\Pnode)$ to be 
the exact cost of a shortest path from~\Pstart to~\Pnode, 
and we define $h(\Pnode)$ to be the estimated cost 
to get from \Pnode to~\Pgoal. 
Then the (estimated) total cost at node~\Pnode is
\begin{equation}
\label{eq:CostTotal}
F(\Pnode)=g(\Pnode)+h(\Pnode).
\end{equation}
We use either~$g_1$ (\eq\ref{eq:g_1}) 
or~$g_2$ (\eq\ref{eq:g_2})
for~$g(\Pnode)$.
If~$h(\Pnode)$ is always bounded from above 
by the exact cost of a shortest path from~\Pnode to~\Pgoal, 
\Astar is guaranteed to find a shortest path from~\Pstart 
to~\Pgoal, 
that is, an optimal aggregation sequence.  
Using the estimation~$F$ (\eq\ref{eq:CostTotal}), 
\Astar is able to reduce the search space.
The better the estimation part~$h$, 
the more \Astar can reduce the search space.
In the following, we show how we compute
estimated cost $h(\Pnode)$.

To narrow down the search space, 
we set up estimation functions 
for type change (\sect\ref{sec:AreaAgg_h_type}), 
compactness (\sect\ref{sec:AreaAgg_h_comp}), 
and length (\sect\ref{sec:AreaAgg_h_length}). 
These functions are meant to direct \Astar towards the goal.
Since the number of subdivisions can be exponential, 
it can happen that we run out of main memory 
before we find an optimal solution. 
To handle this problem, we overestimate the cost. 
Overestimation is a popular technique while using \Astar,
in order to find a feasible solution. 
For example, \textcite{Pohl1973} overestimated 
using dynamic weighting. 
We propose another strategy that fits our problem. 
We first try finding an optimal solution by \Astar. 
If we fail to find one after 
we have visited a predefined number~$W$ of nodes of graph~$G$,
then we restart.
In the retrying, we overestimate the first~$K$ steps 
starting at each node
(see \sects\ref{sec:AreaAgg_h_type}, \ref{sec:AreaAgg_h_comp},
and~\ref{sec:AreaAgg_h_length}).
We may need to increase~$K$ and retry several times 
until we find a feasible solution.
We define~$K$ by
\[
K= 2^k -1,
\]
where~$k\ge 0$ is the number of retryings.
As~$K\le n-1$, it holds that~$k \le \log_2 n +1$, 
which means  that we will 
retry~$\lceil \log_2 n\rceil$ times at most.
When we are at time $t$, there are at most $n-t$ steps 
to arrive at the goal map.
We define the number of practical overestimation steps as
\[
K'= \min \{K, n-t\}.
\]
Whenever overestimating ($k\geq1$), 
\Astar cannot guarantee optimality anymore.

\subsection{Estimating the cost of type change}
\label{sec:AreaAgg_h_type}

To find a lower bound of the cost of type change, 
we simply assume that 
every patch will be aggregated into a patch with type~\Tgoal.
As long as the cost of type change is a metric, this aggregation 
strategy indeed yields a lower bound.
%
For subdivision~\Pnode, let
$(\Pnode=P_{t,i_t}, P_{t+1,i_{\tstar+1}} \dots,P_{n,i_n}=\Pgoal)$,
be the path that always changes the type of a smallest patch 
to~\Tgoal.
Then the estimated cost of type change is
\begin{equation}
\label{eq:h_type}
h_\mathrm{type}(\Pnode)=
\sum_{s=t}^{n-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}}).
\end{equation}

As an example, for \fig\ref{fig:AreaAgg_FirstStep}b, we compute 
$h_\mathrm{type}$ 
according to the aggregation sequence of 
\fig\ref{fig:AreaAgg_h_type}.
Note that the step from $P_{2,i_2}$ to 
$P_{3,i_3}$ 
in 
\fig\ref{fig:AreaAgg_h_type} is impossible in reality 
because the dark patch cannot be aggregated into patch~$v$
as they are not neighbors. 
However, this aggregation is allowed for estimation 
because we may find a shortest path as long as 
the estimated cost is no more than 
the exact cost of a shortest path.
In order to overestimate, we multiply the estimated cost of the 
first $K'$ steps by $K$.
\fo\ref{eq:h_type} is revised to
\begin{equation}
\label{eq:o_type}
h_\mathrm{type}(\Pnode)=
K\sum_{s=t}^{t+K'-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}})+
\sum_{s=t+K'}^{n-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}}).
\nonumber
\end{equation}

\begin{figure*}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_Estimation}
	\caption{An ``aggregation sequence'' for computing 
		$h_{\mathrm{type}}$, 
		based on the aggregation result of 
		\fig\ref{fig:AreaAgg_FirstStep}b}
	\label{fig:AreaAgg_h_type}
\end{figure*}

\subsection{Estimating the cost of compactness}
\label{sec:AreaAgg_h_comp}

Our way to estimate the cost of compactness 
is based on regular polygons.
The more edges a regular polygon has, the more compact it is.
We assume that at each step 
we aggregate the two patches that are the least compact.
Moreover, we assume that the shared boundary of the two patches  has the least number of edges.
We use $\mathcal{N}_\mathrm{ext}$ to 
denote the edge number of the region's exterior boundaries.
As the exterior boundaries will not be changed by aggregation, 
$\mathcal{N}_\mathrm{ext}$ 
is a constant. 
%
Note that the boundary between two patches 
is not necessarily connected 
(see for example the dark boundary with three edges 
in \fig\ref{fig:AreaAgg_h_comp}a).
We denote by~$B(\Psnode)$ 
the set of interior boundaries at time~$s$,
and denote by~$b_\mathrm{min}(\Psnode)$ 
the boundary with the smallest number of edges.
For our estimation, the set of interior boundaries 
at time~$s+1$ 
is~$B(P_{s+1,j})= B(\Psnode)-{\{b_\mathrm{min}(\Psnode)\}}$. 
The estimated number of all the edges for 
such a subdivision~$P_{s+1,j}$ is
\begin{equation}
\label{eq:LeftEdgeNum}
\mathcal{N}_{s+1,j}=
\mathcal{N}_\mathrm{ext} + \sum_{b \in B(P_{s+1,j})} \|b\|.
\end{equation}
where $\|b\|$ is the number of edges of boundary~$b$.

\begin{figure*}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_Estimation}
	\captionof{figure}{An "aggregation" sequence for 
		computing 
		$h_\mathrm{comp}$ (see 
		\eq\ref{eq:o_comp}) based on the 
		number of edges. 
		At each step we remove the boundary with the fewest 
		edges. 		
		The numbers represent the 
		numbers of the interior boundaries' edges.
		This example corresponds to the aggregation step in 
		\fig\ref{fig:AreaAgg_FirstStep}.
	}
	\label{fig:AreaAgg_h_comp}
\end{figure*}

From subdivision~\Psnode to subdivision~$P_{s+1,j}$,
we get a new patch because of aggregation.
The new patch is certainly less compact than a regular polygon 
with~$\mathcal{N}_{s+1,j}$ edges.
In order to estimate the compactness of the new patch, 
we assume that 
the new patch has the shape of a regular polygon 
with~$\mathcal{N}_{s+1,j}$ edges 
(see \eq\ref{eq:LeftEdgeNum}).
A regular polygon with~$\mathcal{N}$ edges has compactness
\begin{equation*}
\label{eq:comp_regular}
c_\mathrm{reg}(\mathcal{N})=
\sqrt{\frac{\pi}{\mathcal{N}} \bigg/
	\tan{\frac{\pi}{\mathcal{N}}}}.
\end{equation*}
Note that~$c_\mathrm{reg}(\mathcal{N})$ increases 
with increasing~$\mathcal{N}$.
A patch with~$\mathcal{N}_{s+1,j}$ edges has
compactness~$c_\mathrm{reg} (\mathcal{N}_{s+1,j})$.
According to our previous assumption, 
at each step we are able to aggregate the two patches 
that are the least compact in the subdivision.
We denote the compactness values of the two patches
by~$c_\mathrm{min}(\Psnode)$ and~$c'_\mathrm{min}(\Psnode)$.
Recall that we use~$C(\Psnode)$ to denote 
the set of compactness values of the patches
in subdivision~$\Psnode$ 
(see \sect\ref{sec:AreaAgg_f_comp}).
Then the set of compactness values 
for subdivision~$P_{s+1,j}$ is 
\begin{equation}
\label{eq:compsetnew}
C(P_{s+1,j})=
C(\Psnode)\cup 
\{c_\mathrm{reg} (\mathcal{N}_{s+1,j})\}
\setminus \{c_\mathrm{min}(\Psnode), c'_\mathrm{min}(\Psnode)\}.
\nonumber
\end{equation}
We compute the estimated average compactness 
by calculating the average 
of the values in set~$C(P_{s+1,j})$.
Finally, we compute the estimated cost of compactness for subdivision~$P_{s+1,j}$ by \eq\ref{eq:f_comp}.

For subdivision~\Pnode, let
$(\Pnode=P_{t,i'_t}, P_{t+1,i'_{\tstar+1}}, 
\dots,P_{n,i'_n}=\Pgoal)$
be the path that always removes the two smallest compactnesses
and gains a compactness of the constructed regular polygon.
The estimated cost of compactness is
\begin{equation}
\label{eq:h_comp}
h_\mathrm{comp}(\Pnode)=
\sum_{s=t}^{n-1}f_\mathrm{comp}(P_{s,i'_s}). \nonumber
\end{equation}
When overestimating, we assume that 
each patch in the subdivision is extremely noncompact,
that is, each patch has compactness~$0$.
One may ask if this assumption is too much.
It is indeed too much for one subdivision, 
but it is just fine for the whole sequence
as we overestimate for only a certain number of subdivisions.
Based on this assumption,
the cost of compactness is $f_\mathrm{comp}(P_{s,i_s})=1/(n-2)$,
according to \eq\ref{eq:f_comp}.
If we overestimate $K'$ steps, 
we revise the estimated cost of compactness to
\begin{equation}
\label{eq:o_comp}
h_\mathrm{comp}(\Pnode)=
\sum_{s=t}^{t+K'-1}\frac{1}{n-2}+
\sum_{s=t+K'}^{n-1}f_\mathrm{comp}(P_{s,i'_s}).
\end{equation}

\subsection{Estimating the cost of length}
\label{sec:AreaAgg_h_length}

At time $s$, there are $n-s+1$ patches.
There can be as few as $n-s$ interior boundaries.
In order to find a lower bound of the cost of length,
we keep only the necessary number, $n-s$, 
of shortest boundaries at each step
(see \fig\ref{fig:AreaAgg_h_length}).
Then we compute the estimated cost of length according to 
\eq\ref{eq:f_length}.

For subdivision~\Pnode, let
$(\Pnode=P_{t,i''_t}, P_{t+1,i''_{\tstar+1}}, \dots,P_{n,i''_n}=\Pgoal)$
be the path that always keeps 
the necessary number of shortest interior boundaries.
The estimated cost of length is
\begin{equation}
\label{eq:h_length}
h_\mathrm{lgth}(\Pnode)=
\sum_{s=t}^{n-1}f_\mathrm{lgth}(P_{s,i''_s}).
\end{equation}
When overestimating,
we use the interior length of the current map as the cost of 
length for $K'$ steps even though we are removing 
interior boundaries.
As a result, we revise \fo\ref{eq:h_length} to
\begin{equation}
\label{eq:o_length}
h_\mathrm{lgth}(\Pnode)=
\sum_{s=t}^{t+K'-1}f_\mathrm{lgth}(P_{t,i})+
\sum_{s=t+K'}^{n-1}f_\mathrm{lgth}(P_{s,i''_s}). \nonumber
\end{equation}

\begin{figure*}[htb]
	\centering
	\includegraphics[page=3]{AreaAgg_Estimation}
	\caption{An "aggregation" sequence for computing 
		$h_\mathrm{lgth}$ 
		(see Equation~\ref{eq:h_length}) 
		based on the lengths of boundaries. 
		At each step we keep the necessary number 
		of boundaries with least lengths in order to find a 
		lower bound of edge length of the interior boundaries 
		$l_\mathrm{int}(t)$. 
		The numbers represent the 
		lengths of the interior boundaries.
		This example corresponds to the aggregation step in 
		\fig\ref{fig:AreaAgg_FirstStep}
	}
	\label{fig:AreaAgg_h_length}
\end{figure*}

\subsection{Combining estimated costs}
\label{sec:AreaAgg_CombinationEstimated}
In accordance 
with our two combinatorial costs in 
\sect\ref{sec:AreaAgg_Combining},
we define two estimated-cost functions:
\begin{equation}
\label{eq:h_1}
h_1(\Pnode)=
(1-\lambda)h_\mathrm{type}(\Pnode)
+\lambda h_{\mathrm{comp}}(\Pnode), \nonumber
\end{equation}
and
\begin{equation}
\label{eq:h_2}
h_2(\Pnode)=
(1-\lambda)h_\mathrm{type}(\Pnode)
+\lambda h_{\mathrm{lgth}}(\Pnode). \nonumber
\end{equation}

\section{Integer Linear Programming}
\label{sec:AreaAgg_ILP}

\emph{Linear programming} is a method 
to optimize a \emph{linear objective}
subject to a set of \emph{linear constraints},
with some \emph{variables}.
For example, suppose that we are selling coffee.
We have~$3.5\,$kg of coffee powder and~$10\,$kg of water.
We mix the powder and the water to provide coffee with 
two kinds of intensity in terms of mass:~$40\%$ and~$20\%$.
The profits of the two kinds of coffee 
are respectively~$5\,$\euro and~$4\,$\euro.
We want to maximize the total profit of selling coffee.
If we offer respectively~$x\,$kg and~$y\,$kg 
of the two kinds of coffee,
then~$x$ and~$y$ are our variables.
Our objective is to
$$
\mathrm{maximize} 	\quad	 5x+4y
$$
To provide~$x\,$kg of coffee with intensity~$40\%$,
we need to use~$0.4x\,$kg of coffee powder 
and~$0.6x\,$kg water.
Analogously, it consumes~$0.2y\,$kg of coffee powder 
and~$0.8y\,$kg of water to produce~$y\,$kg of coffee
with intensity~$20\%$.
Therefore, we have four constraints:
\begin{align*}
0.4x+0.2y	&\le 3.5,				\\
0.6x+0.8y 	&\le 10,	\text{~and}			\\
x,y			&\ge 0.
\end{align*}
With the objective and the constraints, 
we have set up a \emph{linear program} (LP).
We observed that 
all the feasible solutions, i.e., pairs of~$(x,y)$,
fall in the gray area 
shown in \fig\ref{fig:AreaAgg_ILPIllustration}a.
Drawing a line with slope~$-\frac{5}{4}$,
we see that every pair of~$(x,y)$ lying on the line
yields the same result for~$5x+4y$, 
the profit we want to maximize.
For example, every pair of~$(x,y)$ lying on the dashed line
in \fig\ref{fig:AreaAgg_ILPIllustration}a 
yields profit~$40\,$\euro.
If we move the dashed line to the upper right,
then we are able to achieve a larger value for~$5x+4y$. 
In order to maximize the profit, 
we move the dashed line to the upper right as much as possible
and at the same time make sure that 
the it still intersects with the gray area.
Note that if the dashed line 
does not intersect with the gray area,
then there is no feasible pair of~$(x,y)$ 
on the dashed line anymore.
As a result, we get the optimal solution 
when the dashed line hits point~$A$,
where the profit is~$5 \cdot 4 + 4 \cdot 9.5 =58\,$\euro.
\textcite{Karmarkar1984LP}
proved that an LP can be solved in a polynomial time.

Now we change our problem a bit.
We assume that we want to sell coffee in bottles,
where each bottle contains exactly~$1\,$kg of coffee 
with intensity either~$40\%$ or~$20\%$.
Our question becomes how many bottles of each kind of coffee
we should sell in order to maximize the profit.
If we sell the two kinds of coffee 
respectively~$x'$ and~$y'$ bottles,
then our problem becomes:
\begin{alignat*}{3}
&&\text{maximize} 	\quad	&& 5x'+4y' 		&			\\
&&\text{subject to} \quad	&& 0.4x'+0.2y'	&\le 3.5, 	\\
&&					\quad	&& 0.6x'+0.8y' 	&\le 10, 	\\
&&					\quad	&& x', y' 		&\ge 0, 	\\
&&\text{and} 		\quad	&& x', y'		&\in \mathbb{Z}.
\end{alignat*}
For this problem, only the pairs of~$(x,y)$ 
represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
are feasible solutions
(point~$A$ is no longer an optimal solution in this case).
In order to maximize our profit,
we should move the dashed line to the upper right 
as much as possible
and at the same time make sure that 
it hits at least one of the gray dots.
To solve such a problem is known as
\emph{integer linear programming},
which is NP-complete.
Despite the fact, there are
mathematical solvers yielding optimal solutions
for some NP-complete problems in reasonable time
\parencite{Haunert2017Label}.
Also, by using these solvers we profit 
from every improvement, by their producers,
for the same class of problems
\parencite{Haunert2017Label}.
The general form of an \emph{integer linear program} (ILP) is
\begin{alignat*}{3}
&&\text{maximize} 	\quad&& \bm{C}^\mathrm{T}\bm{X}	&		\\
&&\text{subject to} \quad&& \bm{EX}			&\le \bm{H}, 	\\
&&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
\end{alignat*}
where vector~$\bm{X}$ represents integer variables, 
vector~$\bm{C} \in \mathbb{R}^I$, 
vector~$\bm{H} \in \mathbb{R}^J$,
and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
Furthermore, if we require that
$$
\bm{X} 	\in \{0,1\}^I,
$$
then we have only binary variables for an ILP.
Binary variables are important 
because they occur regularly in optimizations
\parencite[section~9.2]{bradley1977applied}.
Also, an ILP with general (bounded) integer variables 
can always be translated to an ILP with binary variables
\parencite[section~2.3]{Williams2009Integer}.
To find optimal sequences for area aggregation, 
we are going to use binary variables in our ILP.

\begin{figure*}[tb]
	\centering
	\includegraphics[page=4]{AreaAgg_ILP}
	\caption{Example of linear programming (a)
		and integer linear programming (b). 
	}
	\label{fig:AreaAgg_ILPIllustration}
\end{figure*}

We want to compare the \Astar algorithm with 
integer linear programming in finding 
optimal solutions for our aggregation problem. 
Since integer linear programming
can handle only linear constraints, 
we define the compactness of a subdivision as 
the length of the subdivision's interior boundaries.
That is, we use cost function~$g_2$ (see \eq\ref{eq:g_2}).
Our basic idea is to formalize the problem of 
finding a shortest path as an ILP.
Then we solve this ILP by minimizing the total cost.
We define the \emph{center} of a patch as the polygon 
to which other polygons in the same patch are assigned. 
At the beginning, every patch consists of only one polygon, 
and this polygon is the center of the patch.
When we aggregate patch~$u$ into patch~$v$, 
all the polygons of~$u$ are assigned to the center of~$v$,
and the type of~$u$'s polygons 
are changed to the type of $v$'s center.
In the following, we show how to formalize our problem 
as an ILP.
For simplicity, we sometimes denote by \emph{patch~$r$} the 
patch using polygon~$r$ as the center at time~$t$.

\subsection{Variables}
\label{sub:AreaAgg_variables}

Our problem is to decide centers for polygons to be assigned.
Each question of type 
``Is polygon~$p$ assigned to center~$r$?''
can be answered with ``yes'' or ``no''.
Hence, we use binary ($0$--$1$) variables.
We need five sets of variables
in order to formulate our pathfinding problem as an ILP.
%
The first set of variables is used to tell the program 
our rules for area aggregation.
\begin{figure*}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_ILP}
	\caption{Some examples of variables~$x$,~$y$, and~$z$ for our ILP. 
		The arrows in the figures show the aggregation steps and
		the dotted lines represent the removed boundaries by the aggregation steps.
	}
	\label{fig:AreaAgg_Variables}
\end{figure*}
We introduce the variable 
\begin{flalign*}
&\myquad[4]
\embrd[V]{x_{t,p,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T, \forall p,r \in P&
\end{flalign*}
with the intended meaning~$x_{t,p,r}=1$ if and only if 
polygon $p$ is assigned to polygon $r$ at time $t$. 
If a polygon is a center at time~$t$, 
then the polygon must be assigned to itself, 
that is, $x_{t,r,r}=1$
(see \fig\ref{fig:AreaAgg_Variables} for some examples).

Our second set of variables is used to compute the
cost of type change.  We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{y_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1\}, \forall p,o,r \in P&
\end{flalign*}
with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
polygon~$p$ is assigned to center $o\in P$ at time~$t-1$ 
and to center~$r$ at time~$t$.
Specifically, $y_{t,p,o,o}=1$ means that
polygon~$p$ is assigned to the same center 
at times~$t-1$ and~$t$ 
(see \fig\ref{fig:AreaAgg_Variables}).

We need a third set of variables 
for computing the cost of length.
We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{z_{t,p,q,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{1,n\}, \forall p,q,r \in P&
\end{flalign*}
with the intended meaning~$z_{t,p,q,r}=1$ 
if and only if at time~$t$
polygons~$p$ and~$q$ are both in patch~$r$.
In this case, their common boundary should be removed
(see \fig\ref{fig:AreaAgg_Variables}).
When variable~$z_{t,p,q,r}=1$ and~$p=q$,
we define the length of their common boundary to be~$0$ 
because we shall not remove any.
Note that time $t\in T\setminus \{1,n\}$.
We do not need~$z_{t,p,q,r}$ for time~$t=1$ 
because at the time
there are no two polygons in the same patch.
Namely, it always holds that~$z_{1,p,q,r}=0$, 
which does not help in our ILP.
We do not need~$z_{t,p,q,r}$ for time~$t=n$
because in this case
all the polygons are in the same patch.
The situation that~$z_{n,p,q,r}=1$ always holds
does not help in our ILP, either.

We use a fourth set of variables
to guarantee contiguity of each patch. 
In other words, we aggregate two patches 
only when they are neighbors (adjacent).
We introduce
\begin{flalign*}
&\myquad[4]
\embrd[V]{c_{t,p,o,r}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus \{n-1,n\}, 
\forall p,o,r \in P \text{~with}~o\ne r,&
\end{flalign*}
with the intended meaning~$c_{t,p,o,r}=1$ 
if and only if at time~$t$
polygon~$p$ is assigned to center~$o$ 
and~$p$ has a neighbor assigned to center~$r$
(see for example \fig\ref{fig:AreaAgg_Variables_Neighbor}).
We do not need a variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
because then there are only two patches left 
and they must be neighbors.

Our last set of variables is needed to 
enforce that
every aggregation step involves a smallest patch. 
We define
\begin{flalign*}
&\myquad[4]
\embrd[V]{w_{t,o}} \in
\embld[U]{\{0,1\}} \qquad 
\forall t\in T\setminus\{n\}, \forall o \in P&
\end{flalign*}
with $w_{t,o}=1$ meaning 
that patch~$o$ is a smallest patch at time~$t$.

In total, the number of variables
in our ILP formulation is~$O(n^4)$.

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_ILP}
	\caption{There are two patches, 
		which respectively use polygons~$o$ and~$r$ 
		as their centers.
		Polygons in the same patch 
		are separated by dotted lines.
		Polygon~$p$, in patch~$o$, 
		has two neighbors assigned to center~$r$,
		i.e., polygons~$q_1$ and~$q_2$.
		In this case, patches~$o$ and~$r$ are neighbors 
		and can be aggregated.
	}
	\label{fig:AreaAgg_Variables_Neighbor}
\end{figure}

\subsection{Objectives}
\label{sub:AreaAgg_objectives}

Our aim is to minimize a weighted sum of the two costs, 
the cost of type change and the cost of length,
that is, we
\begin{equation}
\label{eq:ilpcost}
\mathrm{minimize} \quad 
(1-\lambda)F_\mathrm{type} +\lambda F_\mathrm{lgth},
\nonumber
\end{equation}
where~$\lambda$, as in \eq\ref{eq:g_1}, 
is a parameter 
to assign importances 
of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
According to the objective we introduced in
\sect\ref{sec:AreaAgg_f_type},
the total cost of type change is defined as
\begin{flalign*}
%\label{eq:F_type}
&\myquad[4]
\embrd[V]{F_\mathrm{type}} =
\sum_{t=2}^{n} \sum_{p\in P} \sum_{o\in P} \sum_{r\in P}
\left(\frac{a_p}{A_R} \cdot
\frac{d(T(o),T(r))}{T_{\max}}\cdot 
y_{t,p,o,r}\right), & 
\end{flalign*}
where, similar to \eq\ref{eq:f_type}, 
$a_p$ is the area of polygon~$p$,
$A_R$ is the area of the region, 
and~$T(o)$ and~$T(r)$ are the types of centers~$o$ and~$r$.

We also try to minimize the overall interior lengths of all the 
intermediate subdivisions.
As discussed in \sect\ref{sec:AreaAgg_costlength},
we need a cost that can be computed linearly.
We use the length of the interior boundaries 
as an alternative to compactness.
Recall that $B(\Pstart)$ is the set of interior boundaries 
at time $t=1$ (see \sect\ref{sec:AreaAgg_costlength}).
The sum of the normalized length of 
the remaining interior boundaries at all times 
can be computed by
\begin{flalign}
\label{eq:F_length_raw}
&\myquad[4]
\embrd[V]{F_\mathrm{lgth}} =
\frac{1}{n-2} \sum_{t=2}^{n-1} 
\frac{\sum_{b\in B (\Pstart)} |b| - 
	\frac{1}{2} \sum_{p \in P}\sum_{q \in P}\sum_{r \in P} 
	\big(|b_{pq}|\cdot z_{t,p,q,r}\big)} {D(t)}, &
\end{flalign}
where variable~$b_{pq}$ represents the common boundary 
between polygons~$p$ and~$q$. 
We define the lengths of the common boundary to be~$0$
(i.e., $|b_{pq}|=0$) if $p=q$ 
because no boundary is removed in this case.
Function~$D(t)$, defined by \eq\ref{eq:AreaAgg_Norm}, 
is used to normalize the cost of length.
As in \eq\ref{eq:f_length}, 
denominator~$n-2$ is used to balance 
between the costs of type change and length.
Integrating~$D(t)$ into \eq\ref{eq:F_length_raw}, we have
\begin{flalign*}
%\label{eq:F_length}
&\myquad[4]
\embrd[V]{F_\mathrm{lgth}} =
\frac{n-1}{n-2} \sum_{t=2}^{n-1}
\left(
\frac{1}{n-t} -
\frac{\sum_{p \in P}\sum_{q \in P}\sum_{r \in P} 
	\big(|b_{pq}|\cdot z_{t,p,q,r}\big)}
{2(n-t)\sum_{b\in B (\Pstart)} |b| }
\right). &
\end{flalign*}

\subsection{Constraints}
\label{sub:AreaAgg_Constraints}

In order to formulate our aggregation problem as an ILP, 
we restrict the variables introduced in \sect\ref{sub:AreaAgg_variables} 
by setting up constraints.
Recall that the intended meaning 
of~$x_{t,p,r}=1$ is that, at time~$t$, 
polygon~$p$ is assigned to center~$r$. 
Our first constraint is that, at time~$t$, 
polygon~$p$ is assigned to 
exactly one center. 
To this end, we require that
\begin{flalign}
\label{eq:CstrOneCenter}
&\eqquad
\embrd{\sum_{r\in P} x_{t,p,r}} =\embld{1} 
\inquad \forall t \in {T}, \forall p \in P. &
\end{flalign}

The next constraint is that polygon~$r$ is available to be 
assigned by other polygons only when~$r$ is a center.
In our case, if polygon~$r$ is a center, 
then it must be assigned to itself,
that is, $x_{t,r,r}=1$.
If~$r$ is not a center, then $x_{t,r,r}=0$.
In either case,
\begin{flalign}
\label{eq:CstrAssign}
&\eqquad
\embrd{x_{t,p,r}} \leq \embld{x_{t,r,r}}
\inquad \forall t \in {T}, \forall  p, r \in P. &
\end{flalign}

Aggregating one patch into another results in 
the number of centers decreasing by~$1$.
We make sure that exactly one patch 
is aggregated into another by 
specifying the number of centers
for each point in time, that is,
\begin{flalign}
%\label{eq:CstrCountCenter}
&\eqquad
\embrd{\sum_{r\in P} x_{t,r,r}} =
\embld{n-t+1} \inquad
\forall t \in {T}, &
\end{flalign}
where polygon $r$ is a center at time~$t$ if and only if 
$x_{t,r,r}=1$.

A center can disappear, but will never reappear afterwards.
Hence,
\begin{flalign}
\label{eq:CstrNoReappear}
&\eqquad
\embrd{x_{t,r,r}} \le 
\embld{x_{t-1,r,r}} \inquad 
\forall t \in {T}\setminus \{1\},
\forall r \in P.&
\end{flalign}

On the start map, 
there are some polygons with  goal type $T_\mathrm{goal}$
(see definition in \sect\ref{sec:AreaAgg_h_type}).
At time $t=n$, all polygons are aggregated into one patch.
This patch must have the goal type, $T_\mathrm{goal}$.
In other words, the center of this patch must be one of the 
polygons with the 
goal type on the start map:
\begin{equation}
\label{eq:CstrType}
\sum_{r\in P\colon T(r)=T_\mathrm{goal}}
x_{n,r,r}=1,
\end{equation}
where $T(r)$ is the type of polygon $r$ at time $t=1$.

Next, we use the binary variables~$y_{t,p,o,r}$
introduced in \sect\ref{sub:AreaAgg_variables}.  
Recall that the intended meaning of~$y_{t,p,o,r}=1$ is that 
polygon~$p$ is assigned to center~$o$ at time~$t-1$ 
and to center~$r$ at time~$t$.
To enforce this, we use two types of constraints.

First, if polygon~$p$ is assigned 
to center~$o$ at time~$t-1$ ($x_{t-1,p,o}=1$)
and assigned to center~$r$ at time $t$
($x_{t,p,r}=1$), then $y_{t,p,o,r}=1$.  This is expressed by
\begin{flalign}
\label{eq:CstrY1}
&\eqquad
\embrd{y_{t,p,o,r}} \geq 
\embld{x_{t-1,p,o}+x_{t,p,r}-1} \inquad
\forall t \in {T} \setminus \{1\}, 
\forall p, o, r \in P.&
\end{flalign}

Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
or~$p$ is not assigned to~$r$ at time $t$ ($x_{t,p,o}=0$),
then $y_{t,p,o,r}=0$.
This is expressed by
\begin{flalign}
\label{eq:CstrY2}
&\eqquad
\begin{array}{@{}l}
\embrd{y_{t,p,o,r}} \le \\
\embrd{y_{t,p,o,r}} \le 
\end{array}
\embld{\hspace{0.5pt}
	\begin{array}{@{}l}
	x_{t-1,p,o} \\
	x_{t,p,r}
	\end{array}
	\bigg\} 
}
\inquad \hspace{0.5pt}
\forall t\in T\setminus \{1\}, 
\forall	p,o,r \in P.&	
\end{flalign}

%Third, if centers $o$ and $r$ are identical, 
%then the center of polygon $p$ is not changed.
%In this case, $y_{t,p,o,r}=0$, which is presented by
%\begin{equation}
%\label{eq:CstrY3}
%y_{t,p,o,r}=0 \qquad
%\forall t \in {T} / \{n\}, 
%\forall p, o, r \in P.
%\end{equation}

In \sect\ref{sub:AreaAgg_variables},
we introduced the binary variables~$z_{t,p,q,r}$.
Recall that the intended meaning of $z_{t,p,q,r}=1$ is that, at
time~$t$, polygons~$p$ and~$q$ are both in patch~$r$.
To enforce this, we need three types of constraints.

First, if two polygons~$p$ and~$q$ are assigned 
to center~$r$ at time~$t$ ($x_{t,p,r}=x_{t,q,r}=1$),
then~$z_{t,p,q,r}=1$.  This is expressed by
\begin{flalign}
\label{eq:CstrZ1}
&\eqquad
\embrd{z_{t,p,q,r}} \geq 
\embld{x_{t,p,r}+x_{t,q,r}-1} \inquad
\forall t \in T \setminus \{1,n\}, 
\forall p, q, r \in P.&
\end{flalign}

Second, if not both~$p$ and~$q$ are assigned to~$r$,
then $z_{t,p,q,r}=0$.  This is expressed by
\begin{flalign}
\label{eq:CstrZ2}
&\eqquad
\begin{array}{@{}l}
\embrd{z_{t,p,q,r}} \le  \\
\embrd{z_{t,p,q,r}} \le 
\end{array} 
\embld{\hspace{0.5pt}
	\begin{array}{@{}l}
	x_{t,p,r} \\
	x_{t,q,r}
	\end{array}
	\bigg\} 
}
\inquad \hspace{0.5pt}
\forall t \in T \setminus \{1,n\}, 
\forall p, q, r \in P.&	
\end{flalign}
Note the correspondence between 
constraints~(\ref{eq:CstrY1}) and~(\ref{eq:CstrZ1})
and between 
constraints~(\ref{eq:CstrY2}) and~(\ref{eq:CstrZ2}).

Third, we introduce an abbreviation that will be helpful to 
express
the last type of constraint involving variables~$z_{t,p,q,r}$:
\begin{flalign}
\label{eq:CstrZabbrv}
&\eqquad
\embrd{z_{t,p,q}} = 
\embld{\sum_{r \in P}z_{t,p,q,r}}
\inquad 
\forall t\in T \setminus \{1,n\}, 
\forall	p,q \in P,&
\end{flalign}
where the reason we do not need~$z_{t,p,q}$ for~$t=1$ or~$t=n$
is the same as for $z_{t,p,q,r}$
(see \sect\ref{sub:AreaAgg_variables}).
Note that $z_{t,p,q}$ expresses whether, at time~$t$, 
polygons~$p$ and~$q$ are 
in the same patch ($z_{t,p,q}=1$) or not ($z_{t,p,q}=0$).
%
Note further that 
constraints~(\ref{eq:CstrOneCenter}) and~(\ref{eq:CstrZ2}) 
ensure that~$p$ and~$q$ can only be assigned 
to one common patch, that is, $z_{t,p,q} \le 1$.

Now we use our new variables~$z_{t,p,q}$
to express the following requirement. 
If two polygons have been aggregated into one patch, 
they will always be in the same patch 
at later times~-- although the center of their common patch 
can change after the point in time 
when they were aggregated first. 
In other words, as a function of time~$t$, 
$z_{t,p,q}$ is monotonically increasing:
\begin{flalign}
\label{eq:CstrTogether}
&\eqquad
\embrd{z_{t,p,q}} \ge 
\embld{z_{t-1,p,q}} \inquad
\forall t \in \{3,4,\ldots,n-1\},  
\forall p, q \in P.&
\end{flalign}

The problem of ensuring contiguity inside a patch 
when using integer linear programming 
has received considerable attention.
Usually, a subdivision is represented by a graph
(see \fig\ref{fig:AreaAgg_Variables_Graph}).
%
\textcite{Zoltners1983Territory} regarded each node as a center.
For each center, they found a shortest path 
to each of the other nodes.
Then they required that a center can be assigned 
by a node only if 
at least one immediate predecessor of the node 
in the shortest path had been assigned to the center.
Although this requirement makes their problem easier to be 
solved,
it excludes many feasible patches.
%
\textcite{Williams2002Contiguous} found an optimal spanning tree 
with a user-specified number of nodes, say,~$i$.
In order to ensure contiguity, this method requires that 
there must be~$i-1$ edges in the spanning tree.
%
For a given center, \textcite{Cova2000_Contiguity} 
were able to find all the contiguous patches.
In their method, when a node is to be assigned to a center, 
a path from the node to the center was demanded 
that each node is assigned to the center.
%
Similarly, \textcite{Shirabe2005Contiguity} modeled 
the contiguity problem as a network flow.
He required that there must be a path so that 
some fluid could flow from a node to a sink (center).
%
\textcite{Oehrlein2017Aggregation} utilized a method based 
on \emph{vertex separators}.	
Given center~$r$ and node~$p$, 
a separator is a set of nodes
such that any path from~$r$ to~$p$ 
will contain at least one node of the set.
The contiguity between center~$r$ and node~$p$ is ensured 
if each of the separators contains 
at least one node assigned to the center.
%
The last four ideas can be adapted into our method
as we do not wish to exclude any possible solutions.
However, we use an idea
that is more intuitive for our problem
since we aggregate step by step.

\begin{figure}[tb]
	\centering
	\includegraphics[page=3]{AreaAgg_ILP}
	\caption{The graph of a subdivision.
		Each polygon of the subdivision is represented as a node 
		in the graph.
		There is an edge between two nodes
		if the corresponding two polygons are adjacent.
	}
	\label{fig:AreaAgg_Variables_Graph}
\end{figure}

We aggregate two patches only if they are neighbors.
To ensure this, we need the binary variables~$c_{t,p,o,r}$
introduced in \sect\ref{sub:AreaAgg_variables}.
Recall that the intended meaning of~$c_{t,p,o,r}=1$ 
is that, at time~$t$, 
polygon~$p$ of patch~$o$ has 
at least one neighboring polygon in patch~$r$.
To enforce this behavior of~$c_{t,p,o,r}$, 
we need four types of constraints.

First, at time~$t$, polygon~$p$ must actually be assigned 
to center~$o$,
\begin{flalign}
\label{eq:CstrC_Part}
&\eqquad
\embrd[C]{c_{t,p,o,r}} \le 
\embld[D]{x_{t,p,o}} \inquad
\forall t 	 \in T\setminus \{n-1,n\},  
\forall p, o, r \in P \text{~with}~o\ne r.&
\end{flalign}

Second, at time~$t$, polygon~$p$ has at least 
one neighbor that is assigned to center~$r$,
\begin{flalign}
\label{eq:CstrC_Neighbor}
&\eqquad
\embrd[C]{c_{t,p,o,r}} \le 
\embld[D]{\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r}} \inquad
\forall t 	 \in T\setminus \{n-1,n\},  
\forall p, o, r \in P \text{~with}~o\ne r,&
\end{flalign}
where~$N_\mathrm{nbr}(p)$ represents 
the set of polygons adjacent to~$p$.

Third, if polygon~$p$ is in patch~$o$ and~$p$ has at least 
one neighbor in patch~$r$, then we must enforce~$c_{t,p,o,r}=1$,
\begin{flalign}
\label{eq:CstrC_Positive}
&\eqquad
\begin{array}{@{}l}
\embrd[C]{c_{t,p,o,r}} \ge  \\
\embrd[C]{} %an empty place
\end{array} 
\embld[D]{\hspace{0.5pt}
	\begin{array}{@{}l}
	x_{t,p,o} + x_{t,q,r} -1 \\
	~ %an empty place
	\end{array}
}
\inquad \hspace{0.5pt}
\begin{array}{@{}l}
\forall t 	 \in T\setminus \{n-1,n\},\\
\forall p, o, r \in P \text{~with}~o\ne r,
\forall q \in N_\mathrm{nbr}(p).
\end{array} &	
\end{flalign}

Fourth, if we aggregate patch~$o$ into patch~$r$
from time~$t-1$ to time~$t$, 
then $y_{t,o,o,r}=1$.
In this case, we must make sure that 
the two patches are actually neighbors,
\begin{flalign}
\label{eq:CstrC_Agg}
&\eqquad
\embrd[C]{y_{t,o,o,r}} \le 
\embld[D]{\sum_{p\in P} c_{t-1,p,o,r}} \inquad
\forall t 	 \in T\setminus \{1,n\},  
\forall o, r \in P \text{~with}~o\ne r.&
\end{flalign}

If we do not require that 
each aggregation step must involve a smallest patch,
then we only need constraints
(\ref{eq:CstrOneCenter})--(\ref{eq:CstrC_Agg})
explained so far 
and variables~$x_{t,p,r}$, $y_{t,p,o,r}$, $z_{t,p,q,r}$,
and~$c_{t,p,o,r}$.
If we insist on involving a smallest patch at each step,
then we need more variables and more constraints.

\mypar{Aggregation involving a smallest patch}
In order to make sure that 
each of our aggregation steps involves a smallest patch,
we need another type of variable,~$w_{t,o}$.
Recall that the intended meaning of~$w_{t,o}=1$ is that 
polygon~$o$ is the center of 
a smallest patch at time~$t$.
We will use this to enforce that
this patch is involved in the aggregation step 
from time~$t$ to~$t+1$.
At any time~$t$, 
we pick exactly one smallest patch and aggregate it with 
one of its neighbors;
we do not care whether or not the neighbor is a smallest one.
Therefore, we have
\begin{flalign}
\label{eq:CstrSOneSmallest}
&\eqquad
\embrd[S]{\sum_{o\in P}w_{t,o}} =
\embld[T]{1} \inquad 
\forall t \in {T}\setminus \{n\}.&
\end{flalign}

Assume that patch~$o$ is the smallest patch
which is involved in the aggregation step from~$t$ to~$t+1$,
and that we are aggregating patches~$o$ and~$r$.
There can be two cases.
Patch~$o$ is aggregated into patch~$r$, 
or the other way around.
In the first case, we have variable~$y_{t+1,o,o,r}=1$,
and in the second case, we have~$y_{t+1,r,r,o}=1$.
Either of the two constraints implies 
that polygon~$o$ is indeed a center at time~$t$, 
that is,~$x_{t,o,o} =1$.
In order to enforce that
the aggregation step involves patch~$o$,
we must make sure that~$y_{t+1,o,o,r}=1$ or~$y_{t+1,r,r,o}=1$ 
when $w_{t,o}=1$.
Consequently, we use the constraint
\begin{flalign}
\label{eq:CstrSInvolveSmallest}
%\displaystyle doesn't work for \setminus
%if we do \embld{\sum_{r\in P \setminus \{o\}}
&\eqquad
\embrd[S]{w_{t,o}} \le 
\embld[T]{\displaystyle\sum_{r\in P \setminus \{o\}} \left(y_{t+1,o,o,r} +y_{t+1,r,r,o}\right)} \inquad
\forall t \in {T}\setminus \{n\}, 
\forall o \in P. &
\end{flalign}

Now we need to make sure that
patch~$o$ with $w_{t,o}=1$ is indeed 
a smallest patch at time~$t$.
We define variable~$A_{t,r}$ as the area of 
patch~$r$ at time~$t$, 
that is,
\begin{flalign*}
&\eqquad
\embrd[S]{A_{t,r}} = 
\embld[T]{\sum_{p\in P} a_p \cdot x_{t,p,r},} &
\end{flalign*}
where~$a_p$ is the area of polygon~$p$ 
and is a constant (as viewed by the ILP).
Area~$A_{t,r}$ is positive 
if and only if polygon~$r$ is a center at time~$t$,
that is, if and only if~$x_{t,r,r}=1$.
We define a very large number~$M$ 
to help us construct the corresponding constraints.
It suffices to set~$M$ to 
the area of the whole region, 
i.e., $M=A_R$ (see \eq\ref{eq:f_type}). 
We require that
%\begin{flalign}
%\label{eq:CstrSIndeedSmallest}
%&\eqquad
%\embrd[S]{A_{t,o} - M(1-w_{t,o})} \le
%\embld[T]{A_{t,r}+M(1-x_{t,r,r})} \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r. &
%\end{flalign}
%\begin{flalign}
%\label{eq:CstrSIndeedSmallest}
%&\eqquad
%\embrd[S]{A_{t,o}} -
%\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
%\forall t 	 \in {T}\setminus \{n\}, 
%\forall o, r \in P \text{~with}~o\ne r. &
%\end{flalign}
\begin{equation}
A_{t,o} - M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \inquad
\forall t 	 \in {T}\setminus \{n\}, 
\forall o, r \in P \text{~with}~o\ne r.
\end{equation}
This constraint takes effect only when~$w_{t,o}=1$ 
and~$x_{t,r,r}=1$, which indicates that 
patch~$o$ is smaller than or equal to 
all the other existing patches at time~$t$.

In order to compute an aggregation sequence 
involving a smallest patch at each step, 
we need all the five types of variables and 
constraints~(\ref{eq:CstrOneCenter})--(\ref{eq:CstrSIndeedSmallest}).
In total, the number of constraints is~$O(n^4)$.

\section{Case Study}
\label{sec:AreaAgg_CaseStudy}
We have implemented our methods 
based on C\# (Microsoft Visual Studio~$2015$) 
and ArcObjects SDK 10.4.1.
We used the IBM ILOG
CPLEX Optimization Studio~$12.6.3.0$ to solve our ILP.
Our prototype is open access on 
GitHub\footnote{
	\url{https://github.com/IGNF/ContinuousGeneralisation},
	Accessed: 2018-Jun-18.}.
Our computer ran
Windows~$7$ on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
We measured processing time 
by the built-in C\# class \emph{Stopwatch}.
As required by ArcObjects SDK~$10.4.1$,
we specified our program to run on the $32$-bit platform. 
We added a post-build task about ``largeaddressaware''
in Microsoft Visual Studio so that 
we were able to use up to $3\,$GB of main memory\footnote{
	The details of the setting can be found at 	
	\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
	Accessed: 2017-Nov-01.}.
Our CPLEX version may declare an optimal solution
while it is not really optimal.
To fix this problem, we had to disable 
both primal and dual presolve reductions\footnote{
	For more details about the problem, see
	\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
	Accessed: 2017-Nov-12.}.

We tested our method on a data set 
from the German topographic database ATKIS DLM~$50$. 
The data set represents the place 
``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
Our start map is the result of collapsing areas 
by \citet[pp.~61--66]{haunert2008f}.
The start map has~$5{,}537$ polygons. 
Our goal map was generalized from the start map 
by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
at~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
The goal map has~$734$ polygons, 
which means that there are~$N=734$ regions.
The distribution of region sizes is shown in \fig\ref{fig:AreaAgg_NumRegion}.
%
We used a tree-based method introduced by 
\citet{Rada1989SemanticMetric} 
to define the distances of the types;
the distance is the ``number of edges'' that
we need to travel from one node to another 
node in the tree of type hierarchy\footnote{
	More information about land-cover types can be found at 
	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
	Accessed: 2017-Nov-01.}
(see \fig\ref{fig:AreaAgg_TypeDistances}). 
For example, the distance from type \emph{village}
to type \emph{fence} is~$2$, 
to type \emph{street} is~$4$, and
to type \emph{farm land} is~$6$.
In this tree, the maximum distance is~$6$, 
which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
According to \citet{Rada1989SemanticMetric}, 
the resulting cost function for type change is a metric.

\begin{figure}[tb]
	\captionsetup[subfigure]{labelformat=empty}
	\begin{subfigure}[b]{.49\textwidth}
		\centering
		\includegraphics[page=1]{AreaAgg_Data}
		\caption{Start map, $5{,}537$ polygons, \\
			at scale $1:50{,}000$}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{.49\textwidth}
		\centering
		\includegraphics[page=2]{AreaAgg_Data}
		\caption{Goal map, $734$ polygons, \\
			at scale $1:250{,}000$}
	\end{subfigure}
	%
	%	\par\vspace{\intextsep} %Leave a gap between the two figures
	\par\vspace{\baselineskip} %Leave a gap	figures
	%
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[page=3]{AreaAgg_Data}
		\caption{The 20 land-cover types appearing in our data}
	\end{subfigure}
	\caption{The data of our case study.}
	\label{fig:AreaAgg_Data}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[page=4]{AreaAgg_Data}
	\caption{Distribution of region sizes:
		the $y$-axis shows how many regions of a given size range are contained in our data set.}
	\label{fig:AreaAgg_NumRegion}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{AreaAgg_TypeDistances}
	\caption{The tree of type hierarchy used in our case study.
		For example, the distance between 
		types \emph{village} and \emph{farm land} is~$6$.}
	\label{fig:AreaAgg_TypeDistances}
\end{figure}

\subsection{Using costs of type change and compactness}
\label{sec:AreaAgg_CaseStudy1}

As illustrated in \sect\ref{sec:AreaAgg_Combining},
we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
which is a combination of the costs 
of type change and compactness (see \eq\ref{eq:g_1}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W$ nodes 
(see \sect\ref{sec:AreaAgg_AStar}).
We tried $W=200{,}000$ and $W=400{,}000$
(if we could use more main memory, 
then we could test by using some larger~$W$). 
The results are shown in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
%
Comparing to \Astar, 
the greedy algorithm visited 
fewer nodes and arcs in the graph $G$ 
and used much less time.
However, 
\Astar managed to find solutions with lower total cost,
$117.3$ (or~$117.2$), 
which is~$2.8\%$ less than 
the total cost of the greedy algorithm,~$120.7$.
%
When~$W=200{,}000$,
we are sure that 
we have found optimal solutions 
for~$702$ of the~$734$ regions ($94.3\%$),
while the greedy algorithm solved only~$407$ of the~$702$ regions to optimality.
For the other~$32$ regions, we have found feasible solutions
by both algorithms
(see column \#over in 
Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
Although some of the feasible solutions may also be optimal,
we cannot verify only from the cost values.
\begin{table*}[tb]
	%\small	
	\centering
	\caption{A comparison of the greedy algorithm and \Astar		
		when using cost function~$g_1$ (see \eq\ref{eq:g_1}).
		For \Astar, we used two settings, 
		i.e.,~$W=200{,}000$ and~$W=400{,}000$.
		%
		Symbol~\#over is the number and percentage of regions
		(out of $N=734$) that needed overestimation.
		%
		Variable~$k_\mathrm{sum}$ is 
		the total number of repetitions.
		%
		Symbols~\#nodes and~\#arcs are the total 
		numbers of nodes and arcs that \Astar visited.  
		(For instances where we needed overestimation, 
		only the final attempt was counted.)
		%
		$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
		and~$\sum g_1$
		respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
		$g_\mathrm{comp}(\Pgoal)$, and~$g_1(\Pgoal)$ 
		over all the~$734$ instances 
		(see \eqs\ref{eq:g_type}, \ref{eq:g_comp}, 
		and~\ref{eq:g_1}).
		%
		The percentage in the
		time column is the fraction of the total
		runtime spent on solving the instances
		that needed overestimation.
	}
	\label{tab:AreaAgg_CaseStudy1_Statistics}
	\setlength{\tabcolsep}{0.7ex}
	\begin{tabular}{lCRCCCCCd{3.7}}
		\toprule
		\multicolumn{1}{l}{Methods} &
		\multicolumn{1}{c}{\#over} &
		\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
		\multicolumn{1}{c}{\#nodes} & 
		\multicolumn{1}{c}{\#arcs} & 
		\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
		\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
		\multicolumn{1}{c}{$\sum g_1$} & 
		\multicolumn{1}{c}{Time (min)} \\ 
		\midrule
		Greedy 	&     &     & 5.5\cdot 10^3 & 4.8\cdot 10^3 
		& 53.2 & 188.2 & 120.7 & 2'0\\
		%
		\Astar$_{\!\!200{,}000}$	&  32~(4.4\%) & 102 &  3.6\cdot 
		10^6 
		&    5.7\cdot 10^6	
		& 51.4 & 183.2 & 117.3 & 75'8~(90.5\%)\\
		%
		\Astar$_{\!\!400{,}000}$	&  29~(4.0\%) &   89 &  6.5\cdot 
		10^6 
		&    9.8\cdot 10^6
		& 51.4 & 183.1 & 117.2 & 137'7~(93.9\%) 
		\\ \bottomrule			
	\end{tabular}
\end{table*}

In accordance with \sect\ref{sec:AreaAgg_AStar}, 
for region with ID~$i$ 
we define~$k_i$ as the least number of repetitions 
that we do to find a feasible solution. 
We define the total number of repetitions 
as~$k_\mathrm{sum}=\sum_{i=1}^N k_i$; 
recall that~$N$ is the number of regions.
After increasing~$W$ to~$400{,}000$, 
\Astar found optimal aggregation sequences 
for only three more regions, 
but $k_\mathrm{sum}$ decreased quite a bit, 
from~$102$ to~$89$. 
The numbers of regions that needed certain
overestimation steps are shown in 
\fig\ref{fig:AreaAgg_OverStats}. 
Besides, \Astar visited more arcs and nodes, 
used more time, 
but got (slightly) less cost when increasing~$W$ to~$400{,}000$.
Although the number of regions 
that needed overestimation is relatively small, 
\Astar spent most of the running time 
on those few regions:~$4.4\%$ and~$4.0\%$ of the regions 
cause~$90.5\%$ and~$93.9\%$ of the total running time, 
respectively (see Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
	\caption{The numbers of regions where \Astar was 
		forced to use the given overestimation parameters
		in order to find a solution 
		without exploring more than 
		$W \in \{200{,}000;~400{,}000\}$ 
		nodes of the subdivision graph.}
	\label{fig:AreaAgg_OverStats}
\end{figure}

The details of some regions are presented in 
Table~\ref{tab:CostsInDetail}.
According to the entries with overestimation factor $K_i=0$, 
we often have 
ratios~$R_\mathrm{type}=1$ and~$R_\mathrm{comp}>1$.
When factor~$K_i=0$, we did not overestimate for region~$i$.
The estimated cost must be smaller or equal to the exact cost,
which results in~$R_\mathrm{type}\ge 1$ 
and~$R_\mathrm{comp}\ge 1$.
Ratio~$R_\mathrm{type} = 1$ means that our estimation for the 
cost of type change is the best.
A larger~$R_\mathrm{comp}$ means that our estimation for the 
cost of shape is poorer.

\begin{table*}[tb]
	\caption{The costs in detail of some regions, 
		where~$W=200{,}000$.  
		Parameters~$n$ and~$m$ are the numbers of patches and 
		adjacencies on the start map, respectively.
		Parameter $K$ is the overestimation factor, 
		defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
		We evaluate the quality 
		of our estimations for type change and 
		compactness by listing the numbers~
		$R_\mathrm{type}=g_\mathrm{type}(\Pgoal)
		/h_\mathrm{type}(\Pstart)$ and~
		$R_\mathrm{comp}=g_\mathrm{comp}(\Pgoal)
		/h_\mathrm{comp}(\Pstart)$. 
		Note that if~$h_\mathrm{type}(\Pstart)=0$, 
		we define~$R_\mathrm{type}=1$.
		The marked entries are discussed in the text.
	}
	\label{tab:CostsInDetail}
	\centering
	\includegraphics[page=3]{AreaAgg_CaseStudy1_Plot}
\end{table*}

According to columns~$n$ and~$K$ of \tab\ref{tab:CostsInDetail},
\Astar managed to find optimal solutions 
for all the regions with fewer than~$15$ polygons,
and only found feasible solutions 
for any region with more than~$21$ polygons.
Among the~$702$ regions that \Astar solved to optimality,
the greedy algorithm failed to 
find optimal solutions for~$295$ regions.
Solutions of the greedy algorithm cost
at most~$41.7\%$ more than solutions of \Astar;
for region~$85$, the greedy algorithm yields 
a solution of cost~$0.777$, 
while the solution of \Astar has cost~$0.548$
(see \fig\ref{fig:AreaAgg_CaseStudy1_Rg85}).
As the patches in the two sequences are the same,
the two results have the same cost of compactness.
The main difference is the choice of the first step, 
from~$8$ patches to~$7$.
When aggregating the smallest patch on the start map
with the surrounding patch,
our greedy algorithm chooses the type 
which is closer to the goal type.
In this case, the smallest patch has type~$5112$, and the 
surrounding one has~$2112$.
The type of the goal map is~$4102$.
According to \fig\ref{fig:AreaAgg_TypeDistances},
type distance~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
As a result, our greedy algorithm uses~$5112$ 
as the type for the new patch. 
This choice is a big mistake 
because the type of the largest patch on the start map
will have to be changed twice during the aggregation.
These assignments cost more than the sequence obtained by 
\Astar, where the largest patch on the start map is changed to 
the target type directly.

Among the $32$~regions that 
\Astar failed to solve optimally,
the greedy algorithm outperformed \Astar 
for~$15$ regions ($46.9\%$).
%
Among these, solutions of the greedy algorithm 
cost at most~$15.9\%$ less than solutions of \Astar;
for region~$543$, the greedy algorithm yields 
a solution of cost~$0.112$, 
while the solution of \Astar costs~$0.134$. 
For this instance, \Astar used overestimation parameter~$K=7$
(marked in \tab\ref{tab:CostsInDetail}).
\fig\ref{fig:AreaAgg_CaseStudy1_Rg543} shows 
some intermediate results obtained by
\Astar and the greedy algorithm.
Interestingly, the two methods produced the same sequence until 
there were~$8$ patches left.
Then due to the overestimation, \Astar did some bad moves
because the bad aggregation sequence still seemed better 
than other sequences.
In contrast, the greedy algorithm was looking for locally good 
aggregations.
%
Among the~$32$ regions that \Astar failed to solve optimally,  solutions of the greedy algorithm cost at most~$17.4\%$ 
more than solutions of \Astar; 
for region~$155$, the greedy algorithm yields 
a solution of cost~$0.372$, while
the solution of \Astar costs~$0.317$
(marked in \tab\ref{tab:CostsInDetail}).

Finally, an optimal aggregation sequence of region~$53$
(third-last row in \tab\ref{tab:CostsInDetail})
obtained by \Astar
is shown in \fig\ref{fig:AreaAgg_CaseStudy1_Rg53}.

\begin{figure}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_CaseStudy1}
	\caption{Aggregation sequences of region~$85$ 
		obtained by \Astar and the greedy algorithm.
		In order to save space, we did not show the results when 
		there are~$4$ or~$5$ patches, 
		which one can easily deduce.
		The numbers indicate the numbers of patches.}
	\label{fig:AreaAgg_CaseStudy1_Rg85}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[page=2]{AreaAgg_CaseStudy1}
	\caption{Some intermediate subdivisions of region~$543$ 
		obtained by \Astar and the greedy algorithm.
		In the sequence obtained by \Astar, 
		a pair of circles or a pair of squares indicates that
		the two parts are actually in the same patch.
		The numbers indicate the numbers of patches.
	}
	\label{fig:AreaAgg_CaseStudy1_Rg543}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[page=3]{AreaAgg_CaseStudy1}
	\caption{An optimal sequence of intermediate subdivisions 
		of region~$53$ obtained by \Astar 
		using costs of type change and compactness.		 
		The numbers indicate the numbers of patches.		
	}
	\label{fig:AreaAgg_CaseStudy1_Rg53}
\end{figure}

%\todo[inline]{It turned out that the objective function $g$ 
%seems rather robust
%	against changes of~$\lambda$.  For region~77, we 
%	varied~$\lambda$ in
%	the range $\{0.1,0.5,0.9\}$, but the resulting aggregation 
%	sequences
%	stayed almost the same.  When we used even larger 
%	values 
%	for~$\lambda$ (e.g.,~$0.99$), the (good) influence of type 
%	change was mitigated 
%	and, as a
%	result, we needed to overestimate (with factor~$K=8$).}

\subsection{Using costs of type change and length}
\label{sec:AreaAgg_CaseStudy2}

We compare the greedy algorithm, \Astar, and our ILP
using~$g_2(\Pnode)$,
which is a combination of the costs 
of type change and length (see \eq\ref{eq:g_2}).
For \Astar, we overestimated 
whenever we could not find a solution after 
having visited~$W=200{,}000$ nodes (see 
Sec.~\ref{sec:AreaAgg_AStar}).
The most time-consuming instance for \Astar was region~$94$,
for which \Astar took~$160.0\,$s to find a feasible solution 
with overestimation factor~$K=31$.
To avoid waiting too long,
we set the time limit as~$160\,$s 
for our ILP to solve the optimization problem on one region.
Note that the time limit does not take into account
the time that our ILP uses 
to set up the variables and constraints
(see \sects\ref{sub:AreaAgg_variables} 
and~\ref{sub:AreaAgg_Constraints}).
If no optimal solution is found in this amount of time,
a feasible solution (if found) will be returned.
For some large instances, 
the ILP cannot find any solution.

Using a similar format as in \tab\ref{tab:AreaAgg_CaseStudy1_Statistics},
we present the statistics in 
\tab\ref{tab:AreaAgg_CaseStudy2_Statistics}.
\Astar found optimal solutions for~$695$ of the~$734$ regions.
Again, it spent most of the running time 
on the few regions that needed 
overestimation:~$5.3\%$ of the regions 
cost~$89.5\%$ of the total running time.
The solutions by \Astar cost~$438.2$ in total, which is~$3.9\%$ 
less than~$455.8$, the total cost of the solutions by the greedy 
algorithm.

\begin{table*}[tb]
	%\small	
	\centering
	\caption{A comparison of the greedy algorithm and \Astar		
		when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
		The notations are the same as in
		\tab\ref{tab:AreaAgg_CaseStudy1_Statistics}.
		%
		$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
		and~$\sum g_1$
		respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
		$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
		over all the~$734$ instances 
		(see \eqs\ref{eq:g_type}, \ref{eq:g_length}, 
		and~\ref{eq:g_2}).
	}
	\label{tab:AreaAgg_CaseStudy2_Statistics}
	%	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
	\setlength{\tabcolsep}{0.7ex}
	\begin{tabular}{lCRCCCCCd{3.7}}
		\toprule
		\multicolumn{1}{l}{Methods} &
		\multicolumn{1}{c}{\#over} &
		\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
		\multicolumn{1}{c}{\#nodes} & 
		\multicolumn{1}{c}{\#arcs} & 
		\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
		\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
		\multicolumn{1}{c}{$\sum g_1$} & 
		\multicolumn{1}{c}{Time (min)} \\ 
		\midrule
		Greedy 	&     &     & 5.5\cdot 10^3 & 4.8\cdot 10^3 & 
		53.0 & 
		858.5 & 455.8 & 2'0\\
		%
		\Astar$_{\!\!200{,}000}$	&  39~(5.3\%) & 150 &  3.7 
		\cdot 
		10^6 &    7.3 \cdot 10^6 & 52.0 & 824.5 & 438.2 & 
		62'0~(89.5\%)
		%
		\\ \bottomrule			
	\end{tabular}
\end{table*}

\Astar managed to find optimal solutions 
for all the regions with fewer than~$15$ polygons, and 
found only feasible solutions for the regions 
with more than~$21$ polygons.
%
In the~$39$ (out of~$734$) regions 
that \Astar failed to solve optimally,
the greedy algorithm outperformed \Astar 
for~$25$ regions~($64.1\%$), 
which is~$17.2\%$ more comparing to the first experiment.
%
The ILP managed to find optimal solutions 
for all the regions with fewer than~$8$ polygons,
and failed to find optimal solutions
for any region with more than~$8$ polygons.
In none of the~$39$ regions that \Astar failed to solve 
optimally
did the ILP find a feasible solution.
Overall, the ILP found optimal solutions for~$442$ regions,
and found feasible solutions for~$72$ regions.
There are~$220$ regions for which 
our ILP failed to find any solution.
For~$17$ of those regions, the main memory was not enough to 
set up the variables and the constraints.
For other~$44$ of those regions, 
our ILP ran out of the main memory 
before finding any feasible solution.
Note that we allowed our program to use~$3\,$GB 
of the main memory at most.
After we increased the time limit to~$600\,$s for each region, 
the ILP solved~$491$ regions to optimality, which 
is~$49$ regions more than with the time limit of~$160\,$s.
Each of the~$49$ regions has~$6$ to~$10$ polygons.
\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal} 
shows the percentages of the regions 
that are solved optimally by the ILP with the two time limits.
\fig\ref{fig:AreaAgg_CaseStudy2_ILP} shows 
the number of regions for which 
the ILP found optimal, feasible, or no solutions 
when using the two time limits~$160\,$s and~$600\,$s.

\begin{figure}[tb]
	\centering
	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
	\caption{The percentage of regions that can be solved 
		optimally by \Astar or our ILP.
		Note that the numbers of regions according to~$n$ 
		(the number of polygons on the start map in one region) 
		are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
	\label{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
	%
	\par\vspace{\baselineskip} %Leave a gap	between figures
	%
	\centering
	\includegraphics[page=2]{AreaAgg_CaseStudy2_Plot}
	\caption{The percentage of regions for which we found at 
		least feasible solutions by \Astar or our ILP.
		Note that the numbers of regions according to~$n$ 
		(the number of polygons on the start map in one region) 
		are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
	\label{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[page=3]{AreaAgg_CaseStudy2_Plot}
	\caption{The number of regions for which
		our ILP found optimal, feasible, or no solutions 
		when using time limits $160\,$s and $600\,$s.
		Using more time, our ILP was able to 
		solve more instances to optimality.}
	\label{fig:AreaAgg_CaseStudy2_ILP}
\end{figure}

Among all the instances that were solved to optimality by \Astar
in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
and~\ref{sec:AreaAgg_CaseStudy2}),
region~$358$
(marked in \tab\ref{tab:CostsInDetail})
is the largest one.
In both experiments, the cost of type change is~$0.044$.
The optimal aggregation sequences for this region
obtained by using costs~$g_1$ and~$g_2$
are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
We, however, noticed some unpleasant aggregates.
The step from~$8$ patches to~$7$ patches 
when using cost function~$g_1$ is a bad move
(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
Instead we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
Using cost function~$g_2$, we had a similar problem. 
The subdivision with~$7$ patches is such an example,
where we expect the result of 
\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
In an earlier version of this paper \parencite{Peng2017AStar},
we tried minimizing type changes 
and maximizing the sum of the smallest compactness values, 
over the whole sequence.
For that objective, we had a similar problem as 
in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
This problem, however, can be fixed easily 
by forbidding two patches to aggregate 
if their common boundary is too short.

\begin{figure}[h!tb]
	\centering
	\includegraphics[page=1]{AreaAgg_CaseStudy2}
	\caption{Some intermediate subdivisions of region~$358$ 
		obtained by \Astar with different cost functions.
		The numbers indicate the numbers of patches.
	}
	\label{fig:AreaAgg_CaseStudy2_Rg358}
\end{figure}

%\todo{chart: memory use of greedy, A*, and ILP}

\section{Concluding Remarks}
\label{sec:AreaAgg_Conclusions}
In this paper, we investigated the problem of 
finding optimal sequences for area aggregation.
We compared three methods to solve this problem, namely, 
a greedy algorithm, \Astar, and an ILP-based algorithm.
The greedy algorithm is used as a benchmark.
Unsurprisingly, it ran faster than the other two methods by far.
According to our experiments, \Astar found area aggregation 
sequences
with the least total cost over all regions.
For some instances, however, \Astar had to overestimate
in order to find feasible solutions.
Compared to the greedy algorithm, 
\Astar reduced the total cost by~$3.9\%$.
Although the amount is small, it is worth to use \Astar
because optimization methods can help us to evaluate the quality 
of a model \parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
even an \emph{optimal} sequence can be problematic. 
This result makes us realize that our model of minimizing the 
type change and the compactness has drawbacks.
The ILP-based algorithm finds optimal solutions for some regions,
but for some of the other regions 
it cannot even find a feasible solution.
Compared to the ILP-based algorithm,
\Astar used less memory 
yet found optimal solutions for more regions.

%\todo[inline]{estimate compactness based on length; cauchy 
%schwarz}

For \Astar, we have a good estimation for the cost of type 
change, which helps a lot to reduce the search space. 
Our estimation for the cost of shape 
(compactness or length) is poor.
There are two ways to improve \Astar
in terms of solving more instances to optimality 
while using the same limit of main memory.
First, during the searching we can forget a node of the graph
if all the neighbors of this node have been visited.
By testing a case, we learned that half of the nodes can be 
forgotten during the pathfinding process.
In this way, we can release some main memory 
and visit more nodes.
Once we arrive at the goal, 
we know the cost for 
an optimal solution (the least cost).
As many visited nodes have been forgotten, 
we do not have the shortest path so far.
We need to run \Astar again.
This time we know for sure that 
a path is not optimal if its cost, 
the sum of the exact cost and the estimated cost, 
is more than the least cost 
(of the optimal solution found previously).
Consequently, we are able to prune some branches earlier 
than the first time we run \Astar.
In this way, we manage to save some main memory.
As a result, we are more likely to find optimal solutions
when the main memory is limited.
Second, if we obtain a solution based on overestimation, 
then we know the cost of this non-optimal solution.
We may decrease the overestimation factor by pruning the branches
that cost more than the non-optimal solution.

We may speed up our ILP-based algorithm using a so-called 
cutting-plane approach as \textcite{Oehrlein2017Aggregation}.
Also, we can add more constraints to
reduce the choices of variables.
For example, assignment to a given center~$r$ is symmetric, 
hence
\begin{equation*}
\label{eq:CstrZX}
z_{t,p,q,r}= z_{t,p,q,r} \qquad
\forall t \in {T} \setminus \{1,n\}, 
\forall p, q, r \in P.
\end{equation*}
Whether adding such kinds of constraints always
speeds up our ILP is not clear
because the solver, CPLEX, is a black box to us.
Although integer linear programming may be not good at 
finding optimal sequences for area aggregation,
it is relatively easy to formulate problems as ILPs.
As stated by \citet[p.~861]{Cormen2009}, 
``an efficient algorithm designed specifically for a problem 
will often be more efficient than 
linear programming both in theory and in practice. 
The real power of linear programming comes from 
the ability to solve new problems.''

We may improve both the \Astar algorithm and the ILP-based 
algorithm by integrating the greedy algorithm.
The idea is that we use the greedy algorithm to find 
a solution. 
Then we can use the cost of the solution as an upper bound to 
prune the branches of \Astar and the ILP. 
Once we see that
the cost of a branch is larger than the upper bound,
we can ignore this branch  
because it will not yield an optimal solution.

In cartography, there are many more requirements 
for area aggregation.
For example, one requirement is 
to keep important land-cover areas for a longer time
(such as a settlement surrounded by farmlands).
This requirement can be achieved by incorporating the idea of
\textcite{Dilo2009tGAP}.
They gave each type a weight, then defined the importance of a patch by the product of the area size and the type weight.
While in our method, we used only the area size as importance.
%
Another requirement is that 
aggregating two areas may result in 
an area with a generalized type,
as did in \textcite{vanSmaalen2003}. 
For example, aggregating 
farmland with hedge yields an area with type vegetation.
%
These issues can be considered in our future work.
%

\begin{acks}
We thank Thomas C. van Dijk, Joachim Spoerhase, 
and Sabine Storandt for their valuable suggestions.
We thank Martijn Meijers for 
prereviewing an earlier version of this paper.
\end{acks}

\printbibliography

\end{document}

### 2018-07-24 area_agg_seq_tsas.tex
working on including packages

@@
 \documentclass[acmlarge,review,natbib=false]{acmart}
-
-%%drt24 hacks
-%% Letter paper
-%\setlength{\paperheight}{11in}
-%\setlength{\paperwidth}{8.5in}
-
-% Hack to try to make acmart work with biblatex: https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib
-
-\let\citename\relax
-\RequirePackage[abbreviate=true, dateabbrev=true, isbn=true, doi=true, urldate=comp, url=true, maxbibnames=9, backref=false, backend=bibtex, style=ACM-Reference-Format, language=american,natbib]{biblatex}
-
-%\usepackage{textcomp}
-%\renewcommand{\textuparrow}{$\uparrow$}
-
-%\addbibresource{sample-bibliography-biblatex.bib}
-\addbibresource{Reference/BibReference.bib}
-
-\renewcommand{\bibfont}{\Small}
-
-\usepackage{booktabs} % For formal tables
 \input{area_agg_seq_tsas_setting}
-
-%% Copyright
-%%\setcopyright{none}
-%%\setcopyright{acmcopyright}
-%%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%%\setcopyright{usgov}
-%%\setcopyright{usgovmixed}
-%%\setcopyright{cagov}
-%%\setcopyright{cagovmixed}
-%
-%
-%% DOI
-%\acmDOI{10.475/123_4}
-%
-%% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-%
-%%Conference
-%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-%  Paso, Texas USA}
-%\acmYear{1997}
-%\copyrightyear{2016}
-%
-%\acmPrice{15.00}
-
-\usepackage[ruled]{algorithm2e} % For algorithms
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
-
-% Metadata Information
-\acmJournal{PACMHCI}
-\acmVolume{9}
-\acmNumber{4}
-\acmArticle{39}
-\acmYear{2010}
-\acmMonth{3}
-\acmArticleSeq{11}
-
-%\acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
-%\acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
-
-% Copyright
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-\acmDOI{0000001.0000001}
-
-% Paper history
-\received{February 2007}
-\received{March 2009}
-\received[accepted]{June 2009}
 
@@
 \email{www.geoinfo.uni-bonn.de/haunert}
-
-%% The default list of authors is too long for headers}
-%\renewcommand{\shortauthors}{B. Trovato et al.}
 
@@
 	<concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+	<concept_id>10010405.10010476.10010479</concept_id>
+	<concept_desc>Applied computing~Cartography</concept_desc>
 	<concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
 	</concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\ccsdesc[500]{Applied computing~Cartography}
+
 \keywords{Continuous map generalization, Land cover, 
@@
 %\end{flalign}
-%\begin{flalign}
-%\label{eq:CstrSIndeedSmallest}
-%&\eqquad
-%\embrd[S]{A_{t,o}} -
-%\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
+\begin{flalign}
+\label{eq:CstrSIndeedSmallest}
+&\eqquad
+\embrd[S]{A_{t,o}} -
+\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
+\forall t 	 \in {T}\setminus \{n\}, 
+\forall o, r \in P \text{~with}~o\ne r. &
+\end{flalign}
+%\begin{equation}
+%A_{t,o} - M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \inquad
 %\forall t 	 \in {T}\setminus \{n\}, 
-%\forall o, r \in P \text{~with}~o\ne r. &
-%\end{flalign}
-\begin{equation}
-A_{t,o} - M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \inquad
-\forall t 	 \in {T}\setminus \{n\}, 
-\forall o, r \in P \text{~with}~o\ne r.
-\end{equation}
+%\forall o, r \in P \text{~with}~o\ne r.
+%\end{equation}
 This constraint takes effect only when~$w_{t,o}=1$ 

### 2018-07-27 area_agg_seq_tsas.tex
submitted version to TSAS

@@
-\documentclass[acmlarge,review,natbib=false]{acmart}
+\documentclass[acmsmall,natbib=false]{acmart}
 \input{area_agg_seq_tsas_setting}
@@
 automatic methods for map generalization are needed.
-Given two maps of the same region at two different scales,
-a relevant problem is to compute maps for any intermediate scale.
 We approach this problem for land-cover maps.
-Given two land-cover maps at different scales, 
+%Given two maps of the same region at two different scales,
+%a relevant problem is to compute maps for any intermediate scale.
+Given two land-cover maps at two different scales, 
 we want to find a sequence of small incremental
@@
 finding a shortest path in a (very large) graph.
-For solving such a problem optimally, standard approaches
+%We compared the \Astar algorithm and 
+%integer linear programming in solving this problem.
+For solving such a problem, standard approaches
 are the \Astar algorithm or integer linear programming.
-We compare how the two methods solve our problem.
+%We compare how the two methods solve our problem.
 To avoid long computing times, we allow the two methods to 
@@
 Our main result is that
-\Astar finds optimal solutions for more instances 
+\Astar finds optimal aggregation sequences for more instances 
 than the other two methods
@@
 \keywords{Continuous map generalization, Land cover, 
-	 Type chang, Compactness, Graph, Optimization, Exponential}
+	 Type change, Compactness, Shortest path
+%	 , Optimization, Exponential
+	 }
 
@@
 \includegraphics{AreaAgg_example}
-	\caption{The input and a possible output for an instance of 
-		our problem}
+\caption{The input and a possible output 
+	for an instance of 	our problem}
 \label{fig:AreaAgg_example}
@@
 after having found a sequence for each of them
-we ``interleaf'' these aggregation sequences
+we ``interleave'' these aggregation sequences
 with respect to the order of the smallest patches 
@@
 	to subdivision~${P}_{t+1,j}$ 
-		if ${P}_{t+1,j}$ is the result of 
+	if~${P}_{t+1,j}$ is the result of 
 	aggregating a smallest area~$p$ of~\Pnode with a 
@@
 as little as possible.
-This requirement means that we prefer, for example, aggregating 
-an area with type \emph{swamp} into an area with type \emph{wet 
-	ground} rather than into an area with type \emph{city}.
+This requirement means that we prefer, for example, 
+aggregating an area with type \emph{swamp} 
+into an area with type \emph{wet ground} 
+rather than into an area with type \emph{city}.
 %
@@
 to be identified by human being 
-if it is more compact.
+if it is more compact (less clutter).
 %
@@
 \includegraphics[page=1]{AreaAgg_CostFunctions}
-	\caption{Aggregating land-cover areas according to different 
-		preferences.
+\caption{Aggregating land-cover areas 
+	according to different preferences.
 	Aggregating a small land-cover area into one 
@@
 	is aggregated into patch~$v$.
-		Figures~(c) and~(d) respectively show the number of 
+	\figs(c) and~(d) respectively show the number of 
 	edges and the lengths of the interior polylines after 
@@
 if the type distances fulfill that
-$d(T(u), T_\mathrm{goal}) \ge d(T(v), T_\mathrm{goal})$;
+$d\left(T(u), T_\mathrm{goal}\right) 
+\ge d\left(T(v), T_\mathrm{goal}\right)$;
 otherwise, we aggregate~$v$ into~$u$.
@@
 This idea is the same as that of \textcite{vanOosterom2005},
-except we have a different definition for the compatible.
-In accordance 
-with our two combinatorial costs in 
+except that we have a different definition 
+for the compatibility.
+In accordance with our two combinatorial costs in 
 \sect\ref{sec:AreaAgg_Combining},
 we define two cost functions.
-Suppose that we are at the step of 
-aggregating from subdivision $P_{s,i}$ to subdivision 
-$P_{s+1,j}$.
+Suppose that we are at the step of aggregating 
+from subdivision~$P_{s,i}$ to subdivision~$P_{s+1,j}$.
 The first cost function is 
@@
 
-%\mypar[inline]{Motivate \Astar by comparison with Dijkstra.}
-
 We try to find a shortest path,
 from the start map to the goal map,
-using \Astar \citep{Hart1968}.  
-As the graph~$G$---our search space---can be of exponential size 
+using \Astar \parencite{Hart1968,PatelAStar}.  
+As the graph~$G$---our search space---can 
+be of exponential size 
 (see \sect\ref{sec:AreaAgg_Preliminaries}), 
@@
 
-More formally, we define $g(\Pnode)$ to be 
+More formally, we define~$g(\Pnode)$ to be 
 the exact cost of a shortest path from~\Pstart to~\Pnode, 
-and we define $h(\Pnode)$ to be the estimated cost 
+and we define~$h(\Pnode)$ to be the estimated cost 
 to get from \Pnode to~\Pgoal. 
@@
 There can be as few as $n-s$ interior boundaries.
-In order to find a lower bound of the cost of length,
+In order to find a lower bound for the cost of length,
 we keep only the necessary number, $n-s$, 
@@
 because they occur regularly in optimizations
-\parencite[section~9.2]{bradley1977applied}.
+\parencite[\sect9.2]{bradley1977applied}.
 Also, an ILP with general (bounded) integer variables 
 can always be translated to an ILP with binary variables
-\parencite[section~2.3]{Williams2009Integer}.
+\parencite[\sect2.3]{Williams2009Integer}.
 To find optimal sequences for area aggregation, 
@@
 \includegraphics[page=1]{AreaAgg_ILP}
-	\caption{Some examples of variables~$x$,~$y$, and~$z$ for our ILP. 
-		The arrows in the figures show the aggregation steps and
-		the dotted lines represent the removed boundaries by the aggregation steps.
+\caption{Some examples of the five sets of variables 
+	for our ILP, $x$, $y$, $z$, $c$, and~$w$.
+	The arrows in the drawings 
+	show the aggregation steps and
+	the dotted lines represent 
+	the removed boundaries by the aggregation steps.
+	There are some blank spaces because there is no corresponding variable at the specific times.
 }
@@
 \begin{flalign*}
-&\myquad[4]
+&\myquad[6]
 \embrd[V]{x_{t,p,r}} \in
@@
 \begin{flalign*}
-&\myquad[4]
+&\myquad[6]
 \embrd[V]{y_{t,p,o,r}} \in
@@
 \begin{flalign*}
-&\myquad[4]
+&\myquad[6]
 \embrd[V]{z_{t,p,q,r}} \in
@@
 \begin{flalign*}
-&\myquad[4]
+&\myquad[6]
 \embrd[V]{c_{t,p,o,r}} \in
@@
 and~$p$ has a neighbor assigned to center~$r$
-(see for example \fig\ref{fig:AreaAgg_Variables_Neighbor}).
+(see for example \figs\ref{fig:AreaAgg_Variables}
+and~\ref{fig:AreaAgg_Variables_Neighbor}).
 We do not need a variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
@@
 \begin{flalign*}
-&\myquad[4]
+&\myquad[6]
 \embrd[V]{w_{t,o}} \in
@@
 with $w_{t,o}=1$ meaning 
-that patch~$o$ is a smallest patch at time~$t$.
+that patch~$o$ is a smallest patch at time~$t$
+(see for example \fig\ref{fig:AreaAgg_Variables}).
 
@@
 and assigned to center~$r$ at time $t$
-($x_{t,p,r}=1$), then $y_{t,p,o,r}=1$.  This is expressed by
+($x_{t,p,r}=1$), then $y_{t,p,o,r}=1$. 
+This is expressed by
 \begin{flalign}
@@
 Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
-or~$p$ is not assigned to~$r$ at time $t$ ($x_{t,p,o}=0$),
+or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
 then $y_{t,p,o,r}=0$.
@@
 we introduced the binary variables~$z_{t,p,q,r}$.
-Recall that the intended meaning of $z_{t,p,q,r}=1$ is that, at
+Recall that the intended meaning of~$z_{t,p,q,r}=1$ is that, at
 time~$t$, polygons~$p$ and~$q$ are both in patch~$r$.
@@
 We have implemented our methods 
-based on C\# (Microsoft Visual Studio~$2015$) 
-and ArcObjects SDK 10.4.1.
+based on C\# (Microsoft Visual Studio~2017) 
+and ArcObjects SDK~10.6.0.
 We used the IBM ILOG
-CPLEX Optimization Studio~$12.6.3.0$ to solve our ILP.
+CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
 Our prototype is open access on 
@@
 	\url{https://github.com/IGNF/ContinuousGeneralisation},
-	Accessed: 2018-Jun-18.}.
+	Accessed: Jun 18, 2018.}.
 Our computer ran
-Windows~$7$ on a~$3.3\,$GHz dual core CPU with~$8\,$GB RAM.
+Windows~10 on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$16\,$GB RAM.
 We measured processing time 
 by the built-in C\# class \emph{Stopwatch}.
-As required by ArcObjects SDK~$10.4.1$,
-we specified our program to run on the $32$-bit platform. 
+As required by ArcObjects SDK~10.6.0,
+we specified our program to run on the~$32$-bit platform. 
 We added a post-build task about ``largeaddressaware''
 in Microsoft Visual Studio so that 
-we were able to use up to $3\,$GB of main memory\footnote{
+we were able to use up to~$3\,$GB of main memory\footnote{
 	The details of the setting can be found at 	
 	\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
-	Accessed: 2017-Nov-01.}.
+	Accessed: Nov 1, 2017.}.
 Our CPLEX version may declare an optimal solution
@@
 	\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
-	Accessed: 2017-Nov-12.}.
+	Accessed: Nov 12, 2017.}.
 
 We tested our method on a data set 
-from the German topographic database ATKIS DLM~$50$. 
+from the German topographic database ATKIS DLM~50. 
 The data set represents the place 
@@
 Our start map is the result of collapsing areas 
-by \citet[pp.~61--66]{haunert2008f}.
+by \citet[\chap~6]{haunert2008f}.
 The start map has~$5{,}537$ polygons. 
@@
 	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
-	Accessed: 2017-Nov-01.}
+	Accessed: Nov 1, 2017.}
 (see \fig\ref{fig:AreaAgg_TypeDistances}). 
@@
 \caption{Distribution of region sizes:
-		the $y$-axis shows how many regions of a given size range are contained in our data set.}
+	the $y$-axis shows how many regions 
+	of a given size range are contained in our data set.}
 \label{fig:AreaAgg_NumRegion}
@@
 the greedy algorithm visited 
-fewer nodes and arcs in the graph $G$ 
+fewer nodes and arcs in the graph~$G$ 
 and used much less time.
 However, 
-\Astar managed to find solutions with lower total cost,
-$117.3$ (or~$117.2$), 
+\Astar managed to find solutions with 
+lower total cost,~$117.3$ (or~$117.2$), 
 which is~$2.8\%$ less than 
@@
 %
-When~$W=200{,}000$,
-we are sure that 
+When~$W=200{,}000$, we are sure that 
 we have found optimal solutions 
-for~$702$ of the~$734$ regions ($94.3\%$),
-while the greedy algorithm solved only~$407$ of the~$702$ regions to optimality.
-For the other~$32$ regions, we have found feasible solutions
-by both algorithms
+for~$702$ of the~$734$ regions ($95.6\%$),
+while the greedy algorithm solved 
+only~$407$ ($55.4\%$) to optimality.
+For the other~$32$ regions, 
+both algorithms have found feasible solutions 
 (see column \#over in 
@@
 	Symbol~\#over is the number and percentage of regions
-		(out of $N=734$) that needed overestimation.
+	(out of~$N=734$) that needed overestimation.
 	%
@@
 	Symbols~\#nodes and~\#arcs are the total 
-		numbers of nodes and arcs that \Astar visited.  
-		(For instances where we needed overestimation, 
-		only the final attempt was counted.)
+	numbers of nodes and arcs that \Astar visited  
+	(for instances where we needed overestimation, 
+	only the final attempt was counted).
 	%
@@
 	Greedy 	&     &     & 5.5\cdot 10^3 & 4.8\cdot 10^3 
-		& 53.2 & 188.2 & 120.7 & 2'0\\
+	& 53.2 & 188.2 & 120.7 & 1'1\\
 	%
@@
 	&    5.7\cdot 10^6	
-		& 51.4 & 183.2 & 117.3 & 75'8~(90.5\%)\\
+	& 51.4 & 183.2 & 117.3 & 55'5~(93.1\%)\\
 	%
@@
 	&    9.8\cdot 10^6
-		& 51.4 & 183.1 & 117.2 & 137'7~(93.9\%) 
+	& 51.4 & 183.1 & 117.2 & 102'6~(95.5\%) 
 	\\ \bottomrule			
@@
 on those few regions:~$4.4\%$ and~$4.0\%$ of the regions 
-cause~$90.5\%$ and~$93.9\%$ of the total running time, 
-respectively (see Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
+caused~$93.1\%$ and~$95.5\%$ of the total running time, 
+respectively 
+(see Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
 
@@
 	obtained by \Astar and the greedy algorithm.
-		In order to save space, we did not show the results when 
-		there are~$4$ or~$5$ patches, 
+	In order to save space, we did not show the results 
+	when there are~$4$ or~$5$ patches, 
 	which one can easily deduce.
@@
 
-We compare the greedy algorithm, \Astar, and our ILP
+We compare our greedy algorithm, \Astar, and ILP
 using~$g_2(\Pnode)$,
-which is a combination of the costs 
+a combination of the costs 
 of type change and length (see \eq\ref{eq:g_2}).
@@
 The most time-consuming instance for \Astar was region~$94$,
-for which \Astar took~$160.0\,$s to find a feasible solution 
+for which \Astar took~$111.5\,$s (including repetitions)
+to find a feasible solution 
 with overestimation factor~$K=31$.
 To avoid waiting too long,
-we set the time limit as~$160\,$s 
-for our ILP to solve the optimization problem on one region.
-Note that the time limit does not take into account
+we set the time limit as~$112\,$s 
+for our ILP to run on one region.
+Note that the time limit includes
 the time that our ILP uses 
@@
 and~\ref{sub:AreaAgg_Constraints}).
-If no optimal solution is found in this amount of time,
+If no optimal solution is found in this time limit,
 a feasible solution (if found) will be returned.
@@
 \tab\ref{tab:AreaAgg_CaseStudy2_Statistics}.
-\Astar found optimal solutions for~$695$ of the~$734$ regions.
+\Astar found optimal solutions 
+for~$695$ of the~$734$ regions ($94.7\%$).
 Again, it spent most of the running time 
@@
 overestimation:~$5.3\%$ of the regions 
-cost~$89.5\%$ of the total running time.
-The solutions by \Astar cost~$438.2$ in total, which is~$3.9\%$ 
-less than~$455.8$, the total cost of the solutions by the greedy 
-algorithm.
+caused~$92.1\%$ of the total running time.
+The solutions by \Astar cost~$438.2$ in total, 
+which is~$3.9\%$ less than~$455.8$, 
+the total cost of the solutions by the greedy algorithm.
 
@@
 	\midrule
-		Greedy 	&     &     & 5.5\cdot 10^3 & 4.8\cdot 10^3 & 
-		53.0 & 
-		858.5 & 455.8 & 2'0\\
-		%
-		\Astar$_{\!\!200{,}000}$	&  39~(5.3\%) & 150 &  3.7 
-		\cdot 
-		10^6 &    7.3 \cdot 10^6 & 52.0 & 824.5 & 438.2 & 
-		62'0~(89.5\%)
-		%
-		\\ \bottomrule			
+	Greedy 						&     			&    	& 5.5\cdot 10^3 & 4.8\cdot 10^3 & 53.0 	& 858.5 & 455.8 & 1'3			\\
+	%
+	\Astar$_{\!\!200{,}000}$	& 39~(5.3\%)	& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 & 52.0 	& 824.5 & 438.2 & 47'2~(92.1\%)	\\
+	%
+	ILP							&  			 	&		&				&				&		&		&		& 456'8			\\ \bottomrule
 \end{tabular}
@@
 and failed to find optimal solutions
-for any region with more than~$8$ polygons.
-In none of the~$39$ regions that \Astar failed to solve 
-optimally
+for any region with more than~$9$ polygons.
+In none of the~$39$ regions 
+that \Astar failed to solve optimally
 did the ILP find a feasible solution.
-Overall, the ILP found optimal solutions for~$442$ regions,
-and found feasible solutions for~$72$ regions.
-There are~$220$ regions for which 
+Overall, the ILP found optimal solutions for~$455$ regions
+and found feasible solutions for~$70$ regions.
+The distributions of these regions are shown in
+\figs\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
+and~\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
+There are~$208$ regions for which 
 our ILP failed to find any solution.
-For~$17$ of those regions, the main memory was not enough to 
-set up the variables and the constraints.
-For other~$44$ of those regions, 
+For~$23$ of those regions, 
+we did not have enough main memory 
+to set up the variables and constraints;
+each of these regions has~$20$ polygons at least.
+For~$64$ of those regions, 
 our ILP ran out of the main memory 
-before finding any feasible solution.
+before finding any feasible solution;
+these regions have~$14$ to~$20$ polygons.
 Note that we allowed our program to use~$3\,$GB 
 of the main memory at most.
-After we increased the time limit to~$600\,$s for each region, 
-the ILP solved~$491$ regions to optimality, which 
-is~$49$ regions more than with the time limit of~$160\,$s.
-Each of the~$49$ regions has~$6$ to~$10$ polygons.
+For~$118$ of the $208$~regions, 
+our ILP failed to find any solution
+during the time limit ($112\,$s);
+these regions have~$9$ to~$14$ polygons.
+For the remaining~$3$ regions, 
+the reason of our ILP's failing is unclear 
+due to the fact that 
+the solver CPLEX is like a black box for us.
+After we increased the time limit to~$300\,$s for each region, 
+the ILP solved~$496$ regions to optimality, which 
+is~$41$ regions more than using the time limit~$112\,$s.
+Every of the~$41$ regions has~$6$ to~$10$ polygons.
 \fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
 shows the percentages of the regions 
-that are solved optimally by the ILP with the two time limits.
+that are solved optimally by the three algorithms.
+\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible} 
+shows the percentages of the regions 
+that the three algorithms found feasible solutions.
 \fig\ref{fig:AreaAgg_CaseStudy2_ILP} shows 
@@
 the ILP found optimal, feasible, or no solutions 
-when using the two time limits~$160\,$s and~$600\,$s.
+when using the two time limits, i.e., $112\,$s and~$300\,$s.
 
@@
 \includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
-	\caption{The percentage of regions that can be solved 
-		optimally by \Astar or our ILP.
+\caption{The percentage of regions that are solved 
+	optimally by the greedy algorithm, \Astar, and our ILP.
 	Note that the numbers of regions according to~$n$ 
@@
 \caption{The percentage of regions for which we found at 
-		least feasible solutions by \Astar or our ILP.
+	least feasible solutions by the three algorithms.
 	Note that the numbers of regions according to~$n$ 
@@
 	our ILP found optimal, feasible, or no solutions 
-		when using time limits $160\,$s and $600\,$s.
+	when using time limits~$112\,$s and~$300\,$s.
 	Using more time, our ILP was able to 
@@
 an area with a generalized type,
-as did in \textcite{vanSmaalen2003}. 
+as did by \textcite{vanSmaalen2003}. 
 For example, aggregating 

### 2019-02-17 area_agg_seq_tsas.tex
test

@@
 \title{Finding Optimal Sequences for Area Aggregation  
-	--\protect\\ 
+	---\protect\\ 
 	\Astar vs. Integer Linear Programming}
@@
 To avoid long computing times, we allow the two methods to 
-return nonoptimal results.
+return non-optimal results.
 In addition, we present a greedy algorithm 
@@
 and a smaller-scale map, we first need to compute 
-corresponding points between them (e.g., \citealp{Cecconi2003,Noellenburg2008,Chazal2010BallMap,Deng2015,Li2017_Building,Li2017Annealing}).
+corresponding points between them 
+\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
+Deng2015,Li2017_Building,Li2017Annealing}.
 Then morphing can be realized by interpolating a set of 
@@
 \textcite{Noellenburg2008} presented a method for computing an optimum
-correspondence between two given polylines according to some cost function.
+correspondence between two given polylines 
+according to some cost function.
 While straight-line trajectories 
 are often used for interpolation
-(e.g., \citealp{Cecconi2003,Deng2015}),
-\textcite{Whited2011BallMorph} considered four other alternatives, i.e., \emph{hat}, \emph{tangent}, 
-\emph{circular}, and \emph{parabolic} paths
+\parencite[e.g.,][]{Cecconi2003,Deng2015},
+\textcite{Whited2011BallMorph} considered four other alternatives, 
+i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
+and \emph{parabolic} paths
 based on so-called \emph{ball-map}
@@
 but also because it helps us to evaluate the quality of a model
-\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
+\parencite{Haunert2017Label,
+Haunert2008Assuring,Haunert2016Optimization}.
 Recall that we wish to minimize the changes of types
@@
 many optimization problems cannot be solved efficiently
-(e.g., \citealp{HaunertWolff2010AreaAgg,Haunert2016Partition}).
+\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
 While heuristics can find some solutions in reasonable time,
@@
 on small instances.
+
+\begin{figure}[tb]
+\centering
+\includegraphics{AreaAgg_example}
+\caption{The input and a possible output 
+	for an instance of 	our problem}
+\label{fig:AreaAgg_example}
+\end{figure}
 
@@
 and avoiding any intersection. 
-At the same time, every city, which is represented by a point, stays in the same face as before.
+At the same time, every city, which is represented by a point, 
+stays in the same face as before.
 
 %\todo{may cite \textcite{Bader2001Dissertation}}
-
-\begin{figure}[tb]
-\centering
-\includegraphics{AreaAgg_example}
-\caption{The input and a possible output 
-	for an instance of 	our problem}
-\label{fig:AreaAgg_example}
-\end{figure}
 
@@
 start map and the areas of the goal map.
-This assumption is based on the fact that many algorithms (e.g., \citealp{HaunertWolff2010AreaAgg,vanSmaalen2003,Oehrlein2017Aggregation})
+This assumption is based on the fact that many algorithms 
+\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
+vanSmaalen2003,Oehrlein2017Aggregation}
 that aggregate land-cover areas
@@
 our cost function takes two aspects into account: 
-one is based on semantics and 
-the other is based on shape.
+one based on semantics and 
+the other based on shape.
 %
@@
 we consider a subdivision~\Pnode as more compact than
-another subdivision~$P_{t,i'}$ if the total length of the interior boundaries of~\Pnode is less than that of~$P_{t,i'}$.
+another subdivision~$P_{t,i'}$ 
+if the total length of the interior boundaries of~\Pnode 
+is less than that of~$P_{t,i'}$.
 We add this alternative because we want to make a comparison 
@@
 when compactness is considered in an ILP
-(e.g., \citealp{Minas2016,Wright1983}).
+\parencite[e.g.,][]{Minas2016,Wright1983}.
 \textcite{HaunertWolff2010AreaAgg} employed 
@@
 we aggregate the two patches that are the least compact.
-Moreover, we assume that the shared boundary of the two patches  has the least number of edges.
+Moreover, we assume that the shared boundary of the two patches  
+has the least number of edges.
 We use $\mathcal{N}_\mathrm{ext}$ to 
@@
 of the values in set~$C(P_{s+1,j})$.
-Finally, we compute the estimated cost of compactness for subdivision~$P_{s+1,j}$ by \eq\ref{eq:f_comp}.
+Finally, we compute the estimated cost of compactness 
+for subdivision~$P_{s+1,j}$ by \eq\ref{eq:f_comp}.
 
@@
 We have~$3.5\,$kg of coffee powder and~$10\,$kg of water.
-We mix the powder and the water to provide coffee with 
-two kinds of intensity in terms of mass:~$40\%$ and~$20\%$.
+We mix the powder and the water to provide two kinds coffee 
+with different intensities in terms of mass:~$40\%$ and~$20\%$.
 The profits of the two kinds of coffee 
-are respectively~$5\,$\euro and~$4\,$\euro.
-We want to maximize the total profit of selling coffee.
+are respectively~$5\,$\euro~and~$4\,$\euro.
+Our aim is to maximize the total profit of selling coffee.
 If we offer respectively~$x\,$kg and~$y\,$kg 
@@
 and at the same time make sure that 
-the it still intersects with the gray area.
+it still intersects with the gray area.
 Note that if the dashed line 
@@
 \textcite{Karmarkar1984LP}
-proved that an LP can be solved in a polynomial time.
+proved that an LP can be solved in polynomial time.
 
 Now we change our problem a bit.
-We assume that we want to sell coffee in bottles,
-where each bottle contains exactly~$1\,$kg of coffee 
-with intensity either~$40\%$ or~$20\%$.
-Our question becomes how many bottles of each kind of coffee
+We wish to sell coffee in jugs,
+where each jug contains exactly~$1\,$kg of coffee 
+with intensity~$40\%$ or~$20\%$.
+Our question becomes how many jugs of each kind of coffee
 we should sell in order to maximize the profit.
 If we sell the two kinds of coffee 
-respectively~$x'$ and~$y'$ bottles,
+respectively~$x'$ and~$y'$ jugs,
 then our problem becomes:
@@
 \end{alignat*}
-For this problem, only the pairs of~$(x,y)$ 
+For this problem, only the pairs of~$(x',y')$ 
 represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
 are feasible solutions
-(point~$A$ is no longer an optimal solution in this case).
+(point~$A$ is no longer a solution in this case).
 In order to maximize our profit,
@@
 \parencite{Haunert2017Label}.
-Also, by using these solvers we profit 
+Also, by using these solvers we benefit 
 from every improvement, by their producers,
@@
 \includegraphics[page=4]{AreaAgg_ILP}
-\caption{Example of linear programming (a)
+\caption{Examples of linear programming (a)
 	and integer linear programming (b). 
@@
 	the removed boundaries by the aggregation steps.
-	There are some blank spaces because there is no corresponding variable at the specific times.
+	There are some blank spaces because 
+	there is no corresponding variable at the specific times.
 }
@@
 In order to formulate our aggregation problem as an ILP, 
-we restrict the variables introduced in \sect\ref{sub:AreaAgg_variables} 
+we restrict the variables introduced in 
+\sect\ref{sub:AreaAgg_variables} 
 by setting up constraints.
@@
 \embrd[S]{w_{t,o}} \le 
-\embld[T]{\displaystyle\sum_{r\in P \setminus \{o\}} \left(y_{t+1,o,o,r} +y_{t+1,r,r,o}\right)} \inquad
+\embld[T]{\displaystyle\sum_{r\in P \setminus \{o\}} 
+\left(y_{t+1,o,o,r} +y_{t+1,r,r,o}\right)} \inquad
 \forall t \in {T}\setminus \{n\}, 
@@
 	Accessed: Jun 18, 2018.}.
-Our computer ran
-Windows~10 on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$16\,$GB RAM.
+We ran our case study
+under 64-bit Windows~10 
+on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores;
+the computer has $16\,$GB RAM.
 We measured processing time 
@@
 %
-%	\par\vspace{\intextsep} %Leave a gap between the two figures
+%It doesn't work to directly use 
+%\vspace{\baselineskip} for subfigures.
 \par\vspace{\baselineskip} %Leave a gap	figures
@@
 (see \sect\ref{sec:AreaAgg_AStar}).
-We tried $W=200{,}000$ and $W=400{,}000$
+We tried~$W=200{,}000$ and~$W=400{,}000$
 (if we could use more main memory, 
@@
 we cannot verify only from the cost values.
+
 \begin{table*}[tb]
@@
 	%
-	Symbol~\#over is the number and percentage of regions
-	(out of~$N=734$) that needed overestimation.
+	Symbol~\#OS represents the number of regions 
+    that we obtained optimal solutions.   
+	%
+	Symbol~\#FS represents 
+    the number and the percentage of regions (out of~$N=734$) 
+    that we obtained feasible (non-optimal) solutions.
 	%
@@
 	runtime spent on solving the instances
-	that needed overestimation.
+	that we obtained feasible solutions.
+    For \Astar, the time needed for overestimation
+    is included.
 }
@@
 \setlength{\tabcolsep}{0.7ex}
-\begin{tabular}{lCRCCCCCd{3.7}}
+\begin{tabular}{lRRRCCCCCd{3.7}}
 \toprule
 \multicolumn{1}{l}{Methods} &
-	\multicolumn{1}{c}{\#over} &
+\multicolumn{1}{l}{\#OS} &
+\multicolumn{1}{c}{\#FS} &
 \multicolumn{1}{r}{$k_\mathrm{sum}$} &  
@@
 \midrule
-	Greedy 	&     &     & 5.5\cdot 10^3 & 4.8\cdot 10^3 
-	& 53.2 & 188.2 & 120.7 & 1'1\\
-	%
-	\Astar$_{\!\!200{,}000}$	&  32~(4.4\%) & 102 &  3.6\cdot 
-	10^6 
-	&    5.7\cdot 10^6	
+Greedy 	& 408 
+&326~(44.4\%) 
+&             &5.5\cdot 10^3   &4.8\cdot 10^3   
+&53.2         &188.2           &120.7           &1'2~(44.6\%)\\
+%
+%
+\Astar$_{\!\!200{,}000}$	& 702 
+&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
+& 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
 & 51.4 & 183.2 & 117.3 & 55'5~(93.1\%)\\
 %
-	\Astar$_{\!\!400{,}000}$	&  29~(4.0\%) &   89 &  6.5\cdot 
-	10^6 
-	&    9.8\cdot 10^6
+%
+\Astar$_{\!\!400{,}000}$	& 705 
+&  29~(\parbox{\widthof{$4$}}{$\,$}$4.0\%$)
+&  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
 & 51.4 & 183.1 & 117.2 & 102'6~(95.5\%) 
@@
 \midrule
-	Greedy 						&     			&    	& 5.5\cdot 10^3 & 4.8\cdot 10^3 & 53.0 	& 858.5 & 455.8 & 1'3			\\
-	%
-	\Astar$_{\!\!200{,}000}$	& 39~(5.3\%)	& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 & 52.0 	& 824.5 & 438.2 & 47'2~(92.1\%)	\\
-	%
-	ILP							&  			 	&		&				&				&		&		&		& 456'8			\\ \bottomrule
+Greedy 		 &430             
+&304~(41.4\%)    
+&            &5.5\cdot 10^3   &4.8\cdot 10^3   
+&53.0        &858.5           &455.8           &1'2~(41.5\%)\\
+%
+%
+\Astar$_{\!\!200{,}000}$	& 695
+& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
+& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
+& 52.0 	& 824.5 & 438.2 & 53'6~(91.8\%)	\\
+%
+%
+ILP$_{112\,\mathrm{s}}$		& 453
+& 66~(\parbox{\widthof{$4$}}{$\,$}$9.0\%$)  			 	
+&		&				&				
+&		&		&		& 470'4~(26.2\%)\\
+%
+%
+ILP$_{300\,\mathrm{s}}$		& 496
+& 51~(\parbox{\widthof{$4$}}{$\,$}$6.9\%$)  			 	
+&		&				&				
+&		&		&		& 795'4			\\ 
+\bottomrule
 \end{tabular}
@@
 \textcite{Dilo2009tGAP}.
-They gave each type a weight, then defined the importance of a patch by the product of the area size and the type weight.
+They gave each type a weight, 
+then defined the importance of a patch 
+by the product of the area size and the type weight.
 While in our method, we used only the area size as importance.

### 2019-02-27 area_agg_seq_tsas.tex
moved materials from my thesis to this paper

@@
 We approach this problem for land-cover maps.
-%Given two maps of the same region at two different scales,
-%a relevant problem is to compute maps for any intermediate scale.
 Given two land-cover maps at two different scales, 
 we want to find a sequence of small incremental
-% To help map users not to lose context during zooming,
-% we try to provide maps that change as continuous as possible.
-% Since maps at some different scales often exist, 
-% a relevant problem is to find maps at any intermediate scales.
-% Given two land-cover maps of different scales, 
-% we wish to find a sequence of small incremental
 changes that gradually transforms one map into the other.
@@
 Every polygon on the smaller-scale map
-is the union of a set of polygons on the larger-scale map.
+is the union of a set of adjacent polygons 
+on the larger-scale map.
 
@@
 finding a shortest path in a (very large) graph.
-%We compared the \Astar algorithm and 
-%integer linear programming in solving this problem.
-For solving such a problem, standard approaches
-are the \Astar algorithm or integer linear programming.
-%We compare how the two methods solve our problem.
+We present the \Astar algorithm and integer linear programming
+to solve this optimization problem.
 To avoid long computing times, we allow the two methods to 
 return non-optimal results.
-In addition, we present a greedy algorithm 
-as a benchmark.
+In addition, we present a greedy algorithm as a benchmark.
 We tested the three methods with a
-data set of the official German topographic database ATKIS.
+dataset of the official German topographic database ATKIS.
 Our main result is that
@@
 users need to have access to maps at different scales.
-In our digital age, people realize this access by zooming on 
-computers or mobile phones.
+In order to generate these maps,
+national mapping agencies produce a base map
+and then derive maps at smaller scales by 
+\emph{map generalization}
+More specifically, 
+map generalization is the process of extracting and arranging
+geographical information from detailed data in order to produce maps
+at smaller scales.
+A requirement of map generalization is to emphasize the 
+essential while suppress the unimportant,
+and at the same time maintain logical relationship between 
+objects \parencite{Weibel1997}.
+As manual generalization is labor-intensive
+\parencite{Duchene2014},
+automating map generalization is a promising way 
+to produce up-to-date maps at high speed and low cost 
+\parencite{Mackaness2017Generalization}.
+
+In our digital age, people interactively read maps 
+on computers and mobile phones.
+An often used interaction is zooming. 
 When users zoom in or out, 
@@
 appropriate to the corresponding zoom level.
-A naive solution is 
-to switch between maps at different scales.
-This method, however, can result in 
-large discrete changes, 
-which tend to distract users.
-A more advanced strategy is  
-\emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
-which emphasizes on generalizing in real time.
+However, large discrete changes may distract users.
+The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
+which generalizes features in real time, can mitigate this problem.
 Still, large discrete changes can be introduced.
-To have a better zooming experience, 
-users prefer the changes to be continuous.
-This is why some digital maps such as Google Maps 
-are trying to make zooming as continuous as they can,
-though Google Maps is still based on switching between 
-a certain number of maps at different scales.
+By a usability test, \textcite{Midtbo2007} have shown that 
+a map is easier to follow 
+if the map extent transits smoothly than stepwise. 
+In addition to smoothly transiting map extent, 
+we want to change also map features smoothly 
+when users are zooming.
+we believe that this strategy will allow users 
+to follow maps even more easily.
 The process of producing maps at any different scales
 with smooth changes 
-is called \emph{continuous map generalization} (CMG).
+is known as \emph{continuous map generalization} (CMG), 
+or simply \emph{continuous generalization}.
 Ideally, there should be no discrete change in CMG.
@@
 which are represented as a set of areas.
-Their method repeatedly finds the least-important area, 
+Their method repeatedly finds the least-important area 
 and then either merges it with an adjacent area 
@@
 % Among the methods of computing corresponding points,
-\textcite{Noellenburg2008} presented a method for computing an optimum
+\textcite{Noellenburg2008} computed an optimum
 correspondence between two given polylines 
@@
 For example, when users zoom out, 
-some land cover areas become too small to be seen.
-These areas have to be aggregated.
+some land-cover areas become too small to be seen.
+These areas need to be aggregated.
 When we aggregate one area into another, 
 the type of the former is changed to the type of the latter. 
-In this problem a hard constraint could be that 
+In this problem, a hard constraint could be that 
 we aggregate only two polygons at each step 
@@
 where we stick to hard constraints and 
-try to fulfill soft ones as good as possible.
+try to fulfill soft ones as well as possible.
 Optimization for map generalization is important 
@@
 A model could be to minimize 
-the \emph{smallest} change over all the steps.
+the \emph{greatest} change over all the steps.
 Using optimization, we are able to find optimal solutions
@@
 If even the optimal solutions are bad,
-then we can say that the model is not reasonable.
-In this case, we should try another model, say, 
-to minimize the \emph{average} change over all the steps.
+then the model may be not reasonable.
+In this case, we should improve the model; 
+we may want to minimize 
+the \emph{average} change over all the steps.
 Moreover, optimization is useful for evaluating heuristics.
@@
 to mediate between these constraints, 
-which is done by LSA.
+which can be done by LSA.
 \textcite{Sester2005Optimization} used LSA not only for 
-displacing objects, but also for simplifying buildings. 
-The output boundaries are required to 
-be as close as possible to the original buildings.
+displacing objects but also for simplifying buildings. 
+She required that 
+the output boundaries should be 
+as close to the original buildings as possible.
 \textcite{Tong2015AreaLSA} generalized land-cover areas,
@@
 if it is smooth and close to the original line.
-He repeatedly displace the line 
-until finding a stable state 
-in terms of minimizing his energy function.
+He repeatedly displaced the line 
+until a stable state 
+in terms of minimizing his energy function is found.
 \textcite{HaunertWolff2010AreaAgg} aggregated land-cover areas
-based on mixed-integer linear programming.
-This method is based on global optimization and minimizes 
-type changes as well as a cost for non-compact shapes 
+based on mixed-integer linear programming
+to generate a map at a target scale.
+Their method is based on a global optimization.
+They minimize a combination of type changes and cost for non-compact shapes 
 while satisfying constraints on the sizes of the output regions.
@@
 footprints by solving an integer linear program (ILP).
-They aimed at minimizing the number of edges in the output under 
-the restriction that the simplified buildings must be 
-topologically safe,
+They aimed at minimizing the number of edges in the output 
+under the restriction that 
+the simplified buildings must be topologically safe,
 that is, the selected and extended edges must not intersect with 
@@
 \textcite{Oehrlein2017Aggregation} aggregated the departments 
-of France according to the unemployment rates based on integer 
+of France according to unemployment rates based on integer 
 linear programming; they used a cutting-plane method to 
@@
 and avoiding any intersection. 
-At the same time, every city, which is represented by a point, 
-stays in the same face as before.
-
-%\todo{may cite \textcite{Bader2001Dissertation}}
+At the same time, they required that every city, 
+represented by a point, 
+stays in the same face as before the generalization.
 
@@
 In this field, we have requirements 
-not only for a specific map, 
-but also for relations between maps. 
-%
-Nevertheless, some optimization techniques 
-have been applied to CMG.
+not only for a specific map
+but also for relations between maps at difference scales. 
+%
+Some optimization techniques have been applied to CMG.
 In the aforementioned article,
@@
 to select points of interest.
-They required that 
-a point, once disappeared, should not show up again 
-during zooming out, 
-and that any two points should be 
+They required that a point, once disappeared, 
+should not show up again during zooming out. 
+They also required that any two points should be 
 sufficiently far away from each other.
@@
 they wanted to show as many points as possible 
-for the given scale interval.
+for a given scale interval.
 \textcite{Chimani2014Eat} computed a deletion sequence
@@
 and their objective was to maximize the total weight 
-over all the road networks, at each step.
+over all the road networks of all the steps.
 \textcite{Peng2013LSA} defined trajectories 
@@
 When users zoom out, some land-cover areas become
-tiny polygons, which result in visual clutter.
+too tiny to be seen, which result in visual clutter.
 In order to provide users 
 with good visual experience during zooming operations,
-we want to remove these tiny polygons.
-\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
-proposed to split these tiny parcels 
-and then to merge the split parts into the neighboring polygons.
-\textcite{Meijers2016Split} developed an algorithm 
-to split a polygon (the splittee) 
-based on constrained Delaunay triangulation.
-During splitting, their algorithm is capable of
-taking into account
-the attractivenesses between the splittee and its neighbors.
-When merging, a more attractive neighbor 
-will get a larger portion from the splittee.
-However, our method does not consider splitting.
-We focus on aggregating areas.
-A \emph{land-cover map} is a planar subdivision in which each 
-area belongs to a
-land-cover class or \emph{type}.
-Suppose that there are two land-cover maps of 
-different scales 
+we propose to remove these tiny areas.
+We plan to achieve this goal by 
+aggregating them into neighboring land-cover areas.
+A \emph{land-cover map} is a planar subdivision in which 
+each area belongs to a land-cover class or \emph{type}.
+Suppose that there are two land-cover maps of different scales 
 that cover the same spatial region.
 We consider the problem of finding a sequence 
-of small incremental changes 
-that gradually transforms 
+of small incremental changes that gradually transforms 
 the larger-scale map (the \emph{start map}) to 
@@
 
-With the same motivation, a strategy of hierarchical schemes 
-has been proposed.
+With the same motivation, 
+a strategy of hierarchical schemes has been proposed.
 This strategy generalizes a more-detailed representation 
@@
 based on small incremental changes, 
-e.g., the Generalized Area Partitioning tree 
-(GAP-tree),
-which can be constructed if only the larger-scale map is given
+e.g., the Generalized Area Partitioning tree (GAP-tree).
+This tree can be constructed if only the larger-scale map is given
 \citep{vanOosterom1995Development} 
@@
 Typically, the next change in such a sequence 
-is determined locally, 
-in a greedy fashion.  
-If we insist on finding a sequence that is, 
-according to some global measure, optimal, 
+is determined locally, in a greedy fashion.  
+If we insist on finding a sequence that is optimal 
+according to some global measure,
 the problem becomes complicated.
@@
 result in many-to-one relationships.
-The input and the generalized results of these methods 
-can be used as our input.
+Their inputs and generalized results together
+can be used as our inputs.
 We term the areas of the goal map \emph{regions}.
@@
 with an automatic method for area aggregation, 
-for example, with the method of \citet{HaunertWolff2010AreaAgg}.
-That method produces a land-cover map at a single output scale, 
+for example, by the method of \citet{HaunertWolff2010AreaAgg}.
+That method produces a land-cover map at a single smaller scale, 
 given a land-cover map at a larger scale.
-Although the method of \textcite{HaunertWolff2010AreaAgg}
-leads to results of high quality, 
-it does not yield land-cover maps at intermediate scales.
-
-To generate a good sequence of maps, 
-we must consider the sequence of maps as a whole 
-instead of considering each intermediate-scale map independently.
-To simplify the problem,
-we first consider each region of the goal map 
-(with its components on the start map) 
-independently of the other regions.
+Although \textcite{HaunertWolff2010AreaAgg}
+attain results of high quality, 
+they do not produce land-cover maps at intermediate scales.
+
+In this chapter, we try to find an optimal sequence
+to aggregate the land-cover areas on the start map
+one by one until we arrive the goal map.
+We first independently deal with each region of the goal map 
+(with its components on the start map).
 Once we have found an aggregation sequence for each region, 
-we integrate all the sequences into an overall sequence 
-that transforms the start map into the goal map. 
+we integrate all the sequences into an overall sequence,
+which transforms the start map into the goal map. 
 Our aggregation sequence may be cooperated with
@@
 
-%\todo{may cite \textcite{Suba2014Merge}}
-
 \mypar{Contribution}
@@
 and analyze the size of our model in a worst-case scenario
-(see \sect\ref{sec:AreaAgg_Preliminaries}).
+(\sect\ref{sec:AreaAgg_Preliminaries}).
 We define our cost functions in 
@@
 Third, we model our pathfinding problem as
-an integer linear program, 
-and then solve this program, minimizing our cost function.
-Our linear program uses binary (0--1) variables. 
+an \emph{integer linear program} (ILP), 
+and then we solve this program with minimizing our cost function.
+Our ILP uses binary (0--1) variables. 
 These variables help us to model our problem, 
-but in general, it is NP-hard to solve an ILP optimally.
+but in general, it is NP-hard 
+to solve an ILP optimally.
 By comparing with the greedy algorithm, 
@@
 Our case study 
-uses a data set of the German topographic database ATKIS 
-(see \sect\ref{sec:AreaAgg_CaseStudy}).
+uses a dataset of the German topographic database ATKIS 
+(\sect\ref{sec:AreaAgg_CaseStudy}).
 In the conclusions, we show possible ways to improve our 
@@
 
-We do not deal with the simplification of lines in this paper, 
-since this can be handled separately from the
+We do not deal with simplifying polylines in this chapter.
+The simplification can be handled separately from the
 aggregation of areas, for example, 
 by using one method of 
-\textcite{Douglas1973,Saalfeld1999,Wu2004DP}.
+\textcite{Douglas1973},
+\textcite{Saalfeld1999},
+or \textcite{Wu2004DP}.
 Those methods can be used to set up 
-the binary line generalized (BLG) tree
-\citep{vanOosterom1995Development},
+the binary line generalisation tree (BLG-tree) of
+\textcite{vanOosterom1995Development},
 which is a hierarchical data structure that 
 defines a gradual line simplification process.
+%
+Although splitting polygons is a good step
+of generalizing land-cover areas,
+we do not integrate it into our method at this moment.
+Some examples of splitting are as follows.
+\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
+proposed to split tiny polygons 
+and then to merge the split parts into the neighboring polygons.
+\textcite{Meijers2016Split} developed an algorithm 
+to split a polygon (the splittee) 
+based on a constrained Delaunay triangulation.
+During splitting, their algorithm is capable of
+taking into account
+the attractivenesses between the splittee and its neighbors.
+When merging, a more attractive neighbor 
+will get a larger portion from the splittee.
 
@@
 
-We show how to compute an aggregation sequence for one region. 
+We show how to compute an aggregation sequence 
+for a single region, $R$. 
 For a goal map with many regions,
-after having found a sequence for each of them
-we ``interleave'' these aggregation sequences
+we ``interleave'' the sequences for each of them
 with respect to the order of the smallest patches 
@@
 This integration is similar to the merge step in the 
-merge sort algorithm; 
+Mergesort algorithm; 
 see \textcite[pp.~29--37]{Cormen2009}.
@@
 \centering
-\includegraphics[page=1]{AreaAgg_Preliminaries}
+\includegraphics[page=2]{AreaAgg_Preliminaries}
 \caption{Integrating two aggregation sequences 
@@
 This requirement ensures that the 
-size of the smallest area in the map increases in each step
-and thus the sequence reflects a gradual reduction of the 
+size of the smallest area on the map increases in each step.
+Hence, the sequence reflects a gradual reduction of the 
 map's scale.
 From another perspective, 
-for simplicity we consider 
-the smallest area as the least important, 
+we consider the smallest area as the least important, 
 rather than involving more rules for (non-)importance. 
-Even though the requirement reduces the number of possible 
-solutions,
+Even though the requirement reduces 
+the number of possible solutions,
 there is still enough room for optimization 
@@
 with a single aggregation operation,
-involving the smallest area.
+involving a smallest area.
 Then, any directed path in~$G$ from the start map to the goal map
 defines a possible aggregation sequence.
-Our idea is to compute an optimal aggregation sequence through 
+Our idea is to obtain an optimal aggregation sequence through 
 computing a minimum-weight path from the start to the goal.
@@
 Moreover, putting the idea to practice is far from trivial 
-since the graph $G$ can be huge as we will argue below.
+since graph~$G$ can be huge as we will argue later.
 We compare a greedy algorithm, \Astar, and an ILP-based algorithm
 in finding such paths.
-Note that we only know subdivisions 
-$\Pstart$ and $\Pgoal$ at the beginning.
+Note that we only know 
+subdivisions~$\Pstart$ and~$\Pgoal$ at the beginning.
 We generate a subdivision (node) only when we want to visit it.
@@
 \centering
-\includegraphics[page=2]{AreaAgg_Preliminaries}
+\includegraphics[page=3]{AreaAgg_Preliminaries}
 \caption{The subdivision graph~$G$. 
@@
 	if~${P}_{t+1,j}$ is the result of 
-	aggregating a smallest area~$p$ of~\Pnode with a 
-	neighbor of~$p$.}
+	an aggregating step from~\Pnode.}
 \label{fig:AreaAgg_SubdivisionName}
@@
 A \emph{patch} is a set of polygons whose union is connected. 
-The patch also has the property type.
-We use~$u$ or~$v$ to denote patches.
+Each patch also has a unique land-cover area type.
+We use~$u$ or~$v$ to denote the patches.
 
@@
 from the start map to the goal map. 
-We use~$t \in {T}=\{1,2,\dots,n\}$ to denote \emph{time}. 
+We use~$t \in T =\{1,2,\dots,n\}$ to denote \emph{time}. 
 When~$t=1$, the subdivision consists of~$n$ patches, 
@@
 where layer~${L}_t=\{{P}_{t,1},\dots,{P}_{t,n_t}\}$
-contains every possible subdivision~\Pnode\ with~$n-t+1$ patches (see \fig\ref{fig:AreaAgg_ExponentialSize}).
+contains every possible subdivision~\Pnode\ with~$n-t+1$ patches 
+(see \fig\ref{fig:AreaAgg_ExponentialSize}).
 
@@
 \centering
-\includegraphics[page=3]{AreaAgg_Preliminaries}
+\includegraphics[page=4]{AreaAgg_Preliminaries}
 \caption{An example to show that the size of our problem 
@@
 \mypar{Exponential lower bound}
-We now analyze the size of the subdivision graph~$G$.
-Consider an instance that consists of 
-a start map with $n=2k+1$ rectangles in a row and
-a goal map that is simply the union of the $n$ rectangles
-(see \fig\ref{fig:AreaAgg_ExponentialSize}).
+We now analyze the size of subdivision graph~$G$.
+Our analysis is inspired by \textcite{Keane1975Size},
+where we also use a row of~$n$~areas.
+In our instance
+(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
+the start map consists of~$n=2k+1$ rectangles,
+and the goal map is simply the union of the~$n$ rectangles.
 At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
@@
 For this, the number of choices is~$
-{{2k}\choose{k}}
+\binom{2k}{k}
 = \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
@@
 \ge 2^k = 2^{(n-1)/2}$.
-As a result, the size of our model
+That is to say, the size of our model
 has an exponential lower bound.
@@
 ways to aggregate from the start map to the goal map.
-Apparently, some of the ways are more reasonable than 
-others.
+Apparently, some of the ways are more reasonable than others.
 In our example, we consider 
-the sequence~$(P_{1,1}, P_{2,1},P_{3,1},P_{4,1})$ 
+sequence~$(P_{1,1}, P_{2,1},P_{3,1},P_{4,1})$ 
 more reasonable than 
-the sequence~$(P_{1,1}, P_{2,4},P_{3,5},P_{4,1})$.
-The reason is that the dark area should not expand so much
-as the target color is gray.
-We want to provide users with a most reasonable sequence as we 
-believe that an unreasonable sequence irritates users.
-To find a most reasonable sequence, we introduce cost functions 
-in our problem of finding shortest paths.
+sequence~$(P_{1,1}, P_{2,4},P_{3,5},P_{4,1})$.
+This is because that the dark area should not expand so much
+when the target color is light gray.
+We want to provide users with a most reasonable sequence 
+because we believe that an unreasonable sequence irritates users.
+To find a most reasonable sequence, we introduce cost functions.
 In the cost functions, we charge a higher penalty 
@@
 
-It is difficult to define exactly what reasonable means 
+It is difficult to define what \emph{reasonable} exactly means 
 because users may have different preferences.
-Four preferences are discussed by
+Four preferences have been discussed by
 \textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
-They are aggregating a small land-cover area into one 
+A small land-cover area can be aggregated into another area 
 that isolates the area 
@@
 Our argument is that an area is easier 
-to be identified by human being 
+to be identified by a human being 
 if it is more compact (less clutter).
@@
 We also consider the total \emph{length} 
-of the interior boundaries as an alternative compactness:
-we consider a subdivision~\Pnode as more compact than
-another subdivision~$P_{t,i'}$ 
+of the interior boundaries as an alternative compactness;
+we consider subdivision~\Pnode 
+as more compact than subdivision~$P_{t,i'}$ 
 if the total length of the interior boundaries of~\Pnode 
@@
 are \emph{not} linear;
-see, for example, \textcite{Maceachren1985,Li2013Compactness}.
+for example, see \textcite{Maceachren1985,Li2013Compactness}.
 Although the length of interior boundaries 
@@
 to describe compactness \parencite{Young1988},
-it is often used as a reasonable replacement
+it is often used as a fair alternative
 when compactness is considered in an ILP
@@
 from the centroids to a \emph{reference point}.
-The reference point is the centroid
+The reference point is one of the centroids
 that minimizes the sum.
-The sum of the distances can also be computed linearly.
+The sum of the distances can be computed linearly.
 We use the length of interior boundaries 
-instead of the distance because the former 
+instead of the distance of centroids because the former 
 is more relevant to the shapes of the patches.
@@
 \centering
-\includegraphics[page=1]{AreaAgg_CostFunctions}
+\includegraphics[page=1]{AreaAgg_CostsAndEstimations}
 \caption{Aggregating land-cover areas 
 	according to different preferences.
-	Aggregating a small land-cover area into one 
+	Aggregating a small land-cover area into another one 
 	that isolates the area (b), 
@@
 
-We define the cost of type change as follows.
 Suppose that we are at the step of aggregating 
@@
 where~$A_u$ is the area of patch~$u$, 
-and~$A_R$ is the area of region~$R$.
+and~$A_R$ is the area of region~$R$
+(see \sect\ref{sec:AreaAgg_Preliminaries}).
 We use~$A_R$ and~$T_{\max}$ 
@@
 (see \sect\ref{sec:AreaAgg_CaseStudy}); 
-see \textcite[chapter 2]{Choudhary1992Elements}
-for the definition of a metric.
+\textcite[\chap2]{Choudhary1992Elements}
+shows the definition of a metric.
 A metric distance is symmetric, 
-which is different from the unsymmetric one used in
+which is different from the non-symmetric one used in
 \textcite{Dilo2009tGAP}.
@@
 the distance from type \emph{building} to type \emph{road} is~$0.5$,
-but the distance is~$0$ the other way around.
+but the distance from \emph{road} to \emph{building} is~$0$.
 
@@
 P_{\tstar,i_{\tstar}})$,
-we define the cost of type change over the steps so far by
+we define the cost of type change over the steps by
 \begin{equation}
@@
 g_\mathrm{type}(\Pistar)=
-\sum_{s=1}^{t-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}})
+\sum_{s=1}^{t-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}}).
 \end{equation}
@@
 \centering
-\includegraphics[page=2]{AreaAgg_CostFunctions}
+\includegraphics[page=2]{AreaAgg_CostsAndEstimations}
 \caption{An aggregation step, 
@@
 We use the compactness definition of \citet{Frolov1975}, 
-i.e., the compactness value for patch~$u$ is
+i.e., the compactness value for a patch, say,~$u$ is
 \begin{equation*}
@@
 we define and minimize a cost related to compactness.
-Recalling that at time~$s$ there are~$n-s+1$ patches,
+Recalling that there are~$n-s+1$ patches at time~$s$,
 we define the cost of compactness for subdivision~\Psnode as
@@
 (that is, neglecting~$P_{1,1}$ 
-and the last subdivison in the path) by
+and the last subdivision in the path) by
 \begin{equation}
@@
 We want to find a path~$\Pi$ from~$\Pstart$ to~$\Pnode$ 
-that minimizes, among all such paths,~$g(\Pistar)$.
+that minimizes, among all such paths,~$g_1(\Pistar)$.
 Slightly abusing notation, we denote the cost of
-this optimal path from~${P}_{\mathrm{start}}$ to~\Pnode 
+an optimal path from~${P}_{\mathrm{start}}$ to~\Pnode 
 by~$g_1(\Pnode)$.
@@
 Therefore, we also introduce a combination
-that can be computed linearly, as
+that can be computed linearly. That is,
 \begin{equation}
@@
 \label{sec:AreaAgg_Greedy}
+
 At any time~$t$,
@@
 with one of its neighbors.
-Suppose that patch~$u$ is the smallest patch,
-and patch~$v$ is one of~$u$'s neighbors.
-We aggregate~$u$ into~$v$ 
+We pick the neighbor in a greedy way.
+We suppose that the smallest patch,~$u$, has~$k_u$ neighbors,
+then there are~$2k_u$ ways to aggregate
+(when we aggregate a patch into another patch,
+the union uses the type of the latter).
+In order to guarantee that our final result
+(e.g., the polygon of layer~$L_4$ in 
+\fig\ref{fig:AreaAgg_SubdivisionName})
+will have the type of~$T_\mathrm{goal}$,
+we add one more rule to our greedy algorithm.
+Suppose that patch~$v$ is one of~$u$'s neighbors.
+The greedy algorithm aggregates~$u$ into~$v$ 
 if the type distances fulfill that
@@
 \ge d\left(T(v), T_\mathrm{goal}\right)$;
-otherwise, we aggregate~$v$ into~$u$.
-Recall that when we aggregate a patch into another patch,
-the union takes the type of the latter.
-We compute the costs of aggregating the smallest patch 
-with each of the neighbors, 
-and select the aggregation that costs least.
-In other words, the smallest patch is aggregated with 
+otherwise, the algorithm aggregates~$v$ into~$u$.
+This rule excludes, say,~$k_e$ aggregation choices,
+and we have~$2k_u - k_e$ choices left.
+Then we compute the costs for each of 
+the~$2k_u - k_e$ aggregation choices
+and select the aggregation that has the least cost.
+In other words, we aggregate the smallest patch with 
 its most \emph{compatible} neighbor.
-This idea is the same as that of \textcite{vanOosterom2005},
-except that we have a different definition 
-for the compatibility.
+
 In accordance with our two combinatorial costs in 
@@
 (1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
-+\lambda f_{\mathrm{comp}}(P_{s+1,j}). \nonumber
++\lambda f_{\mathrm{comp}}(P_{s+1,j}).
 \end{equation}
@@
 (1-\lambda)f_\mathrm{type}(P_{s,i},P_{s+1,j})
-+\lambda f_{\mathrm{lgth}}(P_{s+1,j}). \nonumber
++\lambda f_{\mathrm{lgth}}(P_{s+1,j}).
 \end{equation}
-
-\section{Using the \Astar Algorithm}
+We take one of the~$2k_u - k_e$ aggregation choices 
+according to \eqs\ref{eq:f_1} or~\ref{eq:f_2}
+in our two experiments.
+The cost of a whole sequence can be computed by
+\eqs\ref{eq:g_1} or~\ref{eq:g_2}.
+
+\section{Using the \texorpdfstring{\Astar Algorithm}{A* Algorithm}}
 \label{sec:AreaAgg_AStar}
 
-We try to find a shortest path,
-from the start map to the goal map,
-using \Astar \parencite{Hart1968,PatelAStar}.  
-As the graph~$G$---our search space---can 
-be of exponential size 
-(see \sect\ref{sec:AreaAgg_Preliminaries}), 
-we avoid computing the whole graph explicitly.
+\sect\ref{sec:AreaAgg_Preliminaries} has shown that
+the size of finding an optimal aggregation sequence 
+can be exponential.
+That is to say, the graph~$G$---our search space---can 
+be of exponential size.
+In order to avoid computing the whole graph explicitly,
+we use the \Astar algorithm \parencite{Hart1968,PatelAStar}.
 To save time and memory, 
-we generate a subdivision \Pnode only 
+we generate a subdivision, \Pnode, only 
 when we are going to visit it.
@@
 to find a shortest path 
-from subdivisions~$\Pstart$ to~$\Pgoal$.  
-For subdivision \Pnode,
+from subdivision~$\Pstart$ to subdivision~$\Pgoal$.  
+For \Pnode,
 \Astar considers the exact cost of a shortest path 
@@
 and estimates the cost to get from~\Pnode to~\Pgoal. 
+\Astar explores the nodes earlier 
+if they are estimated to be closer to the goal.
 \Astar can be seen as a refinement of Dijkstra's algorithm
-where nodes are explored earlier 
-if they are estimated to be closer to the goal.
-
-More formally, we define~$g(\Pnode)$ to be 
-the exact cost of a shortest path from~\Pstart to~\Pnode, 
-and we define~$h(\Pnode)$ to be the estimated cost 
+\parencite{Dijkstra1959}.
+
+We define~$g(\Pnode)$ to be 
+the exact cost of a shortest path from~\Pstart to~\Pnode 
+and define~$h(\Pnode)$ to be the estimated cost 
 to get from \Pnode to~\Pgoal. 
-Then the (estimated) total cost at node~\Pnode is
+Then, the (estimated) total cost at node~\Pnode is
 \begin{equation}
@@
 We use either~$g_1$ (\eq\ref{eq:g_1}) 
-or~$g_2$ (\eq\ref{eq:g_2})
-for~$g(\Pnode)$.
+or~$g_2$ (\eq\ref{eq:g_2}) for~$g(\Pnode)$;
+accordingly, we use either~$h_1$ (\eq\ref{eq:h_1}) 
+or~$h_2$ (\eq\ref{eq:h_2}) for~$h(\Pnode)$.
 If~$h(\Pnode)$ is always bounded from above 
 by the exact cost of a shortest path from~\Pnode to~\Pgoal, 
-\Astar is guaranteed to find a shortest path from~\Pstart 
+\Astar guarantees to find a shortest path from~\Pstart 
 to~\Pgoal, 
 that is, an optimal aggregation sequence.  
-Using the estimation~$F$ (\eq\ref{eq:CostTotal}), 
+Using estimate~$F$ (\eq\ref{eq:CostTotal}), 
 \Astar is able to reduce the search space.
 The better the estimation part~$h$, 
-the more \Astar can reduce the search space.
-In the following, we show how we compute
-estimated cost $h(\Pnode)$.
+the more search space \Astar can reduce.
+In the following, we show how to compute
+estimated cost~$h(\Pnode)$.
 
@@
 Since the number of subdivisions can be exponential, 
-it can happen that we run out of main memory 
+we may run out of the main memory 
 before we find an optimal solution. 
-To handle this problem, we overestimate the cost. 
-Overestimation is a popular technique while using \Astar,
-in order to find a feasible solution. 
+To handle this problem, we introduce overestimations 
+to find a feasible solution. 
+Overestimations are popular 
+when people cannot find optimal solutions using \Astar. 
 For example, \textcite{Pohl1973} overestimated 
@@
 If we fail to find one after 
-we have visited a predefined number~$W$ of nodes of graph~$G$,
+we have visited a predefined number, 
+say,~$W$ of nodes of graph~$G$,
 then we restart.
@@
 until we find a feasible solution.
-We define~$K$ by
-\[
+Because we do not want to retry too many times,
+we define~$K$ by
+\begin{equation}
+\label{eq:OverestimateK}
 K= 2^k -1,
-\]
+\end{equation}
 where~$k\ge 0$ is the number of retryings.
-As~$K\le n-1$, it holds that~$k \le \log_2 n +1$, 
-which means  that we will 
+When~$k = 0$, we have~$K=0$,
+which means that the first attempt of finding a solution
+does not use overestimation.
+As~$K\le n-1$, it holds that~$k \le \log_2 n$, 
+which means that we need to 
 retry~$\lceil \log_2 n\rceil$ times at most.
-When we are at time $t$, there are at most $n-t$ steps 
+Whenever overestimating ($k\geq1$), 
+\Astar cannot guarantee optimality anymore.
+When we are at time~$t$, there are at most~$n-t$ steps 
 to arrive at the goal map.
 We define the number of practical overestimation steps as
-\[
+\begin{equation}
+\label{eq:OverestimateKPrime}
 K'= \min \{K, n-t\}.
-\]
-Whenever overestimating ($k\geq1$), 
-\Astar cannot guarantee optimality anymore.
+\end{equation}
 
@@
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i_t}, P_{t+1,i_{\tstar+1}} \dots,P_{n,i_n}=\Pgoal)$,
+$(\Pnode=P_{t,i'_t}, P_{t+1,i'_{\tstar+1}} \dots,P_{n,i'_n}=\Pgoal)$,
 be the path that always changes the type of a smallest patch 
@@
 h_\mathrm{type}(\Pnode)=
-\sum_{s=t}^{n-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}}).
+\sum_{s=t}^{n-1}f_\mathrm{type}(P_{s,i'_s},P_{s+1,i'_{s+1}}).
 \end{equation}
@@
 $h_\mathrm{type}$ 
-according to the aggregation sequence of 
+according to the ``aggregation sequence'' of 
 \fig\ref{fig:AreaAgg_h_type}.
-Note that the step from $P_{2,i_2}$ to 
-$P_{3,i_3}$ 
-in 
-\fig\ref{fig:AreaAgg_h_type} is impossible in reality 
+Note that the step from
+subdivision~$P_{2,i'_2}$ to subdivision~$P_{3,i'_3}$ 
+in \fig\ref{fig:AreaAgg_h_type} is impossible in reality 
 because the dark patch cannot be aggregated into patch~$v$
@@
 the exact cost of a shortest path.
-In order to overestimate, we multiply the estimated cost of the 
-first $K'$ steps by $K$.
-\fo\ref{eq:h_type} is revised to
+When we need to overestimate, we multiply the estimated cost of the 
+first~$K'$ steps (see \eq\ref{eq:OverestimateKPrime}) 
+by~$K$ (see \eq\ref{eq:OverestimateK}).
+As a result, \fo\ref{eq:h_type} is revised to
 \begin{equation}
@@
 h_\mathrm{type}(\Pnode)=
-K\sum_{s=t}^{t+K'-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}})+
-\sum_{s=t+K'}^{n-1}f_\mathrm{type}(P_{s,i_s},P_{s+1,i_{s+1}}).
-\nonumber
+K\sum_{s=t}^{t+K'-1}f_\mathrm{type}(P_{s,i'_s},P_{s+1,i'_{s+1}})+
+\sum_{s=t+K'}^{n-1}f_\mathrm{type}(P_{s,i'_s},P_{s+1,i'_{s+1}}).
 \end{equation}
@@
 \centering
-\includegraphics[page=1]{AreaAgg_Estimation}
+\includegraphics[page=3]{AreaAgg_CostsAndEstimations}
 \caption{An ``aggregation sequence'' for computing
-	$h_{\mathrm{type}}$, 
+    the estimated cost of type change~$h_{\mathrm{type}}$
+    (see \eqs\ref{eq:h_type} and~\ref{eq:o_type}),
 	based on the aggregation result of 
-	\fig\ref{fig:AreaAgg_FirstStep}b}
+	\fig\ref{fig:AreaAgg_FirstStep}b.
+    Note that this aggregation sequence is impossible in reality,
+    but it is fine for estimating
+    (see the argument in \sect\ref{sec:AreaAgg_h_type}).}
 \label{fig:AreaAgg_h_type}
@@
 
-Our way to estimate the cost of compactness 
-is based on regular polygons.
+We estimate the cost of compactness based on regular polygons.
 The more edges a regular polygon has, the more compact it is.
-We assume that at each step 
+We assume that, at each step, 
 we aggregate the two patches that are the least compact.
@@
 Note that the boundary between two patches 
-is not necessarily connected 
-(see for example the dark boundary with three edges 
-in \fig\ref{fig:AreaAgg_h_comp}a).
-We denote by~$B(\Psnode)$ 
-the set of interior boundaries at time~$s$,
-and denote by~$b_\mathrm{min}(\Psnode)$ 
+is not necessarily connected; 
+for example, see the dark boundary with three edges 
+in \fig\ref{fig:AreaAgg_h_comp}a.
+For subdivision \Pnode,
+we denote by~$B(\Pnode)$ the set of interior boundaries 
+and denote by~$b_\mathrm{min}(\Pnode)$ 
 the boundary with the smallest number of edges.
 For our estimation, the set of interior boundaries 
-at time~$s+1$ 
-is~$B(P_{s+1,j})= B(\Psnode)-{\{b_\mathrm{min}(\Psnode)\}}$. 
-The estimated number of all the edges for 
-such a subdivision~$P_{s+1,j}$ is
+at time~$t+1$ 
+is~$B(P_{t+1,i''_{t+1}})= B(\Pnode)-{\{b_\mathrm{min}(\Pnode)\}}$. 
+The estimated number of the edges for 
+such a subdivision,~$P_{t+1,i''_{t+1}}$, is
 \begin{equation}
 \label{eq:LeftEdgeNum}
-\mathcal{N}_{s+1,j}=
-\mathcal{N}_\mathrm{ext} + \sum_{b \in B(P_{s+1,j})} \|b\|.
+\mathcal{N}_{t+1,i''_{t+1}}=
+\mathcal{N}_\mathrm{ext} + \sum_{b \in B(P_{t+1,i''_{t+1}})} \|b\|,
 \end{equation}
-where $\|b\|$ is the number of edges of boundary~$b$.
+where notation~$\|b\|$ represents the number of boundary~$b$'s edges.
 
@@
 \centering
-\includegraphics[page=2]{AreaAgg_Estimation}
-\captionof{figure}{An "aggregation" sequence for 
-	computing 
-	$h_\mathrm{comp}$ (see 
-	\eq\ref{eq:o_comp}) based on the 
-	number of edges. 
-	At each step we remove the boundary with the fewest 
-	edges. 		
+\includegraphics[page=4]{AreaAgg_CostsAndEstimations}
+\captionof{figure}{An "aggregation sequence" for 
+	computing the estimated cost of compactness~$h_\mathrm{comp}$ 
+    (see \eqs\ref{eq:h_comp} and~\ref{eq:o_comp}), 
+    based on the number of edges. 
+	At each step we remove the boundary with the fewest edges. 		
 	The numbers represent the 
 	numbers of the interior boundaries' edges.
+    Note that this aggregation sequence is impossible in reality,
+    but it is fine for estimating
+    (see the argument in \sect\ref{sec:AreaAgg_h_type}).    
 	This example corresponds to the aggregation step in 
-	\fig\ref{fig:AreaAgg_FirstStep}.
+	\fig\ref{fig:AreaAgg_FirstStep}b.
 }
@@
 
-From subdivision~\Psnode to subdivision~$P_{s+1,j}$,
-we get a new patch because of aggregation.
+From subdivision~\Pnode to subdivision~$P_{t+1,i''_{t+1}}$,
+we get a new patch because of the aggregation.
 The new patch is certainly less compact than a regular polygon 
-with~$\mathcal{N}_{s+1,j}$ edges.
+with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges.
 In order to estimate the compactness of the new patch, 
@@
 the new patch has the shape of a regular polygon 
-with~$\mathcal{N}_{s+1,j}$ edges 
+with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges 
 (see \eq\ref{eq:LeftEdgeNum}).
@@
 with increasing~$\mathcal{N}$.
-A patch with~$\mathcal{N}_{s+1,j}$ edges has
-compactness~$c_\mathrm{reg} (\mathcal{N}_{s+1,j})$.
+A patch with~$\mathcal{N}_{t+1,i''_{t+1}}$ edges has
+compactness~$c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})$.
 According to our previous assumption, 
-at each step we are able to aggregate the two patches 
+at each step we are always able to aggregate the two patches 
 that are the least compact in the subdivision.
 We denote the compactness values of the two patches
-by~$c_\mathrm{min}(\Psnode)$ and~$c'_\mathrm{min}(\Psnode)$.
-Recall that we use~$C(\Psnode)$ to denote 
+by~$c_\mathrm{min1}(\Pnode)$ and~$c_\mathrm{min2}(\Pnode)$.
+Recall that we use~$C(\Pnode)$ to denote 
 the set of compactness values of the patches
-in subdivision~$\Psnode$ 
+in subdivision~$\Pnode$ 
 (see \sect\ref{sec:AreaAgg_f_comp}).
 Then the set of compactness values 
-for subdivision~$P_{s+1,j}$ is 
+for subdivision~$P_{t+1,i''_{t+1}}$ is 
 \begin{equation}
 \label{eq:compsetnew}
-C(P_{s+1,j})=
+C(P_{t+1,i''_{t+1}})=
 C(\Psnode)\cup 
-\{c_\mathrm{reg} (\mathcal{N}_{s+1,j})\}
-\setminus \{c_\mathrm{min}(\Psnode), c'_\mathrm{min}(\Psnode)\}.
+\{c_\mathrm{reg} (\mathcal{N}_{t+1,i''_{t+1}})\}
+\setminus \{c_\mathrm{min1}(\Pnode), c_\mathrm{min2}(\Pnode)\}.
 \nonumber
@@
 by calculating the average 
-of the values in set~$C(P_{s+1,j})$.
+of the values in set~$C(P_{t+1,i''_{t+1}})$.
 Finally, we compute the estimated cost of compactness 
-for subdivision~$P_{s+1,j}$ by \eq\ref{eq:f_comp}.
+for subdivision~$P_{t+1,i''_{t+1}}$ by \eq\ref{eq:f_comp}.
 
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i'_t}, P_{t+1,i'_{\tstar+1}}, 
-\dots,P_{n,i'_n}=\Pgoal)$
+$(\Pnode=P_{t,i''_t}, P_{t+1,i''_{\tstar+1}}, 
+\dots,P_{n,i''_n}=\Pgoal)$
 be the path that always removes the two smallest compactnesses
@@
 h_\mathrm{comp}(\Pnode)=
-\sum_{s=t}^{n-1}f_\mathrm{comp}(P_{s,i'_s}). \nonumber
+\sum_{s=t}^{n-1}f_\mathrm{comp}(P_{s,i''_s}).
 \end{equation}
@@
 as we overestimate for only a certain number of subdivisions.
-Based on this assumption,
-the cost of compactness is $f_\mathrm{comp}(P_{s,i_s})=1/(n-2)$,
+Based on the assumption, the cost of compactness 
+is~$f_\mathrm{comp}(P_{s,i''_s})=1/(n-2)$,
 according to \eq\ref{eq:f_comp}.
-If we overestimate $K'$ steps, 
+When we need to overestimate $K'$ steps
+(see \eq\ref{eq:OverestimateKPrime}), 
 we revise the estimated cost of compactness to
@@
 \sum_{s=t}^{t+K'-1}\frac{1}{n-2}+
-\sum_{s=t+K'}^{n-1}f_\mathrm{comp}(P_{s,i'_s}).
+\sum_{s=t+K'}^{n-1}f_\mathrm{comp}(P_{s,i''_s}).
 \end{equation}
@@
 (see \fig\ref{fig:AreaAgg_h_length}).
-Then we compute the estimated cost of length according to 
+Then, we compute the estimated cost of length according to 
 \eq\ref{eq:f_length}.
@@
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i''_t}, P_{t+1,i''_{\tstar+1}}, \dots,P_{n,i''_n}=\Pgoal)$
+$(\Pnode=P_{t,i'''_t}, P_{t+1,i'''_{\tstar+1}}, 
+\dots,P_{n,i'''_n}=\Pgoal)$
 be the path that always keeps 
@@
 h_\mathrm{lgth}(\Pnode)=
-\sum_{s=t}^{n-1}f_\mathrm{lgth}(P_{s,i''_s}).
+\sum_{s=t}^{n-1}f_\mathrm{lgth}(P_{s,i'''_s}).
 \end{equation}
 When overestimating,
-we use the interior length of the current map as the cost of 
-length for $K'$ steps even though we are removing 
-interior boundaries.
+we use the interior length of subdivision~\Pnode
+as the cost of length for each of the first $K'$ steps 
+(see \eq\ref{eq:OverestimateKPrime}),
+even though we are removing interior boundaries
+step by step.
 As a result, we revise \fo\ref{eq:h_length} to
@@
 \sum_{s=t}^{t+K'-1}f_\mathrm{lgth}(P_{t,i})+
-\sum_{s=t+K'}^{n-1}f_\mathrm{lgth}(P_{s,i''_s}). \nonumber
+\sum_{s=t+K'}^{n-1}f_\mathrm{lgth}(P_{s,i'''_s}).
 \end{equation}
@@
 \centering
-\includegraphics[page=3]{AreaAgg_Estimation}
-\caption{An "aggregation" sequence for computing 
-	$h_\mathrm{lgth}$ 
-	(see Equation~\ref{eq:h_length}) 
-	based on the lengths of boundaries. 
-	At each step we keep the necessary number 
-	of boundaries with least lengths in order to find a 
-	lower bound of edge length of the interior boundaries 
-	$l_\mathrm{int}(t)$. 
+\includegraphics[page=5]{AreaAgg_CostsAndEstimations}
+\caption{An "aggregation sequence" for computing 
+	the estimated cost of length~$h_\mathrm{lgth}$ 
+	(see \eqs\ref{eq:h_length} and~\ref{eq:o_length}),
+	based on the lengths of interior boundaries. 
+	At each step, we keep the necessary number 
+	of interior boundaries with least lengths in order to find a 
+	lower bound of the total length of the interior boundaries, 
+	i.e., $l_\mathrm{int}(P_{s,i'''_s})$.
 	The numbers represent the 
 	lengths of the interior boundaries.
+    Note that this aggregation sequence is impossible in reality,
+    but it is fine for estimating
+    (see the argument in \sect\ref{sec:AreaAgg_h_type}).    
 	This example corresponds to the aggregation step in 
-	\fig\ref{fig:AreaAgg_FirstStep}
+	\fig\ref{fig:AreaAgg_FirstStep}b.
 }
@@
 (1-\lambda)h_\mathrm{type}(\Pnode)
-+\lambda h_{\mathrm{comp}}(\Pnode), \nonumber
++\lambda h_{\mathrm{comp}}(\Pnode),
 \end{equation}
@@
 (1-\lambda)h_\mathrm{type}(\Pnode)
-+\lambda h_{\mathrm{lgth}}(\Pnode). \nonumber
++\lambda h_{\mathrm{lgth}}(\Pnode).
 \end{equation}
@@
 to optimize a \emph{linear objective}
-subject to a set of \emph{linear constraints},
+subject to a set of \emph{linear constraints}
 with some \emph{variables}.
@@
 $$
-\mathrm{maximize} 	\quad	 5x+4y
+\mathrm{maximize} 	\quad	 5x+4y.
 $$
@@
 with intensity~$20\%$.
-Therefore, we have four constraints:
+As a result, we have four constraints:
 \begin{align*}
@@
 all the feasible solutions, i.e., pairs of~$(x,y)$,
-fall in the gray area 
-shown in \fig\ref{fig:AreaAgg_ILPIllustration}a.
+fall in the gray area of
+\fig\ref{fig:AreaAgg_ILPIllustration}a.
 Drawing a line with slope~$-\frac{5}{4}$,
@@
 we move the dashed line to the upper right as much as possible
-and at the same time make sure that 
+and, at the same time, make sure that 
 it still intersects with the gray area.
@@
 respectively~$x'$ and~$y'$ jugs,
-then our problem becomes:
+then the problem becomes:
 \begin{alignat*}{3}
@@
 For this problem, only the pairs of~$(x',y')$ 
-represented by the gray dots in \fig\ref{fig:AreaAgg_ILPIllustration}b 
+represented by the gray dots of 
+\fig\ref{fig:AreaAgg_ILPIllustration}b 
 are feasible solutions
-(point~$A$ is no longer a solution in this case).
+(point~$A$ is no longer a feasible solution in this case).
 In order to maximize our profit,
@@
 as much as possible
-and at the same time make sure that 
+and, at the same time, make sure that 
 it hits at least one of the gray dots.
@@
 \parencite{Haunert2017Label}.
-Also, by using these solvers we benefit 
-from every improvement, by their producers,
+By using these solvers, 
+we benefit from every improvement, by their producers,
 for the same class of problems
@@
 &&					\quad&& \bm{X} 			&\ge \bm{0}, 	\\
-&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I.
+&&\text{and}		\quad&& \bm{X} 			&\in \mathbb{Z}^I,
 \end{alignat*}
@@
 and~$\bm{E}$ is a $(J \times I)$-matrix over the reals.
-Furthermore, if we require that
+Furthermore, if we require 
 $$
@@
 \parencite[\sect2.3]{Williams2009Integer}.
-To find optimal sequences for area aggregation, 
-we are going to use binary variables in our ILP.
+We are going to use binary variables in our ILP
+because it is more intuitive 
+to model our problem using binary variables
+than using other integers.
 
@@
 integer linear programming in finding 
-optimal solutions for our aggregation problem. 
+optimal sequences for our aggregation problem. 
 Since integer linear programming
@@
 %
+Recall that We use~$T=\{1,2,\dots,n\}$ to represent the set of times
+and use~$P$ to denote the set of $n$ polygons on the start map
+(see \sect\ref{sec:AreaAgg_Preliminaries}).
+%
 The first set of variables is used to tell the program 
@@
 	for our ILP, $x$, $y$, $z$, $c$, and~$w$.
-	The arrows in the drawings 
-	show the aggregation steps and
-	the dotted lines represent 
+	The arrows with curly arms show the aggregation steps,
+    and the dotted lines represent 
 	the removed boundaries by the aggregation steps.
-	There are some blank spaces because 
-	there is no corresponding variable at the specific times.
+	There are some blank spaces in the rows of the variables
+    because there is no corresponding variable at the specific times.
 }
@@
 \begin{flalign*}
-&\myquad[6]
+&\eqquadVariable
 \embrd[V]{x_{t,p,r}} \in
@@
 with the intended meaning~$x_{t,p,r}=1$ if and only if 
-polygon $p$ is assigned to polygon $r$ at time $t$. 
+polygon $p$ is assigned to polygon $r$ at time $t$
+(see \fig\ref{fig:AreaAgg_Variables} for some examples). 
 If a polygon is a center at time~$t$, 
 then the polygon must be assigned to itself, 
-that is, $x_{t,r,r}=1$
-(see \fig\ref{fig:AreaAgg_Variables} for some examples).
+that is, $x_{t,r,r}=1$.
 
@@
 \begin{flalign*}
-&\myquad[6]
+&\eqquadVariable
 \embrd[V]{y_{t,p,o,r}} \in
@@
 with the intended meaning~$y_{t,p,o,r}=1$ if and only if 
-polygon~$p$ is assigned to center $o\in P$ at time~$t-1$ 
-and to center~$r$ at time~$t$.
-Specifically, $y_{t,p,o,o}=1$ means that
+polygon~$p$ is assigned to center~$o$ at time~$t-1$ 
+and assigned to center~$r$ at time~$t$ 
+(see \fig\ref{fig:AreaAgg_Variables}).
+Specifically, case~$y_{t,p,o,o}=1$ means that
 polygon~$p$ is assigned to the same center 
-at times~$t-1$ and~$t$ 
-(see \fig\ref{fig:AreaAgg_Variables}).
+at times~$t-1$ and~$t$.
 
@@
 \begin{flalign*}
-&\myquad[6]
+&\eqquadVariable
 \embrd[V]{z_{t,p,q,r}} \in
@@
 with the intended meaning~$z_{t,p,q,r}=1$ 
-if and only if at time~$t$
-polygons~$p$ and~$q$ are both in patch~$r$.
+if and only if polygons~$p$ and~$q$ 
+are both assigned to center~$r$ at time~$t$
+($p$ and $q$ are in the same patch).
 In this case, their common boundary should be removed
@@
 We do not need~$z_{t,p,q,r}$ for time~$t=1$ 
-because at the time
-there are no two polygons in the same patch.
-Namely, it always holds that~$z_{1,p,q,r}=0$, 
+because there are no two polygons in the same patch.
+Namely, it always holds~$z_{1,p,q,r}=0$, 
 which does not help in our ILP.
 We do not need~$z_{t,p,q,r}$ for time~$t=n$
-because in this case
-all the polygons are in the same patch.
-The situation that~$z_{n,p,q,r}=1$ always holds
-does not help in our ILP, either.
+because all the polygons will be in the same patch.
+In this case, \eq$z_{n,p,q,r}=1$ always holds,
+which does not help in our ILP, either.
 
@@
 \begin{flalign*}
-&\myquad[6]
+&\eqquadVariable
 \embrd[V]{c_{t,p,o,r}} \in
@@
 with the intended meaning~$c_{t,p,o,r}=1$ 
-if and only if at time~$t$
-polygon~$p$ is assigned to center~$o$ 
+if and only if, at time~$t$,
+polygon~$p$ is assigned to center~$o$, 
 and~$p$ has a neighbor assigned to center~$r$
-(see for example \figs\ref{fig:AreaAgg_Variables}
-and~\ref{fig:AreaAgg_Variables_Neighbor}).
-We do not need a variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
-because then there are only two patches left 
+(see \figs\ref{fig:AreaAgg_Variables}
+and~\ref{fig:AreaAgg_Variables_Neighbor} for examples).
+We do not need variable~$c_{t,p,o,r}$ for time~$t=n-1$ 
+because there are only two patches left, 
 and they must be neighbors.
@@
 \begin{flalign*}
-&\myquad[6]
+&\eqquadVariable
 \embrd[V]{w_{t,o}} \in
@@
 \end{flalign*}
-with $w_{t,o}=1$ meaning 
-that patch~$o$ is a smallest patch at time~$t$
+with $w_{t,o}=1$ meaning if and only if, at time~$t$, 
+patch~$o$ is the smallest patch that is involved 
+in the aggregation step from time~$t$ to time~$t-1$
 (see for example \fig\ref{fig:AreaAgg_Variables}).
@@
 
-\subsection{Objectives}
-\label{sub:AreaAgg_objectives}
-
-Our aim is to minimize a weighted sum of the two costs, 
-the cost of type change and the cost of length,
-that is, we
+\subsection{Objective}
+\label{sub:AreaAgg_objective}
+
+We want to minimize a weighted sum of the two costs, 
+the cost of type change and the cost of length
+(analogous to \eq\ref{eq:g_2}).
+That is, our objective is to
 \begin{equation}
@@
 \end{equation}
-where~$\lambda$, as in \eq\ref{eq:g_1}, 
+where~$\lambda$, as in \eq\ref{eq:g_2}, 
 is a parameter 
 to assign importances 
-of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
-According to the objective we introduced in
+of~$F_\mathrm{type}$ and~$F_\mathrm{lgth}$.
+According to the cost introduced in
 \sect\ref{sec:AreaAgg_f_type},
-the total cost of type change is defined as
+we compute the total cost of type change by
 \begin{flalign*}
 %\label{eq:F_type}
-&\myquad[4]
+&\eqquadCost
 \embrd[V]{F_\mathrm{type}} =
@@
 $A_R$ is the area of the region, 
-and~$T(o)$ and~$T(r)$ are the types of centers~$o$ and~$r$.
-
-We also try to minimize the overall interior lengths of all the 
-intermediate subdivisions.
+and~$T(o)$ and~$T(r)$ are 
+the types of centers (polygons)~$o$ and~$r$.
+
+We also wish to minimize the overall interior lengths 
+of all the intermediate subdivisions.
 As discussed in \sect\ref{sec:AreaAgg_costlength},
-we need a cost that can be computed linearly.
-We use the length of the interior boundaries 
+we use the length of the interior boundaries 
 as an alternative to compactness.
-Recall that $B(\Pstart)$ is the set of interior boundaries 
-at time $t=1$ (see \sect\ref{sec:AreaAgg_costlength}).
-The sum of the normalized length of 
-the remaining interior boundaries at all times 
-can be computed by
+Recall that~$B(\Pstart)$ is the set of interior boundaries 
+at time~$t=1$ (see \sect\ref{sec:AreaAgg_costlength}).
+We sum up the normalized lengths of 
+the remaining interior boundaries 
+of all the intermediate subdivisions by
 \begin{flalign}
 \label{eq:F_length_raw}
-&\myquad[4]
+&\eqquadCost
 \embrd[V]{F_\mathrm{lgth}} =
@@
 between polygons~$p$ and~$q$. 
-We define the lengths of the common boundary to be~$0$
+We define the length of the common boundary to be~$0$
 (i.e., $|b_{pq}|=0$) if $p=q$ 
-because no boundary is removed in this case.
+because there is no boundary to be removed in this case.
 Function~$D(t)$, defined by \eq\ref{eq:AreaAgg_Norm}, 
@@
 As in \eq\ref{eq:f_length}, 
-denominator~$n-2$ is used to balance 
-between the costs of type change and length.
-Integrating~$D(t)$ into \eq\ref{eq:F_length_raw}, we have
+we use denominator~$n-2$ to balance 
+between the cost of type change and the cost of length.
+Integrating \eq\ref{eq:AreaAgg_Norm} 
+into \eq\ref{eq:F_length_raw}, we have
 \begin{flalign*}
 %\label{eq:F_length}
-&\myquad[4]
+&\eqquadCost
 \embrd[V]{F_\mathrm{lgth}} =
@@
 Recall that the intended meaning 
-of~$x_{t,p,r}=1$ is that, at time~$t$, 
-polygon~$p$ is assigned to center~$r$. 
-Our first constraint is that, at time~$t$, 
-polygon~$p$ is assigned to 
-exactly one center. 
+of~$x_{t,p,r}=1$ is if and only if 
+polygon~$p$ is assigned to center~$r$ at time~$t$. 
+To realize this functionality,
+our first constraint is that 
+polygon~$p$ is assigned to exactly one center at time~$t$. 
 To this end, we require that
@@
 \label{eq:CstrOneCenter}
-&\eqquad
+&\eqquadConstraintsX
 \embrd{\sum_{r\in P} x_{t,p,r}} =\embld{1} 
@@
 that is, $x_{t,r,r}=1$.
-If~$r$ is not a center, then $x_{t,r,r}=0$.
-In either case,
+If~$r$ is not a center, we have variable~$x_{t,r,r}=0$.
+In either case, we have
 \begin{flalign}
 \label{eq:CstrAssign}
-&\eqquad
+&\eqquadConstraintsX
 \embrd{x_{t,p,r}} \leq \embld{x_{t,r,r}}
@@
 
-Aggregating one patch into another results in 
+Aggregating a patch into another one results in 
 the number of centers decreasing by~$1$.
-We make sure that exactly one patch 
-is aggregated into another by 
-specifying the number of centers
+We achieve that exactly one patch 
+is aggregated into another by specifying the number of centers
 for each point in time, that is,
@@
 %\label{eq:CstrCountCenter}
-&\eqquad
+&\eqquadConstraintsX
 \embrd{\sum_{r\in P} x_{t,r,r}} =
@@
 
-A center can disappear, but will never reappear afterwards.
-Hence,
+When a patch is aggregated into another one,
+the center of the former will not be used as a center anymore.
+Hence, we have
 \begin{flalign}
 \label{eq:CstrNoReappear}
-&\eqquad
+&\eqquadConstraintsX
 \embrd{x_{t,r,r}} \le 
@@
 On the start map, 
-there are some polygons with  goal type $T_\mathrm{goal}$
+there are some polygons with the goal type,~$T_\mathrm{goal}$
 (see definition in \sect\ref{sec:AreaAgg_h_type}).
-At time $t=n$, all polygons are aggregated into one patch.
-This patch must have the goal type, $T_\mathrm{goal}$.
+At time~$t=n$, all polygons are aggregated into one patch.
+This patch must have type~$T_\mathrm{goal}$.
 In other words, the center of this patch must be one of the 
-polygons with the 
-goal type on the start map:
+polygons with type~$T_\mathrm{goal}$ on the start map:
 \begin{equation}
@@
 
-Next, we use the binary variables~$y_{t,p,o,r}$
+Next, we restrict binary variable~$y_{t,p,o,r}$,
 introduced in \sect\ref{sub:AreaAgg_variables}.  
-Recall that the intended meaning of~$y_{t,p,o,r}=1$ is that 
+Recall that the intended meaning of~$y_{t,p,o,r}=1$ 
+is if and only if 
 polygon~$p$ is assigned to center~$o$ at time~$t-1$ 
@@
 and assigned to center~$r$ at time $t$
-($x_{t,p,r}=1$), then $y_{t,p,o,r}=1$. 
-This is expressed by
+($x_{t,p,r}=1$), we have variable~$y_{t,p,o,r}=1$. 
+This requirement is expressed by
 \begin{flalign}
 \label{eq:CstrY1}
-&\eqquad
+&\eqquadConstraintsYZ
 \embrd{y_{t,p,o,r}} \geq 
@@
 Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
-or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
-then $y_{t,p,o,r}=0$.
-This is expressed by
+and/or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
+we have variable~$y_{t,p,o,r}=0$.
+This requirement is expressed by
 \begin{flalign}
 \label{eq:CstrY2}
-&\eqquad
+&\eqquadConstraintsYZ
 \begin{array}{@{}l}
@@
 \end{array}
-\embld{\hspace{0.5pt}
+\embld{\embshift
 	\begin{array}{@{}l}
@@
 }
-\inquad \hspace{0.5pt}
+\inquad \embshift
 \forall t\in T\setminus \{1\}, 
@@
 In \sect\ref{sub:AreaAgg_variables},
-we introduced the binary variables~$z_{t,p,q,r}$.
-Recall that the intended meaning of~$z_{t,p,q,r}=1$ is that, at
-time~$t$, polygons~$p$ and~$q$ are both in patch~$r$.
+we introduced binary variable~$z_{t,p,q,r}$.
+Recall that the intended meaning of~$z_{t,p,q,r}=1$ 
+is if and only if
+polygons~$p$ and~$q$ are both in patch~$r$ at time~$t$.
 To enforce this, we need three types of constraints.
@@
 First, if two polygons~$p$ and~$q$ are assigned 
-to center~$r$ at time~$t$ ($x_{t,p,r}=x_{t,q,r}=1$),
-then~$z_{t,p,q,r}=1$.  This is expressed by
+to center~$r$ at time~$t$ ($x_{t,p,r}=1$ and~$x_{t,q,r}=1$),
+we have variable~$z_{t,p,q,r}=1$. 
+This requirement is expressed by
 \begin{flalign}
 \label{eq:CstrZ1}
-&\eqquad
+&\eqquadConstraintsYZ
 \embrd{z_{t,p,q,r}} \geq 
@@
 
-Second, if not both~$p$ and~$q$ are assigned to~$r$,
-then $z_{t,p,q,r}=0$.  This is expressed by
+Second, at time~$t$, if~$p$ is not assigned to~$r$ ($x_{t,p,r}=0$)
+and/or~$q$ is not assigned to~$r$ ($x_{t,q,r}=0$), 
+we have variable~$z_{t,p,q,r}=0$. 
+This requirement is expressed by
 \begin{flalign}
 \label{eq:CstrZ2}
-&\eqquad
+&\eqquadConstraintsYZ
 \begin{array}{@{}l}
@@
 \end{array} 
-\embld{\hspace{0.5pt}
+\embld{\embshift
 	\begin{array}{@{}l}
@@
 }
-\inquad \hspace{0.5pt}
+\inquad \embshift
 \forall t \in T \setminus \{1,n\}, 
@@
 \end{flalign}
-Note the correspondence between 
-constraints~(\ref{eq:CstrY1}) and~(\ref{eq:CstrZ1})
-and between 
-constraints~(\ref{eq:CstrY2}) and~(\ref{eq:CstrZ2}).
 
@@
 express
-the last type of constraint involving variables~$z_{t,p,q,r}$:
+the last type of constraint involving variable~$z_{t,p,q,r}$:
 \begin{flalign}
 \label{eq:CstrZabbrv}
-&\eqquad
+&\eqquadConstraintsYZ
 \embrd{z_{t,p,q}} = 
@@
 (see \sect\ref{sub:AreaAgg_variables}).
-Note that $z_{t,p,q}$ expresses whether, at time~$t$, 
+Variable~$z_{t,p,q}$ expresses whether, at time~$t$, 
 polygons~$p$ and~$q$ are 
@@
 %
-Note further that 
+Note that 
 constraints~(\ref{eq:CstrOneCenter}) and~(\ref{eq:CstrZ2}) 
-ensure that~$p$ and~$q$ can only be assigned 
-to one common patch, that is, $z_{t,p,q} \le 1$.
-
-Now we use our new variables~$z_{t,p,q}$
-to express the following requirement. 
+ensure that polygons~$p$ and~$q$ can be assigned 
+to one common center at most; therefore, we have~$z_{t,p,q} \le 1$.
+We use our new variable~$z_{t,p,q}$
+to express the following requirement: 
 If two polygons have been aggregated into one patch, 
 they will always be in the same patch 
-at later times~-- although the center of their common patch 
-can change after the point in time 
-when they were aggregated first. 
-In other words, as a function of time~$t$, 
-$z_{t,p,q}$ is monotonically increasing:
+at later times---although 
+the center of their common patch may change. 
+In other words,  
+variable~$z_{t,p,q}$ is monotonically increasing
+as a function of time~$t$:
 \begin{flalign}
 \label{eq:CstrTogether}
-&\eqquad
+&\eqquadConstraintsYZ
 \embrd{z_{t,p,q}} \ge 
@@
 
-The problem of ensuring contiguity inside a patch 
-when using integer linear programming 
-has received considerable attention.
+Now we present our constraints of 
+ensuring contiguity inside a patch.
+This problem has received considerable attention 
+in integer linear programming.
 Usually, a subdivision is represented by a graph
@@
 to each of the other nodes.
-Then they required that a center can be assigned 
+Then, they required that a center can be assigned 
 by a node only if 
@@
 in the shortest path had been assigned to the center.
-Although this requirement makes their problem easier to be 
-solved,
+Although this requirement makes 
+their problem easier to be solved,
 it excludes many feasible patches.
 %
-\textcite{Williams2002Contiguous} found an optimal spanning tree 
-with a user-specified number of nodes, say,~$i$.
-In order to ensure contiguity, this method requires that 
-there must be~$i-1$ edges in the spanning tree.
+\textcite{Williams2002Contiguous} 
+built an optimal spanning tree for the nodes.
+In order to ensure contiguity, 
+the method picks a user-specified number of nodes that constitute 
+an optimal subtree of the previously built spanning tree.
 %
@@
 a path from the node to the center was demanded 
-that each node is assigned to the center.
+that each node of the path is assigned to the center.
 %
@@
 He required that there must be a path so that 
-some fluid could flow from a node to a sink (center).
+some fluid can flow from a node to a sink (center).
 %
@@
 We aggregate two patches only if they are neighbors.
-To ensure this, we need the binary variables~$c_{t,p,o,r}$
+To ensure this, we need binary variable~$c_{t,p,o,r}$
 introduced in \sect\ref{sub:AreaAgg_variables}.
 Recall that the intended meaning of~$c_{t,p,o,r}=1$ 
-is that, at time~$t$, 
+is if and only if, at time~$t$, 
 polygon~$p$ of patch~$o$ has 
@@
 
-First, at time~$t$, polygon~$p$ must actually be assigned 
-to center~$o$,
+First, polygon~$p$ must actually be assigned 
+to center~$o$ at time~$t$ ($x_{t,p,o}=1$).
+In contrast, if~$p$ is not assigned to~$o$ ($x_{t,p,o}=0$),
+then variable~$c_{t,p,o,r}$ is impossible to tell
+if patch~$o$ and patch~$r$ are neighbors.
+In this case, we must not aggregate the two patches ($c_{t,p,o,r}=0$);
+otherwise, we may end up having noncontiguous patches.
+As a result,
 \begin{flalign}
 \label{eq:CstrC_Part}
-&\eqquad
-\embrd[C]{c_{t,p,o,r}} \le 
-\embld[D]{x_{t,p,o}} \inquad
-\forall t 	 \in T\setminus \{n-1,n\},  
-\forall p, o, r \in P \text{~with}~o\ne r.&
+&\eqquadConstraintsC
+\begin{array}{@{}l}
+\embrd[C]{c_{t,p,o,r}} \le  \\
+\embrd[C]{} %an empty place
+\end{array} 
+\embld[D]{\embshift
+	\begin{array}{@{}l}
+	x_{t,p,o} \\
+	~ %an empty place
+	\end{array}
+}
+\inquadC \embshift
+\begin{array}{@{}l}
+\forall t 	 \in T\setminus \{n-1,n\},\\
+\forall p, o, r \in P \text{~with}~o\ne r.
+\end{array} &	
 \end{flalign}
 
-Second, at time~$t$, polygon~$p$ has at least 
-one neighbor that is assigned to center~$r$,
+Second, at time~$t$, at least one of polygon~$p$'s neighbor(s),
+say, polygon~$q$ has to be assigned to center~$r$ ($x_{t,q,r}=1$).
+If not, then variable~$c_{t,p,o,r}$ is impossible to tell
+if patches~$o$ and $r$ are neighbors.
+Analogous to the condition of constraint~(\ref{eq:CstrC_Part}),
+we have
 \begin{flalign}
 \label{eq:CstrC_Neighbor}
-&\eqquad
-\embrd[C]{c_{t,p,o,r}} \le 
-\embld[D]{\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r}} \inquad
-\forall t 	 \in T\setminus \{n-1,n\},  
-\forall p, o, r \in P \text{~with}~o\ne r,&
+&\eqquadConstraintsC
+\begin{array}{@{}l}
+\embrd[C]{c_{t,p,o,r}} \le  \\
+\embrd[C]{} %an empty place
+\end{array} 
+\embld[D]{\embshift
+	\begin{array}{@{}l}\displaystyle
+	\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r} \\
+	~ %an empty place
+	\end{array}
+}
+\inquadC \embshift
+\begin{array}{@{}l}
+\forall t 	 \in T\setminus \{n-1,n\},\\
+\forall p, o, r \in P \text{~with}~o\ne r,
+\end{array} &	
 \end{flalign}
@@
 
-Third, if polygon~$p$ is in patch~$o$ and~$p$ has at least 
-one neighbor in patch~$r$, then we must enforce~$c_{t,p,o,r}=1$,
+Third, if polygon~$p$ is in patch~$o$ ($x_{t,p,o}=1$)
+and~$p$ has at least one neighbor, say, 
+polygon~$q$ in patch~$r$ ($x_{t,q,r}=1$),
+then we must enforce variable~$c_{t,p,o,r}=1$
+(according to the definition of this variable).
+We have
 \begin{flalign}
 \label{eq:CstrC_Positive}
-&\eqquad
+&\eqquadConstraintsC
 \begin{array}{@{}l}
@@
 \end{array} 
-\embld[D]{\hspace{0.5pt}
+\embld[D]{\embshift
 	\begin{array}{@{}l}
@@
 }
-\inquad \hspace{0.5pt}
+\inquadC \embshift
 \begin{array}{@{}l}
@@
 from time~$t-1$ to time~$t$, 
-then $y_{t,o,o,r}=1$.
+we have variable~$y_{t,o,o,r}=1$
+(see the definition of this variable 
+in \sect\ref{sub:AreaAgg_variables}).
 In this case, we must make sure that 
-the two patches are actually neighbors,
+the two patches are actually neighbors at time~$t-1$.
+That is to say, at least one of patch~$o$'s polygons 
+has at least one neighbor in patch~$r$ at time~$t-1$.
+If not, we have~$y_{t,o,o,r}=0$.
+That is, it holds
 \begin{flalign}
 \label{eq:CstrC_Agg}
-&\eqquad
+&\eqquadConstraintsC
 \embrd[C]{y_{t,o,o,r}} \le 
-\embld[D]{\sum_{p\in P} c_{t-1,p,o,r}} \inquad
+\embld[D]{\sum_{p\in P} c_{t-1,p,o,r}} \inquadC
 \forall t 	 \in T\setminus \{1,n\},  
@@
 (\ref{eq:CstrOneCenter})--(\ref{eq:CstrC_Agg})
-explained so far 
 and variables~$x_{t,p,r}$, $y_{t,p,o,r}$, $z_{t,p,q,r}$,
@@
 we need another type of variable,~$w_{t,o}$.
-Recall that the intended meaning of~$w_{t,o}=1$ is that 
+Recall that the intended meaning of~$w_{t,o}=1$ is 
+if and only if 
 polygon~$o$ is the center of 
@@
 At any time~$t$, 
-we pick exactly one smallest patch and aggregate it with 
-one of its neighbors;
+we pick exactly one smallest patch (there can be many) 
+and aggregate it with one of its neighbors;
 we do not care whether or not the neighbor is a smallest one.
@@
 \label{eq:CstrSOneSmallest}
-&\eqquad
+&\eqquadConstraintW
 \embrd[S]{\sum_{o\in P}w_{t,o}} =
@@
 Assume that patch~$o$ is the smallest patch
-which is involved in the aggregation step from~$t$ to~$t+1$,
-and that we are aggregating patches~$o$ and~$r$.
+involved in the aggregation step from~$t$ to~$t+1$
+and that we are aggregating patch~$o$ and another patch, say,~$r$.
 There can be two cases.
-Patch~$o$ is aggregated into patch~$r$, 
-or the other way around.
+We aggregate~$o$ into~$r$ 
+or aggregate~$r$ into~$o$.
 In the first case, we have variable~$y_{t+1,o,o,r}=1$,
-and in the second case, we have~$y_{t+1,r,r,o}=1$.
-Either of the two constraints implies 
+and, in the second case, we have~$y_{t+1,r,r,o}=1$.
+Either of the two cases implies 
 that polygon~$o$ is indeed a center at time~$t$, 
@@
 In order to enforce that
-the aggregation step involves patch~$o$,
-we must make sure that~$y_{t+1,o,o,r}=1$ or~$y_{t+1,r,r,o}=1$ 
-when $w_{t,o}=1$.
+the aggregation step involves patch~$o$ and another patch,
+we must make sure~$y_{t+1,o,o,r}=1$ or~$y_{t+1,r,r,o}=1$
+when~$w_{t,o}=1$.
 Consequently, we use the constraint
@@
 %if we do \embld{\sum_{r\in P \setminus \{o\}}
-&\eqquad
+&\eqquadConstraintW
 \embrd[S]{w_{t,o}} \le 
@@
 We define variable~$A_{t,r}$ as the area of 
-patch~$r$ at time~$t$, 
-that is,
+patch~$r$ at time~$t$. 
+That is, we have
 \begin{flalign*}
-&\eqquad
+&\eqquadConstraintW
 \embrd[S]{A_{t,r}} = 
@@
 where~$a_p$ is the area of polygon~$p$ 
-and is a constant (as viewed by the ILP).
+and, as viewed by the ILP, is a constant.
 Area~$A_{t,r}$ is positive 
-if and only if polygon~$r$ is a center at time~$t$,
-that is, if and only if~$x_{t,r,r}=1$.
-We define a very large number~$M$ 
+if and only if polygon~$r$ is a center at time~$t$ ($x_{t,r,r}=1$).
+We define constant~$M$ as a very large number
 to help us construct the corresponding constraints.
@@
 i.e., $M=A_R$ (see \eq\ref{eq:f_type}). 
-We require that
+We require
 %\begin{flalign}
 %\label{eq:CstrSIndeedSmallest}
-%&\eqquad
+%&\eqquadConstraints
 %\embrd[S]{A_{t,o} - M(1-w_{t,o})} \le
@@
 %\end{flalign}
-\begin{flalign}
-\label{eq:CstrSIndeedSmallest}
-&\eqquad
-\embrd[S]{A_{t,o}} -
-\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
-\forall t 	 \in {T}\setminus \{n\}, 
-\forall o, r \in P \text{~with}~o\ne r. &
-\end{flalign}
+%\begin{flalign}
+%\label{eq:CstrSIndeedSmallest_Remove}
+%&\eqquadConstraintW
+%\embrd[S]{A_{t,o}} -
+%\embld[T]{M(1-w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r})} \inquad
+%\forall t 	 \in {T}\setminus \{n\}, 
+%\forall o, r \in P \text{~with}~o\ne r. &
+%\end{flalign}
 %\begin{equation}
@@
 %\end{equation}
+\begin{flalign}
+\label{eq:CstrSIndeedSmallest}
+&\eqquadConstraintW
+\begin{array}{@{}l}
+\embrd[S]{A_{t,o}- M(1} -\\
+\embrd[S]{} %an empty place
+\end{array} 
+\embld[T]{\embshift
+	\begin{array}{@{}l}
+	w_{t,o}) \le A_{t,r}+M(1-x_{t,r,r}) \\
+	~ %an empty place
+	\end{array}
+}
+\inquad \embshift
+\begin{array}{@{}l}
+\forall t 	 \in T\setminus \{n\},\\
+\forall o, r \in P \text{~with}~o\ne r.
+\end{array} &	
+\end{flalign}
 This constraint takes effect only when~$w_{t,o}=1$ 
@@
 involving a smallest patch at each step, 
-we need all the five types of variables and 
+we need all the five types of variables and all the
 constraints~(\ref{eq:CstrOneCenter})--(\ref{eq:CstrSIndeedSmallest}).
@@
 CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
-Our prototype is open access on 
-GitHub\footnote{
+Our prototype is open access on GitHub\footnote{%
 \url{https://github.com/IGNF/ContinuousGeneralisation},
@@
 in Microsoft Visual Studio so that 
-we were able to use up to~$3\,$GB of main memory\footnote{
-	The details of the setting can be found at 	
-	\url{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
+we were able to use up to~$3\,$GB of the 
+main memory\footnote{The details of the setting can be found at \url
+{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
 Accessed: Nov 1, 2017.}.
@@
 To fix this problem, we had to disable 
-both primal and dual presolve reductions\footnote{
-	For more details about the problem, see
+both primal and dual presolve 
+reductions\footnote{For more details about the problem, see
 \url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
@@
 
-We tested our method on a data set 
+We tested our method on a dataset 
 from the German topographic database ATKIS DLM~50. 
-The data set represents the place 
+The dataset represents the place 
 ``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
 Our start map is the result of collapsing areas 
-by \citet[\chap~6]{haunert2008f}.
+by \citet[\chap6]{haunert2008f}.
 The start map has~$5{,}537$ polygons. 
@@
 by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
-at~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
+to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
 The goal map has~$734$ polygons, 
 which means that there are~$N=734$ regions.
-The distribution of region sizes is shown in \fig\ref{fig:AreaAgg_NumRegion}.
+The distribution of region sizes is shown in 
+\fig\ref{fig:AreaAgg_NumRegion}.
 %
@@
 the distance is the ``number of edges'' that
-we need to travel from one node to another 
-node in the tree of type hierarchy\footnote{
-	More information about land-cover types can be found at 
+we need to travel from one node to another node in the tree of 
+type hierarchy\footnote{More information 
+    about land-cover types can be found at 
 	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
@@
 \begin{figure}[tb]
-\captionsetup[subfigure]{labelformat=empty}
+%\captionsetup[subfigure]{labelformat=empty}
 \begin{subfigure}[b]{.49\textwidth}
@@
 \includegraphics[page=4]{AreaAgg_Data}
-\caption{Distribution of region sizes:
+\caption{Distribution of the region sizes:
 	the $y$-axis shows how many regions 
-	of a given size range are contained in our data set.}
+	of a given size range are contained in our dataset.}
 \label{fig:AreaAgg_NumRegion}
@@
 \centering
-\includegraphics{AreaAgg_TypeDistances}
+\includegraphics[page=5]{AreaAgg_Data}
 \caption{The tree of type hierarchy used in our case study.
@@
 the greedy algorithm visited 
-fewer nodes and arcs in the graph~$G$ 
+fewer nodes and arcs in graph~$G$ 
 and used much less time.
-However, 
-\Astar managed to find solutions with 
+However, \Astar managed to find solutions with 
 lower total cost,~$117.3$ (or~$117.2$), 
@@
 while the greedy algorithm solved 
-only~$407$ ($55.4\%$) to optimality.
+only~$408$ ($55.6\%$) to optimality;
+see column \#OS in 
+Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
 For the other~$32$ regions, 
 both algorithms have found feasible solutions 
-(see column \#over in 
+(see column \#FS in 
 Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
 Although some of the feasible solutions may also be optimal,
-we cannot verify only from the cost values.
+we cannot verify that only from the cost values.
 
 \begin{table*}[tb]
-%\small	
-\centering
 \caption{A comparison of the greedy algorithm and \Astar		
@@
 	%
-	Symbol~\#OS represents the number of regions 
+	Column~\#OS shows the numbers of regions 
     that we obtained optimal solutions.   
 	%
-	Symbol~\#FS represents 
-    the number and the percentage of regions (out of~$N=734$) 
+	Column~\#FS presents 
+    the numbers and the percentages of regions (out of~$N=734$) 
     that we obtained feasible (non-optimal) solutions.
@@
 	%
-	Symbols~\#nodes and~\#arcs are the total 
+	Columns~\#nodes and~\#arcs are the total 
 	numbers of nodes and arcs that \Astar visited  
@@
 	%
-	$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
+	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
 	and~$\sum g_1$
@@
 	%
-	The percentage in the
-	time column is the fraction of the total
-	runtime spent on solving the instances
+	The percentage in the \emph{Time}
+	column is the fraction of the runtime 
+    spent on solving the instances
 	that we obtained feasible solutions.
@@
 \label{tab:AreaAgg_CaseStudy1_Statistics}
+\centering
+\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
 \setlength{\tabcolsep}{0.7ex}
@@
 &             &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.2         &188.2           &120.7           &1'2~(44.6\%)\\
-%
-%
-\Astar$_{\!\!200{,}000}$	& 702 
+&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
+%
+%
+\AstarTwo	& 702 
 &  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
 & 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
-& 51.4 & 183.2 & 117.3 & 55'5~(93.1\%)\\
-%
-%
-\Astar$_{\!\!400{,}000}$	& 705 
-&  29~(\parbox{\widthof{$4$}}{$\,$}$4.0\%$)
+& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
+%
+%
+\AstarFour	& 704 
+&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
 &  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
-& 51.4 & 183.1 & 117.2 & 102'6~(95.5\%) 
+& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
 \\ \bottomrule			
@@
 We define the total number of repetitions 
-as~$k_\mathrm{sum}=\sum_{i=1}^N k_i$; 
-recall that~$N$ is the number of regions.
+as~$k_\mathrm{sum}=\sum_{i=1}^N k_i$, 
+where~$N=734$ is the number of the regions.
 After increasing~$W$ to~$400{,}000$, 
 \Astar found optimal aggregation sequences 
-for only three more regions, 
+for only two more regions, 
 but $k_\mathrm{sum}$ decreased quite a bit, 
@@
 \Astar spent most of the running time 
-on those few regions:~$4.4\%$ and~$4.0\%$ of the regions 
-caused~$93.1\%$ and~$95.5\%$ of the total running time, 
+on those few regions:~$4.4\%$ and~$4.1\%$ of the regions 
+caused~$93.2\%$ and~$95.5\%$ of the total running time, 
 respectively 
@@
 cost of type change is the best.
-A larger~$R_\mathrm{comp}$ means that our estimation for the 
-cost of shape is poorer.
+A larger~$R_\mathrm{comp}$ means 
+a poorer estimation for the cost of shape.
 
@@
 	Note that if~$h_\mathrm{type}(\Pstart)=0$,
-	we define~$R_\mathrm{type}=1$.
+    then we have~$g_\mathrm{type}(\Pgoal)=0$; 
+	in this case, we define~$R_\mathrm{type}=1$.
 	The marked entries are discussed in the text.
@@
 According to columns~$n$ and~$K$ of \tab\ref{tab:CostsInDetail},
-\Astar managed to find optimal solutions 
+\AstarTwo managed to find optimal solutions 
 for all the regions with fewer than~$15$ polygons,
@@
 for any region with more than~$21$ polygons.
-Among the~$702$ regions that \Astar solved to optimality,
+Among the~$702$ regions that 
+\AstarTwo solved to optimality,
 the greedy algorithm failed to 
-find optimal solutions for~$295$ regions.
+find optimal solutions for~$294$ regions.
 Solutions of the greedy algorithm cost
-at most~$41.7\%$ more than solutions of \Astar;
+at most~$41.7\%$ more than 
+solutions of \AstarTwo;
 for region~$85$, the greedy algorithm yields 
 a solution of cost~$0.777$, 
-while the solution of \Astar has cost~$0.548$
+while the solution of \AstarTwo has cost~$0.548$
 (see \fig\ref{fig:AreaAgg_CaseStudy1_Rg85}).
@@
 surrounding one has~$2112$.
-The type of the goal map is~$4102$.
+The type of the goal patch is~$4102$.
 According to \fig\ref{fig:AreaAgg_TypeDistances},
-type distance~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
+type distances~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
 As a result, our greedy algorithm uses~$5112$ 
@@
 will have to be changed twice during the aggregation.
-These assignments cost more than the sequence obtained by 
-\Astar, where the largest patch on the start map is changed to 
+These changes cause a cost more than the sequence obtained by 
+\AstarTwo, 
+where the largest patch on the start map is changed to 
 the target type directly.
@@
 Among the $32$~regions that 
-\Astar failed to solve optimally,
-the greedy algorithm outperformed \Astar 
+\AstarTwo failed to solve optimally,
+the greedy algorithm outperformed \AstarTwo 
 for~$15$ regions ($46.9\%$).
@@
 Among these, solutions of the greedy algorithm 
-cost at most~$15.9\%$ less than solutions of \Astar;
+cost at most~$15.9\%$ less than solutions of \AstarTwo;
 for region~$543$, the greedy algorithm yields 
 a solution of cost~$0.112$, 
-while the solution of \Astar costs~$0.134$. 
-For this instance, \Astar used overestimation parameter~$K=7$
+while the solution of \AstarTwo costs~$0.134$. 
+For this instance, 
+\AstarTwo used overestimation parameter~$K=7$
 (marked in \tab\ref{tab:CostsInDetail}).
@@
 some intermediate results obtained by
-\Astar and the greedy algorithm.
+\AstarTwo and the greedy algorithm.
 Interestingly, the two methods produced the same sequence until 
 there were~$8$ patches left.
-Then due to the overestimation, \Astar did some bad moves
+Then due to the overestimation, 
+\AstarTwo did some bad moves
 because the bad aggregation sequence still seemed better 
@@
 %
-Among the~$32$ regions that \Astar failed to solve optimally,  solutions of the greedy algorithm cost at most~$17.4\%$ 
-more than solutions of \Astar; 
+Among the~$32$ regions that 
+\AstarTwo failed to solve optimally,  
+solutions of the greedy algorithm cost at most~$17.4\%$ 
+more than solutions of \AstarTwo; 
 for region~$155$, the greedy algorithm yields 
 a solution of cost~$0.372$, while
-the solution of \Astar costs~$0.317$
+the solution of \AstarTwo costs~$0.317$
 (marked in \tab\ref{tab:CostsInDetail}).
@@
 (third-last row in \tab\ref{tab:CostsInDetail})
-obtained by \Astar
+obtained by \AstarTwo
 is shown in \fig\ref{fig:AreaAgg_CaseStudy1_Rg53}.
@@
 	which one can easily deduce.
-	The numbers indicate the numbers of patches.}
+	The numbers indicate the numbers of patches.
+    %
+    In the sequence obtained by \Astar, 
+    the type of the largest polygon on the start map 
+    changed only once, which is good; 
+    while the type of the largest polygon changed twice 
+    in the sequence obtained by the Greedy algorithm.}
 \label{fig:AreaAgg_CaseStudy1_Rg85}
@@
 
-We compare our greedy algorithm, \Astar, and ILP
+We compare the greedy algorithm, \Astar, and ILP
 using~$g_2(\Pnode)$,
@@
 whenever we could not find a solution after 
-having visited~$W=200{,}000$ nodes (see 
-Sec.~\ref{sec:AreaAgg_AStar}).
+having visited~$W=200{,}000$ nodes 
+(see \sect\ref{sec:AreaAgg_AStar}).
 The most time-consuming instance for \Astar was region~$94$,
-for which \Astar took~$111.5\,$s (including repetitions)
+for which \Astar took~$104.1\,$s (including repetitions)
 to find a feasible solution 
@@
 To avoid waiting too long,
-we set the time limit as~$112\,$s 
+we set the time limit to~$100\,$s 
 for our ILP to run on one region.
-Note that the time limit includes
-the time that our ILP uses 
+Note that the time limit included
+the time that our ILP used 
 to set up the variables and constraints
@@
 and~\ref{sub:AreaAgg_Constraints}).
-If no optimal solution is found in this time limit,
-a feasible solution (if found) will be returned.
+If no optimal solution was found in this time limit,
+a feasible solution (if found) would be returned.
 For some large instances, 
-the ILP cannot find any solution.
-
-Using a similar format as in \tab\ref{tab:AreaAgg_CaseStudy1_Statistics},
+the ILP could not find any solution.
+
+Using a similar format as in 
+\tab\ref{tab:AreaAgg_CaseStudy1_Statistics},
 we present the statistics in 
@@
 overestimation:~$5.3\%$ of the regions 
-caused~$92.1\%$ of the total running time.
+caused~$92.3\%$ of the total running time.
 The solutions by \Astar cost~$438.2$ in total, 
@@
 \begin{table*}[tb]
-%\small	
-\centering
-\caption{A comparison of the greedy algorithm and \Astar		
+\caption{A comparison of the greedy algorithm, 
+    the \Astar algorithm, and the ILP-based algorithm		
 	when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
@@
 	%
-	$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
-	and~$\sum g_1$
-	respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
+	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{lgth}$, 
+	and~$\sum g_2$
+	respectively represent the sums of~$g_\mathrm{type}(\Pgoal)$,
 	$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
@@
 %	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
+\centering
+\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
 \setlength{\tabcolsep}{0.7ex}
@@
 \multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
-\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
-\multicolumn{1}{c}{$\sum g_1$} & 
+\multicolumn{1}{c}{$\sum g_\mathrm{lgth}$} & 
+\multicolumn{1}{c}{$\sum g_2$} & 
 \multicolumn{1}{c}{Time (min)} \\ 
@@
 &            &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.0        &858.5           &455.8           &1'2~(41.5\%)\\
-%
-%
-\Astar$_{\!\!200{,}000}$	& 695
+&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
+%
+%
+\AstarTwo	& 695
 & 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
 & 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
-& 52.0 	& 824.5 & 438.2 & 53'6~(91.8\%)	\\
-%
-%
-ILP$_{112\,\mathrm{s}}$		& 453
-& 66~(\parbox{\widthof{$4$}}{$\,$}$9.0\%$)  			 	
+& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
+%
+%
+\ILPOne		& 449
+& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
 &		&				&				
-&		&		&		& 470'4~(26.2\%)\\
-%
-%
-ILP$_{300\,\mathrm{s}}$		& 496
-& 51~(\parbox{\widthof{$4$}}{$\,$}$6.9\%$)  			 	
+&		&		&		& 421'5~(27.3\%) \\
+%
+%
+\ILPTwo		& 475
+& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
 &		&				&				
-&		&		&		& 795'4			\\ 
+&		&		&		& 719'2~(26.4\%) \\ 
 \bottomrule
@@
 the greedy algorithm outperformed \Astar 
-for~$25$ regions~($64.1\%$), 
-which is~$17.2\%$ more comparing to the first experiment.
-%
-The ILP managed to find optimal solutions 
+for~$8$ regions~($20.5\%$), 
+which is~$26.4\%$ less comparing to the first experiment ($46.9\%$).
+%
+\ILPOne managed to find optimal solutions 
 for all the regions with fewer than~$8$ polygons,
 and failed to find optimal solutions
-for any region with more than~$9$ polygons.
+for any region with more than~$8$ polygons.
 In none of the~$39$ regions 
 that \Astar failed to solve optimally
-did the ILP find a feasible solution.
-Overall, the ILP found optimal solutions for~$455$ regions
-and found feasible solutions for~$70$ regions.
+did \ILPOne find a feasible solution.
+Overall, \ILPOne 
+found optimal solutions for~$449$ regions
+and found feasible solutions for~$69$ regions.
 The distributions of these regions are shown in
@@
 and~\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
-There are~$208$ regions for which 
-our ILP failed to find any solution.
-For~$23$ of those regions, 
+There are~$216$ regions for which 
+our \ILPOne failed to find any solution.
+For~$22$ of those regions, 
 we did not have enough main memory 
 to set up the variables and constraints;
-each of these regions has~$20$ polygons at least.
-For~$64$ of those regions, 
-our ILP ran out of the main memory 
+each of these regions has~$21$ polygons at least.
+For~$67$ of those regions, 
+our \ILPOne ran out of the main memory 
 before finding any feasible solution;
@@
 of the main memory at most.
-For~$118$ of the $208$~regions, 
-our ILP failed to find any solution
-during the time limit ($112\,$s);
-these regions have~$9$ to~$14$ polygons.
-For the remaining~$3$ regions, 
-the reason of our ILP's failing is unclear 
+For~$123$ of the $216$~regions, 
+\ILPOne failed to find any solution
+during the time limit;
+these regions have~$9$ to~$13$ polygons.
+For the remaining~$4$ regions, 
+the reason of our ILP's fail is unclear 
 due to the fact that 
 the solver CPLEX is like a black box for us.
-After we increased the time limit to~$300\,$s for each region, 
-the ILP solved~$496$ regions to optimality, which 
-is~$41$ regions more than using the time limit~$112\,$s.
-Every of the~$41$ regions has~$6$ to~$10$ polygons.
+After we increased the time limit to~$200\,$s for each region, 
+\ILPTwo solved~$475$ regions to optimality, which 
+is~$26$ regions more than using \ILPOne.
+Every of the~$26$ regions has~$6$ to~$10$ polygons.
 \fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
@@
 the ILP found optimal, feasible, or no solutions 
-when using the two time limits, i.e., $112\,$s and~$300\,$s.
+when using the two time limits, i.e., $100\,$s and~$200\,$s.
 
@@
 \includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
-\caption{The percentage of regions that are solved 
+\caption{The percentage of regions that were solved 
 	optimally by the greedy algorithm, \Astar, and our ILP.
@@
 	our ILP found optimal, feasible, or no solutions 
-	when using time limits~$112\,$s and~$300\,$s.
+	when using time limits~$100\,$s and~$200\,$s.
 	Using more time, our ILP was able to 
@@
 \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
-In an earlier version of this paper \parencite{Peng2017AStar},
-we tried minimizing type changes 
+In an earlier version of this chapter \parencite{Peng2017AStar},
+we tried a combination of minimizing type changes 
 and maximizing the sum of the smallest compactness values, 
@@
 \label{sec:AreaAgg_Conclusions}
-In this paper, we investigated the problem of 
+In this chapter, we investigated the problem of 
 finding optimal sequences for area aggregation.
@@
 Compared to the greedy algorithm, 
-\Astar reduced the total cost by~$3.9\%$.
+\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
+in the two experiments.
 Although the amount is small, it is worth to use \Astar
-because optimization methods can help us to evaluate the quality 
-of a model \parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
+because optimization methods can help us 
+to evaluate the quality of a model 
+\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
 For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
-even an \emph{optimal} sequence can be problematic. 
-This result makes us realize that our model of minimizing the 
-type change and the compactness has drawbacks.
+even an \emph{optimal} sequence can be bad.
+If it were not for \Astar, 
+we could not tell if the bad result was caused 
+by the greedy algorithm or the model.
+Because of \Astar, we are sure that the bad result is from
+our model of minimizing the 
+type change and the compactness.
 The ILP-based algorithm finds optimal solutions for some regions,
@@
 
-For \Astar, we have a good estimation for the cost of type 
+Our \Astar has a good estimation for the cost of type 
 change, which helps a lot to reduce the search space. 
@@
 First, during the searching we can forget a node of the graph
+(see \fig\ref{fig:AreaAgg_SubdivisionName})
 if all the neighbors of this node have been visited.
@@
 For example, assignment to a given center~$r$ is symmetric, 
-hence
+hence we have
 \begin{equation*}
 \label{eq:CstrZX}
-z_{t,p,q,r}= z_{t,p,q,r} \qquad
+z_{t,p,q,r}= z_{t,q,p,r} \qquad
 \forall t \in {T} \setminus \{1,n\}, 
@@
 the cost of a branch is larger than the upper bound,
-we can ignore this branch  
+we can ignore that branch  
 because it will not yield an optimal solution.
@@
 For example, aggregating 
-farmland with hedge yields an area with type vegetation.
+\emph{farmland} with \emph{hedge} 
+yields an area with type \emph{vegetation}.
 %

### 2019-03-10 area_agg_seq_tsas.tex
added the proof of NP-hardness

@@
 
+\fancyhead[LO]{Finding Optimal Sequences for Area Aggregation}
+
 \begin{document}
-\title{Finding Optimal Sequences for Area Aggregation  
-	---\protect\\ 
-	\Astar vs. Integer Linear Programming}
+\title{Finding Optimal Sequences for Area Aggregation---\protect\\ 
+	\Astar vs. Integer Linear Programming
+    }
 %\titlenote{Produces the permission block, and
@@
 and then derive maps at smaller scales by 
-\emph{map generalization}
+\emph{map generalization}.
 More specifically, 
@@
 
-In this chapter, we try to find an optimal sequence
+In this paper, we try to find an optimal sequence
 to aggregate the land-cover areas on the start map
@@
 (\sect\ref{sec:AreaAgg_Preliminaries}).
+We prove that our problem is NP-hard
+(\sect\ref{sec:AreaAgg_NP-hardness}).
 We define our cost functions in 
@@
 
-We do not deal with simplifying polylines in this chapter.
+We do not deal with simplifying polylines in this paper.
 The simplification can be handled separately from the
@@
 \mypar{Model}
-We consider a directed graph $G$, 
+We consider a directed graph $G_\mathrm{S}$, 
 which we call the \emph{subdivision graph} 
 (see \fig\ref{fig:AreaAgg_SubdivisionName}). 
-The node set $V$ of~$G$ contains a node for every
-possible map (or \emph{subdivision}), including the start map, all
-possible intermediate-scale maps, and the goal map.
-The arc set~$E$ of~$G$ contains an arc $(\Pnode, P_{t+1,j})$ 
-between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V$ 
+The node set $V_\mathrm{S}$ of~$G_\mathrm{S}$ 
+contains a node for every
+possible map (or \emph{subdivision}), including the start map, 
+all possible intermediate-scale maps, and the goal map.
+The arc set~$E_\mathrm{S}$ of~$G_\mathrm{S}$ 
+contains an arc $(\Pnode, P_{t+1,j})$ 
+between any two maps~$\Pnode$ and~$P_{t+1,j}$ in~$V_\mathrm{S}$ 
 if~$P_{t+1,j}$ can be reached from~$\Pnode$ 
@@
 involving a smallest area.
-Then, any directed path in~$G$ from the start map to the goal map
+Then, any directed path in~$G_\mathrm{S}$ 
+from the start map to the goal map
 defines a possible aggregation sequence.
@@
 Moreover, putting the idea to practice is far from trivial 
-since graph~$G$ can be huge as we will argue later.
+since graph~$G_\mathrm{S}$ can be huge as we will argue later.
 We compare a greedy algorithm, \Astar, and an ILP-based algorithm
@@
 \includegraphics[page=3]{AreaAgg_Preliminaries}
-\caption{The subdivision graph~$G$. 
+\caption{The subdivision graph~$G_\mathrm{S}$. 
 	The nodes of the graph are the subdivisions. 
@@
 
+Sometimes, we need a graph to represent the adjacencies of
+the land-cover areas in a subdivision,
+we call such a graph $G_\mathrm{A}$
+(see \fig\ref{fig:AreaAgg_Variables_Graph}).
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=3]{AreaAgg_ILP}
+\caption{The graph of a subdivision.
+	Each polygon of the subdivision is represented as a node 
+	in the graph.
+	There is an edge between two nodes
+	if the corresponding two polygons are adjacent.
+}
+\label{fig:AreaAgg_Variables_Graph}
+\end{figure}
+
 \mypar{Exponential lower bound}
-We now analyze the size of subdivision graph~$G$.
+We now analyze the size of subdivision graph~$G_\mathrm{S}$.
 Our analysis is inspired by \textcite{Keane1975Size},
@@
 has an exponential lower bound.
+
+\section{NP-hardness Proof}
+\label{sec:AreaAgg_NP-hardness}
+
+Although we have shown that the graph of subdivisions
+has an exponential size,
+one may develop a clever algorithm 
+to find an optimal sequence efficiently.
+In the following, we prove that 
+finding such a sequence is indeed NP-hard.
+In the proof, we neglect the cost of compactness or the cost of length.
+Considering one of the two costs 
+will make the finding even more difficult.
+
+\newtheorem{thm}{Theorem}
+\begin{thm}
+\textsc{AreaAggregationSequence} is NP-hard 
+even if we only consider the cost of type change.
+\end{thm}
+
+\begin{proof}
+Our NP-hardness proof is by reduction from 
+the NP-complete problem \textsc{PlanarVertexCover}, 
+which is to decide, for a given 
+planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
+whether there exists a vertex cover 
+with at most a given number~$k_\mathrm{A}$ of vertices. 
+For an instance of \textsc{PlanarVertexCover}
+(\fig\ref{fig:AreaAgg_Reduction}a), 
+we define a corresponding instance of \textsc{AreaAggregationSequence}
+whose start map consists of red, black, and white areas and 
+whose goal map consists of only one large red patch.
+The adjacency graphs of the two maps are illustrated 
+in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
+where the colors of the vertices represent 
+the colors of the corresponding areas.
+More precisely, for each vertex of~$G_\mathrm{A}$
+in \fig\ref{fig:AreaAgg_Reduction}a, 
+we define a red vertex and a black vertex, 
+which we connect with an edge. 
+For each edge of~$G_\mathrm{A}$, 
+we define two white vertices and 
+connect them with the two black vertices
+(\fig\ref{fig:AreaAgg_Reduction}b).
+
+\begin{figure}[h]
+\centering
+\includegraphics[page=1]{AreaAgg_NPHard}
+\caption{The reduction for our NP-hardness proof.
+    The dashed polygon in (c) shows 
+    that the vertices are merged.}
+\label{fig:AreaAgg_Reduction}
+\end{figure}
+
+We define the weights of the vertices 
+in \fig\ref{fig:AreaAgg_Reduction}b as follows:
+\begin{itemize}
+\item Every white vertex has weight~$1$.
+\item Every black vertex has weight~$2$.
+\item Every red vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
+which is equal to the total weight of all white and black vertices.
+\end{itemize}
+Since in each aggregation step, 
+we require the smallest area to be aggregated with one of its neighbors, 
+our definition of the weights to a certain degree determines 
+the order in which the vertices are selected:
+\begin{itemize}
+\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
+a white vertex is selected and merged with one of its neighbors, 
+such that the white vertex receives the neighbor's color or vice versa.
+\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
+a non-red vertex is selected and merged with one of its neighbors.
+\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
+\end{itemize}
+
+To complete the reduction, 
+we need to define the costs of color changes. 
+For any color change, 
+we charge one unit of cost per unit weight.
+Due to our construction, Phases II and III can be accomplished with
+a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
+no matter how Phase I is accomplished.
+This is because, after Phase I, 
+every non-red patch will be adjacent to a red patch (vertex).
+Thus, if any non-red patch becomes selected in Phase II, 
+it can aggregate with a red patch (vertex) and 
+receive the color red. 
+This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
+(which is equal to the total weight of 
+all initially white and black vertices) and, 
+since after Phase II all patches are red, 
+Phase III does not cause any additional cost.  
+It is also clear that 
+there is no cheaper way to accomplish Phases II and III,
+since it is impossible to color a vertex red in Phase I.
+Consequently, since the total cost of Phases II and III is fixed, 
+it is only interesting to ask 
+at which cost Phase I can be accomplished.
+It turns out that, if $G_\mathrm{A}$ 
+has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
+then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
+only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
+need to change their color from black to white, and 
+each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
+To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
+then the corresponding instance of \textsc{AreaAggregationSequence} 
+has a solution of 
+total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
+
+It remains to be shown that, 
+if $C_\mathrm{A}^*$ is a minimum vertex cover of $G_\mathrm{A}$, 
+then there is no solution with total cost 
+less than $2|C_\mathrm{A}^*|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
+To see why, we assume that such a solution exists.
+If we keep the black color of a vertex from $C_\mathrm{A}^*$ 
+(the total cost decreases by $2$),
+then we will need to at least change two white vertices
+to black vertices
+(the total cost increases by $2$ at least).
+Therefore, we have found a contradiction to our assumption.
+
+\begin{figure}[h]
+\centering
+\includegraphics[page=2]{AreaAgg_NPHard}
+\caption{The situation after Phase I has been conducted 
+    such that all black vertices corresponding to a vertex cover 
+    of~$G_\mathrm{A}$ have been recolored white.
+    The dashed polygons show that the vertices are merged.}
+\label{fig:reduction2}
+\end{figure}
+\end{proof}
 
@@
 A metric distance is symmetric, 
-which is different from the non-symmetric one used in
+which is different from the asymmetric one used in
 \textcite{Dilo2009tGAP}.
@@
 can be exponential.
-That is to say, the graph~$G$---our search space---can 
+That is to say, the graph~$G_\mathrm{S}$---our search space---can 
 be of exponential size.
@@
 we have visited a predefined number, 
-say,~$W$ of nodes of graph~$G$,
+say,~$W$ of nodes of graph~$G_\mathrm{S}$,
 then we restart.
@@
 since we aggregate step by step.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=3]{AreaAgg_ILP}
-\caption{The graph of a subdivision.
-	Each polygon of the subdivision is represented as a node 
-	in the graph.
-	There is an edge between two nodes
-	if the corresponding two polygons are adjacent.
-}
-\label{fig:AreaAgg_Variables_Graph}
-\end{figure}
 
@@
     about land-cover types can be found at 
-	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
+%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
 	Accessed: Nov 1, 2017.}
@@
 the greedy algorithm visited 
-fewer nodes and arcs in graph~$G$ 
+fewer nodes and arcs in graph~$G_\mathrm{S}$ 
 and used much less time.
@@
 \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
-In an earlier version of this chapter \parencite{Peng2017AStar},
+In an earlier version of this paper \parencite{Peng2017AStar},
 we tried a combination of minimizing type changes 
@@
 \label{sec:AreaAgg_Conclusions}
-In this chapter, we investigated the problem of 
+In this paper, we investigated the problem of 
 finding optimal sequences for area aggregation.

### 2019-03-17 area_agg_seq_tsas.tex
addressed the comments from TSAS

@@
 based on global optimization.
+We have proved that this problem is NP-hard.
 We formalize this optimization problem as that of 
@@
 e.g., \textcite{Suba2016Road} state.
-
-CMG has received a lot of attention
+We believe that digital maps will eventually 
+achieve smooth changes for zooming,
+and CMG is an effective way to realize smooth changes.
+
+\mypar{Problem definition}
+In this paper, we deal with CMG of land-cover areas.
+The land-cover area is of significant importance on maps.
+When users zoom out, some land-cover areas become
+too tiny to be seen, which result in visual clutter.
+In order to provide users 
+with good visual experience during zooming operations,
+we propose to remove these tiny areas.
+We plan to achieve this goal by 
+aggregating them into neighboring land-cover areas.
+A \emph{land-cover map} is a planar subdivision in which 
+each area belongs to a land-cover class or \emph{type}.
+Suppose that there are two land-cover maps of different scales 
+that cover the same spatial region.
+We consider the problem of finding a sequence 
+of small incremental changes that gradually transforms 
+the larger-scale map (the \emph{start map}) to 
+the smaller-scale map (the \emph{goal map}).
+We use this sequence to generate and show land-cover maps at 
+intermediate scales (see \fig\ref{fig:AreaAgg_example}).
+In this way, we try to avoid large and discrete changes
+during zooming.
+
+\begin{figure}[tb]
+\centering
+\includegraphics{AreaAgg_example}
+\caption{The input and a possible output of an aggregation sequence 
+	for an instance of our problem}
+\label{fig:AreaAgg_example}
+\end{figure}
+
+With the same motivation, 
+a strategy of hierarchical schemes has been proposed.
+This strategy generalizes a more-detailed representation 
+to obtain a less-detailed representation 
+based on small incremental changes, 
+e.g., the Generalized Area Partitioning tree (GAP-tree).
+This tree can be constructed if only the larger-scale map is given
+\citep{vanOosterom1995Development} 
+or if both the larger-scale map and the smaller-scale map 
+are given \citep{HaunertDilo2009}.
+Typically, the next change in such a sequence 
+is determined locally, in a greedy fashion.  
+If we insist on finding a sequence that is optimal 
+according to some global measure,
+the problem becomes complicated.
+
+We assume that there exist many-to-one relationships between the 
+areas of the
+start map and the areas of the goal map.
+This assumption is based on the fact that many algorithms 
+\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
+vanSmaalen2003,Oehrlein2017Aggregation}
+that aggregate land-cover areas
+result in many-to-one relationships.
+Their inputs and generalized results together
+can be used as our inputs.
+We term the areas of the goal map \emph{regions}.
+That is, every region is the union of a set of areas 
+on the start map.
+The type of a region may differ from the types of its 
+components. 
+For example, a small water area together with 
+multiple adjacent forest areas may constitute 
+a large forest region on the smaller-scale map.
+However, we assume that every region, on the goal map, 
+contains at least one area of the same type on the start map.
+Our assumptions hold if the goal map has been produced 
+with an automatic method for area aggregation, 
+for example, by the method of \citet{HaunertWolff2010AreaAgg}.
+That method produces a land-cover map at a single smaller scale, 
+given a land-cover map at a larger scale.
+Although \textcite{HaunertWolff2010AreaAgg}
+attain results of high quality, 
+they do not produce land-cover maps at intermediate scales.
+
+In this paper, we try to find an optimal sequence
+to aggregate the land-cover areas on the start map
+one by one until we arrive the goal map.
+We first independently deal with each region of the goal map 
+(with its components on the start map).
+Once we have found an aggregation sequence for each region, 
+we integrate all the sequences into an overall sequence,
+which transforms the start map into the goal map. 
+Our aggregation sequence may be cooperated with
+the GAP-face tree \citep{vanOosterom2005},
+the map cube model \citep{Timpf1998},
+or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
+to support on-the-fly visualization.
+Smoothly (dis-)appearing areas can be realized
+by integrating our results into the \emph{space-scale cube}
+\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.
+
+\mypar{Contribution}
+We formally define our problem, 
+introduce the basic concepts of our method, 
+and analyze the size of our model in a worst-case scenario
+(\sect\ref{sec:AreaAgg_Preliminaries}).
+We define our cost functions in 
+\sect\ref{sec:AreaAgg_CostFunctions}.
+We prove that our problem is NP-hard
+(\sect\ref{sec:AreaAgg_NP-hardness}).
+Then, we develop and compare three methods 
+for finding aggregation sequences.
+First, we present 
+a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
+Second, we develop a new global optimization approach
+based on the \Astar algorithm 
+(\sect\ref{sec:AreaAgg_AStar}).
+Third, we model our pathfinding problem as
+an \emph{integer linear program} (ILP), 
+and then we solve this program with minimizing our cost function.
+Our ILP uses binary (0--1) variables. 
+These variables help us to model our problem, 
+but in general, it is NP-hard 
+to solve an ILP optimally.
+By comparing with the greedy algorithm, 
+which is used as a benchmark,
+we are able to see whether it is worth 
+to use \Astar or the ILP-based algorithm, 
+which are more complex and slower.  
+Our case study 
+uses a dataset of the German topographic database ATKIS 
+(\sect\ref{sec:AreaAgg_CaseStudy}).
+In the conclusions, we show possible ways to improve our 
+methods in \sect\ref{sec:AreaAgg_Conclusions}.
+
+We do not deal with simplifying polylines in this paper.
+The simplification can be handled separately from the
+aggregation of areas, for example, 
+by using one method of 
+\textcite{Douglas1973},
+\textcite{Saalfeld1999},
+or \textcite{Wu2004DP}.
+Those methods can be used to set up 
+the binary line generalisation tree (BLG-tree) of
+\textcite{vanOosterom1995Development},
+which is a hierarchical data structure that 
+defines a gradual line simplification process.
+%
+Although splitting polygons is a good step
+of generalizing land-cover areas,
+we do not integrate it into our method at this moment.
+Some examples of splitting are as follows.
+\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
+proposed to split tiny polygons 
+and then to merge the split parts into the neighboring polygons.
+\textcite{Meijers2016Split} developed an algorithm 
+to split a polygon (the splittee) 
+based on a constrained Delaunay triangulation.
+During splitting, their algorithm is capable of
+taking into account
+the attractivenesses between the splittee and its neighbors.
+When merging, a more attractive neighbor 
+will get a larger portion from the splittee.
+
+\section{Related Work}
+
+\subsection{Continuous map generalization}
+
+\emph{Continuous map generalization} (CMG)
+has received a lot of attention
 from cartographers and computer scientists.
@@
 
-\mypar{Optimization in map generalization}
+\subsection{Optimization in map generalization}
+
 Map generalization generally specifies 
@@
 on small instances.
-
-\begin{figure}[tb]
-\centering
-\includegraphics{AreaAgg_example}
-\caption{The input and a possible output 
-	for an instance of 	our problem}
-\label{fig:AreaAgg_example}
-\end{figure}
 
@@
 
-\mypar{Optimization in \emph{continuous} map generalization}
+\subsection{Optimization in \emph{continuous} map generalization}
+
 Optimization becomes more delicate
@@
 
-\mypar{Problem definition}
-The land-cover area is of significant importance on maps.
-When users zoom out, some land-cover areas become
-too tiny to be seen, which result in visual clutter.
-In order to provide users 
-with good visual experience during zooming operations,
-we propose to remove these tiny areas.
-We plan to achieve this goal by 
-aggregating them into neighboring land-cover areas.
-A \emph{land-cover map} is a planar subdivision in which 
-each area belongs to a land-cover class or \emph{type}.
-Suppose that there are two land-cover maps of different scales 
-that cover the same spatial region.
-We consider the problem of finding a sequence 
-of small incremental changes that gradually transforms 
-the larger-scale map (the \emph{start map}) to 
-the smaller-scale map (the \emph{goal map}).
-We use this sequence to generate and show land-cover maps at 
-intermediate scales (see \fig\ref{fig:AreaAgg_example}).
-In this way, we try to avoid large and discrete changes
-during zooming.
-
-With the same motivation, 
-a strategy of hierarchical schemes has been proposed.
-This strategy generalizes a more-detailed representation 
-to obtain a less-detailed representation 
-based on small incremental changes, 
-e.g., the Generalized Area Partitioning tree (GAP-tree).
-This tree can be constructed if only the larger-scale map is given
-\citep{vanOosterom1995Development} 
-or if both the larger-scale map and the smaller-scale map 
-are given \citep{HaunertDilo2009}.
-Typically, the next change in such a sequence 
-is determined locally, in a greedy fashion.  
-If we insist on finding a sequence that is optimal 
-according to some global measure,
-the problem becomes complicated.
-
-We assume that there exist many-to-one relationships between the 
-areas of the
-start map and the areas of the goal map.
-This assumption is based on the fact that many algorithms 
-\parencite[e.g.,][]{HaunertWolff2010AreaAgg,
-vanSmaalen2003,Oehrlein2017Aggregation}
-that aggregate land-cover areas
-result in many-to-one relationships.
-Their inputs and generalized results together
-can be used as our inputs.
-We term the areas of the goal map \emph{regions}.
-That is, every region is the union of a set of areas 
-on the start map.
-The type of a region may differ from the types of its 
-components. 
-For example, a small water area together with 
-multiple adjacent forest areas may constitute 
-a large forest region on the smaller-scale map.
-However, we assume that every region, on the goal map, 
-contains at least one area of the same type on the start map.
-Our assumptions hold if the goal map has been produced 
-with an automatic method for area aggregation, 
-for example, by the method of \citet{HaunertWolff2010AreaAgg}.
-That method produces a land-cover map at a single smaller scale, 
-given a land-cover map at a larger scale.
-Although \textcite{HaunertWolff2010AreaAgg}
-attain results of high quality, 
-they do not produce land-cover maps at intermediate scales.
-
-In this paper, we try to find an optimal sequence
-to aggregate the land-cover areas on the start map
-one by one until we arrive the goal map.
-We first independently deal with each region of the goal map 
-(with its components on the start map).
-Once we have found an aggregation sequence for each region, 
-we integrate all the sequences into an overall sequence,
-which transforms the start map into the goal map. 
-Our aggregation sequence may be cooperated with
-the GAP-face tree \citep{vanOosterom2005},
-the map cube model \citep{Timpf1998},
-or ScaleMaster \citep{Brewer2007Guidelines,Touya2013ScaleMaster}, 
-to support on-the-fly visualization.
-Smoothly (dis-)appearing areas can be realized
-by integrating our results into the \emph{space-scale cube}
-\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.
-
-\mypar{Contribution}
-We formally define our problem, 
-introduce the basic concepts of our method, 
-and analyze the size of our model in a worst-case scenario
-(\sect\ref{sec:AreaAgg_Preliminaries}).
-We prove that our problem is NP-hard
-(\sect\ref{sec:AreaAgg_NP-hardness}).
-We define our cost functions in 
-\sect\ref{sec:AreaAgg_CostFunctions}.
-Then, we compare three methods for finding aggregation sequences.
-First, we develop 
-a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
-Second, we present a new global optimization approach
-based on the \Astar algorithm 
-(\sect\ref{sec:AreaAgg_AStar}).
-Third, we model our pathfinding problem as
-an \emph{integer linear program} (ILP), 
-and then we solve this program with minimizing our cost function.
-Our ILP uses binary (0--1) variables. 
-These variables help us to model our problem, 
-but in general, it is NP-hard 
-to solve an ILP optimally.
-By comparing with the greedy algorithm, 
-which is used as a benchmark,
-we are able to see whether it is worth 
-to use \Astar or the ILP-based algorithm, 
-which are more complex and slower.  
-Our case study 
-uses a dataset of the German topographic database ATKIS 
-(\sect\ref{sec:AreaAgg_CaseStudy}).
-In the conclusions, we show possible ways to improve our 
-methods in \sect\ref{sec:AreaAgg_Conclusions}.
-
-We do not deal with simplifying polylines in this paper.
-The simplification can be handled separately from the
-aggregation of areas, for example, 
-by using one method of 
-\textcite{Douglas1973},
-\textcite{Saalfeld1999},
-or \textcite{Wu2004DP}.
-Those methods can be used to set up 
-the binary line generalisation tree (BLG-tree) of
-\textcite{vanOosterom1995Development},
-which is a hierarchical data structure that 
-defines a gradual line simplification process.
-%
-Although splitting polygons is a good step
-of generalizing land-cover areas,
-we do not integrate it into our method at this moment.
-Some examples of splitting are as follows.
-\textcite{Smith2007MasterMap,Thiemann2018LandCover} 
-proposed to split tiny polygons 
-and then to merge the split parts into the neighboring polygons.
-\textcite{Meijers2016Split} developed an algorithm 
-to split a polygon (the splittee) 
-based on a constrained Delaunay triangulation.
-During splitting, their algorithm is capable of
-taking into account
-the attractivenesses between the splittee and its neighbors.
-When merging, a more attractive neighbor 
-will get a larger portion from the splittee.
-
 \section{Preliminaries}
@@
 More precisely, in each step the smallest area~$u$ is merged 
-with one of its neighbors (adjacent areas)~$v$
+with one of its neighbors~$v$ 
+($v$ does not have to be the smallest neighbor)
 such that~$u$ and~$v$ are replaced by their union.
@@
 
-\section{NP-hardness Proof}
-\label{sec:AreaAgg_NP-hardness}
-
-Although we have shown that the graph of subdivisions
-has an exponential size,
-one may develop a clever algorithm 
-to find an optimal sequence efficiently.
-In the following, we prove that 
-finding such a sequence is indeed NP-hard.
-In the proof, we neglect the cost of compactness or the cost of length.
-Considering one of the two costs 
-will make the finding even more difficult.
-
-\newtheorem{thm}{Theorem}
-\begin{thm}
-\textsc{AreaAggregationSequence} is NP-hard 
-even if we only consider the cost of type change.
-\end{thm}
-
-\begin{proof}
-Our NP-hardness proof is by reduction from 
-the NP-complete problem \textsc{PlanarVertexCover}, 
-which is to decide, for a given 
-planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
-whether there exists a vertex cover 
-with at most a given number~$k_\mathrm{A}$ of vertices. 
-For an instance of \textsc{PlanarVertexCover}
-(\fig\ref{fig:AreaAgg_Reduction}a), 
-we define a corresponding instance of \textsc{AreaAggregationSequence}
-whose start map consists of red, black, and white areas and 
-whose goal map consists of only one large red patch.
-The adjacency graphs of the two maps are illustrated 
-in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
-where the colors of the vertices represent 
-the colors of the corresponding areas.
-More precisely, for each vertex of~$G_\mathrm{A}$
-in \fig\ref{fig:AreaAgg_Reduction}a, 
-we define a red vertex and a black vertex, 
-which we connect with an edge. 
-For each edge of~$G_\mathrm{A}$, 
-we define two white vertices and 
-connect them with the two black vertices
-(\fig\ref{fig:AreaAgg_Reduction}b).
-
-\begin{figure}[h]
-\centering
-\includegraphics[page=1]{AreaAgg_NPHard}
-\caption{The reduction for our NP-hardness proof.
-    The dashed polygon in (c) shows 
-    that the vertices are merged.}
-\label{fig:AreaAgg_Reduction}
-\end{figure}
-
-We define the weights of the vertices 
-in \fig\ref{fig:AreaAgg_Reduction}b as follows:
-\begin{itemize}
-\item Every white vertex has weight~$1$.
-\item Every black vertex has weight~$2$.
-\item Every red vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
-which is equal to the total weight of all white and black vertices.
-\end{itemize}
-Since in each aggregation step, 
-we require the smallest area to be aggregated with one of its neighbors, 
-our definition of the weights to a certain degree determines 
-the order in which the vertices are selected:
-\begin{itemize}
-\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
-a white vertex is selected and merged with one of its neighbors, 
-such that the white vertex receives the neighbor's color or vice versa.
-\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
-a non-red vertex is selected and merged with one of its neighbors.
-\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
-\end{itemize}
-
-To complete the reduction, 
-we need to define the costs of color changes. 
-For any color change, 
-we charge one unit of cost per unit weight.
-Due to our construction, Phases II and III can be accomplished with
-a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
-no matter how Phase I is accomplished.
-This is because, after Phase I, 
-every non-red patch will be adjacent to a red patch (vertex).
-Thus, if any non-red patch becomes selected in Phase II, 
-it can aggregate with a red patch (vertex) and 
-receive the color red. 
-This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
-(which is equal to the total weight of 
-all initially white and black vertices) and, 
-since after Phase II all patches are red, 
-Phase III does not cause any additional cost.  
-It is also clear that 
-there is no cheaper way to accomplish Phases II and III,
-since it is impossible to color a vertex red in Phase I.
-Consequently, since the total cost of Phases II and III is fixed, 
-it is only interesting to ask 
-at which cost Phase I can be accomplished.
-It turns out that, if $G_\mathrm{A}$ 
-has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
-then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
-only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
-need to change their color from black to white, and 
-each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
-To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
-then the corresponding instance of \textsc{AreaAggregationSequence} 
-has a solution of 
-total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
-
-It remains to be shown that, 
-if $C_\mathrm{A}^*$ is a minimum vertex cover of $G_\mathrm{A}$, 
-then there is no solution with total cost 
-less than $2|C_\mathrm{A}^*|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
-To see why, we assume that such a solution exists.
-If we keep the black color of a vertex from $C_\mathrm{A}^*$ 
-(the total cost decreases by $2$),
-then we will need to at least change two white vertices
-to black vertices
-(the total cost increases by $2$ at least).
-Therefore, we have found a contradiction to our assumption.
-
-\begin{figure}[h]
-\centering
-\includegraphics[page=2]{AreaAgg_NPHard}
-\caption{The situation after Phase I has been conducted 
-    such that all black vertices corresponding to a vertex cover 
-    of~$G_\mathrm{A}$ have been recolored white.
-    The dashed polygons show that the vertices are merged.}
-\label{fig:reduction2}
-\end{figure}
-\end{proof}
-
 \section{Cost Functions}
@@
 if it is more compact (less clutter).
+In this paper, we ignore the fact that
+some features may inherently take linear forms
+(e.g., rivers).
 %
@@
 i.e., the compactness value for a patch, say,~$u$ is
-\begin{equation*}
+\begin{equation}
 \label{eq:comp}
 c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
-\end{equation*}
+\end{equation}
 where~$A_u$ and~$l_u$ are 
@@
 \label{sec:AreaAgg_Combining}
-In order to minimize the type change 
-and maximize the compactness,
-we combine the two cost functions as
+
+When we generate a sequence of intermediate-scale maps,
+we want to change the types of the land-cover areas 
+as little as possible
+and want to have compact land-cover areas.
+Therefore, we combine 
+the cost of type change (\eq\ref{eq:g_type})
+and the cost of compactness (\eq\ref{eq:g_comp}).
+That is,
 \begin{equation}
@@
 As said before, we want to make a comparison involving
-integer linear programming.
-Therefore, we also introduce a combination
-that can be computed linearly. That is,
+integer linear programming 
+while our cost of compactness (see \eq\ref{eq:comp})
+cannot be computed linearly in an integer linear program.
+Therefore, we combine 
+the cost of type change (\eq\ref{eq:g_type})
+and the cost of length (\eq\ref{eq:g_length}),
+which can be computed linearly in an integer linear program. 
+That is,
 \begin{equation}
@@
 We compare the greedy algorithm, \Astar, and an ILP-based 
-algorithm using $g_2$.
+algorithm using~$g_2$.
+
+\section{NP-hardness Proof}
+\label{sec:AreaAgg_NP-hardness}
+
+Although we have shown that the graph of subdivisions
+has an exponential size
+(see \sect\ref{sec:AreaAgg_Preliminaries}),
+one may develop a clever algorithm 
+to find an optimal sequence efficiently.
+In the following, we prove that 
+finding such a sequence is indeed NP-hard.
+In the proof, we neglect the cost of compactness or the cost of length.
+Considering one of the two costs 
+will make the finding even more difficult.
+
+\newtheorem{thm}{Theorem}
+\begin{thm}
+\textsc{AreaAggregationSequence} is NP-hard 
+even if we only consider the cost of type change.
+\end{thm}
+
+\begin{proof}
+Our NP-hardness proof is by reduction from 
+the NP-complete problem \textsc{PlanarVertexCover}, 
+which is to decide, for a given 
+planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
+whether there exists a vertex cover 
+with at most a given number~$k_\mathrm{A}$ of vertices. 
+For an instance of \textsc{PlanarVertexCover}
+(\fig\ref{fig:AreaAgg_Reduction}a), 
+we define a corresponding instance of \textsc{AreaAggregationSequence}
+whose start map consists of gray, black, and white areas and 
+whose goal map consists of only one large gray patch.
+The adjacency graphs of the two maps are illustrated 
+in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
+where the colors of the vertices represent 
+the colors of the corresponding areas.
+More precisely, for each vertex of~$G_\mathrm{A}$
+in \fig\ref{fig:AreaAgg_Reduction}a, 
+we define a gray vertex and a black vertex, 
+which we connect with an edge. 
+For each edge of~$G_\mathrm{A}$, 
+we define two white vertices and 
+connect them with the two black vertices
+(\fig\ref{fig:AreaAgg_Reduction}b).
+
+\begin{figure}[h]
+\centering
+\includegraphics[page=1]{AreaAgg_NPHard}
+\caption{The reduction for our NP-hardness proof.
+    The dashed polygon in (c) shows 
+    that the vertices are merged.}
+\label{fig:AreaAgg_Reduction}
+\end{figure}
+
+We define the weights of the vertices 
+in \fig\ref{fig:AreaAgg_Reduction}b as follows:
+\begin{itemize}
+\item Every white vertex has weight~$1$.
+\item Every black vertex has weight~$2$.
+\item Every gray vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
+which is equal to the total weight of all white and black vertices.
+\end{itemize}
+Since in each aggregation step, 
+we require the smallest area to be aggregated with one of its neighbors, 
+our definition of the weights to a certain degree determines 
+the order in which the vertices are selected:
+\begin{itemize}
+\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
+a white vertex is selected and merged with one of its neighbors, 
+such that the white vertex receives the neighbor's color or vice versa.
+\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
+a non-gray vertex is selected and merged with one of its neighbors.
+\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
+\end{itemize}
+
+To complete the reduction, 
+we need to define the costs of color changes. 
+For any color change, 
+we charge one unit of cost per unit weight.
+Due to our construction, Phases II and III can be accomplished with
+a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
+no matter how Phase I is accomplished.
+This is because, after Phase I, 
+every non-gray patch will be adjacent to a gray patch (vertex).
+Thus, if any non-gray patch becomes selected in Phase II, 
+it can aggregate with a gray patch (vertex) and 
+receive the color gray. 
+This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
+(which is equal to the total weight of 
+all initially white and black vertices) and, 
+since after Phase II all patches are gray, 
+Phase III does not cause any additional cost.  
+It is also clear that 
+there is no cheaper way to accomplish Phases II and III,
+since it is impossible to color a vertex gray in Phase I.
+Consequently, since the total cost of Phases II and III is fixed, 
+it is only interesting to ask 
+at which cost Phase I can be accomplished.
+It turns out that, if $G_\mathrm{A}$ 
+has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
+then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
+only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
+need to change their color from black to white, and 
+each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
+To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
+then the corresponding instance of \textsc{AreaAggregationSequence} 
+has a solution of 
+total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
+
+It remains to be shown that, 
+if $C_\mathrm{A}^*$ is a minimum vertex cover of $G_\mathrm{A}$, 
+then there is no solution with total cost 
+less than $2|C_\mathrm{A}^*|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.
+To see why, we assume that such a solution exists.
+If we keep the black color of a vertex from $C_\mathrm{A}^*$ 
+(the total cost decreases by $2$),
+then we will need to at least change two white vertices
+to black vertices
+(the total cost increases by $2$ at least).
+Therefore, we have found a contradiction to our assumption.
+
+\begin{figure}[h]
+\centering
+\includegraphics[page=2]{AreaAgg_NPHard}
+\caption{The situation after Phase I has been conducted 
+    such that all black vertices corresponding to a vertex cover 
+    of~$G_\mathrm{A}$ have been recolored white.
+    The dashed polygons show that the vertices are merged.}
+\label{fig:reduction2}
+\end{figure}
+\end{proof}
 
@@
 	and integer linear programming (b).
+    In (a), any point in the gray area is a feasible solution;
+    in (b), only the gray points are feasible solutions.
 }
@@
 	of region~$53$ obtained by \Astar 
-	using costs of type change and compactness.		 
+	using the costs of type change and compactness.		 
 	The numbers indicate the numbers of patches.		
@@
 and~\ref{sec:AreaAgg_CaseStudy2}),
-region~$358$
-(marked in \tab\ref{tab:CostsInDetail})
+region~$358$ (marked in \tab\ref{tab:CostsInDetail})
 is the largest one.
@@
 	The numbers indicate the numbers of patches.
+    The step from $8$ patches to $7$ patches 
+    when using cost function~$g1$ is a bad move; see figure (b). 
+    Instead, we expect the result of figure (a). 
+    Using cost function~$g2$, we had a similar problem. 
+    The subdivision with $7$ patches is such an example, 
+    where we expect the result of figure (c).
 }

### 2019-03-22 area_agg_seq_tsas.tex
added discussion about DAGs; several improvements

@@
 }
-\email{dongliang.peng@uni-wuerzburg.de}
+\email{www1.informatik.uni-wuerzburg.de/peng}
 
@@
 We assume that the two input maps consist of polygons 
-each of which belongs to a given land-cover class. 
+each of which belongs to a given land-cover type. 
 Every polygon on the smaller-scale map
@@
 
-We assume that there exist many-to-one relationships between the 
-areas of the
-start map and the areas of the goal map.
+We assume that there exist many-to-one relationships 
+between the areas of the start map and the areas of the goal map.
 This assumption is based on the fact that many algorithms 
@@
 vanSmaalen2003,Oehrlein2017Aggregation}
-that aggregate land-cover areas
-result in many-to-one relationships.
+result in many-to-one relationships
+when aggregating land-cover areas.
 Their inputs and generalized results together
 can be used as our inputs.
+However, we should not use those algorithms
+to generate a sequence of maps at different scales, 
+because those algorithms do not take into account 
+the consistence of the generated maps.
 We term the areas of the goal map \emph{regions}.
@@
 on the start map.
-The type of a region may differ from the types of its 
-components. 
+The type of a region may differ from the types of its components. 
 For example, a small water area together with 
@@
 attain results of high quality, 
-they do not produce land-cover maps at intermediate scales.
+they do not produce a sequence land-cover maps.
 
@@
 we integrate all the sequences into an overall sequence,
-which transforms the start map into the goal map. 
+which transforms the start map into the goal map
+(see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
 Our aggregation sequence may be cooperated with
@@
 
+\begin{figure*}[tb]
+\centering
+\includegraphics[page=2]{AreaAgg_Preliminaries}
+\caption{Integrating two aggregation sequences 
+	of different regions: 
+	the resulting sequence contains the given sequences 
+	as subsequences and 
+	always takes the subdivision with smallest patch next.
+	The gray arrows show the integration of the two regions.
+}
+\label{fig:AreaAgg_IntegrateSequence}
+\end{figure*}
+
 \mypar{Contribution}
-We formally define our problem, 
-introduce the basic concepts of our method, 
-and analyze the size of our model in a worst-case scenario
+We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
+Then, we formally model our problem, 
+analyze the size of our model in a worst-case scenario,
+introduce our methods,
+and present the basic concepts of our method
 (\sect\ref{sec:AreaAgg_Preliminaries}).
-We define our cost functions in 
-\sect\ref{sec:AreaAgg_CostFunctions}.
+We define our cost functions 
+(\sect\ref{sec:AreaAgg_CostFunctions}).
 We prove that our problem is NP-hard
@@
 an \emph{integer linear program} (ILP), 
-and then we solve this program with minimizing our cost function.
+and we solve this ILP with minimizing our cost function
+(\sect\ref{sec:AreaAgg_ILP}).
 Our ILP uses binary (0--1) variables. 
@@
 In the conclusions, we show possible ways to improve our 
-methods in \sect\ref{sec:AreaAgg_Conclusions}.
+methods (\sect\ref{sec:AreaAgg_Conclusions}).
 
@@
 \section{Related Work}
+\label{sec:AreaAgg_RelatedWork}
 
@@
 is the only region on the goal map.
-\begin{figure*}[tb]
-\centering
-\includegraphics[page=2]{AreaAgg_Preliminaries}
-\caption{Integrating two aggregation sequences 
-	of different regions: 
-	the resulting sequence contains the given sequences 
-	as subsequences and 
-	always takes the subdivision with smallest patch next.
-	The gray arrows show the integration of the two regions.
-}
-\label{fig:AreaAgg_IntegrateSequence}
-\end{figure*}
 
@@
 The node set $V_\mathrm{S}$ of~$G_\mathrm{S}$ 
-contains a node for every
-possible map (or \emph{subdivision}), including the start map, 
+contains nodes for all the
+possible maps (or \emph{subdivisions}), including the start map, 
 all possible intermediate-scale maps, and the goal map.
@@
 involving a smallest area.
-Then, any directed path in~$G_\mathrm{S}$ 
+On this basis, any directed path in~$G_\mathrm{S}$ 
 from the start map to the goal map
 defines a possible aggregation sequence.
-Our idea is to obtain an optimal aggregation sequence through 
-computing a minimum-weight path from the start to the goal.
-This idea obviously requires that the arc weights are 
-set such that a minimum-weight start--goal
-path does actually correspond to an aggregation sequence of 
-maximum cartographic quality.  
-Moreover, putting the idea to practice is far from trivial 
-since graph~$G_\mathrm{S}$ can be huge as we will argue later.
-We compare a greedy algorithm, \Astar, and an ILP-based algorithm
-in finding such paths.
-Note that we only know 
-subdivisions~$\Pstart$ and~$\Pgoal$ at the beginning.
-We generate a subdivision (node) only when we want to visit it.
 
@@
 \end{figure}
+
+\mypar{Exponential lower bound}
+We now analyze the size of subdivision graph~$G_\mathrm{S}$.
+Our analysis is inspired by \textcite{Keane1975Size},
+where we use a row of~$n$ land-cover areas.
+In our instance
+(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
+the start map consists of~$n=2k+1$ rectangles,
+and the goal map is simply the union of the~$n$ rectangles.
+At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
+intermediate vertical boundaries. 
+For this, the number of choices is~$
+\binom{2k}{k}
+= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
+{k\cdot (k-1)\cdot \ldots \cdot 1}
+\ge 2^k = 2^{(n-1)/2}$.
+That is to say, the size of our model
+has exponential lower bound.
+
+\mypar{Methods}
+Our idea is to obtain an optimal aggregation sequence through 
+computing a minimum-weight path from the start to the goal 
+(see \fig\ref{fig:AreaAgg_SubdivisionName}).
+This idea obviously requires that the arc weights are 
+set such that a minimum-weight start--goal
+path does actually correspond to an aggregation sequence of 
+maximum cartographic quality.  
+Moreover, putting the idea to practice is far from trivial 
+since graph~$G_\mathrm{S}$ can be huge.
+We compare a greedy algorithm, \Astar, and an ILP-based algorithm
+in finding such paths.
+Note that our inputs are only
+subdivisions~$\Pstart$ and~$\Pgoal$.
+We generate a subdivision (node) only when we want to visit it.
+
+In directed acyclic graphs, shortest paths can be found slightly faster 
+than in general directed or undirected graphs.
+An off-the-shelf shortest-path algorithm for directed acyclic graphs,
+however, will explore the whole graph, which has exponential size.
+The challenge in our work was to tune the A* algorithm such that it
+explores only a small fraction of the graph.
 
@@
 \end{figure}
-
-\mypar{Exponential lower bound}
-We now analyze the size of subdivision graph~$G_\mathrm{S}$.
-Our analysis is inspired by \textcite{Keane1975Size},
-where we also use a row of~$n$~areas.
-In our instance
-(see \fig\ref{fig:AreaAgg_ExponentialSize}), 
-the start map consists of~$n=2k+1$ rectangles,
-and the goal map is simply the union of the~$n$ rectangles.
-At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
-intermediate vertical boundaries. 
-For this, the number of choices is~$
-\binom{2k}{k}
-= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
-{k\cdot (k-1)\cdot \ldots \cdot 1}
-\ge 2^k = 2^{(n-1)/2}$.
-That is to say, the size of our model
-has an exponential lower bound.
 
@@
 Considering one of the two costs 
-will make the finding even more difficult.
+will make the computation even more difficult.
 
@@
 which we connect with an edge. 
-For each edge of~$G_\mathrm{A}$, 
+For each edge $\{u,v\}$ of~$G_\mathrm{A}$, 
 we define two white vertices and 
-connect them with the two black vertices
+connect each of them both with the black vertex for $u$
+and the black vertex for $v$
 (\fig\ref{fig:AreaAgg_Reduction}b).
@@
 \end{itemize}
-Since in each aggregation step, 
-we require the smallest area to be aggregated with one of its neighbors, 
-our definition of the weights to a certain degree determines 
+When we merge two vertices, 
+the weight of the new vertex is the sum of the two.
+In each aggregation step, 
+we require the smallest area to be aggregated with one of its neighbors.
+The area sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
+Therefore, our definition of the weights to a certain degree determines 
 the order in which the vertices are selected:
@@
 a white vertex is selected and merged with one of its neighbors, 
-such that the white vertex receives the neighbor's color or vice versa.
+such that the white vertex receives the neighbor's color or vice versa
+(\fig\ref{fig:reduction2} shows a possible result).
 \item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
@@
 Thus, if any non-gray patch becomes selected in Phase II, 
-it can aggregate with a gray patch (vertex) and 
+it can be aggregated with a gray patch (vertex) and 
 receive the color gray. 
@@
 when we are going to visit it.
-\Astar uses a clever best-first search 
+The \Astar algorithm uses a clever best-first search 
 to find a shortest path 
@@
 and estimates the cost to get from~\Pnode to~\Pgoal. 
-\Astar explores the nodes earlier 
+The \Astar algorithm explores the nodes earlier 
 if they are estimated to be closer to the goal.
-\Astar can be seen as a refinement of Dijkstra's algorithm
+The \Astar algorithm can be seen as a refinement of Dijkstra's algorithm
 \parencite{Dijkstra1959}.
@@
 \end{equation*}
-Note that~$c_\mathrm{reg}(\mathcal{N})$ increases 
+Note that compactness~$c_\mathrm{reg}(\mathcal{N})$ increases 
 with increasing~$\mathcal{N}$.
@@
 \label{sec:AreaAgg_ILP}
+
+We want to compare the \Astar algorithm with 
+integer linear programming in finding 
+optimal sequences for our aggregation problem. 
+Since integer linear programming
+can handle only linear constraints, 
+we define the compactness of a subdivision as 
+the length of the subdivision's interior boundaries.
+That is, we use cost function~$g_2$ (see \eq\ref{eq:g_2}).
+Our basic idea is to formalize the problem of 
+finding a shortest path as an ILP.
+Then we solve this ILP by minimizing the total cost.
+As the \Astar algorithm performed better in our case study,
+here we skip the formulation of our ILP.
+The formulation can be found in Appendix~\ref{app:AreaAgg_ILP}.
+
+\section{Case Study}
+\label{sec:AreaAgg_CaseStudy}
+We have implemented our methods 
+based on C\# (Microsoft Visual Studio~2017) 
+and ArcObjects SDK~10.6.0.
+We used the IBM ILOG
+CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
+Our prototype is open access on GitHub\footnote{%
+\url{https://github.com/IGNF/ContinuousGeneralisation},
+Accessed: Jun 18, 2018.}.
+We ran our case study
+under 64-bit Windows~10 
+on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores;
+the computer has $16\,$GB RAM.
+We measured processing time 
+by the built-in C\# class \emph{Stopwatch}.
+As required by ArcObjects SDK~10.6.0,
+we specified our program to run on the~$32$-bit platform. 
+We added a post-build task about ``largeaddressaware''
+in Microsoft Visual Studio so that 
+we were able to use up to~$3\,$GB of the 
+main memory\footnote{The details of the setting can be found at \url
+{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
+Accessed: Nov 1, 2017.}.
+Our CPLEX version may declare an optimal solution
+while it is not really optimal.
+To fix this problem, we had to disable 
+both primal and dual presolve 
+reductions\footnote{For more details about the problem, see
+\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
+Accessed: Nov 12, 2017.}.
+
+We tested our method on a dataset 
+from the German topographic database ATKIS DLM~50. 
+The dataset represents the place 
+``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
+Our start map is the result of collapsing areas 
+by \citet[\chap6]{haunert2008f}.
+The start map has~$5{,}537$ polygons. 
+Our goal map was generalized from the start map 
+by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
+to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
+The goal map has~$734$ polygons, 
+which means that there are~$N=734$ regions.
+The distribution of region sizes is shown in 
+\fig\ref{fig:AreaAgg_NumRegion}.
+%
+We used a tree-based method introduced by 
+\citet{Rada1989SemanticMetric} 
+to define the distances of the types;
+the distance is the ``number of edges'' that
+we need to travel from one node to another node in the tree of 
+type hierarchy\footnote{More information 
+    about land-cover types can be found at 
+%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
+	Accessed: Nov 1, 2017.}
+(see \fig\ref{fig:AreaAgg_TypeDistances}). 
+For example, the distance from type \emph{village}
+to type \emph{fence} is~$2$, 
+to type \emph{street} is~$4$, and
+to type \emph{farm land} is~$6$.
+In this tree, the maximum distance is~$6$, 
+which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
+According to \citet{Rada1989SemanticMetric}, 
+the resulting cost function for type change is a metric.
+
+\begin{figure}[tb]
+%\captionsetup[subfigure]{labelformat=empty}
+\begin{subfigure}[b]{.49\textwidth}
+\centering
+\includegraphics[page=1]{AreaAgg_Data}
+\caption{Start map, $5{,}537$ polygons, \\
+	at scale $1:50{,}000$}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{.49\textwidth}
+\centering
+\includegraphics[page=2]{AreaAgg_Data}
+\caption{Goal map, $734$ polygons, \\
+	at scale $1:250{,}000$}
+\end{subfigure}
+%
+%It doesn't work to directly use 
+%\vspace{\baselineskip} for subfigures.
+\par\vspace{\baselineskip} %Leave a gap	figures
+%
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[page=3]{AreaAgg_Data}
+\caption{The 20 land-cover types appearing in our data}
+\end{subfigure}
+\caption{The data of our case study.}
+\label{fig:AreaAgg_Data}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=4]{AreaAgg_Data}
+\caption{Distribution of the region sizes:
+	the $y$-axis shows how many regions 
+	of a given size range are contained in our dataset.}
+\label{fig:AreaAgg_NumRegion}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=5]{AreaAgg_Data}
+\caption{The tree of type hierarchy used in our case study.
+	For example, the distance between 
+	types \emph{village} and \emph{farm land} is~$6$.}
+\label{fig:AreaAgg_TypeDistances}
+\end{figure}
+
+\subsection{Using costs of type change and compactness}
+\label{sec:AreaAgg_CaseStudy1}
+
+As illustrated in \sect\ref{sec:AreaAgg_Combining},
+we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
+which is a combination of the costs 
+of type change and compactness (see \eq\ref{eq:g_1}).
+For \Astar, we overestimated 
+whenever we could not find a solution after 
+having visited~$W$ nodes 
+(see \sect\ref{sec:AreaAgg_AStar}).
+We tried~$W=200{,}000$ and~$W=400{,}000$
+(if we could use more main memory, 
+then we could test by using some larger~$W$). 
+The results are shown in 
+Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
+%
+Comparing to \Astar, 
+the greedy algorithm visited 
+fewer nodes and arcs in graph~$G_\mathrm{S}$ 
+and used much less time.
+However, \Astar managed to find solutions with 
+lower total cost,~$117.3$ (or~$117.2$), 
+which is~$2.8\%$ less than 
+the total cost of the greedy algorithm,~$120.7$.
+%
+When~$W=200{,}000$, we are sure that 
+we have found optimal solutions 
+for~$702$ of the~$734$ regions ($95.6\%$),
+while the greedy algorithm solved 
+only~$408$ ($55.6\%$) to optimality;
+see column \#OS in 
+Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
+For the other~$32$ regions, 
+both algorithms have found feasible solutions 
+(see column \#FS in 
+Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
+Although some of the feasible solutions may also be optimal,
+we cannot verify that only from the cost values.
+
+\begin{table*}[tb]
+\caption{A comparison of the greedy algorithm and \Astar		
+	when using cost function~$g_1$ (see \eq\ref{eq:g_1}).
+	For \Astar, we used two settings, 
+	i.e.,~$W=200{,}000$ and~$W=400{,}000$.
+	%
+	Column~\#OS shows the numbers of regions 
+    that we obtained optimal solutions.   
+	%
+	Column~\#FS presents 
+    the numbers and the percentages of regions (out of~$N=734$) 
+    that we obtained feasible (non-optimal) solutions.
+	%
+	Variable~$k_\mathrm{sum}$ is 
+	the total number of repetitions.
+	%
+	Columns~\#nodes and~\#arcs are the total 
+	numbers of nodes and arcs that \Astar visited  
+	(for instances where we needed overestimation, 
+	only the final attempt was counted).
+	%
+	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
+	and~$\sum g_1$
+	respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
+	$g_\mathrm{comp}(\Pgoal)$, and~$g_1(\Pgoal)$ 
+	over all the~$734$ instances 
+	(see \eqs\ref{eq:g_type}, \ref{eq:g_comp}, 
+	and~\ref{eq:g_1}).
+	%
+	The percentage in the \emph{Time}
+	column is the fraction of the runtime 
+    spent on solving the instances
+	that we obtained feasible solutions.
+    For \Astar, the time needed for overestimation
+    is included.
+}
+\label{tab:AreaAgg_CaseStudy1_Statistics}
+\centering
+\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
+\setlength{\tabcolsep}{0.7ex}
+\begin{tabular}{lRRRCCCCCd{3.7}}
+\toprule
+\multicolumn{1}{l}{Methods} &
+\multicolumn{1}{l}{\#OS} &
+\multicolumn{1}{c}{\#FS} &
+\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
+\multicolumn{1}{c}{\#nodes} & 
+\multicolumn{1}{c}{\#arcs} & 
+\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
+\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
+\multicolumn{1}{c}{$\sum g_1$} & 
+\multicolumn{1}{c}{Time (min)} \\ 
+\midrule
+Greedy 	& 408 
+&326~(44.4\%) 
+&             &5.5\cdot 10^3   &4.8\cdot 10^3   
+&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
+%
+%
+\AstarTwo	& 702 
+&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
+& 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
+& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
+%
+%
+\AstarFour	& 704 
+&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
+&  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
+& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
+\\ \bottomrule			
+\end{tabular}
+\end{table*}
+
+In accordance with \sect\ref{sec:AreaAgg_AStar}, 
+for region with ID~$i$ 
+we define~$k_i$ as the least number of repetitions 
+that we do to find a feasible solution. 
+We define the total number of repetitions 
+as~$k_\mathrm{sum}=\sum_{i=1}^N k_i$, 
+where~$N=734$ is the number of the regions.
+After increasing~$W$ to~$400{,}000$, 
+\Astar found optimal aggregation sequences 
+for only two more regions, 
+but $k_\mathrm{sum}$ decreased quite a bit, 
+from~$102$ to~$89$. 
+The numbers of regions that needed certain
+overestimation steps are shown in 
+\fig\ref{fig:AreaAgg_OverStats}. 
+Besides, \Astar visited more arcs and nodes, 
+used more time, 
+but got (slightly) less cost when increasing~$W$ to~$400{,}000$.
+Although the number of regions 
+that needed overestimation is relatively small, 
+\Astar spent most of the running time 
+on those few regions:~$4.4\%$ and~$4.1\%$ of the regions 
+caused~$93.2\%$ and~$95.5\%$ of the total running time, 
+respectively 
+(see Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
+\caption{The numbers of regions where \Astar was 
+	forced to use the given overestimation parameters
+	in order to find a solution 
+	without exploring more than 
+	$W \in \{200{,}000;~400{,}000\}$ 
+	nodes of the subdivision graph.}
+\label{fig:AreaAgg_OverStats}
+\end{figure}
+
+The details of some regions are presented in 
+Table~\ref{tab:CostsInDetail}.
+According to the entries with overestimation factor $K_i=0$, 
+we often have 
+ratios~$R_\mathrm{type}=1$ and~$R_\mathrm{comp}>1$.
+When factor~$K_i=0$, we did not overestimate for region~$i$.
+The estimated cost must be smaller or equal to the exact cost,
+which results in~$R_\mathrm{type}\ge 1$ 
+and~$R_\mathrm{comp}\ge 1$.
+Ratio~$R_\mathrm{type} = 1$ means that our estimation for the 
+cost of type change is the best.
+A larger~$R_\mathrm{comp}$ means 
+a poorer estimation for the cost of shape.
+
+\begin{table*}[tb]
+\caption{The costs in detail of some regions, 
+	where~$W=200{,}000$.  
+	Parameters~$n$ and~$m$ are the numbers of patches and 
+	adjacencies on the start map, respectively.
+	Parameter $K$ is the overestimation factor, 
+	defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
+	We evaluate the quality 
+	of our estimations for type change and 
+	compactness by listing the numbers~
+	$R_\mathrm{type}=g_\mathrm{type}(\Pgoal)
+	/h_\mathrm{type}(\Pstart)$ and~
+	$R_\mathrm{comp}=g_\mathrm{comp}(\Pgoal)
+	/h_\mathrm{comp}(\Pstart)$. 
+	Note that if~$h_\mathrm{type}(\Pstart)=0$,
+    then we have~$g_\mathrm{type}(\Pgoal)=0$; 
+	in this case, we define~$R_\mathrm{type}=1$.
+	The marked entries are discussed in the text.
+}
+\label{tab:CostsInDetail}
+\centering
+\includegraphics[page=3]{AreaAgg_CaseStudy1_Plot}
+\end{table*}
+
+According to columns~$n$ and~$K$ of \tab\ref{tab:CostsInDetail},
+\AstarTwo managed to find optimal solutions 
+for all the regions with fewer than~$15$ polygons,
+and only found feasible solutions 
+for any region with more than~$21$ polygons.
+Among the~$702$ regions that 
+\AstarTwo solved to optimality,
+the greedy algorithm failed to 
+find optimal solutions for~$294$ regions.
+Solutions of the greedy algorithm cost
+at most~$41.7\%$ more than 
+solutions of \AstarTwo;
+for region~$85$, the greedy algorithm yields 
+a solution of cost~$0.777$, 
+while the solution of \AstarTwo has cost~$0.548$
+(see \fig\ref{fig:AreaAgg_CaseStudy1_Rg85}).
+As the patches in the two sequences are the same,
+the two results have the same cost of compactness.
+The main difference is the choice of the first step, 
+from~$8$ patches to~$7$.
+When aggregating the smallest patch on the start map
+with the surrounding patch,
+our greedy algorithm chooses the type 
+which is closer to the goal type.
+In this case, the smallest patch has type~$5112$, and the 
+surrounding one has~$2112$.
+The type of the goal patch is~$4102$.
+According to \fig\ref{fig:AreaAgg_TypeDistances},
+type distances~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
+As a result, our greedy algorithm uses~$5112$ 
+as the type for the new patch. 
+This choice is a big mistake 
+because the type of the largest patch on the start map
+will have to be changed twice during the aggregation.
+These changes cause a cost more than the sequence obtained by 
+\AstarTwo, 
+where the largest patch on the start map is changed to 
+the target type directly.
+
+Among the $32$~regions that 
+\AstarTwo failed to solve optimally,
+the greedy algorithm outperformed \AstarTwo 
+for~$15$ regions ($46.9\%$).
+%
+Among these, solutions of the greedy algorithm 
+cost at most~$15.9\%$ less than solutions of \AstarTwo;
+for region~$543$, the greedy algorithm yields 
+a solution of cost~$0.112$, 
+while the solution of \AstarTwo costs~$0.134$. 
+For this instance, 
+\AstarTwo used overestimation parameter~$K=7$
+(marked in \tab\ref{tab:CostsInDetail}).
+\fig\ref{fig:AreaAgg_CaseStudy1_Rg543} shows 
+some intermediate results obtained by
+\AstarTwo and the greedy algorithm.
+Interestingly, the two methods produced the same sequence until 
+there were~$8$ patches left.
+Then due to the overestimation, 
+\AstarTwo did some bad moves
+because the bad aggregation sequence still seemed better 
+than other sequences.
+In contrast, the greedy algorithm was looking for locally good 
+aggregations.
+%
+Among the~$32$ regions that 
+\AstarTwo failed to solve optimally,  
+solutions of the greedy algorithm cost at most~$17.4\%$ 
+more than solutions of \AstarTwo; 
+for region~$155$, the greedy algorithm yields 
+a solution of cost~$0.372$, while
+the solution of \AstarTwo costs~$0.317$
+(marked in \tab\ref{tab:CostsInDetail}).
+
+Finally, an optimal aggregation sequence of region~$53$
+(third-last row in \tab\ref{tab:CostsInDetail})
+obtained by \AstarTwo
+is shown in \fig\ref{fig:AreaAgg_CaseStudy1_Rg53}.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=1]{AreaAgg_CaseStudy1}
+\caption{Aggregation sequences of region~$85$ 
+	obtained by \Astar and the greedy algorithm.
+	In order to save space, we did not show the results 
+	when there are~$4$ or~$5$ patches, 
+	which one can easily deduce.
+	The numbers indicate the numbers of patches.
+    %
+    In the sequence obtained by \Astar, 
+    the type of the largest polygon on the start map 
+    changed only once, which is good; 
+    while the type of the largest polygon changed twice 
+    in the sequence obtained by the Greedy algorithm.}
+\label{fig:AreaAgg_CaseStudy1_Rg85}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=2]{AreaAgg_CaseStudy1}
+\caption{Some intermediate subdivisions of region~$543$ 
+	obtained by \Astar and the greedy algorithm.
+	In the sequence obtained by \Astar, 
+	a pair of circles or a pair of squares indicates that
+	the two parts are actually in the same patch.
+	The numbers indicate the numbers of patches.
+}
+\label{fig:AreaAgg_CaseStudy1_Rg543}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=3]{AreaAgg_CaseStudy1}
+\caption{An optimal sequence of intermediate subdivisions 
+	of region~$53$ obtained by \Astar 
+	using the costs of type change and compactness.		 
+	The numbers indicate the numbers of patches.		
+}
+\label{fig:AreaAgg_CaseStudy1_Rg53}
+\end{figure}
+
+%\todo[inline]{It turned out that the objective function $g$ 
+%seems rather robust
+%	against changes of~$\lambda$.  For region~77, we 
+%	varied~$\lambda$ in
+%	the range $\{0.1,0.5,0.9\}$, but the resulting aggregation 
+%	sequences
+%	stayed almost the same.  When we used even larger 
+%	values 
+%	for~$\lambda$ (e.g.,~$0.99$), the (good) influence of type 
+%	change was mitigated 
+%	and, as a
+%	result, we needed to overestimate (with factor~$K=8$).}
+
+\subsection{Using costs of type change and length}
+\label{sec:AreaAgg_CaseStudy2}
+
+We compare the greedy algorithm, \Astar, and ILP
+using~$g_2(\Pnode)$,
+a combination of the costs 
+of type change and length (see \eq\ref{eq:g_2}).
+For \Astar, we overestimated 
+whenever we could not find a solution after 
+having visited~$W=200{,}000$ nodes 
+(see \sect\ref{sec:AreaAgg_AStar}).
+The most time-consuming instance for \Astar was region~$94$,
+for which \Astar took~$104.1\,$s (including repetitions)
+to find a feasible solution 
+with overestimation factor~$K=31$.
+To avoid waiting too long,
+we set the time limit to~$100\,$s 
+for our ILP to run on one region.
+Note that the time limit included
+the time that our ILP used 
+to set up the variables and constraints
+(see \sects\ref{sub:AreaAgg_variables} 
+and~\ref{sub:AreaAgg_Constraints}).
+If no optimal solution was found in this time limit,
+a feasible solution (if found) would be returned.
+For some large instances, 
+the ILP could not find any solution.
+
+Using a similar format as in 
+\tab\ref{tab:AreaAgg_CaseStudy1_Statistics},
+we present the statistics in 
+\tab\ref{tab:AreaAgg_CaseStudy2_Statistics}.
+\Astar found optimal solutions 
+for~$695$ of the~$734$ regions ($94.7\%$).
+Again, it spent most of the running time 
+on the few regions that needed 
+overestimation:~$5.3\%$ of the regions 
+caused~$92.3\%$ of the total running time.
+The solutions by \Astar cost~$438.2$ in total, 
+which is~$3.9\%$ less than~$455.8$, 
+the total cost of the solutions by the greedy algorithm.
+
+\begin{table*}[tb]
+\caption{A comparison of the greedy algorithm, 
+    the \Astar algorithm, and the ILP-based algorithm		
+	when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
+	The notations are the same as in
+	\tab\ref{tab:AreaAgg_CaseStudy1_Statistics}.
+	%
+	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{lgth}$, 
+	and~$\sum g_2$
+	respectively represent the sums of~$g_\mathrm{type}(\Pgoal)$,
+	$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
+	over all the~$734$ instances 
+	(see \eqs\ref{eq:g_type}, \ref{eq:g_length}, 
+	and~\ref{eq:g_2}).
+}
+\label{tab:AreaAgg_CaseStudy2_Statistics}
+%	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
+\centering
+\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
+\setlength{\tabcolsep}{0.7ex}
+\begin{tabular}{lRRRCCCCCd{3.7}}
+\toprule
+\multicolumn{1}{l}{Methods} &
+\multicolumn{1}{l}{\#OS} &
+\multicolumn{1}{c}{\#FS} &
+\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
+\multicolumn{1}{c}{\#nodes} & 
+\multicolumn{1}{c}{\#arcs} & 
+\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
+\multicolumn{1}{c}{$\sum g_\mathrm{lgth}$} & 
+\multicolumn{1}{c}{$\sum g_2$} & 
+\multicolumn{1}{c}{Time (min)} \\ 
+\midrule
+Greedy 		 &430             
+&304~(41.4\%)    
+&            &5.5\cdot 10^3   &4.8\cdot 10^3   
+&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
+%
+%
+\AstarTwo	& 695
+& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
+& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
+& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
+%
+%
+\ILPOne		& 449
+& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
+&		&				&				
+&		&		&		& 421'5~(27.3\%) \\
+%
+%
+\ILPTwo		& 475
+& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
+&		&				&				
+&		&		&		& 719'2~(26.4\%) \\ 
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\Astar managed to find optimal solutions 
+for all the regions with fewer than~$15$ polygons, and 
+found only feasible solutions for the regions 
+with more than~$21$ polygons.
+%
+In the~$39$ (out of~$734$) regions 
+that \Astar failed to solve optimally,
+the greedy algorithm outperformed \Astar 
+for~$8$ regions~($20.5\%$), 
+which is~$26.4\%$ less comparing to the first experiment ($46.9\%$).
+%
+\ILPOne managed to find optimal solutions 
+for all the regions with fewer than~$8$ polygons,
+and failed to find optimal solutions
+for any region with more than~$8$ polygons.
+In none of the~$39$ regions 
+that \Astar failed to solve optimally
+did \ILPOne find a feasible solution.
+Overall, \ILPOne 
+found optimal solutions for~$449$ regions
+and found feasible solutions for~$69$ regions.
+The distributions of these regions are shown in
+\figs\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
+and~\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
+There are~$216$ regions for which 
+our \ILPOne failed to find any solution.
+For~$22$ of those regions, 
+we did not have enough main memory 
+to set up the variables and constraints;
+each of these regions has~$21$ polygons at least.
+For~$67$ of those regions, 
+our \ILPOne ran out of the main memory 
+before finding any feasible solution;
+these regions have~$14$ to~$20$ polygons.
+Note that we allowed our program to use~$3\,$GB 
+of the main memory at most.
+For~$123$ of the $216$~regions, 
+\ILPOne failed to find any solution
+during the time limit;
+these regions have~$9$ to~$13$ polygons.
+For the remaining~$4$ regions, 
+the reason of our ILP's fail is unclear 
+due to the fact that 
+the solver CPLEX is like a black box for us.
+After we increased the time limit to~$200\,$s for each region, 
+\ILPTwo solved~$475$ regions to optimality, which 
+is~$26$ regions more than using \ILPOne.
+Every of the~$26$ regions has~$6$ to~$10$ polygons.
+\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
+shows the percentages of the regions 
+that are solved optimally by the three algorithms.
+\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible} 
+shows the percentages of the regions 
+that the three algorithms found feasible solutions.
+\fig\ref{fig:AreaAgg_CaseStudy2_ILP} shows 
+the number of regions for which 
+the ILP found optimal, feasible, or no solutions 
+when using the two time limits, i.e., $100\,$s and~$200\,$s.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
+\caption{The percentage of regions that were solved 
+	optimally by the greedy algorithm, \Astar, and our ILP.
+	Note that the numbers of regions according to~$n$ 
+	(the number of polygons on the start map in one region) 
+	are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
+\label{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
+%
+\par\vspace{\baselineskip} %Leave a gap	between figures
+%
+\centering
+\includegraphics[page=2]{AreaAgg_CaseStudy2_Plot}
+\caption{The percentage of regions for which we found at 
+	least feasible solutions by the three algorithms.
+	Note that the numbers of regions according to~$n$ 
+	(the number of polygons on the start map in one region) 
+	are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
+\label{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=3]{AreaAgg_CaseStudy2_Plot}
+\caption{The number of regions for which
+	our ILP found optimal, feasible, or no solutions 
+	when using time limits~$100\,$s and~$200\,$s.
+	Using more time, our ILP was able to 
+	solve more instances to optimality.}
+\label{fig:AreaAgg_CaseStudy2_ILP}
+\end{figure}
+
+Among all the instances that were solved to optimality by \Astar
+in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
+and~\ref{sec:AreaAgg_CaseStudy2}),
+region~$358$ (marked in \tab\ref{tab:CostsInDetail})
+is the largest one.
+In both experiments, the cost of type change is~$0.044$.
+The optimal aggregation sequences for this region
+obtained by using costs~$g_1$ and~$g_2$
+are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
+We, however, noticed some unpleasant aggregates.
+The step from~$8$ patches to~$7$ patches 
+when using cost function~$g_1$ is a bad move
+(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
+Instead we expect the result of 
+\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
+Using cost function~$g_2$, we had a similar problem. 
+The subdivision with~$7$ patches is such an example,
+where we expect the result of 
+\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
+In an earlier version of this paper \parencite{Peng2017AStar},
+we tried a combination of minimizing type changes 
+and maximizing the sum of the smallest compactness values, 
+over the whole sequence.
+For that objective, we had a similar problem as 
+in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
+This problem, however, can be fixed easily 
+by forbidding two patches to aggregate 
+if their common boundary is too short.
+
+\begin{figure}[h!tb]
+\centering
+\includegraphics[page=1]{AreaAgg_CaseStudy2}
+\caption{Some intermediate subdivisions of region~$358$ 
+	obtained by \Astar with different cost functions.
+	The numbers indicate the numbers of patches.
+    The step from $8$ patches to $7$ patches 
+    when using cost function~$g1$ is a bad move; see figure (b). 
+    Instead, we expect the result of figure (a). 
+    Using cost function~$g2$, we had a similar problem. 
+    The subdivision with $7$ patches is such an example, 
+    where we expect the result of figure (c).
+}
+\label{fig:AreaAgg_CaseStudy2_Rg358}
+\end{figure}
+
+%\todo{chart: memory use of greedy, A*, and ILP}
+
+\section{Concluding Remarks}
+\label{sec:AreaAgg_Conclusions}
+In this paper, we investigated the problem of 
+finding optimal sequences for area aggregation.
+We compared three methods to solve this problem, namely, 
+a greedy algorithm, \Astar, and an ILP-based algorithm.
+The greedy algorithm is used as a benchmark.
+Unsurprisingly, it ran faster than the other two methods by far.
+According to our experiments, \Astar found area aggregation 
+sequences
+with the least total cost over all regions.
+For some instances, however, \Astar had to overestimate
+in order to find feasible solutions.
+Compared to the greedy algorithm, 
+\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
+in the two experiments.
+Although the amount is small, it is worth to use \Astar
+because optimization methods can help us 
+to evaluate the quality of a model 
+\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
+For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
+even an \emph{optimal} sequence can be bad.
+If it were not for \Astar, 
+we could not tell if the bad result was caused 
+by the greedy algorithm or the model.
+Because of \Astar, we are sure that the bad result is from
+our model of minimizing the 
+type change and the compactness.
+The ILP-based algorithm finds optimal solutions for some regions,
+but for some of the other regions 
+it cannot even find a feasible solution.
+Compared to the ILP-based algorithm,
+\Astar used less memory 
+yet found optimal solutions for more regions.
+
+%\todo[inline]{estimate compactness based on length; cauchy 
+%schwarz}
+
+Our \Astar has a good estimation for the cost of type 
+change, which helps a lot to reduce the search space. 
+Our estimation for the cost of shape 
+(compactness or length) is poor.
+There are two ways to improve \Astar
+in terms of solving more instances to optimality 
+while using the same limit of main memory.
+First, during the searching we can forget a node of the graph
+(see \fig\ref{fig:AreaAgg_SubdivisionName})
+if all the neighbors of this node have been visited.
+By testing a case, we learned that half of the nodes can be 
+forgotten during the pathfinding process.
+In this way, we can release some main memory 
+and visit more nodes.
+Once we arrive at the goal, 
+we know the cost for 
+an optimal solution (the least cost).
+As many visited nodes have been forgotten, 
+we do not have the shortest path so far.
+We need to run \Astar again.
+This time we know for sure that 
+a path is not optimal if its cost, 
+the sum of the exact cost and the estimated cost, 
+is more than the least cost 
+(of the optimal solution found previously).
+Consequently, we are able to prune some branches earlier 
+than the first time we run \Astar.
+In this way, we manage to save some main memory.
+As a result, we are more likely to find optimal solutions
+when the main memory is limited.
+Second, if we obtain a solution based on overestimation, 
+then we know the cost of this non-optimal solution.
+We may decrease the overestimation factor by pruning the branches
+that cost more than the non-optimal solution.
+
+We may speed up our ILP-based algorithm using a so-called 
+cutting-plane approach as \textcite{Oehrlein2017Aggregation}.
+Also, we can add more constraints to
+reduce the choices of variables.
+For example, assignment to a given center~$r$ is symmetric, 
+hence we have
+\begin{equation*}
+\label{eq:CstrZX}
+z_{t,p,q,r}= z_{t,q,p,r} \qquad
+\forall t \in {T} \setminus \{1,n\}, 
+\forall p, q, r \in P.
+\end{equation*}
+Whether adding such kinds of constraints always
+speeds up our ILP is not clear
+because the solver, CPLEX, is a black box to us.
+Although integer linear programming may be not good at 
+finding optimal sequences for area aggregation,
+it is relatively easy to formulate problems as ILPs.
+As stated by \citet[p.~861]{Cormen2009}, 
+``an efficient algorithm designed specifically for a problem 
+will often be more efficient than 
+linear programming both in theory and in practice. 
+The real power of linear programming comes from 
+the ability to solve new problems.''
+
+We may improve both the \Astar algorithm and the ILP-based 
+algorithm by integrating the greedy algorithm.
+The idea is that we use the greedy algorithm to find 
+a solution. 
+Then we can use the cost of the solution as an upper bound to 
+prune the branches of \Astar and the ILP. 
+Once we see that
+the cost of a branch is larger than the upper bound,
+we can ignore that branch  
+because it will not yield an optimal solution.
+
+In cartography, there are many more requirements 
+for area aggregation.
+For example, one requirement is 
+to keep important land-cover areas for a longer time
+(such as a settlement surrounded by farmlands).
+This requirement can be achieved by incorporating the idea of
+\textcite{Dilo2009tGAP}.
+They gave each type a weight, 
+then defined the importance of a patch 
+by the product of the area size and the type weight.
+While in our method, we used only the area size as importance.
+%
+Another requirement is that 
+aggregating two areas may result in 
+an area with a generalized type,
+as did by \textcite{vanSmaalen2003}. 
+For example, aggregating 
+\emph{farmland} with \emph{hedge} 
+yields an area with type \emph{vegetation}.
+%
+These issues can be considered in our future work.
+%
+
+\begin{acks}
+We thank Thomas C. van Dijk, Joachim Spoerhase, 
+and Sabine Storandt for their valuable suggestions.
+We thank Martijn Meijers for 
+prereviewing an earlier version of this paper.
+\end{acks}
+
+\printbibliography
+
+\appendix
+\section{Formulation of Integer Linear Programming}
+\label{app:AreaAgg_ILP}
 
@@
 
-\section{Case Study}
-\label{sec:AreaAgg_CaseStudy}
-We have implemented our methods 
-based on C\# (Microsoft Visual Studio~2017) 
-and ArcObjects SDK~10.6.0.
-We used the IBM ILOG
-CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
-Our prototype is open access on GitHub\footnote{%
-\url{https://github.com/IGNF/ContinuousGeneralisation},
-Accessed: Jun 18, 2018.}.
-We ran our case study
-under 64-bit Windows~10 
-on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores;
-the computer has $16\,$GB RAM.
-We measured processing time 
-by the built-in C\# class \emph{Stopwatch}.
-As required by ArcObjects SDK~10.6.0,
-we specified our program to run on the~$32$-bit platform. 
-We added a post-build task about ``largeaddressaware''
-in Microsoft Visual Studio so that 
-we were able to use up to~$3\,$GB of the 
-main memory\footnote{The details of the setting can be found at \url
-{http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
-Accessed: Nov 1, 2017.}.
-Our CPLEX version may declare an optimal solution
-while it is not really optimal.
-To fix this problem, we had to disable 
-both primal and dual presolve 
-reductions\footnote{For more details about the problem, see
-\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
-Accessed: Nov 12, 2017.}.
-
-We tested our method on a dataset 
-from the German topographic database ATKIS DLM~50. 
-The dataset represents the place 
-``Buchholz in der Nordheide'' at scale~$1:50{,}000$. 
-Our start map is the result of collapsing areas 
-by \citet[\chap6]{haunert2008f}.
-The start map has~$5{,}537$ polygons. 
-Our goal map was generalized from the start map 
-by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
-to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
-The goal map has~$734$ polygons, 
-which means that there are~$N=734$ regions.
-The distribution of region sizes is shown in 
-\fig\ref{fig:AreaAgg_NumRegion}.
-%
-We used a tree-based method introduced by 
-\citet{Rada1989SemanticMetric} 
-to define the distances of the types;
-the distance is the ``number of edges'' that
-we need to travel from one node to another node in the tree of 
-type hierarchy\footnote{More information 
-    about land-cover types can be found at 
-%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
-	Accessed: Nov 1, 2017.}
-(see \fig\ref{fig:AreaAgg_TypeDistances}). 
-For example, the distance from type \emph{village}
-to type \emph{fence} is~$2$, 
-to type \emph{street} is~$4$, and
-to type \emph{farm land} is~$6$.
-In this tree, the maximum distance is~$6$, 
-which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
-According to \citet{Rada1989SemanticMetric}, 
-the resulting cost function for type change is a metric.
-
-\begin{figure}[tb]
-%\captionsetup[subfigure]{labelformat=empty}
-\begin{subfigure}[b]{.49\textwidth}
-\centering
-\includegraphics[page=1]{AreaAgg_Data}
-\caption{Start map, $5{,}537$ polygons, \\
-	at scale $1:50{,}000$}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{.49\textwidth}
-\centering
-\includegraphics[page=2]{AreaAgg_Data}
-\caption{Goal map, $734$ polygons, \\
-	at scale $1:250{,}000$}
-\end{subfigure}
-%
-%It doesn't work to directly use 
-%\vspace{\baselineskip} for subfigures.
-\par\vspace{\baselineskip} %Leave a gap	figures
-%
-\begin{subfigure}{\textwidth}
-\centering
-\includegraphics[page=3]{AreaAgg_Data}
-\caption{The 20 land-cover types appearing in our data}
-\end{subfigure}
-\caption{The data of our case study.}
-\label{fig:AreaAgg_Data}
-\end{figure}
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=4]{AreaAgg_Data}
-\caption{Distribution of the region sizes:
-	the $y$-axis shows how many regions 
-	of a given size range are contained in our dataset.}
-\label{fig:AreaAgg_NumRegion}
-\end{figure}
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=5]{AreaAgg_Data}
-\caption{The tree of type hierarchy used in our case study.
-	For example, the distance between 
-	types \emph{village} and \emph{farm land} is~$6$.}
-\label{fig:AreaAgg_TypeDistances}
-\end{figure}
-
-\subsection{Using costs of type change and compactness}
-\label{sec:AreaAgg_CaseStudy1}
-
-As illustrated in \sect\ref{sec:AreaAgg_Combining},
-we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
-which is a combination of the costs 
-of type change and compactness (see \eq\ref{eq:g_1}).
-For \Astar, we overestimated 
-whenever we could not find a solution after 
-having visited~$W$ nodes 
-(see \sect\ref{sec:AreaAgg_AStar}).
-We tried~$W=200{,}000$ and~$W=400{,}000$
-(if we could use more main memory, 
-then we could test by using some larger~$W$). 
-The results are shown in 
-Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
-%
-Comparing to \Astar, 
-the greedy algorithm visited 
-fewer nodes and arcs in graph~$G_\mathrm{S}$ 
-and used much less time.
-However, \Astar managed to find solutions with 
-lower total cost,~$117.3$ (or~$117.2$), 
-which is~$2.8\%$ less than 
-the total cost of the greedy algorithm,~$120.7$.
-%
-When~$W=200{,}000$, we are sure that 
-we have found optimal solutions 
-for~$702$ of the~$734$ regions ($95.6\%$),
-while the greedy algorithm solved 
-only~$408$ ($55.6\%$) to optimality;
-see column \#OS in 
-Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}.
-For the other~$32$ regions, 
-both algorithms have found feasible solutions 
-(see column \#FS in 
-Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
-Although some of the feasible solutions may also be optimal,
-we cannot verify that only from the cost values.
-
-\begin{table*}[tb]
-\caption{A comparison of the greedy algorithm and \Astar		
-	when using cost function~$g_1$ (see \eq\ref{eq:g_1}).
-	For \Astar, we used two settings, 
-	i.e.,~$W=200{,}000$ and~$W=400{,}000$.
-	%
-	Column~\#OS shows the numbers of regions 
-    that we obtained optimal solutions.   
-	%
-	Column~\#FS presents 
-    the numbers and the percentages of regions (out of~$N=734$) 
-    that we obtained feasible (non-optimal) solutions.
-	%
-	Variable~$k_\mathrm{sum}$ is 
-	the total number of repetitions.
-	%
-	Columns~\#nodes and~\#arcs are the total 
-	numbers of nodes and arcs that \Astar visited  
-	(for instances where we needed overestimation, 
-	only the final attempt was counted).
-	%
-	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{comp}$, 
-	and~$\sum g_1$
-	respectively denotes the sums of~$g_\mathrm{type}(\Pgoal)$,
-	$g_\mathrm{comp}(\Pgoal)$, and~$g_1(\Pgoal)$ 
-	over all the~$734$ instances 
-	(see \eqs\ref{eq:g_type}, \ref{eq:g_comp}, 
-	and~\ref{eq:g_1}).
-	%
-	The percentage in the \emph{Time}
-	column is the fraction of the runtime 
-    spent on solving the instances
-	that we obtained feasible solutions.
-    For \Astar, the time needed for overestimation
-    is included.
-}
-\label{tab:AreaAgg_CaseStudy1_Statistics}
-\centering
-\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
-\setlength{\tabcolsep}{0.7ex}
-\begin{tabular}{lRRRCCCCCd{3.7}}
-\toprule
-\multicolumn{1}{l}{Methods} &
-\multicolumn{1}{l}{\#OS} &
-\multicolumn{1}{c}{\#FS} &
-\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
-\multicolumn{1}{c}{\#nodes} & 
-\multicolumn{1}{c}{\#arcs} & 
-\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
-\multicolumn{1}{c}{$\sum g_\mathrm{comp}$} & 
-\multicolumn{1}{c}{$\sum g_1$} & 
-\multicolumn{1}{c}{Time (min)} \\ 
-\midrule
-Greedy 	& 408 
-&326~(44.4\%) 
-&             &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
-%
-%
-\AstarTwo	& 702 
-&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
-& 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
-& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
-%
-%
-\AstarFour	& 704 
-&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
-&  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
-& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
-\\ \bottomrule			
-\end{tabular}
-\end{table*}
-
-In accordance with \sect\ref{sec:AreaAgg_AStar}, 
-for region with ID~$i$ 
-we define~$k_i$ as the least number of repetitions 
-that we do to find a feasible solution. 
-We define the total number of repetitions 
-as~$k_\mathrm{sum}=\sum_{i=1}^N k_i$, 
-where~$N=734$ is the number of the regions.
-After increasing~$W$ to~$400{,}000$, 
-\Astar found optimal aggregation sequences 
-for only two more regions, 
-but $k_\mathrm{sum}$ decreased quite a bit, 
-from~$102$ to~$89$. 
-The numbers of regions that needed certain
-overestimation steps are shown in 
-\fig\ref{fig:AreaAgg_OverStats}. 
-Besides, \Astar visited more arcs and nodes, 
-used more time, 
-but got (slightly) less cost when increasing~$W$ to~$400{,}000$.
-Although the number of regions 
-that needed overestimation is relatively small, 
-\Astar spent most of the running time 
-on those few regions:~$4.4\%$ and~$4.1\%$ of the regions 
-caused~$93.2\%$ and~$95.5\%$ of the total running time, 
-respectively 
-(see Table~\ref{tab:AreaAgg_CaseStudy1_Statistics}).
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
-\caption{The numbers of regions where \Astar was 
-	forced to use the given overestimation parameters
-	in order to find a solution 
-	without exploring more than 
-	$W \in \{200{,}000;~400{,}000\}$ 
-	nodes of the subdivision graph.}
-\label{fig:AreaAgg_OverStats}
-\end{figure}
-
-The details of some regions are presented in 
-Table~\ref{tab:CostsInDetail}.
-According to the entries with overestimation factor $K_i=0$, 
-we often have 
-ratios~$R_\mathrm{type}=1$ and~$R_\mathrm{comp}>1$.
-When factor~$K_i=0$, we did not overestimate for region~$i$.
-The estimated cost must be smaller or equal to the exact cost,
-which results in~$R_\mathrm{type}\ge 1$ 
-and~$R_\mathrm{comp}\ge 1$.
-Ratio~$R_\mathrm{type} = 1$ means that our estimation for the 
-cost of type change is the best.
-A larger~$R_\mathrm{comp}$ means 
-a poorer estimation for the cost of shape.
-
-\begin{table*}[tb]
-\caption{The costs in detail of some regions, 
-	where~$W=200{,}000$.  
-	Parameters~$n$ and~$m$ are the numbers of patches and 
-	adjacencies on the start map, respectively.
-	Parameter $K$ is the overestimation factor, 
-	defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
-	We evaluate the quality 
-	of our estimations for type change and 
-	compactness by listing the numbers~
-	$R_\mathrm{type}=g_\mathrm{type}(\Pgoal)
-	/h_\mathrm{type}(\Pstart)$ and~
-	$R_\mathrm{comp}=g_\mathrm{comp}(\Pgoal)
-	/h_\mathrm{comp}(\Pstart)$. 
-	Note that if~$h_\mathrm{type}(\Pstart)=0$,
-    then we have~$g_\mathrm{type}(\Pgoal)=0$; 
-	in this case, we define~$R_\mathrm{type}=1$.
-	The marked entries are discussed in the text.
-}
-\label{tab:CostsInDetail}
-\centering
-\includegraphics[page=3]{AreaAgg_CaseStudy1_Plot}
-\end{table*}
-
-According to columns~$n$ and~$K$ of \tab\ref{tab:CostsInDetail},
-\AstarTwo managed to find optimal solutions 
-for all the regions with fewer than~$15$ polygons,
-and only found feasible solutions 
-for any region with more than~$21$ polygons.
-Among the~$702$ regions that 
-\AstarTwo solved to optimality,
-the greedy algorithm failed to 
-find optimal solutions for~$294$ regions.
-Solutions of the greedy algorithm cost
-at most~$41.7\%$ more than 
-solutions of \AstarTwo;
-for region~$85$, the greedy algorithm yields 
-a solution of cost~$0.777$, 
-while the solution of \AstarTwo has cost~$0.548$
-(see \fig\ref{fig:AreaAgg_CaseStudy1_Rg85}).
-As the patches in the two sequences are the same,
-the two results have the same cost of compactness.
-The main difference is the choice of the first step, 
-from~$8$ patches to~$7$.
-When aggregating the smallest patch on the start map
-with the surrounding patch,
-our greedy algorithm chooses the type 
-which is closer to the goal type.
-In this case, the smallest patch has type~$5112$, and the 
-surrounding one has~$2112$.
-The type of the goal patch is~$4102$.
-According to \fig\ref{fig:AreaAgg_TypeDistances},
-type distances~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
-As a result, our greedy algorithm uses~$5112$ 
-as the type for the new patch. 
-This choice is a big mistake 
-because the type of the largest patch on the start map
-will have to be changed twice during the aggregation.
-These changes cause a cost more than the sequence obtained by 
-\AstarTwo, 
-where the largest patch on the start map is changed to 
-the target type directly.
-
-Among the $32$~regions that 
-\AstarTwo failed to solve optimally,
-the greedy algorithm outperformed \AstarTwo 
-for~$15$ regions ($46.9\%$).
-%
-Among these, solutions of the greedy algorithm 
-cost at most~$15.9\%$ less than solutions of \AstarTwo;
-for region~$543$, the greedy algorithm yields 
-a solution of cost~$0.112$, 
-while the solution of \AstarTwo costs~$0.134$. 
-For this instance, 
-\AstarTwo used overestimation parameter~$K=7$
-(marked in \tab\ref{tab:CostsInDetail}).
-\fig\ref{fig:AreaAgg_CaseStudy1_Rg543} shows 
-some intermediate results obtained by
-\AstarTwo and the greedy algorithm.
-Interestingly, the two methods produced the same sequence until 
-there were~$8$ patches left.
-Then due to the overestimation, 
-\AstarTwo did some bad moves
-because the bad aggregation sequence still seemed better 
-than other sequences.
-In contrast, the greedy algorithm was looking for locally good 
-aggregations.
-%
-Among the~$32$ regions that 
-\AstarTwo failed to solve optimally,  
-solutions of the greedy algorithm cost at most~$17.4\%$ 
-more than solutions of \AstarTwo; 
-for region~$155$, the greedy algorithm yields 
-a solution of cost~$0.372$, while
-the solution of \AstarTwo costs~$0.317$
-(marked in \tab\ref{tab:CostsInDetail}).
-
-Finally, an optimal aggregation sequence of region~$53$
-(third-last row in \tab\ref{tab:CostsInDetail})
-obtained by \AstarTwo
-is shown in \fig\ref{fig:AreaAgg_CaseStudy1_Rg53}.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=1]{AreaAgg_CaseStudy1}
-\caption{Aggregation sequences of region~$85$ 
-	obtained by \Astar and the greedy algorithm.
-	In order to save space, we did not show the results 
-	when there are~$4$ or~$5$ patches, 
-	which one can easily deduce.
-	The numbers indicate the numbers of patches.
-    %
-    In the sequence obtained by \Astar, 
-    the type of the largest polygon on the start map 
-    changed only once, which is good; 
-    while the type of the largest polygon changed twice 
-    in the sequence obtained by the Greedy algorithm.}
-\label{fig:AreaAgg_CaseStudy1_Rg85}
-\end{figure}
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=2]{AreaAgg_CaseStudy1}
-\caption{Some intermediate subdivisions of region~$543$ 
-	obtained by \Astar and the greedy algorithm.
-	In the sequence obtained by \Astar, 
-	a pair of circles or a pair of squares indicates that
-	the two parts are actually in the same patch.
-	The numbers indicate the numbers of patches.
-}
-\label{fig:AreaAgg_CaseStudy1_Rg543}
-\end{figure}
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=3]{AreaAgg_CaseStudy1}
-\caption{An optimal sequence of intermediate subdivisions 
-	of region~$53$ obtained by \Astar 
-	using the costs of type change and compactness.		 
-	The numbers indicate the numbers of patches.		
-}
-\label{fig:AreaAgg_CaseStudy1_Rg53}
-\end{figure}
-
-%\todo[inline]{It turned out that the objective function $g$ 
-%seems rather robust
-%	against changes of~$\lambda$.  For region~77, we 
-%	varied~$\lambda$ in
-%	the range $\{0.1,0.5,0.9\}$, but the resulting aggregation 
-%	sequences
-%	stayed almost the same.  When we used even larger 
-%	values 
-%	for~$\lambda$ (e.g.,~$0.99$), the (good) influence of type 
-%	change was mitigated 
-%	and, as a
-%	result, we needed to overestimate (with factor~$K=8$).}
-
-\subsection{Using costs of type change and length}
-\label{sec:AreaAgg_CaseStudy2}
-
-We compare the greedy algorithm, \Astar, and ILP
-using~$g_2(\Pnode)$,
-a combination of the costs 
-of type change and length (see \eq\ref{eq:g_2}).
-For \Astar, we overestimated 
-whenever we could not find a solution after 
-having visited~$W=200{,}000$ nodes 
-(see \sect\ref{sec:AreaAgg_AStar}).
-The most time-consuming instance for \Astar was region~$94$,
-for which \Astar took~$104.1\,$s (including repetitions)
-to find a feasible solution 
-with overestimation factor~$K=31$.
-To avoid waiting too long,
-we set the time limit to~$100\,$s 
-for our ILP to run on one region.
-Note that the time limit included
-the time that our ILP used 
-to set up the variables and constraints
-(see \sects\ref{sub:AreaAgg_variables} 
-and~\ref{sub:AreaAgg_Constraints}).
-If no optimal solution was found in this time limit,
-a feasible solution (if found) would be returned.
-For some large instances, 
-the ILP could not find any solution.
-
-Using a similar format as in 
-\tab\ref{tab:AreaAgg_CaseStudy1_Statistics},
-we present the statistics in 
-\tab\ref{tab:AreaAgg_CaseStudy2_Statistics}.
-\Astar found optimal solutions 
-for~$695$ of the~$734$ regions ($94.7\%$).
-Again, it spent most of the running time 
-on the few regions that needed 
-overestimation:~$5.3\%$ of the regions 
-caused~$92.3\%$ of the total running time.
-The solutions by \Astar cost~$438.2$ in total, 
-which is~$3.9\%$ less than~$455.8$, 
-the total cost of the solutions by the greedy algorithm.
-
-\begin{table*}[tb]
-\caption{A comparison of the greedy algorithm, 
-    the \Astar algorithm, and the ILP-based algorithm		
-	when using cost function~$g_2$ (see \eq\ref{eq:g_2}).
-	The notations are the same as in
-	\tab\ref{tab:AreaAgg_CaseStudy1_Statistics}.
-	%
-	Columns~$\sum g_\mathrm{type}$, $\sum g_\mathrm{lgth}$, 
-	and~$\sum g_2$
-	respectively represent the sums of~$g_\mathrm{type}(\Pgoal)$,
-	$g_\mathrm{lgth}(\Pgoal)$, and~$g_2(\Pgoal)$ 
-	over all the~$734$ instances 
-	(see \eqs\ref{eq:g_type}, \ref{eq:g_length}, 
-	and~\ref{eq:g_2}).
-}
-\label{tab:AreaAgg_CaseStudy2_Statistics}
-%	\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
-\centering
-\fontsize{9}{11}\selectfont %for my thesis; should before \setlength{\tabcolsep}{0.7ex}
-\setlength{\tabcolsep}{0.7ex}
-\begin{tabular}{lRRRCCCCCd{3.7}}
-\toprule
-\multicolumn{1}{l}{Methods} &
-\multicolumn{1}{l}{\#OS} &
-\multicolumn{1}{c}{\#FS} &
-\multicolumn{1}{r}{$k_\mathrm{sum}$} &  
-\multicolumn{1}{c}{\#nodes} & 
-\multicolumn{1}{c}{\#arcs} & 
-\multicolumn{1}{c}{$\sum g_\mathrm{type}$} & 
-\multicolumn{1}{c}{$\sum g_\mathrm{lgth}$} & 
-\multicolumn{1}{c}{$\sum g_2$} & 
-\multicolumn{1}{c}{Time (min)} \\ 
-\midrule
-Greedy 		 &430             
-&304~(41.4\%)    
-&            &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
-%
-%
-\AstarTwo	& 695
-& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
-& 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
-& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
-%
-%
-\ILPOne		& 449
-& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
-&		&				&				
-&		&		&		& 421'5~(27.3\%) \\
-%
-%
-\ILPTwo		& 475
-& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
-&		&				&				
-&		&		&		& 719'2~(26.4\%) \\ 
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\Astar managed to find optimal solutions 
-for all the regions with fewer than~$15$ polygons, and 
-found only feasible solutions for the regions 
-with more than~$21$ polygons.
-%
-In the~$39$ (out of~$734$) regions 
-that \Astar failed to solve optimally,
-the greedy algorithm outperformed \Astar 
-for~$8$ regions~($20.5\%$), 
-which is~$26.4\%$ less comparing to the first experiment ($46.9\%$).
-%
-\ILPOne managed to find optimal solutions 
-for all the regions with fewer than~$8$ polygons,
-and failed to find optimal solutions
-for any region with more than~$8$ polygons.
-In none of the~$39$ regions 
-that \Astar failed to solve optimally
-did \ILPOne find a feasible solution.
-Overall, \ILPOne 
-found optimal solutions for~$449$ regions
-and found feasible solutions for~$69$ regions.
-The distributions of these regions are shown in
-\figs\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
-and~\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
-There are~$216$ regions for which 
-our \ILPOne failed to find any solution.
-For~$22$ of those regions, 
-we did not have enough main memory 
-to set up the variables and constraints;
-each of these regions has~$21$ polygons at least.
-For~$67$ of those regions, 
-our \ILPOne ran out of the main memory 
-before finding any feasible solution;
-these regions have~$14$ to~$20$ polygons.
-Note that we allowed our program to use~$3\,$GB 
-of the main memory at most.
-For~$123$ of the $216$~regions, 
-\ILPOne failed to find any solution
-during the time limit;
-these regions have~$9$ to~$13$ polygons.
-For the remaining~$4$ regions, 
-the reason of our ILP's fail is unclear 
-due to the fact that 
-the solver CPLEX is like a black box for us.
-After we increased the time limit to~$200\,$s for each region, 
-\ILPTwo solved~$475$ regions to optimality, which 
-is~$26$ regions more than using \ILPOne.
-Every of the~$26$ regions has~$6$ to~$10$ polygons.
-\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
-shows the percentages of the regions 
-that are solved optimally by the three algorithms.
-\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible} 
-shows the percentages of the regions 
-that the three algorithms found feasible solutions.
-\fig\ref{fig:AreaAgg_CaseStudy2_ILP} shows 
-the number of regions for which 
-the ILP found optimal, feasible, or no solutions 
-when using the two time limits, i.e., $100\,$s and~$200\,$s.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=1]{AreaAgg_CaseStudy2_Plot}
-\caption{The percentage of regions that were solved 
-	optimally by the greedy algorithm, \Astar, and our ILP.
-	Note that the numbers of regions according to~$n$ 
-	(the number of polygons on the start map in one region) 
-	are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
-\label{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
-%
-\par\vspace{\baselineskip} %Leave a gap	between figures
-%
-\centering
-\includegraphics[page=2]{AreaAgg_CaseStudy2_Plot}
-\caption{The percentage of regions for which we found at 
-	least feasible solutions by the three algorithms.
-	Note that the numbers of regions according to~$n$ 
-	(the number of polygons on the start map in one region) 
-	are shown in \fig\ref{fig:AreaAgg_NumRegion}.}
-\label{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
-\end{figure}
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=3]{AreaAgg_CaseStudy2_Plot}
-\caption{The number of regions for which
-	our ILP found optimal, feasible, or no solutions 
-	when using time limits~$100\,$s and~$200\,$s.
-	Using more time, our ILP was able to 
-	solve more instances to optimality.}
-\label{fig:AreaAgg_CaseStudy2_ILP}
-\end{figure}
-
-Among all the instances that were solved to optimality by \Astar
-in both experiments (i.e., \sects\ref{sec:AreaAgg_CaseStudy1} 
-and~\ref{sec:AreaAgg_CaseStudy2}),
-region~$358$ (marked in \tab\ref{tab:CostsInDetail})
-is the largest one.
-In both experiments, the cost of type change is~$0.044$.
-The optimal aggregation sequences for this region
-obtained by using costs~$g_1$ and~$g_2$
-are shown in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}.
-We, however, noticed some unpleasant aggregates.
-The step from~$8$ patches to~$7$ patches 
-when using cost function~$g_1$ is a bad move
-(see \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b).
-Instead we expect the result of 
-\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}a.
-Using cost function~$g_2$, we had a similar problem. 
-The subdivision with~$7$ patches is such an example,
-where we expect the result of 
-\fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
-In an earlier version of this paper \parencite{Peng2017AStar},
-we tried a combination of minimizing type changes 
-and maximizing the sum of the smallest compactness values, 
-over the whole sequence.
-For that objective, we had a similar problem as 
-in \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b.
-This problem, however, can be fixed easily 
-by forbidding two patches to aggregate 
-if their common boundary is too short.
-
-\begin{figure}[h!tb]
-\centering
-\includegraphics[page=1]{AreaAgg_CaseStudy2}
-\caption{Some intermediate subdivisions of region~$358$ 
-	obtained by \Astar with different cost functions.
-	The numbers indicate the numbers of patches.
-    The step from $8$ patches to $7$ patches 
-    when using cost function~$g1$ is a bad move; see figure (b). 
-    Instead, we expect the result of figure (a). 
-    Using cost function~$g2$, we had a similar problem. 
-    The subdivision with $7$ patches is such an example, 
-    where we expect the result of figure (c).
-}
-\label{fig:AreaAgg_CaseStudy2_Rg358}
-\end{figure}
-
-%\todo{chart: memory use of greedy, A*, and ILP}
-
-\section{Concluding Remarks}
-\label{sec:AreaAgg_Conclusions}
-In this paper, we investigated the problem of 
-finding optimal sequences for area aggregation.
-We compared three methods to solve this problem, namely, 
-a greedy algorithm, \Astar, and an ILP-based algorithm.
-The greedy algorithm is used as a benchmark.
-Unsurprisingly, it ran faster than the other two methods by far.
-According to our experiments, \Astar found area aggregation 
-sequences
-with the least total cost over all regions.
-For some instances, however, \Astar had to overestimate
-in order to find feasible solutions.
-Compared to the greedy algorithm, 
-\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
-in the two experiments.
-Although the amount is small, it is worth to use \Astar
-because optimization methods can help us 
-to evaluate the quality of a model 
-\parencite{Haunert2017Label,Haunert2008Assuring,Haunert2016Optimization}.
-For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
-even an \emph{optimal} sequence can be bad.
-If it were not for \Astar, 
-we could not tell if the bad result was caused 
-by the greedy algorithm or the model.
-Because of \Astar, we are sure that the bad result is from
-our model of minimizing the 
-type change and the compactness.
-The ILP-based algorithm finds optimal solutions for some regions,
-but for some of the other regions 
-it cannot even find a feasible solution.
-Compared to the ILP-based algorithm,
-\Astar used less memory 
-yet found optimal solutions for more regions.
-
-%\todo[inline]{estimate compactness based on length; cauchy 
-%schwarz}
-
-Our \Astar has a good estimation for the cost of type 
-change, which helps a lot to reduce the search space. 
-Our estimation for the cost of shape 
-(compactness or length) is poor.
-There are two ways to improve \Astar
-in terms of solving more instances to optimality 
-while using the same limit of main memory.
-First, during the searching we can forget a node of the graph
-(see \fig\ref{fig:AreaAgg_SubdivisionName})
-if all the neighbors of this node have been visited.
-By testing a case, we learned that half of the nodes can be 
-forgotten during the pathfinding process.
-In this way, we can release some main memory 
-and visit more nodes.
-Once we arrive at the goal, 
-we know the cost for 
-an optimal solution (the least cost).
-As many visited nodes have been forgotten, 
-we do not have the shortest path so far.
-We need to run \Astar again.
-This time we know for sure that 
-a path is not optimal if its cost, 
-the sum of the exact cost and the estimated cost, 
-is more than the least cost 
-(of the optimal solution found previously).
-Consequently, we are able to prune some branches earlier 
-than the first time we run \Astar.
-In this way, we manage to save some main memory.
-As a result, we are more likely to find optimal solutions
-when the main memory is limited.
-Second, if we obtain a solution based on overestimation, 
-then we know the cost of this non-optimal solution.
-We may decrease the overestimation factor by pruning the branches
-that cost more than the non-optimal solution.
-
-We may speed up our ILP-based algorithm using a so-called 
-cutting-plane approach as \textcite{Oehrlein2017Aggregation}.
-Also, we can add more constraints to
-reduce the choices of variables.
-For example, assignment to a given center~$r$ is symmetric, 
-hence we have
-\begin{equation*}
-\label{eq:CstrZX}
-z_{t,p,q,r}= z_{t,q,p,r} \qquad
-\forall t \in {T} \setminus \{1,n\}, 
-\forall p, q, r \in P.
-\end{equation*}
-Whether adding such kinds of constraints always
-speeds up our ILP is not clear
-because the solver, CPLEX, is a black box to us.
-Although integer linear programming may be not good at 
-finding optimal sequences for area aggregation,
-it is relatively easy to formulate problems as ILPs.
-As stated by \citet[p.~861]{Cormen2009}, 
-``an efficient algorithm designed specifically for a problem 
-will often be more efficient than 
-linear programming both in theory and in practice. 
-The real power of linear programming comes from 
-the ability to solve new problems.''
-
-We may improve both the \Astar algorithm and the ILP-based 
-algorithm by integrating the greedy algorithm.
-The idea is that we use the greedy algorithm to find 
-a solution. 
-Then we can use the cost of the solution as an upper bound to 
-prune the branches of \Astar and the ILP. 
-Once we see that
-the cost of a branch is larger than the upper bound,
-we can ignore that branch  
-because it will not yield an optimal solution.
-
-In cartography, there are many more requirements 
-for area aggregation.
-For example, one requirement is 
-to keep important land-cover areas for a longer time
-(such as a settlement surrounded by farmlands).
-This requirement can be achieved by incorporating the idea of
-\textcite{Dilo2009tGAP}.
-They gave each type a weight, 
-then defined the importance of a patch 
-by the product of the area size and the type weight.
-While in our method, we used only the area size as importance.
-%
-Another requirement is that 
-aggregating two areas may result in 
-an area with a generalized type,
-as did by \textcite{vanSmaalen2003}. 
-For example, aggregating 
-\emph{farmland} with \emph{hedge} 
-yields an area with type \emph{vegetation}.
-%
-These issues can be considered in our future work.
-%
-
-\begin{acks}
-We thank Thomas C. van Dijk, Joachim Spoerhase, 
-and Sabine Storandt for their valuable suggestions.
-We thank Martijn Meijers for 
-prereviewing an earlier version of this paper.
-\end{acks}
-
-\printbibliography
-
 \end{document}

### 2019-03-23 area_agg_seq_tsas.tex
showed exponential lower bound using patches with different sizes

@@
 	 Type change, Compactness, Shortest path
-%	 , Optimization, Exponential
+%	 , Optimization, Exponential, NP-hard
 	 }
@@
 However, we should not use those algorithms
-to generate a sequence of maps at different scales, 
+to generate a sequence of maps at different scales
 because those algorithms do not take into account 
@@
 (\sect\ref{sec:AreaAgg_CaseStudy}).
-In the conclusions, we show possible ways to improve our 
+In the concluding remarks, we show possible ways to improve our 
 methods (\sect\ref{sec:AreaAgg_Conclusions}).
@@
 Mergesort algorithm; 
-see \textcite[pp.~29--37]{Cormen2009}.
+see \textcite[\sect2.3]{Cormen2009}.
 To allow us to describe our method more easily,
@@
 
-\mypar{Model}
+\subsection{Model}
+\label{sec:AreaAgg_Model}
 We consider a directed graph $G_\mathrm{S}$, 
@@
 
-\mypar{Exponential lower bound}
+\subsection{Notation}
+\label{sec:AreaAgg_Notation}
+
+We represent each land-cover area by a polygon with a type.
+We denote by~$P$ the set of polygons on the start map.
+We use~$p$, $q$, $r$, or~$o$ to denote polygons.
+A \emph{patch} is a set of polygons whose union is connected. 
+Each patch also has a unique land-cover area type.
+We use~$u$ or~$v$ to denote the patches.
+
+Recall that we are dealing with a single region and 
+there are~$n$ land-cover areas on the start map in this region. 
+Hence, the desired aggregation sequence consists of~$n-1$ steps. 
+There are~$n$ subdivisions on a path 
+from the start map to the goal map. 
+We use~$t \in T =\{1,2,\dots,n\}$ to denote \emph{time}. 
+When~$t=1$, the subdivision consists of~$n$ patches, 
+and there is only one patch remaining when~$t=n$.
+The subdivision graph consists of layers~${L}_1,\dots,{L}_n$, 
+where layer~${L}_t=\{{P}_{t,1},\dots,{P}_{t,n_t}\}$
+contains every possible subdivision~\Pnode\ with~$n-t+1$ patches 
+(see \fig\ref{fig:AreaAgg_ExponentialSize}).
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=4]{AreaAgg_Preliminaries}
+\caption{An example to show that 
+    the size of subdivision graph~$G_\mathrm{S}$
+	has exponential lower bound.}
+\label{fig:AreaAgg_ExponentialSize}
+\end{figure}
+
+Sometimes, we need a graph to represent the adjacencies of
+the land-cover areas in a subdivision,
+we call such a graph $G_\mathrm{A}$
+(see \fig\ref{fig:AreaAgg_Variables_Graph}).
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=3]{AreaAgg_ILP}
+\caption{The graph of a subdivision.
+	Each polygon of the subdivision is represented as a node 
+	in the graph.
+	There is an edge between two nodes
+	if the corresponding two polygons are adjacent.
+}
+\label{fig:AreaAgg_Variables_Graph}
+\end{figure}
+
+\subsection{Exponential lower bound}
+\label{sec:AreaAgg_Exponential}
 We now analyze the size of subdivision graph~$G_\mathrm{S}$.
@@
 (see \fig\ref{fig:AreaAgg_ExponentialSize}), 
-the start map consists of~$n=2k+1$ rectangles,
-and the goal map is simply the union of the~$n$ rectangles.
-At layer~$L_{k+1}$, we need to remove~$k$ of the~$2k$ 
-intermediate vertical boundaries. 
-For this, the number of choices is~$
-\binom{2k}{k}
-= \frac{2k\cdot (2k-1)\cdot \ldots \cdot (k+1)}
-{k\cdot (k-1)\cdot \ldots \cdot 1}
-\ge 2^k = 2^{(n-1)/2}$.
-That is to say, the size of our model
+the start map consists of~$n=2k+1$ rectangular patches,
+and the goal map is simply the union of the~$n$ patches.
+The patches have area 
+sizes~$
+%\left( 
+100 + \frac{1}{n}, 99+ \frac{2}{n}, 
+100 + \frac{3}{n}, 99+ \frac{4}{n}, \ldots, 
+99 + \frac{n-1}{n}, \text{and~} 101 
+%\right)
+$, 
+from left to right.
+According to our rule, we always 
+aggregate the smallest patch with one of its neighbors.
+Therefore, in the first~$k$ steps from the start map,
+we aggregate every other patch with one of its neighbors.
+At each of the steps, we have two choices,
+aggregating with the left patch or with the right one.
+As a result, there are~$2^k = 2^{(n-1)/2}$ subdivisions 
+in layer~$L_{k+1}$.
+That is to say, the size of subdivision graph~$G_\mathrm{S}$
 has exponential lower bound.
 
-\mypar{Methods}
+\subsection{Methods}
+\label{sec:AreaAgg_Methods}
+
 Our idea is to obtain an optimal aggregation sequence through 
@@
 than in general directed or undirected graphs.
-An off-the-shelf shortest-path algorithm for directed acyclic graphs,
+An off-the-shelf shortest-path algorithm for directed acyclic graphs
+(e.g., \textcite[\sect25.2]{Cormen2009}),
 however, will explore the whole graph, which has exponential size.
@@
 explores only a small fraction of the graph.
-
-\mypar{Notation}
-We represent each land-cover area by a polygon with a type.
-We denote by $P$ the set of polygons on the start map.
-We use~$p$, $q$, $r$, or~$o$ to denote polygons.
-A \emph{patch} is a set of polygons whose union is connected. 
-Each patch also has a unique land-cover area type.
-We use~$u$ or~$v$ to denote the patches.
-
-Recall that we are dealing with a single region and 
-there are~$n$ land-cover areas on the start map in this region. 
-Hence, the desired aggregation sequence consists of~$n-1$ steps. 
-There are~$n$ subdivisions on a path 
-from the start map to the goal map. 
-We use~$t \in T =\{1,2,\dots,n\}$ to denote \emph{time}. 
-When~$t=1$, the subdivision consists of~$n$ patches, 
-and there is only one patch remaining when~$t=n$.
-The subdivision graph consists of layers~${L}_1,\dots,{L}_n$, 
-where layer~${L}_t=\{{P}_{t,1},\dots,{P}_{t,n_t}\}$
-contains every possible subdivision~\Pnode\ with~$n-t+1$ patches 
-(see \fig\ref{fig:AreaAgg_ExponentialSize}).
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=4]{AreaAgg_Preliminaries}
-\caption{An example to show that the size of our problem 
-	has an exponential lower bound.}
-\label{fig:AreaAgg_ExponentialSize}
-\end{figure}
-
-Sometimes, we need a graph to represent the adjacencies of
-the land-cover areas in a subdivision,
-we call such a graph $G_\mathrm{A}$
-(see \fig\ref{fig:AreaAgg_Variables_Graph}).
-
-\begin{figure}[tb]
-\centering
-\includegraphics[page=3]{AreaAgg_ILP}
-\caption{The graph of a subdivision.
-	Each polygon of the subdivision is represented as a node 
-	in the graph.
-	There is an edge between two nodes
-	if the corresponding two polygons are adjacent.
-}
-\label{fig:AreaAgg_Variables_Graph}
-\end{figure}
 

### 2019-04-21 area_agg_seq_tsas.tex
improved our paper while writing review response

@@
 
-\fancyhead[LO]{Finding Optimal Sequences for Area Aggregation}
-
 \begin{document}
-\title{Finding Optimal Sequences for Area Aggregation---\protect\\ 
-	\Astar vs. Integer Linear Programming
+\title
+[Finding Optimal Sequences for Area Aggregation] %short title
+{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
+    {\protect\\ \Astar vs.\ Integer Linear Programming} %title of the paper
+    {A* vs.\ Integer Linear Programming} %title of the pdf
 }
+
 %\titlenote{Produces the permission block, and
@@
 We believe that digital maps will eventually 
-achieve smooth changes for zooming,
-and CMG is an effective way to realize smooth changes.
+achieve smooth changes for zooming.
+A simple way is to fade in and fade out raster maps
+as did by \textcite{Pantazis2009b}.
+However, we would like to carry out the changes in a more elegant way;
+we would like to change map features gradually.
 
@@
 aggregating them into neighboring land-cover areas.
+
 A \emph{land-cover map} is a planar subdivision in which 
@@
 because those algorithms do not take into account 
-the consistence of the generated maps.
+the consistence between the generated maps.
+We use both a start map and a goal map instead of using only the start map
+because our generated maps at intermediate scales should be able to
+benefit from a goal map with high quality.
 We term the areas of the goal map \emph{regions}.
@@
 to aggregate the land-cover areas on the start map
-one by one until we arrive the goal map.
+one by one until we arrive at the goal map.
 We first independently deal with each region of the goal map 
@@
 Haunert2008Assuring,Haunert2016Optimization}.
-Recall that we wish to minimize the changes of types
-when aggregating areas one by one.
-A model could be to minimize 
+When we wish to minimize the changes of types
+in aggregating areas one by one,
+a model could be to minimize 
 the \emph{greatest} change over all the steps.
-Using optimization, we are able to find optimal solutions
-of this model at least for small instances.
-If even the optimal solutions are bad,
-then the model may be not reasonable.
+Using a greedy algorithm,
+we can minimize the change at each step,
+but the result does not necessarily minimize the greatest change
+over all the steps.
+If a result is bad,
+we cannot tell if the bad result comes from the model 
+or from the greedy algorithm.
+Using optimization,
+we are able to find optimal solutions
+of the model at least for small instances.
+If even an optimal solution is bad,
+then we can exclude that the bad result 
+is from the greedy algorithm.
+That is to say,
+the bad result is because of the model.
 In this case, we should improve the model; 
@@
 How to aggregate exactly is decided by 
-optimizing a global cost function.
+optimizing a global cost function
+(see \sect\ref{sec:AreaAgg_CostFunctions}).
 This requirement ensures that the 
@@
 A \emph{patch} is a set of polygons whose union is connected. 
-Each patch also has a unique land-cover area type.
+Each patch also has a unique land-cover type.
 We use~$u$ or~$v$ to denote the patches.
@@
 we aggregate every other patch with one of its neighbors.
-At each of the steps, we have two choices,
+However, we do not know which one is the right choice
+at each of the steps,
+in order to minimize our costs (see \sect\ref{sec:AreaAgg_CostFunctions}).
+We have to try both of the two choices,
 aggregating with the left patch or with the right one.
@@
 An off-the-shelf shortest-path algorithm for directed acyclic graphs
+%\parencite[e.g.,][\sect25.2]{Cormen2009},
 (e.g., \textcite[\sect25.2]{Cormen2009}),
@@
 if it is more compact (less clutter).
-In this paper, we ignore the fact that
-some features may inherently take linear forms
-(e.g., rivers).
 %
@@
 \caption{Aggregating land-cover areas 
-	according to different preferences.
+	according to different preferences
+    by \textcite{Cheng2006}.
 	Aggregating a small land-cover area into another one 
@@
 \cdot
-\frac{d(T(u),T(v))}{T_{\max}},
+\frac{d_\mathrm{type}(T(u),T(v))}{d_\mathrm{type\_max}},
 \end{equation}
@@
 (see \sect\ref{sec:AreaAgg_Preliminaries}).
-We use~$A_R$ and~$T_{\max}$ 
+We use~$A_R$ and~$d_\mathrm{type\_max}$ 
 to normalize the cost of type change. 
-Constant~$T_{\max}$, the maximum cost over all type changes,  
+Constant~$d_\mathrm{type\_max}$, the maximum cost over all type changes,  
 is known from the input. 
 The input specifies, for each pair~$(T_1,T_2)$ of types, 
-cost~$d(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
+cost~$d_\mathrm{type}(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
 Specifically, we denote by~$T_\mathrm{goal}$ the type of 
@@
 
-\begin{figure}[h]
+\begin{figure}[tb]
 \centering
@@
 if the type distances fulfill that
-$d\left(T(u), T_\mathrm{goal}\right) 
-\ge d\left(T(v), T_\mathrm{goal}\right)$;
+$d_\mathrm{type}\left(T(u), T_\mathrm{goal}\right) 
+\ge d_\mathrm{type}\left(T(v), T_\mathrm{goal}\right)$;
 otherwise, the algorithm aggregates~$v$ into~$u$.
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[tb]
 \centering
@@
 	lower bound of the total length of the interior boundaries, 
-	i.e., $l_\mathrm{int}(P_{s,i'''_s})$.
+	i.e., $\ell_\mathrm{int}(P_{s,i'''_s})$.
 	The numbers represent the 
@@
 In this tree, the maximum distance is~$6$, 
-which means~$T_\mathrm{max}=6$ for \eq\ref{eq:f_type}.
+which means~$d_\mathrm{type\_max}=6$ for \eq\ref{eq:f_type}.
 According to \citet{Rada1989SemanticMetric}, 
@@
 According to \fig\ref{fig:AreaAgg_TypeDistances},
-type distances~$d(5112,4102)=4$ and~$d(2112,4102)=6$.
+type distances~$d_\mathrm{type}(5112,4102)=4$ and~$d_\mathrm{type}(2112,4102)=6$.
 As a result, our greedy algorithm uses~$5112$ 
@@
     while the type of the largest polygon changed twice 
-    in the sequence obtained by the Greedy algorithm.}
+    in the sequence obtained by the greedy algorithm.}
 \label{fig:AreaAgg_CaseStudy1_Rg85}
@@
 %	result, we needed to overestimate (with factor~$K=8$).}
+
+\clearpage
 
@@
 
+%\clearpage
+
 \section{Concluding Remarks}
@@
 %
+In our setting, we ignored the fact that
+some features may inherently take linear forms
+(e.g., rivers).
+%
 These issues can be considered in our future work.
@@
 \printbibliography
+
+\clearpage
 
@@
 \left(\frac{a_p}{A_R} \cdot
-\frac{d(T(o),T(r))}{T_{\max}}\cdot 
+\frac{d_\mathrm{type}\left(T(o),T(r)\right)}{d_\mathrm{type\_max}}\cdot 
 y_{t,p,o,r}\right), & 
@@
 	\frac{1}{2} \sum_{p \in P}\sum_{q \in P}\sum_{r \in P} 
-	\big(|b_{pq}|\cdot z_{t,p,q,r}\big)} {D(t)}, &
+	\left(|b_{pq}|\cdot z_{t,p,q,r}\right)} {D(t)}, &
 \end{flalign}
@@
 \frac{\sum_{p \in P}\sum_{q \in P}\sum_{r \in P} 
-	\big(|b_{pq}|\cdot z_{t,p,q,r}\big)}
+	\left(|b_{pq}|\cdot z_{t,p,q,r}\right)}
 {2(n-t)\sum_{b\in B (\Pstart)} |b| }

### 2019-04-21 review_response/review_response.tex
added review_response.tex

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence 
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/) 
%
% BASIC INSTRUCTIONS: 
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,11pt]{reviewresponse}
\input{review_response_setting}

\begin{document}

\thispagestyle{plain}

\begin{center}
	{\Large\myTitle} \vspace{0.5cm} \\
%	{\large\myJournal} \vspace{0.5cm} \\
	\today \vspace{0.5cm} \\
	\myAuthors \\
	\url{\myEmail} \vspace{1cm} \\
	\myDept
\end{center}

\tableofcontents

\begin{abstract}
	We thank the anonymous reviewers for their comments.
    These comments are very useful for us to improve our paper. 
    Below, we address every comment carefully and 
    explain the corresponding changes in the manuscript.
\end{abstract}

\section{Reviewer 1}

\rcommentnoskip{
The paper describes an interpretation of the area aggregation problem as the computation of a shortest path in a suitably defined graph.
The contents of the paper are an interesting read and certainly well within the scope of TSAS.

Though I have some comments/questions about certain parts (see below), the paper is of good quality already and warrants (eventual) acceptance.         
}

\textbf{Response} Thanks for the positive comments.

\rcomment{
Problem complexity. Though the exponential lower bound works, the given example seems excessively degenerate. It works only by assuming that all rectangles have identical area---otherwise, the ``smallest area must aggregate'' severely limits the options. Can the construction be altered to show an exponential lower bound where all regions have unique sizes? (or under some other assumption that is more realistic).

Complementing this paragraph, I'm also wondering if anything is known about whether the specific problem considered here is NP-hard?  
}

\textbf{Response}
We have improved our proof of the exponential lower bound.
In the new proof, all the rectangles have unique sizes;
see Section 3.3 (Exponential Lower Bound).
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

\rcomment{
Compactness. 
Two models for compactness are given, one being linear and the other not. 
The motivation for needing the linear model is clear, 
but how different are these models? 
Is there any literature that already describes the correlation between these? 
Otherwise, I feel that the paper could be enriched 
by considering the correlation between the two in this setting 
(how well does \Astar-$g_2$ perform in terms of \Astar-$g_1$ / 
does it give similar quality when measuring $g_2$-results using $g_1$, 
or something like that). 
(Assuming you have the data/solutions, this would be comparatively easy to do?)
}

\textbf{Response} 
To the best of our knowledge, 
there is no literature describing 
the correlation between the two models for compactness.
\textcite{Li2013Compactness} reviewed some measures for compactness.

This comment will lead to an interesting research.
Of course, it is easy to compute the~$g_1$ value of the result of~\Astar-$g_2$,
and vice versa, since we have the data.
If we present the values, then it would be better to also theoretically analyze the correlation between the two compactness formulas,
which could lead to a new paper.
We may perform this research in our future work.

\rcomment{
Greedy algorithm. 
I'm missing some motivation in the paper for the given greedy choice. 
Specifically, why was this method chosen over other clear candidates? 
(e.g., always ensuring the smallest region is recolored, 
regardless of what the target eventually is?). 
Fig 18. describes a ``bad choice'' for the given greedy strategy, 
but I see no motivation/example of why it would be a good choice.
}

\textbf{Response} We have a start map and a goal map.
Our greedy algorithm must ensure that 
our final result (e.g., the polygon of layer $L_4$ in
Figure 3) will have the type of $T_\mathrm{goal}$.
This is why we should not always recolor the smallest region.
We have added this argument in Section 6 (A Greedy Algorithm).

We use a start map and a goal map because 
our aggregation sequence should be able to 
benefit from a goal map with high quality.
We have added this argument 
in ``Problem definition'' of Section 1 (Introduction).

We have added more details 
into the caption of Fig 18 (Fig 17 in the new version).

\rcomment{
Though I would rate the organization as ``acceptable'', there are many parts where I feel the presentation can be streamlined. Some points of attention:

The contributions only appear on page 5. Much of the text before is ``related work'', but much of it is only tangentially related (e.g. the apparent need to defend optimization approaches)

The problem definition is partially in the preliminaries and in the introduction (though the paragraph ``problem definition'' in the introduction seems to only partially define that problem and then continue with related work).

(Partial) suggestion: restructure such that problem definition and contributions come before ``optimization in map generalization'' and structure the paragraphs of ``optimization in...'' as related work). 
}

\textbf{Response}
We have put ``Problem definition'' and ``Contribution'' 
into Section 1 (Introduction).
We have made an individual section for related work;
see Section 2 (Related Work).

\rcomment{
Personally, I found there to be little value in the 2-page explanation on what linear programming is. It seems out of place to me, and a good place to streamline(/shorten) the exposition.

Variables, objective function and constraints are explained in separate paragraphs. I'm wondering if there is a different organization possible that requires less of the ``recall that ...'' phrasing. For example, some of the basic constraints that relate the meaning of the various variables could just be given immediately.

But that will allow integration of considerations and solutions. For example, when reading the definition of~$c_{t,p,o,r}$, I immediate wonder why that variable helps to solve connectivity (why can't two neighboring areas identify each other as the neighbor...)

It is a style-preference I suppose, but I'd rather have the ILP be built up of variables+constraints+explanation of the various smaller parts, rather than having all the variables up front (and needing to recall).

Also, something that would help a lot here is to use more meaningful variable names (instead of $x,y,z, \ldots$), such that it is easier to remember what's what.

}

\textbf{Response}
Some researchers from Geographic Information Science 
may not be familiar with integer linear programming.
Therefore, we use the coffee example to illustrate the ideas of LP and ILP.
We have put the method of using integer linear programming into Appendix.

We think it is easier for readers 
to find the definitions of variables, objectives, and constraints
if we present them in separate paragraphs.
If we mix the definitions, readers may need to search for a specific definition 
in more paragraphs as some constraints consist of two kinds of variables.

We would also like to use more meaningful variable names, 
but we do not have a good idea to do so as our variables are quite complex.

\rcomment{
With the experimental results, many of the figures and tables are far away from their referencing text. I would suggest introducing some clearpage commands to get them closer to each other, and(/or) adding some more detail to the captions to explain the main observations in the caption as well.
}

\textbf{Response} We have added a clearpage before 
Section 9.2 (Using costs of type change and length).
We have added some details to the captions of 
Figure 17, Figure 23, and Table 1 (see the new version of our paper).

\rcomment{
Introduction: to what degree is continuous generalization, 
in terms of having no discrete changes, 
possible / desirable / realistic?
}

\textbf{Response} We believe that continuous generalization is possible,
desirable, and realistic. 
We have added more arguments in Section 1 (Introduction).

\rcomment{Fig. 5 (and associated text) describes four alternative aggregation preferences. It seems that (unless degenerate) options (b) and (c, d, e) cannot be applicable simultaneously.
}

\textbf{Response} Figure 5 shows some ideas of \textcite{Cheng2006}.
It is fine options (b) and (c, d, e) cannot be applicable simultaneously.
We present this figure to show some inspirations that we got from reading the paper.
We have added the reference of \textcite{Cheng2006} into the caption.

\rcomment{Section 3.1. Is there a specific reason why the metric considers only the change between two levels? It seems that, unless the resulting patch is immediately part of another aggregation, the choice made has a longer lasting effect. In other words, in all subsequent maps, the choice causes some ``error'' in the intermediate map, yet this is only measured once.
}

\textbf{Response}
A reason is that we want to make the changes small 
so that users can follow maps easily.
We have added this argument in Section 1 (Introduction).

\rcomment{Fig. 24 -- the problem is attributed to the small shared boundary. But is this not ``simply'' an issue of compactness? (That is, the compactness is not weighted heavily enough / or not captured adequately?).
}
\textbf{Response} This is a good point of view.
In order to make the reason clear, we will need to do more experiments.
That can be our future work.

\rcomment{Can this approach also work if no target map is not given (or has no predefined type)?
}

\textbf{Response} No, we need a target map in order to use the \Astar algorithm,
which finds a shortest path from a start to a target.
However, if there is no target map, we can always generate one 
by an existing algorithm \parencite[e.g.][]{HaunertWolff2010AreaAgg};
see Section 1.

\rcomment{p2: "at any different scales" \\
p3: "as good as" -> "as well as" \\
p3: "He repeatedly displace the line until finding..." -> 
displaced/displaces \& until a ... is found  \\
p4: "based on constr. DT" -> "based on a constr. DT" or 
"based on constr. DTs". \\
p8: "by human being" -> "by a human being" \\
p32: should the equation here not have $p$ and $q$ swapped on one of the sides? \\
}

\textbf{Response} We have improved our paper according to all the six comments.

\clearpage

\section{Reviewer 2}

\rcommentnoskip{
This paper introduces a problem of continuous map generalization in which a set of polygons (referred to as the start map) is sequentially merged into a smaller set of polygons (referred to as the goal map) and compare different approaches in terms of effectiveness and efficiency. Any aggregation sequence must satisfy specific constraints, and of all such sequences, one that minimizes a specific objective function is considered as optimal.

The paper is well written, but there may be some issues to be addressed before it is further considered for publication.

In particular, the importance of the problem is questionable. The problem relies on the following assumptions: 1) The start map and the goal map consist of polygons each of which belongs to a given land-cover type. 2) Every polygon on the goal map is the union of a set of polygons on the start map. The first assumption is fine, but the second assumption considerably limits the problem’s applicability. It seems to me that the problem is interesting if the two maps come from different sources. If the goal map has been derived from the start map, the problem won’t be too different from other problems of continuous map generalization available in the literature.
}

\textbf{Response}
Even if the goal map has been derived from the start map,
the problem is still difficult if we want to have an optimal aggregation sequence.
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).
No literature has tried to solve this problem.

\rcomment{In ``A model could be to minimize the smallest change over all the steps'' (page 3) doesn't sound right. Do you mean to minimize ``greatest'' change? I may overlook something, though.
}

\textbf{Response} We indeed meant that 
an idea could be to minimize the ``smallest'' change
because we wanted to show that ideas could be bad.
However, in the new version of our paper, we changed ``smallest''
to ``greatest'' because using ``smallest'' sounds too stupid.

\rcomment{
The detailed introduction of ``Integer Linear Programming'' (with a coffee example) is not necessary.
}

\textbf{Response}
Some researchers from Geographic Information Science 
may not be familiar with integer linear programming.
Therefore, we use the coffee example to illustrate the ideas of LP and ILP.
We have put the method of using integer linear programming into Appendix.

\rcomment{The discussion on the relevance of compactness to the problem is weak. Should we impose the compactness criterion on all polygons? Some landscape features may inherently take linear forms, e.g., corridors. Does the measurement presented in Sec. 3.2 take into account the irregularity of polygons’ shapes (especially on the start map)? Is it possible (or likely or unlikely) that a non-compact polygon to be aggregated causes any bias in the aggregation sequence? 
}

\textbf{Response}
Indeed, our method will be more reasonable 
by taking into account irregular shapes.
This extension can be a future work of our paper.
In Section 10 (Concluding Remarks),
we have added
``In our setting, we ignored the fact that
some features may inherently take linear forms
(e.g., rivers)''.

\clearpage

\section{Reviewer 3}

\rcommentnoskip{

The introduction is very clear, and motivates the reader to read further.

I'm usually not a fan of having the related work woven into the introduction, but in this case, the presentation remains clear, the proposed problem is well-defined, and the contributions are delineated from the related work. In particular, the examples of Figure 1 and Figure 2 take the reader by the hand to help them understand the problem. Specifically, the authors nicely clarify that both the ``start map'' and the ``goal map'' are BOTH input parameters.

This clarifies that the goal of this paper is not to find a good generalized map, but rather, how to smoothly generate it.

Overall, the introduction is a pleasure to read. 
}

\textbf{Response} We have put the related work in an individual section;
see Section 2 (Related Work).

\rcomment{Major Revision 1:

Your model is clear and well-described. The presented subdivision graph is clearly understood.

I understand that you are using shortest-path algorithms such as A* on this graph. However, this graph is a directed acyclic graph (DAG), for which more efficient solutions for shortest-path search are known, such as ones based on topological sorting. It appears to me, that the DAG property of the subdivision graph can be exploited to achieve higher efficiency.

Baseline algorithms used for the experimental evaluation should include shortest path algorithms which are designed for DAGs.
}

\textbf{Response} We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

An off-the-shelf shortest-path algorithm for directed acyclic graphs
(e.g., \textcite[\sect25.2]{Cormen2009})
will explore the whole graph, which has exponential size.
Therefore, it is almost impossible to use a DAG-based algorithm
for our problem.
We have added this argument in Section 3.4 (Methods).

\rcomment{Major Revision 2:

The exponential lower bound in Section 2  appears to be wrong. It shows that your solution has an exponential lower bound, but it does not show that the problem has an exponential lower bound.

This is similar to the problem of sorting at array of~$n$ numerical values: There is an exponential number ($n!$) of possible intermediate steps. Any approach that enumerates all of these $n!$ possible orderings is exponential. Yet, the problem of sorting an array is not exponential.

The same appears to apply here: Would it be possible to simply aggregate the smallest region in each step, yielding a total run-time of $n$?

Would that solution be optimal? That would depend on your cost function, which is not yet defined in this part of the paper.

But in the preliminaries, you state that: ``To find a sequence of small changes that transforms the start map into the goal map, we require that every change involves only two areas of the current map. More precisely, in each step the smallest area~$u$ is merged with one of its neighbors (adjacent areas) $v$ such that~$u$ and~$v$ are replaced by their union.''

This implies that a greedy approach that always takes the smallest values would be optimal, thus leading to the ``merge-sort'' like approach sketched earlier in the paper.

Your proof of an exponential lower bound must show, not only that there exists and exponential number of states, but that any correct algorithm must explore an exponential number of states in the worst-case. Or, in other words, in the worst-case, an exponential number of nodes cannot be pruned. 
But if the task is simply to merge the smallest area with the smallest adjacent areas, then only one option remains unpruned in each step, yielding linear run-time.

Note that I am not saying that the problem is not exponentially hard for certain cost functions. But you need to clarify, for the cost function that you propose, whether the problem is exponentially hard, and how greedy and dynamic programming algorithms can not possibly find the correct answer, efficiently.
}

\textbf{Response}
We have improved our illustration of exponential lower bound;
see Section 3.3 (Exponential Lower Bound).
We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

\rcomment{

I'm confused about the combination of cost functions. You propose three different cost functions, based on type ($g_\mathrm{type}$), based on compactness ($g_\mathrm{comp}$), and based on length ($g_\mathrm{lgth}$). However, in Section 3.4., you only ``combine the two cost functions''.

Why not combine all three? Why is the third defined? Why are there two combinations using two different two-subsets of cost functions?
}

\textbf{Response}
As illustrated in Section~4 (Cost Functions),
our cost function takes two aspects into account: 
one based on semantics and the other based on shape.
This is why we define~$g_\mathrm{type}$ and~$g_\mathrm{comp}$.
We also want to compare the \Astar and a method based on integer linear programming
in solving our problem, while $g_\mathrm{comp}$ cannot be computed linearly.
So we combine~$g_\mathrm{type}$ and~$g_\mathrm{lgth}$ when we make the comparison.
We have made this more clearly in Section~4.4 (Combining Cost Functions).

\rcomment{
Major Revision 3:

Section 4 is incomplete. This section defines a first part of a greedy baseline algorithm, and defines two cost functions. However, it is not clear how a greedy algorithm would utilize these cost functions.

A greedy algorithm should simply choose the patch which minimizes 
$argmax_\mathrm{candidate~patches}$ CostFunctionDefeindInSection3.

The authors need to properly define the Greedy algorithm. Reading the experiments, I'm merely assuming that the greedy algorithm does what I expect it to do (see above).
}

\textbf{Response} We have improved the section,
which becomes Section 6 (A Greedy Algorithm) in the new version of our paper.

\rcomment{
Very Major Problem 1:

The proposed Integer Linear Programming algorithm does not have convincing results. It only terminates for goal polygons having a trivially small number of sub-polygons. Even in the cases where it terminates, the result is worse than A*, and not significantly better than the naive greedy.

Due to these terrible results, I feel that there is not much intellectual merit in this approach. I suggest that authors remove details of this approach, almost entirely. The authors could still use this approach as a competitor (explained in one paragraph) in the experiments. But as a main contribution, this approach fails to deliver any meaningful results.

Instead, the authors may try different approaches that exploit that the subdivision graph is a DAG. Exploiting this property may allow significant improvement over A*.
}

\textbf{Response}
We have put the method of using integer linear programming into Appendix.

We have added a section to show that our problem is NP-Hard;
see Section 5 (NP-Hardness Proof).

An off-the-shelf shortest-path algorithm for directed acyclic graphs
(e.g., \textcite[\sect25.2]{Cormen2009})
will explore the whole graph, which has exponential size.
Therefore, it is almost impossible to use a DAG-based algorithm
for our problem.
We have added this argument in Section 3.4 (Methods).

\rcomment{Minor comments:

Page 6 Line 45: ``The patch also has the property type''. 
Please clarify what this means. I am assuming, that you want to say that each patch also has a unique land-cover area type.
In Equation 1: Region~$R$ is undefined? Should it be~$v$ instead of~$R$?

I cannot understand the idea of Figure 9. It appears that Figure 9a is not a valid partitioning.
}

\textbf{Response} According to your suggestion, 
we changed ``The patch also has the property type''
to ``Each patch also has a unique land-cover type''.
In the new version, we define region~$R$ in Section 3 (Preliminaries).

Figure 9a is not a valid partition, but it is fine for estimation.
In the new version of our paper, we add a reference to Section 7.1.

\rcomment{To summarize:

I like the problem defined in this paper, and I like the motivation and presentation. However, the main approach presented in this work (using Linear Programming) does not yield any useful theoretic or experimental results. Thus, the intellectual merit of this approach is highly questionable.

If the authors could find a better performing solution, that has more technical contribution than the \Astar and Greedy approaches, this could be a great paper!

Overall, I feel that this is more of a ``Submit as New'' recommendation from my side. But since I have to decide between Major Revision and Reject, I chose the former.
}

\textbf{Response} Formalizing our problem as a path finding and solving it with the \Astar are two of our main contributions.
We do not have a better solution so far.
We have put the method of using integer linear programming into Appendix.

\clearpage

\section{Reviewer 4}

\rcommentnoskip{
The paper deals with a very common problem when drawing a map at different scales. Typically, when drawing a `zoomed-out' view of a map, not all details need to or in fact should be drawn to avoid cluttering of the visualization. How to deal with unwanted details depends on the nature of the respective details, for roads, one typically just drops smaller and unimportant roads while zooming out. The focus of this paper is how to deal with areas while zooming out -- here simply dropping them is typically not what is desired, e.g., if we have a city partitioned in many quarters, from some distance these quarters should not simply disappear but rather be merged to represent the area of the city as a whole.

The authors focus on sequential merges, that is, always two areas are aggregated in a single step until a target subdivision is reached. Not surprisingly there are exponentially many ways of reaching the target subdivision. By associating costs to each merge step (based on type changes, compactness and boundary lengths), they can evaluate any merge sequence. While of course aiming for an optimal solution they first propose a simple greedy algorithm. Then an A* based approach is presented which in principle can find the optimum solution, yet typically runs out of memory, so a variant which cannot guarantee to find the optimum is employed. Finally an ILP formulation is presented. The approaches are evaluated in the experimental section. 
}

\textbf{Response} Thanks for the summary.

\rcomment{
[Strengths]
The paper is very nicely written, the reader is cautiously introduced to all concepts. The problem as such is interesting and important. 
}

\textbf{Response} Thanks for the positive comments.

\rcomment{
[Weaknesses]
What is the conceptual difference to [25]? This seems very much related with the main difference that the current work also cares about the quality of intermediate aggregations.
Somehow I found the experimental evaluation somewhat underwhelming. The gain from running A* which is about two orders of magnitudes slower seems miniscule to me. Likewise the application of an ILP solver seems overkill. In fact I do not have a good feeling for whether a slightly better solution via ILP or A* really makes a difference for me when I see the respective intermediate maps.

While I think it is a nice paper, I miss a crip or surprising insight or algorithmic technique. In fact in particular in the light of [25] it seems as a somewhat straightforward extension. Also, I suspect that whether the final results are pleasing to the eye or not, is more dependent on the choice of the cost functions rather than the optimal or close-to-optimal computation of a merge sequence.

The paper should certainly be published, but for a flagship journal like TSAS I do not think that the paper is strong enough.
}

\textbf{Response} 
\textcite{HaunertWolff2010AreaAgg}, 
reference 25 of the previously submitted version, 
deals with map generalization,
while our method deals with \emph{continuous} map generalization.
Even the results of the \Astar algorithm are only slightly better
than that of the greedy algorithm, 
it is still worth to use the results of the \Astar algorithm.
We can save the results obtained by the \Astar algorithm on a server,
when users are zooming on a map, we can simply send the precomputed results.

It is true that whether the final results are pleasing to the eye or not 
is also dependent on the choice of the cost, 
but it is still important to get optimum results according to a certain cost.
Even using a perfect cost function, a greedy algorithm can return a bad result.
If we get a bad result from a greedy algorithm,
then it is difficult to tell if the bad result is from the choice of the cost
or from the greedy algorithm.
We have explained this more clearly in Section 2.2 
(Optimization in Map Generalization).

%
%\rcomment{
%Generally, the paper would benefit from a bit of reorganization.
%}
%
%\textbf{Response} 
%We have reorganized our paper somewhat.
%
%\rcomment{
%Your writing is clear and concise (thank you!), but I often found myself having to accept that explanation of some critical component might come later (which it generally does). One example of this is with regard to type-change cost, which is described well with respect to its weighted calculation at a given node along a given path, but itself is never defined until you present a case study with ATKIS data.
%}
%
%\textbf{Response} 
%We have improved our writing according to this comment. Speaking of type-change cost, we think it is better to give the details with ATKIS data because the type-change cost is dependent on the data and known from the input.
%
%\rcomment{
%I found myself wondering what exactly costs were measured by as soon as they were mentioned (i.e., what units are used in the function $\mathrm{Cost}(x,y)$). You explain shape-change costs well (counts of boundaries, etc.), but you only give a measure of type-change costs in your case study.I admit I'm a little surprised at your choice -- ordinal count of sequenced land cover class -- because it is fraught with subjectivity and error, and stands in contrast to the admirable rigor you employ at every other point. Despite a reasonable effort by anyone classifying land cover types, they are certainly not ordinal (except perhaps for small "local" cases like sparse vs. dense forest). That means that the ordinal differences you count in your calculation of type-change cost are meaningless. (a suggestion: type-change cost estimation measured as the area changed (i.e., area made uncertain) at each possible aggregation).
%}
%
%\textbf{Response} 
%We think you misunderstood our definition of $\mathrm{Cost}(x,y)$. In the revised version, we added the tree for type-change cost. Now it is clearer how we define the cost.
%
%
%\rcomment{
%The paper is nicely formal, but my sense is that you're perhaps not accounting for (messy) real-world geography enough. You seem to be very casually ignoring class heterogeneity in your aggregated polygons. (If you develop an appropriate type-change cost metric, you could keep reasonable track of this.) How well does your algorithm handle area-fractured or thin linear areas such as braided streams, highways, canals?
%}
%
%\textbf{Response}
%Indeed, we haven't considered thin linear areas such as braided streams, highways, canals. These thin linear areas had been removed from a earlier work by \citet[Chapter~6]{haunert2008f}.
%
%\rcomment{
%	You mention in the conclusion (and not before!) that one objective is to keep more "important" patches for longer -- yet you do not do this at all here. What you do is cull the smallest patches at each step (i.e., you are using area as the criteria, not importance). Also, twice you make relatively objective assumptions in your algorithm that I don't think you satisfactorily explain, and they need explanation because they're geographic impossibilities: 1) why do you work toward a single classed polygon at $t_\mathrm{goal}$? and 2) in your type-cost estimation for \AstarNoSpace, does allowing impossible mergers as you do make for a realistic cost estimation?
%}
%
%\textbf{Response}
%We have not considered more "important" patches for longer because this consideration needs more effort. We may consider more "important" patches in our future work. We work toward a single classed polygon at $t_\mathrm{goal}$ because there are many algorithms \citep[e.g.,][]{haunertwolff2010b, vanSmaalen2003, Cheng2006} that aggregate some land-cover areas into one single land-cover area. The data and the generalized results of these algorithms can be used as our input. Our estimation for type-change cost is fine with a realistic cost estimation because we may find a shortest path as long as the estimation is bounded from above by the exact cost of a shortest path.
%
%\rcomment{
%The notion of a seed patch never comes up after being introduced.
%}
%
%\textbf{Response} 
%The notion of a seed (core) patch was used in a previous version. Sorry for that we forgot to remove the notion in the submission. Now we have removed it.
%
%
%\rcomment{
%Surely there is more literature on polygon aggregation/segmentation using graph theory approaches in other fields like computer vision? You should review this material.
%}
%
%\textbf{Response}
%We have reviewed more literatures on polygon aggregation; see the section of introduction.	
%
%\rcomment{
%Clarify sooner that the particular neighboring polygon into which the smallest polygon is aggregated is made by a global optimization of cost.
%}
%
%\textbf{Response}
%We have improved our paper according to this comment; see the section of preliminaries.
%
%\rcomment{
%Equation 3: what's $n$ exactly? Number of possible succeeding nodes? Or do you mean the number of nodes in the path?
%}
%
%\textbf{Response}
%Variable $n$ is the number of land-cover areas on the start map. The union of the $n$ areas is the only region on the goal map. We have added the description of $n$ in the section of preliminaries.
%
%\rcomment{
%I would appreciate a better rationale for why you absorb the smallest polygon at each iteration. For example, it would be difficult to make the case that the smallest is the least important (because small things in the real world can be greatly important), but relatively easy to say it's the least visibly-important (as per ideas like Tobler's map resolution, or Li and Openshaw's Natural Principle).
%}
%
%\textbf{Response}
%We consider the smallest area as the least important, instead of involving more rules for importance, to avoid making our problem too complicated. We have added this argument in the section of preliminaries.
%
%\rcomment{
%Be careful to keep a clear terminological distinction between different meanings of "edge" - in 2.4, you're talking about what I would call arcs, or line segments, between vertices in a polyline, whereas "edge" was used earlier to refer to the graph theory concept.
%}
%
%\textbf{Response}
%In the revised version, we use "arc" to refer to the graph theory concept. We use "edge" for the line segments of the patch boundaries. 
%
%
%\rcomment{
%Fig 11 - not useful, even though all the others are. This figure would be better if you gave the same region at the same series of iterations with multiple K values (i.e., isolate the K variable).
%}
%
%\textbf{Response} 
%This figure is actually useful. In our method, we repeat increasing overestimation factor until we have a feasible solution. The results displayed in the figure are from the least repetitions we need in order to have feasible solutions. We have made this idea clearer in the revised version.
%
%\rcomment{
%In the conclusions, you seem certain that too much overestimation of costs led to poor results, whereas earlier in the paper you suggest it could be that, or a poor estimation metric.
%}
%
%\textbf{Response}
%A larger overestimation factor does not necessarily mean a poorer result. A better estimation can help \AstarSpace reduce more search space. We have added these descriptions in the revised version; see the section of formalizing area aggregation as a pathfinding problem and the section of conclusions.
%
%\clearpage
%
%\section{Reviewer 2}
%
%\rcomment{
%The "Model", "Notation", and "Exponential lower bound" are fundamentals of the research. They should be put in the methodology section.
%}
%
%\textbf{Response} 
%We made a new section "Preliminaries", and put "Model", "Notation", and "Exponential lower bound" in the new section.
%
%\rcomment{
%Why use \AstarSpace algorithm? Any other alternative methods?
%}
%
%\textbf{Response} 
%We have compared the \AstarSpace algorithm with the integer linear programming (ILP) algorithm. We have added a sentence about this comparison in the revised version; see the section of conclusions. We should also compare the \AstarSpace algorithm with a greedy algorithm, which is our future work.
%
%\rcomment{
%In the experiment, it should be better if the results can be compared to other methods.
%}
%
%\textbf{Response} 
%We compared the algorithm with the ILPs algorithm, and the \AstarSpace algorithm did a better job. We have added a sentence about this comparison in the revised version; see the section of conclusions.
%
%\rcomment{
%In the paper, too many active voice is used. Sentences with "we want/consider/define..." can be revised to passive voice.
%}
%
%\textbf{Response} 
%We have removed some inappropriate active voice. However, we believe that active voice is more direct and clear, so we often use active voice.
%
%\rcomment{
%In Fig1, "input (goal map)" -> "output (goal map)".
%}
%
%\textbf{Response} 
%In Fig1, "input (goal map)" is correct.

%\clearpage

%	\section{Reviewer 3}
%	
%	\rcomment
%	{
%		I would like to see a few add ons to substantiate the approach in particular
%		regarding its limits...
%	}
%	
%	\textbf{Response}
%	
%	We want to thank the reviewer for this comment. In order to satisfy this
%	petition we have added a new Subsection...
%	
%	We thank the reviewer for this comment and we agree with him/her. We have
%	rewritten the paragraph following his/her comments: 	
%	
%	\begin{quotation}\noindent
%		Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem
%		Ipsum has been the industry's standard dummy text ever since the 1500s, when an
%		\newtext{unknown printer} took a galley of type and scrambled it to make a type
%		specimen book. It has survived not only five centuries, but also the leap into
%		electronic typesetting, remaining essentially unchanged. It was popularised in
%		the 1960s \newtext{the release of Letraset sheets containing Lorem Ipsum
%			passages}, and more recently with desktop publishing software like Aldus
%		PageMaker including versions of Lorem Ipsum.
%	\end{quotation}

%	 Uncomment in case references are needed
%\bibliographystyle{apalike}
%\bibliography{References}

\printbibliography

\end{document}

### 2019-04-24 review_response/review_response.tex
improved our paper and response according to Jan's comments

@@
 We thank the anonymous reviewers for their comments.
-    These comments are very useful for us to improve our paper. 
-    Below, we address every comment carefully and 
-    explain the corresponding changes in the manuscript.
+These comments were very helpful for us to improve our paper. 
+In this document, 
+we provide detailed responses to each of the reviewers' comments. 
+The following list summarizes our most important changes:
+\begin{itemize}
+    \item  An NP-hardness proof has been added.
+    \item  The illustration of the exponential lower bound has been improved.
+    \item  The approach based on integer linear programming 
+    has been moved to the appendix.
+    \item  Several comments concerning the applied compactness measures 
+    have been incorporated.
+\end{itemize}
 \end{abstract}
@@
 \textbf{Response}
-To the best of our knowledge, 
-there is no literature describing 
-the correlation between the two models for compactness.
-\textcite{Li2013Compactness} reviewed some measures for compactness.
+In theory, a patch, $u$, with a small perimeter can be extremely non-compact according to measure~$c(u)$ in \eq3, thus the two measures that we consider are not interchangeable.
+However, if we assume that all areas of the map have the same size (i.e., $A_u$ is a constant), it would make no difference whether we minimize an area's perimeter or maximize the area's compactness~$c(u)$.
+Obviously, the areas in our data set have different sizes.
+However, since we iteratively remove the smallest area, the differences do not become too large.
+Therefore, measuring the overall compactness of a map based on the total length of all the interior boundaries is quite reasonable.
+We have added this argument into Section~4.3 (Cost of Length).
 
-This comment will lead to an interesting research.
-Of course, it is easy to compute the~$g_1$ value of the result of~\Astar-$g_2$,
-and vice versa, since we have the data.
-If we present the values, then it would be better to also theoretically analyze the correlation between the two compactness formulas,
-which could lead to a new paper.
-We may perform this research in our future work.
+%To the best of our knowledge, 
+%there is no literature describing 
+%the correlation between the two models for compactness.
+%\textcite{Li2013Compactness} reviewed some measures for compactness.
+%
+%This comment will lead to an interesting research.
+%Of course, it is easy to compute the~$g_1$ value of the result of~\Astar-$g_2$,
+%and vice versa, since we have the data.
+%If we present the values, then it would be better to also theoretically analyze the correlation between the two compactness formulas,
+%which could lead to a new paper.
+%We may perform this research in our future work.
 
@@
 
-\textbf{Response} We have a start map and a goal map.
+\textbf{Response} 
+A motivation for our greedy algorithm is that 
+a very similar iterative algorithm has been used by
+\textcite{vanOosterom1995Development} 
+for constructing the tGAP data structure.
+However, we have to make minor modifications to ensure that 
+the computed aggregation sequence ends with the goal map that, 
+in our situation, is given as a part of the input.
+We use our greedy algorithm as a benchmark
+so that we are able to see 
+whether the \Astar algorithm or the ILP-based algorithm 
+indeed perform better.
+We have added this argument into Section 6 (A Greedy Algorithm).
+
+We have a start map and a goal map.
 Our greedy algorithm must ensure that 
@@
 This is why we should not always recolor the smallest region.
-We have added this argument in Section 6 (A Greedy Algorithm).
+We have added this argument into Section 6 (A Greedy Algorithm).
 
@@
 We have added this argument 
-in ``Problem definition'' of Section 1 (Introduction).
+into ``Problem definition'' of Section 1 (Introduction).
 
@@
 
-\textbf{Response} We believe that continuous generalization is possible,
-desirable, and realistic. 
+\textbf{Response} 
+We consider CMG as the process of producing maps 
+covering a continuous interval of scales,
+where CMG considers constraints and quality measures 
+that act across different scales. 
+In our work, for example, the quality of an aggregation sequence 
+is measured as a whole; 
+whereas in classical generalization approaches, 
+only the quality of a map at some output scale is measured.
+We consider CMG possible, desirable, and realistic.
+In CMG, it is not necessary that 
+all changes that occur during zooming are animated in a continuous fashion. 
+That fashion may generally be possible. 
+A simple way is to fade in and fade out raster maps
+as did by \textcite{Pantazis2009b}, 
+but it is not at all clear 
+whether such animations would improve the experience of the map user.
+By contrast, we would like to carry out the changes in a more elegant way;
+we would like to change map features gradually.
 We have added more arguments in Section 1 (Introduction).
@@
 \textbf{Response} Figure 5 shows some ideas of \textcite{Cheng2006}.
-It is fine options (b) and (c, d, e) cannot be applicable simultaneously.
-We present this figure to show some inspirations that we got from reading the paper.
+We agree with the reviewer that
+options (b) and (c, d, e) cannot be applicable simultaneously.
+Still, we think that the figure is useful to exemplify possible choices.
 We have added the reference of \textcite{Cheng2006} into the caption.
@@
 }
-\textbf{Response} This is a good point of view.
-In order to make the reason clear, we will need to do more experiments.
-That can be our future work.
+\textbf{Response} 
+This is an interesting question.
+According to our experiences, 
+the weight factor that we applied defines a reasonable trade-off 
+between the different conflicting objectives, 
+when considering a solution as a whole. 
+However, we are far from claiming that 
+the applied weight factor has been optimally chosen. 
+This would probably require a user study, 
+which would be beyond the scope of our article.
 
@@
 No literature has tried to solve this problem.
+
+If the two maps come from different sources, one could compute a map overlay and use the result (with combined boundaries from both input maps and land cover classes from the given large-scale map) as the start map.
+We have added this argument into ``Problem definition''
+of Section 1 (Introduction).
 
@@
 So we combine~$g_\mathrm{type}$ and~$g_\mathrm{lgth}$ when we make the comparison.
-We have made this more clearly in Section~4.4 (Combining Cost Functions).
+We have made this more clear in Section~4.4 (Combining Cost Functions).
 
@@
 it is still worth to use the results of the \Astar algorithm.
-We can save the results obtained by the \Astar algorithm on a server,
-when users are zooming on a map, we can simply send the precomputed results.
+We can save the results obtained by the \Astar algorithm on a server.
+When users are zooming on a map, we can simply send the precomputed results.
 

### 2019-04-24 area_agg_seq_tsas.tex
improved our paper and response according to Jan's comments

@@
 The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
-which generalizes features in real time, can mitigate this problem.
+which generalizes map features (e.g., polyglines and polygons) 
+in real time, can mitigate this problem.
 Still, large discrete changes can be introduced.
@@
 e.g., \textcite{Suba2016Road} state.
-We believe that digital maps will eventually 
-achieve smooth changes for zooming.
+
+We consider CMG as the process of producing maps 
+covering a continuous interval of scales,
+where CMG considers constraints and quality measures 
+that act across different scales. 
+In our work, for example, the quality of an aggregation sequence 
+is measured as a whole; 
+whereas in classical generalization approaches, 
+only the quality of a map at some output scale is measured.
+We consider CMG possible, desirable, and realistic.
+In CMG, it is not necessary that 
+all changes that occur during zooming are animated in a continuous fashion. 
+That fashion may generally be possible. 
 A simple way is to fade in and fade out raster maps
-as did by \textcite{Pantazis2009b}.
-However, we would like to carry out the changes in a more elegant way;
+as did by \textcite{Pantazis2009b}, 
+but it is not at all clear 
+whether such animations would improve the experience of the map user.
+By contrast, we would like to carry out the changes in a more elegant way;
 we would like to change map features gradually.
@@
 given a land-cover map at a larger scale.
-Although \textcite{HaunertWolff2010AreaAgg}
+Note that although \textcite{HaunertWolff2010AreaAgg}
 attain results of high quality, 
 they do not produce a sequence land-cover maps.
+
+Our method can also be extended to find an aggregation sequence 
+for two maps (a start map and a goal map) that are from different sources.
+In that case, one could compute a map overlay of the two maps
+and use the result 
+(with combined boundaries from both input maps and land cover classes 
+from the given large-scale map) 
+as the start map.
 
@@
 which is used as a benchmark,
-we are able to see whether it is worth 
-to use \Astar or the ILP-based algorithm, 
-which are more complex and slower.  
+we are able to see whether \Astar or the ILP-based algorithm, 
+which are more complex and slower, indeed perform better.  
 Our case study 
@@
 \label{eq:f_comp}
-f_{\mathrm{comp}}(\Psnode)=
+f_\mathrm{comp}(\Psnode)=
 \frac{1-\frac{1}{n-s+1} \sum_{c\in C(\Psnode)}c}{n-2},
@@
 \label{eq:f_length}
-f_{\mathrm{lgth}}(\Psnode)=
+f_\mathrm{lgth}(\Psnode)=
 \frac{\big(\sum_{b\in B (\Psnode)} 
@@
 \end{equation}
+
+Note that in theory, a patch, $u$, with a small perimeter 
+can be extremely non-compact 
+according to measure~$c(u)$ in \eq\ref{eq:comp}, 
+thus the two measures, $f_\mathrm{comp}$ and~$f_\mathrm{lgth}$, 
+are not interchangeable. 
+However, if we assume that all areas of the map have the same size 
+(i.e., $A_u$ of \eq\ref{eq:comp} is a constant), 
+it would make no difference whether 
+we minimize an area's perimeter 
+or maximize the area's compactness~$c(u)$. 
+Obviously, the areas in our dataset have different sizes. 
+However, since we iteratively remove the smallest area, 
+the differences do not become too large. 
+Therefore, measuring the overall compactness of a map 
+based on the total length of all the interior boundaries is quite reasonable.
 
@@
 \label{sec:AreaAgg_Greedy}
+
+A motivation for the greedy algorithm is that 
+a very similar iterative algorithm has been used by
+\textcite{vanOosterom1995Development} 
+for constructing the tGAP data structure.
+However, we have to make minor modifications to ensure that 
+the computed aggregation sequence ends with the goal map that, 
+in our situation, is given as a part of the input.
+We use our greedy algorithm as a benchmark
+so that we are able to see 
+whether the \Astar algorithm or the ILP-based algorithm 
+indeed perform better.
 

### 2019-04-25 review_response/review_response.tex
improved according to Jan's feedback about reviewer 1 comment 11

@@
 (how well does \Astar-$g_2$ perform in terms of \Astar-$g_1$ / 
-does it give similar quality when measuring $g_2$-results using $g_1$, 
+does it give similar quality when measuring~$g_2$-results using~$g_1$, 
 or something like that). 
@@
 which would be beyond the scope of our article.
+We have added a corresponding argument into Section 9.2
+(Using costs of type change and length).
 
-\rcomment{Can this approach also work if no target map is not given (or has no predefined type)?
+\rcomment{Can this approach also work if no target map is not given 
+(or has no predefined type)?
 }

### 2019-04-25 area_agg_seq_tsas.tex
improved according to Jan's feedback about reviewer 1 comment 11

@@
 \multicolumn{1}{l}{Methods} &
-\multicolumn{1}{l}{\#OS} &
+\multicolumn{1}{c}{\#OS} &
 \multicolumn{1}{c}{\#FS} &
@@
 \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}c.
-In an earlier version of this paper \parencite{Peng2017AStar},
+In an earlier version of this paper \parencite[see][]{Peng2017AStar},
 we tried a combination of minimizing type changes 
@@
 if their common boundary is too short.
+Moreover, there are two more possible solutions.
+First, we could integrate the shared length
+into our cost function, as did by \textcite{vanOosterom1995Development}.
+Second, we could weight the cost of shape more heavily
+(i.e., increasing weight factor~$\lambda$ of \eqs\ref{eq:g_1} and~\ref{eq:g_2}).
+According to our experiences, 
+the weight factor that we applied defines a reasonable trade-off 
+between the different conflicting objectives, 
+when considering a solution as a whole. 
+However, we are far from claiming that 
+the applied weight factor has been optimally chosen. 
+This would probably require a user study.
 

### 2019-04-26 area_agg_seq_tsas.tex
improved according to Jan's comment

@@
 Note that our inputs are only
-subdivisions~$\Pstart$ and~$\Pgoal$.
+subdivisions~$\Pstart$ and~$\Pgoal$
+(see \fig\ref{fig:AreaAgg_SubdivisionName}).
 We generate a subdivision (node) only when we want to visit it.
@@
 however, will explore the whole graph, which has exponential size.
+The \Astar algorithm can be seen as 
+a refinement of Dijkstra's algorithm, 
+which for a user-specified given source 
+computes shortest paths to all other nodes in an edge-weighted graph
+\parencite{Dijkstra1959}. 
+Even when using Dijkstra's algorithm 
+to compute only a single shortest path to a user-specified destination, 
+a large number of nodes need to be explored. 
+The same holds for shortest-path algorithms 
+that make use of a topological order of the nodes 
+in a directed acyclic graph. 
+Compared to these algorithms, 
+the \Astar algorithm can greatly reduce the number of explored nodes.
 The challenge in our work was to tune the A* algorithm such that it

### 2019-04-26 review_response/review_response.tex
improved according to Jan's comment
improved the abstract of response

@@
 \begin{abstract}
+We submitted an earlier version of this paper to 
+\emph{Transactions on Spatial Algorithms and Systems}
+on July 27, 2018.
+According to the concerns of the reviewers,
+the Editor-in-Chief, Walid Aref, rejected that version.
+He encouraged us to address the concerns and 
+``submit as a new paper''.
+
 We thank the anonymous reviewers for their comments.
@@
 The contents of the paper are an interesting read and certainly well within the scope of TSAS.
-
 Though I have some comments/questions about certain parts (see below), the paper is of good quality already and warrants (eventual) acceptance.         
@@
 Also, something that would help a lot here is to use more meaningful variable names (instead of $x,y,z, \ldots$), such that it is easier to remember what's what.
-
 }

### 2020-03-31 area_agg_seq_tsas.tex
some small improvements

@@
 when users are zooming.
-we believe that this strategy will allow users 
+We believe that this strategy will allow users 
 to follow maps even more easily.
@@
 \centering
-\includegraphics{AreaAgg_example}
-\caption{The input and a possible output of an aggregation sequence 
-	for an instance of our problem}
+\includegraphics[page=1]{AreaAgg_Preliminaries}
+\caption{The input and a possible output for an instance of 
+our problem.}
 \label{fig:AreaAgg_example}
@@
 This tree can be constructed if only the larger-scale map is given
-\citep{vanOosterom1995Development} 
+\citep{vanOosterom2005} 
 or if both the larger-scale map and the smaller-scale map 
@@
 benefit from a goal map with high quality.
+
 We term the areas of the goal map \emph{regions}.
@@
 given a land-cover map at a larger scale.
-Note that although \textcite{HaunertWolff2010AreaAgg}
+Although \textcite{HaunertWolff2010AreaAgg}
 attain results of high quality, 
-they do not produce a sequence land-cover maps.
+they do not produce a sequence of land-cover maps.
 
@@
 \includegraphics[page=3]{AreaAgg_Preliminaries}
-\caption{The subdivision graph~$G_\mathrm{S}$. 
+\caption{The subdivision graph, $G_\mathrm{S}$. 
 	The nodes of the graph are the subdivisions. 
@@
 	if~${P}_{t+1,j}$ is the result of 
-	an aggregating step from~\Pnode.}
+	an aggregation step from~\Pnode.}
 \label{fig:AreaAgg_SubdivisionName}
@@
 However, we do not know which one is the right choice
-at each of the steps,
+at each of the steps
 in order to minimize our costs (see \sect\ref{sec:AreaAgg_CostFunctions}).
@@
 Our idea is to obtain an optimal aggregation sequence through 
-computing a minimum-weight path from the start to the goal 
+computing a path with minimum weight, from the start to the goal 
 (see \fig\ref{fig:AreaAgg_SubdivisionName}).
@@
 the \Astar algorithm can greatly reduce the number of explored nodes.
-The challenge in our work was to tune the A* algorithm such that it
-explores only a small fraction of the graph.
+The challenge in our work was to tune the \Astar algorithm such that 
+it explores only a small fraction of the graph.
 
@@
 is known from the input. 
-The input specifies, for each pair~$(T_1,T_2)$ of types, 
+The input specifies
 cost~$d_\mathrm{type}(T_1,T_2)$ of changing type~$T_1$ to type~$T_2$.
@@
 as the cost function of type change
-(see \sect\ref{sec:AreaAgg_CaseStudy}); 
-\textcite[\chap2]{Choudhary1992Elements}
-shows the definition of a metric.
+(see \sect\ref{sec:AreaAgg_CaseStudy}).
 A metric distance is symmetric, 
@@
 We use the compactness definition of \citet{Frolov1975}, 
-i.e., the compactness value for a patch, say,~$u$ is
+i.e., the compactness value of a patch, say,~$u$ is
 \begin{equation}
@@
 For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
-the set of the patches' compactnesses.
-
-We wish to maximize the sum of the average compactnesses 
+the set of the patches' compactness values.
+
+We wish to maximize the sum of the average compactness values 
 over all intermediate maps,
@@
     The dashed polygon in (c) shows 
-    that the vertices are merged.}
+    the merged vertices.}
 \label{fig:AreaAgg_Reduction}
@@
 a very similar iterative algorithm has been used by
-\textcite{vanOosterom1995Development} 
+\textcite{vanOosterom2005} 
 for constructing the tGAP data structure.
@@
     about land-cover types can be found at 
-%	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
+	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
 	Accessed: Nov 1, 2017.}
@@
 As illustrated in \sect\ref{sec:AreaAgg_Combining},
-we compare \Astar and the greedy algorithm using $g_1(\Pnode)$,
+we compare the \Astar algorithm and 
+the greedy algorithm using $g_1(\Pnode)$,
 which is a combination of the costs 
@@
 First, we could integrate the shared length
-into our cost function, as did by \textcite{vanOosterom1995Development}.
+into our cost function, as did by \textcite{vanOosterom2005}.
 Second, we could weight the cost of shape more heavily
@@
     The step from $8$ patches to $7$ patches 
-    when using cost function~$g1$ is a bad move; see figure (b). 
+    when using cost function~$g_1$ is a bad move; see figure (b). 
     Instead, we expect the result of figure (a). 
-    Using cost function~$g2$, we had a similar problem. 
+    Using cost function~$g_2$, we had a similar problem. 
     The subdivision with $7$ patches is such an example, 
@@
 
-Our second set of variables is used to compute the
+We use the second set of variables in order to compute the
 cost of type change. We introduce
@@
 
-\mypar{Aggregation involving a smallest patch}
+\subsubsection{Aggregation involving a smallest patch}
 In order to make sure that 

### 2020-06-24 area_agg_seq_tsas.tex
improved citing
improved according to reviewers' comments

@@
 {Finding Optimal Sequences for Area Aggregation---\texorpdfstring
-    {\protect\\ \Astar vs.\ Integer Linear Programming} %title of the paper
+    {\Astar vs.\ Integer Linear Programming} %title of the paper
     {A* vs.\ Integer Linear Programming} %title of the pdf
@@
 
-In each step of the sequence that we compute, 
+In each step of the \mine{computed} sequence, 
 the smallest area is merged with one of its neighbors. 
@@
 to follow maps even more easily.
-The process of producing maps at any different scales
-with smooth changes 
+The process of producing maps \mine{with a smooth scale transition}
 is known as \emph{continuous map generalization} (CMG), 
@@
 the discrete changes are small enough not to be noticed as,
-e.g., \textcite{Suba2016Road} state.
-
-We consider CMG as the process of producing maps 
-covering a continuous interval of scales,
-where CMG considers constraints and quality measures 
-that act across different scales. 
-In our work, for example, the quality of an aggregation sequence 
-is measured as a whole; 
-whereas in classical generalization approaches, 
-only the quality of a map at some output scale is measured.
-We consider CMG possible, desirable, and realistic.
-In CMG, it is not necessary that 
-all changes that occur during zooming are animated in a continuous fashion. 
-That fashion may generally be possible. 
-A simple way is to fade in and fade out raster maps
+e.g., \textcite{Suba2016Road} stated.
+%We consider CMG as the process of producing maps 
+%covering a continuous interval of scales,
+%where CMG considers constraints and quality measures 
+%that act across different scales. 
+%In our work, for example, the quality of an aggregation sequence 
+%is measured as a whole; 
+%whereas in classical generalization approaches, 
+%only the quality of a map at \mine{an} output scale is measured.
+%We consider CMG possible, desirable, and realistic.
+%In CMG, it is not necessary that 
+%all changes that occur during zooming are animated in a continuous fashion. 
+%That fashion may generally be possible.
+
+A simple way \mine{of realizing CMG} is to fade in and fade out raster maps
 as did by \textcite{Pantazis2009b}, 
 but it is not at all clear 
-whether such animations would improve the experience of the map user.
-By contrast, we would like to carry out the changes in a more elegant way;
-we would like to change map features gradually.
+whether such animations would improve the experience of map users.
+\mine{Furthermore, although it is possible to generalize raster maps,
+we consider it more straightforward to work on vector maps.
+For example, \textcite{Jaakkola1998Generalization}
+generalized raster maps, but he used essentially the same object-based operators 
+that are common in the map generalization of vector data.
+He even converted raster data to vector data
+when he wanted to simplify the boundaries of the land-cover areas.
+Therefore, our paper will work on a vector map of land-cover areas.}
+
+%As , we would like to carry out the changes in a more elegant way;
+%we would like to change map features gradually.
+
+%He generalizes raster maps, using essentially the same object-based map generalization operators that are common in the generalization of vector data.
+I.e., patches consisting of pixels of equal land-cover types are considered as objects which can be merged with neighboring patches.
 
@@
 with good visual experience during zooming operations,
-we propose to remove these tiny areas.
-We plan to achieve this goal by 
-aggregating them into neighboring land-cover areas.
+we propose to \mine{aggregate the tiny areas} 
+into their neighboring areas.
 
@@
 multiple adjacent forest areas may constitute 
-a large forest region on the smaller-scale map.
+a large forest region on the \mine{goal} map.
 However, we assume that every region, on the goal map, 
@@
 attain results of high quality, 
-they do not produce a sequence of land-cover maps.
+they do not produce a sequence of maps.
 
@@
 (with combined boundaries from both input maps and land cover classes 
-from the given large-scale map) 
+from the given larger-scale map) 
 as the start map.
@@
 by integrating our results into the \emph{space-scale cube}
-\parencite{vanOosterom2014tGAP,vanOosterom2014tGAPSSC}.
+\parencite{vanOosterom2014Support,vanOosterom2014tGAPSSC}.
 
@@
 \mypar{Contribution}
-We show related work (\sect\ref{sec:AreaAgg_RelatedWork}).
+We \mine{first} show \mine{some} related work (\sect\ref{sec:AreaAgg_RelatedWork}).
 Then, we formally model our problem, 
@@
 defines a gradual line simplification process.
-%
+\mine{Note that simplifying polylines will not speed up 
+our three algorithms.
+The reason is that we compute the areas of the polygons 
+and the lengths of the boundaries in a preprocessing.
+These values will be associated with
+a graph representation of the dataset, 
+where polygons are represented as vertices and 
+a boundary separating two polygons (no matter how detailed it is) 
+is represented with a single edge.
+During computation, the three algorithms do not need to go through 
+the vertices of the land-cover areas.
+}
+
 Although splitting polygons is a good step
@@
 taking into account
-the attractivenesses between the splittee and its neighbors.
-When merging, a more attractive neighbor 
+the attractivenesses between the splittee and its neighbors;
+when merging, a more attractive neighbor 
 will get a larger portion from the splittee.
@@
 on \emph{compatible triangulations}.
-\Textcite{vanOosterom2014tGAP} used
+\Textcite{vanOosterom2014Support} used
 a data structure called
@@
 \centering
-\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
+\includegraphics[page=1]{AreaAgg_CaseStudy1_Plot}
 \caption{The numbers of regions where \Astar was 
@@
 \centering
-\includegraphics[page=3]{AreaAgg_CaseStudy1_Plot}
+\includegraphics[page=2]{AreaAgg_CaseStudy1_Plot}
 \end{table*}
@@
 We compared three methods to solve this problem, namely, 
-a greedy algorithm, \Astar, and an ILP-based algorithm.
+a greedy algorithm, the \Astar algorithm, and an ILP-based algorithm.
 The greedy algorithm is used as a benchmark.
 Unsurprisingly, it ran faster than the other two methods by far.
-According to our experiments, \Astar found area aggregation 
-sequences
+According to our experiments, \Astar found area aggregation sequences
 with the least total cost over all regions.
@@
 we could not tell if the bad result was caused 
-by the greedy algorithm or the model.
+by the greedy algorithm or \mine{by} the model.
 Because of \Astar, we are sure that the bad result is from
@@
 and Sabine Storandt for their valuable suggestions.
-We thank Martijn Meijers for 
+We are grateful to Martijn Meijers for 
 prereviewing an earlier version of this paper.
+\mine{We thank the anonymous reviewers for their comments,
+which were very helpful for us to improve the paper.}
 \end{acks}

### 2020-07-01 area_agg_seq_tsas.tex
Some small changes; also removed pdf file from repo.

@@
 [Finding Optimal Sequences for Area Aggregation] %short title
-{Finding Optimal Sequences for Area Aggregation---\texorpdfstring
+{Finding Optimal Sequences for Area Aggregation---\\
+  \texorpdfstring
     {\Astar vs.\ Integer Linear Programming} %title of the paper
@@
 \includegraphics[page=1]{AreaAgg_NPHard}
-\caption{The reduction for our NP-hardness proof.
-    The dashed polygon in (c) shows 
-    the merged vertices.}
+\caption{Our NP-hardness reduction.  The dashed area in~(c) represents
+  the vertices that are merged.}
 \label{fig:AreaAgg_Reduction}
@@
 the order in which the vertices are selected:
-\begin{itemize}
-\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
+\begin{description}[leftmargin=1.7cm,style=sameline]
+\item[\emph{Phase I}:] In each of the first~$2|E_\mathrm{A}|$ steps, 
 a white vertex is selected and merged with one of its neighbors, 
@@
 (\fig\ref{fig:reduction2} shows a possible result).
-\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
+\item[\emph{Phase II}:] In each of the next~$|V_\mathrm{A}|$ steps, 
 a non-gray vertex is selected and merged with one of its neighbors.
-\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
-\end{itemize}
+\item[\emph{Phase III}:] $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
+\end{description}
 
@@
     of~$G_\mathrm{A}$ have been recolored white.
-    The dashed polygons show that the vertices are merged.}
+    The dashed areas represent the vertices that are merged.}
 \label{fig:reduction2}
@@
 \end{subfigure}
-%
-%It doesn't work to directly use 
-%\vspace{\baselineskip} for subfigures.
-\par\vspace{\baselineskip} %Leave a gap	figures
-%
+
+\bigskip
+\bigskip
+
 \begin{subfigure}{\textwidth}
@@
 
+%\begin{figure}[p]
+%\begin{minipage}{\textwidth}
 \begin{figure}[tb]
@@
 \end{figure}
-
+% \end{minipage}
+
+%\begin{minipage}{\textwidth}
 \begin{figure}[tb]
@@
 \end{figure}
+%\end{minipage}
+%\end{figure}
 
@@
 	when using time limits~$100\,$s and~$200\,$s.
-	Using more time, our ILP was able to 
-	solve more instances to optimality.}
+	Using twice the time, our ILP was able to 
+	solve only 5.8$\,$\% more instances to optimality.}
 \label{fig:AreaAgg_CaseStudy2_ILP}

### 2020-07-02 area_agg_seq_tsas.tex
using the latest version of acmart.cls
improved the tex of title

@@
   \texorpdfstring
-    {\Astar vs.\ Integer Linear Programming} %title of the paper
-    {A* vs.\ Integer Linear Programming} %title of the pdf
+    {\Astar vs.\ Integer Linear Programming}%title of the paper
+    {A* vs.\ Integer Linear Programming}%title of the pdf
 }
@@
 \orcid{0000-0001-6848-3545}
+\affiliation{%
+  \institution{GIS Technology, 
+  	Delft University of Technology}
+%  \streetaddress{P.O. Box 1212}
+%  \city{Dublin}
+%  \state{Ohio}
+%  \postcode{43017-6221}
+  \country{The Netherlands}
+}
 \affiliation{%
@@
 }
-\email{www1.informatik.uni-wuerzburg.de/peng}
+\email{http://www.gdmc.nl/staff/}
 

### 2020-07-13 area_agg_seq_tsas.tex
polished the paper

@@
   \texorpdfstring
-    {\Astar vs.\ Integer Linear Programming}%title of the paper
-    {A* vs.\ Integer Linear Programming}%title of the pdf
+    {\Astar} %title of the paper
+    {A*} %title of the pdf 
+    vs.\ Integer Linear Programming
 }
@@
 \author{Dongliang Peng}
-%\authornote{Dr.~Trovato insisted his name be first.}
+\authornote{Dongliang Peng did his main contribution 
+when he was a PhD student at University of W\"urzburg.}
 \orcid{0000-0001-6848-3545}
@@
   	Delft University of Technology}
-%  \streetaddress{P.O. Box 1212}
-%  \city{Dublin}
-%  \state{Ohio}
-%  \postcode{43017-6221}
+  \streetaddress{Julianalaan 134}
+  \city{Delft}
+  \state{South Holland}
+  \postcode{2628 BL}
   \country{The Netherlands}
 }
+\email{http://www.gdmc.nl/staff/}
 \affiliation{%
@@
   	University of W\"urzburg}
-%  \streetaddress{P.O. Box 1212}
-%  \city{Dublin}
-%  \state{Ohio}
-%  \postcode{43017-6221}
+  \streetaddress{Am Hubland}
+  \city{W\"urzburg}
+  \state{Bavaria}
+  \postcode{D-97074}    
   \country{Germany}
 }
-\email{http://www.gdmc.nl/staff/}
+\email{http://www1.informatik.uni-wuerzburg.de/peng}
 
@@
   	University of W\"urzburg}
+  \streetaddress{Am Hubland}
+  \city{W\"urzburg}
+  \state{Bavaria}
+  \postcode{D-97074}    
   \country{Germany}
@@
   University of Bonn}
+  \streetaddress{Meckenheimer Allee 172}
+  \city{Bonn}
+  \state{North Rhine-Westphalia}
+  \postcode{D-53115}  
   \country{Germany}
@@
 
-\keywords{Continuous map generalization, Land cover, 
+\keywords{Continuous map generalization, Land-cover area, 
 	 Type change, Compactness, Shortest path
@@
 The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
-which generalizes map features (e.g., polyglines and polygons) 
+which generalizes map features (e.g., polylines and polygons) 
 in real time, can mitigate this problem.
@@
 a map is easier to follow 
-if the map extent transits smoothly than stepwise. 
-In addition to smoothly transiting map extent, 
+if the map extent changes smoothly than stepwise. 
+In addition to smoothly changing map extent, 
 we want to change also map features smoothly 
@@
 We believe that this strategy will allow users 
-to follow maps even more easily.
+to follow maps even more easily and thus keep their context better.
 The process of producing maps \mine{with a smooth scale transition}
@@
 However, the term is also used when 
-the discrete changes are small enough not to be noticed as,
-e.g., \textcite{Suba2016Road} stated.
+the discrete changes are small enough not to be noticed
+\parencite[e.g.,][]{Suba2016Road}.
+% as,
+%e.g., \textcite{Suba2016Road} stated.
 %We consider CMG as the process of producing maps 
@@
 A \emph{land-cover map} is a planar subdivision in which 
-each area belongs to a land-cover class or \emph{type}.
+each area belongs to a land-cover \emph{class} or \emph{type}.
 Suppose that there are two land-cover maps of different scales 
@@
 e.g., the Generalized Area Partitioning tree (GAP-tree).
-This tree can be constructed if only the larger-scale map is given
+That tree can be constructed if only the larger-scale map is given
 \citep{vanOosterom2005} 
@@
 If we insist on finding a sequence that is optimal 
-according to some global measure,
+according to some global measures,
 the problem becomes complicated.
@@
 because those algorithms do not take into account 
-the consistence between the generated maps.
+the consistency between the generated maps.
 We use both a start map and a goal map instead of using only the start map
@@
 for example, by the method of \citet{HaunertWolff2010AreaAgg}.
-That method produces a land-cover map at a single smaller scale, 
-given a land-cover map at a larger scale.
+That method used a land-cover map at a larger scale as input and 
+produced a land-cover map at a single smaller scale.
 Although \textcite{HaunertWolff2010AreaAgg}
-attain results of high quality, 
-they do not produce a sequence of maps.
+attained results of high quality, 
+they did not produce a sequence of maps.
 
@@
 and use the result 
-(with combined boundaries from both input maps and land cover classes 
+(with combined boundaries from both input maps and 
+with land-cover classes 
 from the given larger-scale map) 
@@
 (see \fig\ref{fig:AreaAgg_IntegrateSequence}). 
-Our aggregation sequence may be cooperated with
+Our aggregation sequence may be incorporated into
 the GAP-face tree \citep{vanOosterom2005},
@@
 	of different regions: 
-	the resulting sequence contains the given sequences 
+	the resultant sequence contains the given sequences 
 	as subsequences and 
-	always takes the subdivision with smallest patch next.
+	always takes the subdivision with the smallest patch next.
 	The gray arrows show the integration of the two regions.
@@
 We \mine{first} show \mine{some} related work (\sect\ref{sec:AreaAgg_RelatedWork}).
-Then, we formally model our problem, 
+Then, we model our problem, present some basic concepts,
 analyze the size of our model in a worst-case scenario,
-introduce our methods,
-and present the basic concepts of our method
+and introduce our methods
 (\sect\ref{sec:AreaAgg_Preliminaries}).
@@
 
-We do not deal with simplifying polylines in this paper.
+We do not simplify polylines in this paper.
 The simplification can be handled separately from the
@@
 \textcite{Sester2005_CG} suggested simplifying building
-footprints based on small incremental steps and 
+footprints based on small incremental steps 
 to animate each step smoothly.
@@
 buildings to built-up areas by aggregating buildings 
-whenever they become too close.
+whenever they became too close.
 \textcite{Touya2017Progressive} progressively replaced
@@
 rivers~\parencite{Peng2012River,Girres2014}. 
-Actually, this strategy is the key idea of the
+Actually, that strategy is the key idea of the
 morphing-based methods for CMG.
@@
 correspondence between two given polylines 
-according to some cost function.
+according to some cost functions.
 While straight-line trajectories 
@@
 \parencite{Chazal2010BallMap}.
-\textcite{Peng2013LSA} defined trajectories requiring that
-angles in vertices and edge lengths should change linearly.
-As these requirements may not agree with each other,
-their method mediates between them using 
-least-squares adjustments.
 \textcite{Peng2016Admin} morphed county boundaries
@@
 One of their contributions is that
-a polygon is merged into another polygon continuously
-by moving the boundary of the former.
+a polygon merges another polygon continuously
+by expanding over the latter.
 \textcite{Huang2017Matrix} proposed a matrix-based structure 
@@
 We categorize requirements as hard and soft constraints.
-For example, when users zoom out, 
-some land-cover areas become too small to be seen.
-These areas need to be aggregated.
-When we aggregate one area into another, 
+For example,
+when we aggregate a land-cover area into another, 
 the type of the former is changed to the type of the latter. 
 In this problem, a hard constraint could be that 
-we aggregate only two polygons at each step 
+we aggregate only two areas at each step 
 in order to keep changes small
@@
 not only because it finds optimal solutions,
-but also because it helps us to evaluate the quality of a model
+but also because it helps us evaluate the quality of a model
 \parencite{Haunert2017Label,
@@
 Their aim was to minimize the number of edges
-while keeping the result boundaries close to the original ones
+while keeping the resultant boundaries close to the original ones
 and avoiding any intersection. 
@@
 when we deal with CMG.
-In this field, we have requirements 
+In this field, there are requirements 
 not only for a specific map
@@
 to match points of two polylines to support morphing
-according to some matching cost.
+according to some matching costs.
 \textcite{sahw-oarps-ICAGW13} used 
@@
 \textcite{Peng2013LSA} defined trajectories 
-based on LSA for morphing between polylines, 
-where LSA is used to mediate between the requirements 
-for angles and edge lengths of the intermediate polylines.
+based on LSA for morphing between polylines.
+Their method required both angles in vertices and edge lengths
+change linearly.
+As those requirements may not agree with each other,
+their method mediates between them using LSA.
 
@@
 every change involves only two areas of the current map.
-More precisely, in each step the smallest area~$u$ is merged 
+More precisely, in each step the smallest area~$u$ is aggregated 
 with one of its neighbors~$v$ 
@@
 We denote by~$P$ the set of polygons on the start map.
-We use~$p$, $q$, $r$, or~$o$ to denote polygons.
+We use variables~$p$, $q$, $r$, or~$o$ to denote polygons.
 A \emph{patch} is a set of polygons whose union is connected. 
 Each patch also has a unique land-cover type.
-We use~$u$ or~$v$ to denote the patches.
+We use variables~$u$ or~$v$ to denote the patches.
 
@@
 and the goal map is simply the union of the~$n$ patches.
-The patches have area 
-sizes~$
+From left to right on the start map, 
+the patches have area sizes~$
 %\left( 
@@
 %\right)
-$, 
-from left to right.
+$.
 According to our rule, we always 
 aggregate the smallest patch with one of its neighbors.
-Therefore, in the first~$k$ steps from the start map,
+Therefore, in the first~$k$ steps,
 we aggregate every other patch with one of its neighbors.
@@
 (see \fig\ref{fig:AreaAgg_SubdivisionName}).
-We generate a subdivision (node) only when we want to visit it.
+We generate an intermediate subdivision (node) only 
+when we want to visit it.
 
@@
 The \Astar algorithm can be seen as 
-a refinement of Dijkstra's algorithm, 
-which for a user-specified given source 
+a refinement of Dijkstra's algorithm. 
+For a user-specified given source, Dijkstra's algorithm
 computes shortest paths to all other nodes in an edge-weighted graph
@@
 the \Astar algorithm can greatly reduce the number of explored nodes.
-The challenge in our work was to tune the \Astar algorithm such that 
+The challenge in our work is to tune the \Astar algorithm such that 
 it explores only a small fraction of the graph.
@@
 sequence~$(P_{1,1}, P_{2,4},P_{3,5},P_{4,1})$.
-This is because that the dark area should not expand so much
+This is because that the dark area should not expand
 when the target color is light gray.
-We want to provide users with a most reasonable sequence 
+We want to provide map users with a most reasonable sequence 
 because we believe that an unreasonable sequence irritates users.
@@
 
-It is difficult to define what \emph{reasonable} exactly means 
+It is difficult to define \emph{reasonableness}
 because users may have different preferences.
@@
 (\fig\ref{fig:AreaAgg_Preferences}e).
-To keep our aggregation problem independent of user preferences,
+To keep our aggregation problem independent of users' preferences,
 our cost function takes two aspects into account: 
@@
 we consider subdivision~\Pnode 
-as more compact than subdivision~$P_{t,i'}$ 
+more compact than subdivision~$P_{t,i'}$ 
 if the total length of the interior boundaries of~\Pnode 
@@
 \parencite[e.g.,][]{Minas2016,Wright1983}.
-\textcite{HaunertWolff2010AreaAgg} employed 
+The ILP of \textcite{HaunertWolff2010AreaAgg} employed 
 the centroids of a set of land-cover areas.
@@
 is more relevant to the shapes of the patches.
-Also, \textcite{Harrie2015Readability} showed that
-longer lines generally yield lower map readability.
+Furthermore, \textcite{Harrie2015Readability} showed that
+longer lines generally yielded lower map readability.
 
@@
 	according to different preferences
-    by \textcite{Cheng2006}.
+    proposed by \textcite{Cheng2006}:
 	Aggregating a small land-cover area into another one 
@@
 We use the compactness definition of \citet{Frolov1975}, 
-i.e., the compactness value of a patch, say,~$u$ is
+i.e., the compactness value of patch~$u$ is
 \begin{equation}
@@
 the area and the perimeter. 
-For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
+For subdivision \Psnode, we denote by~$C(\Psnode)$ 
 the set of the patches' compactness values.
@@
 \end{equation}
-where we use values~$n-s+1$ and~$n-2$ to normalize 
-the cost of compactness.
+where value~$n-s+1$ is used to 
+compute the average compactness of subdivision~\Psnode.
+We use value~$n-2$ to normalize the cost of compactness
+because there are~$n-2$ intermediate subdivisions 
+in an aggregation sequence.
 
@@
 We denote the set of interior boundaries 
-for a subdivision~$\Psnode$ by~$B(\Psnode)$.
+of subdivision~$\Psnode$ by~$B(\Psnode)$.
 The cost in terms of interior length of 
@@
 can be extremely non-compact 
-according to measure~$c(u)$ in \eq\ref{eq:comp}, 
-thus the two measures, $f_\mathrm{comp}$ and~$f_\mathrm{lgth}$, 
+according to measure~$c(u)$ of \eq\ref{eq:comp}, 
+thus measures $f_\mathrm{comp}$ and~$f_\mathrm{lgth}$
 are not interchangeable. 
-However, if we assume that all areas of the map have the same size 
+If we assume that all land-cover areas of the map 
+have the same areal size 
 (i.e., $A_u$ of \eq\ref{eq:comp} is a constant), 
 it would make no difference whether 
-we minimize an area's perimeter 
-or maximize the area's compactness~$c(u)$. 
+we minimize~$g_\mathrm{comp}$ or~$g_\mathrm{lgth}$. 
 Obviously, the areas in our dataset have different sizes. 
@@
 Therefore, measuring the overall compactness of a map 
-based on the total length of all the interior boundaries is quite reasonable.
+based on the total length of all the interior boundaries 
+is quite reasonable.
 
@@
 where~$\lambda \in [0,1]$ is a parameter 
-to assign importances 
-of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
+to assign importances of the two costs.
 We simply use~$\lambda=0.5$ in our experiments. 
@@
 by~$g_1(\Pnode)$.
-Using $g_1(\Pnode)$, we compare a greedy algorithm and \Astar
+Using $g_1(\Pgoal)$, we compare a greedy algorithm and \Astar
 in finding optimal sequences for area aggregation.
@@
 while our cost of compactness (see \eq\ref{eq:comp})
-cannot be computed linearly in an integer linear program.
+cannot be computed linearly in an ILP.
 Therefore, we combine 
 the cost of type change (\eq\ref{eq:g_type})
-and the cost of length (\eq\ref{eq:g_length}),
-which can be computed linearly in an integer linear program. 
+and the cost of length (\eq\ref{eq:g_length})
+so that we have a cost function
+can be computed linearly in an ILP. 
 That is,
@@
 We compare the greedy algorithm, \Astar, and an ILP-based 
-algorithm using~$g_2$.
+algorithm using~$g_2(\Pgoal)$.
 
@@
 one may develop a clever algorithm 
-to find an optimal sequence efficiently.
+to efficiently find an optimal sequence.
 In the following, we prove that 
@@
 \includegraphics[page=1]{AreaAgg_NPHard}
-\caption{Our NP-hardness reduction.  The dashed area in~(c) represents
+\caption{Our NP-hardness reduction.  The dashed polygon in~(c) represents
   the vertices that are merged.}
@@
 we require the smallest area to be aggregated with one of its neighbors.
-The area sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
+The areal sizes correspond to the weights of the vertices in \fig\ref{fig:AreaAgg_Reduction}b.   
 Therefore, our definition of the weights to a certain degree determines 
@@
 \end{description}
+
+\begin{figure}[tb]
+\centering
+\includegraphics[page=2]{AreaAgg_NPHard}
+\caption{The situation after Phase I has been conducted 
+    such that all black vertices corresponding to a vertex cover 
+    of~$G_\mathrm{A}$ have been recolored white.
+    The dashed polygon represent the vertices that are merged.}
+\label{fig:reduction2}
+\end{figure}
 
@@
 It is also clear that 
-there is no cheaper way to accomplish Phases II and III,
-since it is impossible to color a vertex gray in Phase I.
+there is no cheaper way to accomplish Phases II and III
+because it is impossible to color a vertex gray in Phase I.
 Consequently, since the total cost of Phases II and III is fixed, 
@@
 
-\begin{figure}[tb]
-\centering
-\includegraphics[page=2]{AreaAgg_NPHard}
-\caption{The situation after Phase I has been conducted 
-    such that all black vertices corresponding to a vertex cover 
-    of~$G_\mathrm{A}$ have been recolored white.
-    The dashed areas represent the vertices that are merged.}
-\label{fig:reduction2}
-\end{figure}
 \end{proof}
@@
 our greedy algorithm aggregates the smallest patch
-with one of its neighbors.
-We pick the neighbor in a greedy way.
+with one of its neighbors,
+where the neighbor is picked in a greedy way.
 We suppose that the smallest patch,~$u$, has~$k_u$ neighbors,
 then there are~$2k_u$ ways to aggregate
-(when we aggregate a patch into another patch,
-the union uses the type of the latter).
+(when we aggregate a patch with another patch,
+the union can use one of the two types).
 In order to guarantee that our final result
-(e.g., the polygon of layer~$L_4$ in 
+(e.g., the patch of layer~$L_4$ in 
 \fig\ref{fig:AreaAgg_SubdivisionName})
-will have the type of~$T_\mathrm{goal}$,
+will have type~$T_\mathrm{goal}$,
 we add one more rule to our greedy algorithm.
@@
 the~$2k_u - k_e$ aggregation choices
-and select the aggregation that has the least cost.
+and select the choice that has the least cost.
 In other words, we aggregate the smallest patch with 
@@
 \end{equation}
-We take one of the~$2k_u - k_e$ aggregation choices 
+We select one of the~$2k_u - k_e$ aggregation choices 
 according to \eqs\ref{eq:f_1} or~\ref{eq:f_2}
@@
 The cost of a whole sequence can be computed by
-\eqs\ref{eq:g_1} or~\ref{eq:g_2}.
-
-\section{Using the \texorpdfstring{\Astar Algorithm}{A* Algorithm}}
+\eqs\ref{eq:g_1} and~\ref{eq:g_2}, respectively.
+
+\section{Using the \texorpdfstring{\Astar}{A*} Algorithm}
 \label{sec:AreaAgg_AStar}
@@
 if they are estimated to be closer to the goal.
-The \Astar algorithm can be seen as a refinement of Dijkstra's algorithm
-\parencite{Dijkstra1959}.
 
@@
 \Astar is able to reduce the search space.
-The better the estimation part~$h$, 
+The better the estimation part~$h(\Pnode)$, 
 the more search space \Astar can reduce.
@@
 which means that the first attempt of finding a solution
-does not use overestimation.
+does not use an overestimation.
 As~$K\le n-1$, it holds that~$k \le \log_2 n$, 
@@
 \Astar cannot guarantee optimality anymore.
-When we are at time~$t$, there are at most~$n-t$ steps 
+When we are at time~$t$, there are~$n-t$ steps 
 to arrive at the goal map.
@@
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i'_t}, P_{t+1,i'_{\tstar+1}} \dots,P_{n,i'_n}=\Pgoal)$,
+$(P_{t,i'_t}, P_{t+1,i'_{\tstar+1}} \dots,P_{n,i'_n})$,
+where~$P_{t,i'_t}=\Pnode$ and~$P_{n,i'_n}=\Pgoal$,
 be the path that always changes the type of a smallest patch 
@@
 Note that the boundary between two patches 
-is not necessarily connected; 
-for example, see the dark boundary with three edges 
-in \fig\ref{fig:AreaAgg_h_comp}a.
+is not necessarily connected
+(for example, see the dark boundary with three edges 
+in \fig\ref{fig:AreaAgg_h_comp}a).
 For subdivision \Pnode,
@@
     (see the argument in \sect\ref{sec:AreaAgg_h_type}).    
-	This example corresponds to the aggregation step in 
+	This example is based on the aggregation result of 
 	\fig\ref{fig:AreaAgg_FirstStep}b.
@@
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i''_t}, P_{t+1,i''_{\tstar+1}}, 
-\dots,P_{n,i''_n}=\Pgoal)$
+$(P_{t,i''_t}, P_{t+1,i''_{\tstar+1}}, \dots,P_{n,i''_n})$,
+where~$P_{t,i''_t}=\Pnode$ and~$P_{n,i''_n}=\Pgoal$,
 be the path that always removes the two smallest compactnesses
@@
 For subdivision~\Pnode, let
-$(\Pnode=P_{t,i'''_t}, P_{t+1,i'''_{\tstar+1}}, 
-\dots,P_{n,i'''_n}=\Pgoal)$
+$(P_{t,i'''_t}, P_{t+1,i'''_{\tstar+1}}, \dots,P_{n,i'''_n})$,
+where~$P_{t,i'''_t}=\Pnode$ and~$P_{n,i'''_n}=\Pgoal$,
 be the path that always keeps 
@@
 and ArcObjects SDK~10.6.0.
-We used the IBM ILOG
+We used IBM ILOG
 CPLEX Optimization Studio~12.6.3.0 to solve our ILP.
@@
 \url{https://github.com/IGNF/ContinuousGeneralisation},
-Accessed: Jun 18, 2018.}.
+Accessed: July 11, 2020.}.
 We ran our case study
 under 64-bit Windows~10 
-on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores;
-the computer has $16\,$GB RAM.
+on Intel(R) Core(TM) i7-6700 CPU @~$3.40\,$GHz with~$4$ cores.
+The computer has $16\,$GB RAM.
 We measured processing time 
@@
 {http://stackoverflow.com/questions/2597790/can-i-set-largeaddressaware-from-within-visual-studio},
-Accessed: Nov 1, 2017.}.
+Accessed: July 11, 2020.}.
 Our CPLEX version may declare an optimal solution
@@
 reductions\footnote{For more details about the problem, see
-\url{http://www-01.ibm.com/support/docview.wss?uid=swg1RS02094},
-Accessed: Nov 12, 2017.}.
+\url{https://www.ibm.com/support/pages/apar/RS02094},
+Accessed: July 11, 2020.}.
 
@@
 by \citet[\chap6]{haunert2008f}.
-The start map has~$5{,}537$ polygons. 
+The start map has~$5{,}537$ polygons
+(see \fig\ref{fig:AreaAgg_Data}a). 
 Our goal map was generalized from the start map 
 by~\citet{HaunertWolff2010AreaAgg}, setting the scale 
-to~$1:250{,}000$ (see \fig\ref{fig:AreaAgg_Data}). 
+to~$1:250{,}000$. 
 The goal map has~$734$ polygons, 
-which means that there are~$N=734$ regions.
+which means that there are~$N=734$ regions
+(see \fig\ref{fig:AreaAgg_Data}b).
 The distribution of region sizes is shown in 
@@
 \citet{Rada1989SemanticMetric} 
-to define the distances of the types;
-the distance is the ``number of edges'' that
+to define the distances of the types \parencite[pp.~3--6]{ATKIS2003}.
+The distance is the ``number of edges'' that
 we need to travel from one node to another node in the tree of 
-type hierarchy\footnote{More information 
-    about land-cover types can be found at 
-	\url{http://www.atkis.de/dstinfo/dstinfo2.dst_gliederung},
-	Accessed: Nov 1, 2017.}
+type hierarchy
 (see \fig\ref{fig:AreaAgg_TypeDistances}). 
@@
 According to \citet{Rada1989SemanticMetric}, 
-the resulting cost function for type change is a metric.
+the distance function of the type is a metric.
 
@@
 (if we could use more main memory, 
-then we could test by using some larger~$W$). 
+then we could test by using a larger~$W$). 
 The results are shown in 
@@
 lower total cost,~$117.3$ (or~$117.2$), 
-which is~$2.8\%$ less than 
+which is~$2.8\,\%$ less than 
 the total cost of the greedy algorithm,~$120.7$.
@@
 we have found optimal solutions 
-for~$702$ of the~$734$ regions ($95.6\%$),
+for~$702$ of the~$734$ regions ($95.6\,\%$),
 while the greedy algorithm solved 
-only~$408$ ($55.6\%$) to optimality;
+only~$408$ ($55.6\,\%$) to optimality;
 see column \#OS in 
@@
 	Columns~\#nodes and~\#arcs are the total 
-	numbers of nodes and arcs that \Astar visited  
-	(for instances where we needed overestimation, 
+	numbers of nodes and arcs that the algorithms visited  
+	(for an instance where \Astar needed overestimation, 
 	only the final attempt was counted).
@@
 Greedy 	& 408 
-&326~(44.4\%) 
+&326~(44.4\,\%) 
 &             &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.2         &188.2           &120.7           &0'1~(74.6\%)\\
+&53.2         &188.2           &120.7           &0'1~(74.6\,\%)\\
 %
@@
 \AstarTwo	& 702 
-&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\%$) 
+&  32~(\parbox{\widthof{$4$}}{$\,$}$4.4\,\%$) 
 & 102 &  3.6\cdot 10^6 &    5.7\cdot 10^6	
-& 51.4 & 183.2 & 117.3 & 51'6~(93.2\%)\\
+& 51.4 & 183.2 & 117.3 & 51'6~(93.2\,\%)\\
 %
@@
 \AstarFour	& 704 
-&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\%$)
+&  30~(\parbox{\widthof{$4$}}{$\,$}$4.1\,\%$)
 &  89 &  6.5\cdot 10^6 &    9.8\cdot 10^6
-& 51.4 & 183.1 & 117.2 & 93'1~(95.5\%)
+& 51.4 & 183.1 & 117.2 & 93'1~(95.5\,\%)
 \\ \bottomrule			
@@
 we define~$k_i$ as the least number of repetitions 
-that we do to find a feasible solution. 
+to find a feasible solution. 
 We define the total number of repetitions 
@@
 \fig\ref{fig:AreaAgg_OverStats}. 
-Besides, \Astar visited more arcs and nodes, 
-used more time, 
-but got (slightly) less cost when increasing~$W$ to~$400{,}000$.
+When increasing~$W$ to~$400{,}000$, 
+\Astar visited more arcs and nodes, used more time, 
+but got (slightly) less cost.
 Although the number of regions 
@@
 \Astar spent most of the running time 
-on those few regions:~$4.4\%$ and~$4.1\%$ of the regions 
-caused~$93.2\%$ and~$95.5\%$ of the total running time, 
+on those few regions:~$4.4\,\%$ and~$4.1\,\%$ of the regions 
+caused~$93.2\,\%$ and~$95.5\,\%$ of the total running time, 
 respectively 
@@
 Table~\ref{tab:CostsInDetail}.
-According to the entries with overestimation factor $K_i=0$, 
-we often have 
+For the rows with overestimation factor~$K_i=0$, 
+\Astar often has 
 ratios~$R_\mathrm{type}=1$ and~$R_\mathrm{comp}>1$.
-When factor~$K_i=0$, we did not overestimate for region~$i$.
-The estimated cost must be smaller or equal to the exact cost,
+When factor~$K_i=0$, \Astar did not overestimate for region~$i$.
+In this case, the estimated cost is smaller or equal to the exact cost,
 which results in~$R_\mathrm{type}\ge 1$ 
 and~$R_\mathrm{comp}\ge 1$.
-Ratio~$R_\mathrm{type} = 1$ means that our estimation for the 
+Ratio~$R_\mathrm{type} = 1$ means that the estimation for the 
 cost of type change is the best.
@@
 	Parameter $K$ is the overestimation factor, 
-	defined in \sect\ref{sec:AreaAgg_Preliminaries}. 
+	defined in \sect\ref{sec:AreaAgg_AStar}. 
 	We evaluate the quality 
@@
 	in this case, we define~$R_\mathrm{type}=1$.
-	The marked entries are discussed in the text.
+	The marked rows are discussed in the text.
 }
@@
 Solutions of the greedy algorithm cost
-at most~$41.7\%$ more than 
+at most~$41.7\,\%$ more than 
 solutions of \AstarTwo;
@@
 a solution of cost~$0.777$, 
-while the solution of \AstarTwo has cost~$0.548$
-(see \fig\ref{fig:AreaAgg_CaseStudy1_Rg85}).
-As the patches in the two sequences are the same,
+while the solution of \AstarTwo has cost~$0.548$.
+\fig\ref{fig:AreaAgg_CaseStudy1_Rg85} shows the aggregation sequences
+obtained by the two algorithms.
+As the shapes in the two sequences are the same,
 the two results have the same cost of compactness.
@@
 will have to be changed twice during the aggregation.
-These changes cause a cost more than the sequence obtained by 
+These changes cause a cost more than the cost needed by 
 \AstarTwo, 
 where the largest patch on the start map is changed to 
-the target type directly.
+the target type directly at the last step.
 
@@
 the greedy algorithm outperformed \AstarTwo 
-for~$15$ regions ($46.9\%$).
+for~$15$ regions ($46.9\,\%$).
 %
 Among these, solutions of the greedy algorithm 
-cost at most~$15.9\%$ less than solutions of \AstarTwo;
+cost at most~$15.9\,\%$ less than solutions of \AstarTwo;
 for region~$543$, the greedy algorithm yields 
@@
 \AstarTwo failed to solve optimally,  
-solutions of the greedy algorithm cost at most~$17.4\%$ 
+solutions of the greedy algorithm cost at most~$17.4\,\%$ 
 more than solutions of \AstarTwo; 
@@
 	when there are~$4$ or~$5$ patches, 
-	which one can easily deduce.
+	which can be easily deduced.
 	The numbers indicate the numbers of patches.
@@
 	a pair of circles or a pair of squares indicates that
-	the two parts are actually in the same patch.
+	the two parts actually belong to the same patch.
 	The numbers indicate the numbers of patches.
@@
 \includegraphics[page=3]{AreaAgg_CaseStudy1}
-\caption{An optimal sequence of intermediate subdivisions 
-	of region~$53$ obtained by \Astar 
+\caption{An optimal sequence of region~$53$ obtained by \Astar 
 	using the costs of type change and compactness.		 
@@
 %	varied~$\lambda$ in
-%	the range $\{0.1,0.5,0.9\}$, but the resulting aggregation 
+%	the range $\{0.1,0.5,0.9\}$, but the resultant aggregation 
 %	sequences
@@
 \Astar found optimal solutions 
-for~$695$ of the~$734$ regions ($94.7\%$).
+for~$695$ of the~$734$ regions ($94.7\,\%$).
 Again, it spent most of the running time 
 on the few regions that needed 
-overestimation:~$5.3\%$ of the regions 
-caused~$92.3\%$ of the total running time.
+overestimation:~$5.3\,\%$ of the regions 
+caused~$92.3\,\%$ of the total running time.
 The solutions by \Astar cost~$438.2$ in total, 
-which is~$3.9\%$ less than~$455.8$, 
+which is~$3.9\,\%$ less than~$455.8$, 
 the total cost of the solutions by the greedy algorithm.
@@
 Greedy 		 &430             
-&304~(41.4\%)    
+&304~(41.4\,\%)    
 &            &5.5\cdot 10^3   &4.8\cdot 10^3   
-&53.0        &858.5           &455.8           &0'1~(70.7\%)\\
+&53.0        &858.5           &455.8           &0'1~(70.7\,\%)\\
 %
@@
 \AstarTwo	& 695
-& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\%$)	
+& 39~(\parbox{\widthof{$4$}}{$\,$}$5.3\,\%$)	
 & 150 	& 3.7\cdot 10^6 & 7.3\cdot 10^6 
-& 52.0 	& 824.5 & 438.2 &44'8~(92.3\%)	\\
+& 52.0 	& 824.5 & 438.2 &44'8~(92.3\,\%)	\\
 %
@@
 \ILPOne		& 449
-& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\%$)  			 	
+& 69~(\parbox{\widthof{$4$}}{$\,$}$9.4\,\%$)  			 	
 &		&				&				
-&		&		&		& 421'5~(27.3\%) \\
+&		&		&		& 421'5~(27.3\,\%) \\
 %
@@
 \ILPTwo		& 475
-& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\%$)  			 	
+& 57~(\parbox{\widthof{$4$}}{$\,$}$7.8\,\%$)  			 	
 &		&				&				
-&		&		&		& 719'2~(26.4\%) \\ 
+&		&		&		& 719'2~(26.4\,\%) \\ 
 \bottomrule
@@
 the greedy algorithm outperformed \Astar 
-for~$8$ regions~($20.5\%$), 
-which is~$26.4\%$ less comparing to the first experiment ($46.9\%$).
+for~$8$ regions~($20.5\,\%$), 
+which is~$26.4\,\%$ less comparing to the first experiment ($46.9\,\%$).
 %
@@
 \figs\ref{fig:AreaAgg_CaseStudy2_Percentage_Optimal}
-and~\fig\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}
+and~\ref{fig:AreaAgg_CaseStudy2_Percentage_Feasible}.
 There are~$216$ regions for which 
-our \ILPOne failed to find any solution.
+\ILPOne failed to find any solution.
 For~$22$ of those regions, 
@@
 For~$67$ of those regions, 
-our \ILPOne ran out of the main memory 
+\ILPOne ran out of the main memory 
 before finding any feasible solution;
@@
 	Using twice the time, our ILP was able to 
-	solve only 5.8$\,$\% more instances to optimality.}
+	solve only $5.8\,\%$ more instances to optimality.}
 \label{fig:AreaAgg_CaseStudy2_ILP}
@@
 the weight factor that we applied defines a reasonable trade-off 
-between the different conflicting objectives, 
-when considering a solution as a whole. 
+between the different conflicting objectives. 
 However, we are far from claiming that 
@@
 Compared to the greedy algorithm, 
-\Astar reduced the total costs by~$2.8\%$ and~$3.9\%$
+\Astar reduced the total costs by~$2.8\,\%$ and~$3.9\,\%$
 in the two experiments.
@@
 For example, \fig\ref{fig:AreaAgg_CaseStudy2_Rg358}b shows that
-even an \emph{optimal} sequence can be bad.
+even an \emph{optimal} sequence has problems.
 If it were not for \Astar, 
-we could not tell if the bad result was caused 
-by the greedy algorithm or \mine{by} the model.
-Because of \Astar, we are sure that the bad result is from
+we could not tell if the problem was caused 
+by the greedy algorithm or by the model.
+Because of \Astar, we are sure that the problem is from
 our model of minimizing the 
@@
 We need to run \Astar again.
-This time we know for sure that 
+This time, we know for sure that 
 a path is not optimal if its cost, 
@@
 We may speed up our ILP-based algorithm using a so-called 
-cutting-plane approach as \textcite{Oehrlein2017Aggregation}.
+cutting-plane approach as did by \textcite{Oehrlein2017Aggregation}.
 Also, we can add more constraints to
@@
 
+\section*{Data and codes availability statement}
+
+The data and codes used in this case study 
+can be found at \emph{figshare} 
+(see \url{https://figshare.com/s/199e049e2a0f9c18d19a}).
+The data was derived from open-access dataset TOP10NL,
+which is a topographic map produced by Kadaster
+(see \url{https://www.pdok.nl/downloads/-/article/basisregistratie-topografie-brt-topnl}).
+
 \begin{acks}
@@
 We mix the powder and the water to provide two kinds coffee 
-with different intensities in terms of mass:~$40\%$ and~$20\%$.
+with different intensities in terms of mass:~$40\,\%$ and~$20\,\%$.
 The profits of the two kinds of coffee 
@@
 $$
-To provide~$x\,$kg of coffee with intensity~$40\%$,
+To provide~$x\,$kg of coffee with intensity~$40\,\%$,
 we need to use~$0.4x\,$kg of coffee powder 
-and~$0.6x\,$kg water.
+and~$0.6x\,$kg of water.
 Analogously, it consumes~$0.2y\,$kg of coffee powder 
 and~$0.8y\,$kg of water to produce~$y\,$kg of coffee
-with intensity~$20\%$.
-As a result, we have four constraints:
+with intensity~$20\,\%$.
+On this basis, we have four constraints:
 \begin{align*}
@@
 where each jug contains exactly~$1\,$kg of coffee 
-with intensity~$40\%$ or~$20\%$.
+with intensity~$40\,\%$ or~$20\,\%$.
 Our question becomes how many jugs of each kind of coffee
@@
 (point~$A$ is no longer a feasible solution in this case).
-In order to maximize our profit,
+In order to maximize the profit,
 we should move the dashed line to the upper right 
@@
 $$
-then we have only binary variables for an ILP.
+then all the variables are binary.
 Binary variables are important 
@@
 Also, an ILP with general (bounded) integer variables 
-can always be translated to an ILP with binary variables
+can always be translated to an ILP with only binary variables
 \parencite[\sect2.3]{Williams2009Integer}.
@@
 	and integer linear programming (b).
-    In (a), any point in the gray area is a feasible solution;
-    in (b), only the gray points are feasible solutions.
+    In (a), each point in the gray area is a feasible solution;
+    in (b), only each of the gray points is a feasible solutions.
 }
@@
 finding a shortest path as an ILP.
-Then we solve this ILP by minimizing the total cost.
+Then we solve this ILP with minimizing the total cost.
 We define the \emph{center} of a patch as the polygon 
@@
 The first set of variables is used to tell the program 
-our rules for area aggregation.
+the status of area aggregation.
 \begin{figure*}[tb]
@@
 \caption{Some examples of the five sets of variables 
-	for our ILP, $x$, $y$, $z$, $c$, and~$w$.
+    (i.e., $x$, $y$, $z$, $c$, and~$w$)	for our ILP.
 	The arrows with curly arms show the aggregation steps,
@@
 the number of centers decreasing by~$1$.
-We achieve that exactly one patch 
-is aggregated into another by specifying the number of centers
-for each point in time, that is,
+By specifying the number of centers
+for each point in time,
+we achieve that exactly one patch 
+is aggregated into another in a step. That is,
 \begin{flalign}
@@
 to center~$o$ at time~$t-1$ ($x_{t-1,p,o}=1$)
-and assigned to center~$r$ at time $t$
-($x_{t,p,r}=1$), we have variable~$y_{t,p,o,r}=1$. 
+and assigned to center~$r$ at time~$t$
+($x_{t,p,r}=1$), then there exists~$y_{t,p,o,r}=1$. 
 This requirement is expressed by
@@
 Second, if~$p$ is not assigned to~$o$ at~$t-1$ ($x_{t-1,p,o}=0$)
-and/or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
-we have variable~$y_{t,p,o,r}=0$.
+or~$p$ is not assigned to~$r$ at time~$t$ ($x_{t,p,o}=0$),
+then there exists~$y_{t,p,o,r}=0$.
 This requirement is expressed by
@@
 to center~$r$ at time~$t$ ($x_{t,p,r}=1$ and~$x_{t,q,r}=1$),
-we have variable~$z_{t,p,q,r}=1$. 
+then there exists~$z_{t,p,q,r}=1$. 
 This requirement is expressed by
@@
 Second, at time~$t$, if~$p$ is not assigned to~$r$ ($x_{t,p,r}=0$)
-and/or~$q$ is not assigned to~$r$ ($x_{t,q,r}=0$), 
-we have variable~$z_{t,p,q,r}=0$. 
+or~$q$ is not assigned to~$r$ ($x_{t,q,r}=0$), 
+then there exists~$z_{t,p,q,r}=0$. 
 This requirement is expressed by
@@
 ensure that polygons~$p$ and~$q$ can be assigned 
-to one common center at most; therefore, we have~$z_{t,p,q} \le 1$.
+to one common center at most; 
+therefore, there exists~$z_{t,p,q} \le 1$.
 We use our new variable~$z_{t,p,q}$
@@
 In order to ensure contiguity, 
-the method picks a user-specified number of nodes that constitute 
+that method picks a user-specified number of nodes that constitute 
 an optimal subtree of the previously built spanning tree.
@@
 otherwise, we may end up having noncontiguous patches.
-As a result,
+As a result, we have
+%\begin{flalign}
+%\label{eq:CstrC_Part_twolines}
+%&\eqquadConstraintsC
+%\begin{array}{@{}l}
+%\embrd[C]{c_{t,p,o,r}} \le  \\
+%\embrd[C]{} %an empty place
+%\end{array} 
+%\embld[D]{\embshift
+%	\begin{array}{@{}l}
+%	x_{t,p,o} \\
+%	~ %an empty place
+%	\end{array}
+%}
+%\inquadC \embshift
+%\begin{array}{@{}l}
+%\forall t 	 \in T\setminus \{n-1,n\},\\
+%\forall p, o, r \in P \text{~with}~o\ne r.
+%\end{array} &	
+%\end{flalign}
 \begin{flalign}
@@
 &\eqquadConstraintsC
-\begin{array}{@{}l}
-\embrd[C]{c_{t,p,o,r}} \le  \\
-\embrd[C]{} %an empty place
-\end{array} 
-\embld[D]{\embshift
-	\begin{array}{@{}l}
-	x_{t,p,o} \\
-	~ %an empty place
-	\end{array}
-}
-\inquadC \embshift
-\begin{array}{@{}l}
-\forall t 	 \in T\setminus \{n-1,n\},\\
-\forall p, o, r \in P \text{~with}~o\ne r.
-\end{array} &	
+\embrd[C]{c_{t,p,o,r}} \le 
+\embld[D]{x_{t,p,o}} \inquadC
+\forall t 	 \in T\setminus \{n-1,n\},  
+\forall p, o, r \in P \text{~with}~o\ne r.&
 \end{flalign}
@@
 Second, at time~$t$, at least one of polygon~$p$'s neighbor(s),
-say, polygon~$q$ has to be assigned to center~$r$ ($x_{t,q,r}=1$).
+say, polygon~$q$ must be assigned to center~$r$ ($x_{t,q,r}=1$).
 If not, then variable~$c_{t,p,o,r}$ is impossible to tell
@@
 we have
+%\begin{flalign}
+%\label{eq:CstrC_Neighbor_twolines}
+%&\eqquadConstraintsC
+%\begin{array}{@{}l}
+%\embrd[C]{c_{t,p,o,r}} \le  \\
+%\embrd[C]{} %an empty place
+%\end{array} 
+%\embld[D]{\embshift
+%	\begin{array}{@{}l}\displaystyle
+%	\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r} \\
+%	~ %an empty place
+%	\end{array}
+%}
+%\inquadC \embshift
+%\begin{array}{@{}l}
+%\forall t 	 \in T\setminus \{n-1,n\},\\
+%\forall p, o, r \in P \text{~with}~o\ne r,
+%\end{array} &	
+%\end{flalign}
 \begin{flalign}
@@
 &\eqquadConstraintsC
-\begin{array}{@{}l}
-\embrd[C]{c_{t,p,o,r}} \le  \\
-\embrd[C]{} %an empty place
-\end{array} 
-\embld[D]{\embshift
-	\begin{array}{@{}l}\displaystyle
-	\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r} \\
-	~ %an empty place
-	\end{array}
-}
-\inquadC \embshift
-\begin{array}{@{}l}
-\forall t 	 \in T\setminus \{n-1,n\},\\
-\forall p, o, r \in P \text{~with}~o\ne r,
-\end{array} &	
+\embrd[C]{c_{t,p,o,r}} \le 
+\embld[D]{\sum_{q\in N_\mathrm{nbr}(p)} x_{t,q,r}} \inquadC
+\forall t 	 \in T\setminus \{n-1,n\},  
+\forall p, o, r \in P \text{~with}~o\ne r,&
 \end{flalign}
@@
 \begin{flalign}
-\label{eq:CstrC_Positive}
+\label{eq:CstrC_Positive_twolines}
 &\eqquadConstraintsC
@@
 \end{flalign}
+%\begin{flalign}
+%\label{eq:CstrC_Positive_oneline}
+%&\eqquadConstraintsC
+%\embrd[C]{c_{t,p,o,r}} \ge 
+%\embld[D]{x_{t,p,o} + x_{t,q,r} -1} \inquadC
+%\forall t 	 \in T\setminus \{n-1,n\},  
+%\forall p, o, r \in P \text{~with}~o\ne r,
+%\forall q \in N_\mathrm{nbr}(p).&
+%\end{flalign}
 
@@
 when~$w_{t,o}=1$.
-Consequently, we use the constraint
+Consequently, we use constraint
 \begin{flalign}
@@
 a smallest patch at time~$t$.
-We define variable~$A_{t,r}$ as the area of 
-patch~$r$ at time~$t$. 
-That is, we have
+Let variable~$A_{t,r}$ be the area of 
+patch~$r$ at time~$t$, we have
 \begin{flalign*}
@@
 %\begin{flalign}
-%\label{eq:CstrSIndeedSmallest}
+%\label{eq:CstrSIndeedSmallest_align_le}
 %&\eqquadConstraints
@@
 %\begin{flalign}
-%\label{eq:CstrSIndeedSmallest_Remove}
+%\label{eq:CstrSIndeedSmallest_oneline}
 %&\eqquadConstraintW
@@
 This constraint takes effect only when~$w_{t,o}=1$ 
-and~$x_{t,r,r}=1$, which indicates that 
+and~$x_{t,r,r}=1$ as~$w_{t,o} \in {\{0,1\}}$ 
+and~$x_{t,r,r} \in {\{0,1\}}$.
+This set of constraints force that 
 patch~$o$ is smaller than or equal to 
-all the other existing patches at time~$t$.
+all the other patches at time~$t$.
 

### 2020-07-14 area_agg_seq_tsas.tex
added data and codes availability statement

@@
 \ccsdesc[500]{Applied computing~Cartography}
+
+\setcopyright{othergov}
+\acmYear{2020} \acmVolume{1} \acmNumber{1} \acmArticle{1} \acmMonth{1} \acmPrice{15.00}\acmDOI{10.1145/3409290}
 
@@
 can be found at \emph{figshare} 
-(see \url{https://figshare.com/s/199e049e2a0f9c18d19a}).
-The data was derived from open-access dataset TOP10NL,
-which is a topographic map produced by Kadaster
-(see \url{https://www.pdok.nl/downloads/-/article/basisregistratie-topografie-brt-topnl}).
+(see \url{https://doi.org/10.1145/3409290} or
+\url{https://figshare.com/articles/software/Data_and_codes_for_optimal_sequences/12652853}).
+This data set has been substantially preprocessed and 
+does not represent the land use as recorded by the German mapping authorities.
+For ATKIS test data that has not been preprocessed, please refer to
+\url{https://www.lgln.niedersachsen.de/startseite/online_angebote_amp_services/service/testdaten/testdaten-51644.html}.
 
